### 2020-11-26 Pilot_data_presentation.Rmd
change break interval to 1 for testing

---
title: "Online masked priming"
subtitle: "Can we get the same quality data as in a laboratory study?"
author: "Bernhard Angele, Pablo Gomez, & Manuel Perea"
institute: "Bournemouth/Valencia/San Bernardino/The Internet"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(sp)
library(leaflet)
library(lmerTest)
library(tidyverse)
library(cowplot)
library(stargazer)
source("RainCloudPlots.R")
```

# Doing research during a pandemic

- No eye-tracking!
- But lots of bored people sitting at home
- What are language-related paradigms that we can do remotely?
  - Surveys (not terribly interesting for many language researchers)
  - Self-paced reading
  - RSVP
  - Lexical decision tasks

---

# Is priming possible online?

- Overt priming certainly is
- But masked priming relies on very precise timing of the stimuli.
- Ken Forster did it a long time ago with GIFs:

  - 40 ms prime duration: 
  ![40 ms prime](http://www.u.arizona.edu/~kforster/priming/mp_demo_1.gif)
  - 100 ms prime duration: 
  ![100 ms prime](http://www.u.arizona.edu/~kforster/priming/mp_demo_2.gif)

- But a demo on a website and an online experiment are two very different things!

---

# Using the three Ps (Psychopy, Pavlovia, and Prolific) to collect data

- Psychopy is an experiment presentation software allowing precise display of stimuli
  - It's written in Python, but there is now the option of translating the experiments into Javascript (PsychoJS) for online presentation.
  - Pavlovia is a paid service that integrates with Psychopy and hosts the experiment code and the collected data
  - Prolific is a participant recruitment service (like Mechanical Turk, but more research-focused and less US-centric)

---

# Our experiment

- Based on Gomez, Perea, & Ratcliff (2013)

- Gomez et al. used the diffusion model to fit data from masked and unmasked prime presentation and found that masked and unmasked priming affect different model parameters:
  - masked identity priming affects the $T_{er}$ parameter which represents encoding processes
  - unmasked priming affects both $T_er$ and the drift rates parameter corresponding to the quality of information

- If we can show that the data from an online experiment pattern with the masked priming data from Gomez et al. rather than the unmasked priming data, that demonstrates the reliability of the online masked priming paradigm.

---

Design

- Targets: 240 words and 240 nonwords
- Conditions: 
  - prime duration (33 vs. 50 ms)
    - this corresponds to 2 vs. 3 refresh cycles at 60 Hz
  - prime condition: identical vs. unrelated
- 60 word/nonword stimuli per group

---

Participants

```{r participant_map, echo = FALSE, message=FALSE}

participant_data <- read_csv("participant_data.csv")
coordinates(participant_data) <- c("Location Longitude","Location Latitude")
leaflet(participant_data) %>% addMarkers(label = .$`Confirm Prolific ID`) %>% addTiles()
```

---

# Results

```{r main_code, echo = FALSE, warning=FALSE, message = FALSE}

csv_data <- fs::dir_ls(path = "./data", glob = "*.csv") %>%
  map_dfr(read_csv, .id = "source", col_type = cols(
  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
  filter(!is.na(TrialID) & TrialID < 1000) %>%
  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)

# get participants with correct responses

accuracy_by_participant <- csv_data %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())

participants_to_include <- accuracy_by_participant %>% filter(N == 480 & acc > .8)

participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows

# for now, we only have two participants with accuracy > .8 and a full data set

data_to_include <- csv_data %>% filter(source %in% participants_to_include$source) %>% mutate(StimulusType = StimulusType %>% factor, Condition = Condition %>% factor, PrimeDuration = PrimeDuration %>% factor, rt = rt * 1000)

write_csv(data_to_include, path = "current_data.csv")

data_summary_rt <- data_to_include %>% group_by(StimulusType, Condition, PrimeDuration) %>% summarise(M = mean(rt), SD = sd(rt), N = n())

# data above 1500 ms excluded

plot_raincloud(data_to_include %>% filter(corr == 1 & rt < 1500), x_column = "Condition", y_column = "rt", x_label = "Condition", y_label = "RT in ms (correct responses)", main_title = "RT by condition and word type") + 
  # put labels on the mean for easier comparison
  stat_summary(fun.data = function(x) {data.frame(label = format(mean(x), digits = 2), y = mean(x))}, 
                                      geom = "text",
                                      #width = 1,
                                      position = position_nudge(x = 0.5, y = 0),
                                      #size = 0.2,
                                      color = "black") +
  facet_grid(cols = vars(PrimeDuration), rows = vars(StimulusType), labeller = label_context)

```

---
# LMM for RT (words, correct responses)
```{r lmms}
lmm1 <- lmer(data = data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (Condition+PrimeDuration|source) + (PrimeDuration|Target))

summary(lmm1)

```

---
# gLMM for accuracy (Words)
```{r logistic_lmm}
lmm_acc <- glmer(data = data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt < 1500), corr ~ Condition + PrimeDuration + (1|Target), family = binomial(link = "logit"))

summary(lmm_acc)

```

### 2020-11-26 pilot_data_analysis.Rmd
change break interval to 1 for testing

--- 2020-11-26 Pilot_data_presentation.Rmd
@@
 ---
-title: "Online masked priming"
-subtitle: "Can we get the same quality data as in a laboratory study?"
-author: "Bernhard Angele, Pablo Gomez, & Manuel Perea"
-institute: "Bournemouth/Valencia/San Bernardino/The Internet"
-date: "`r Sys.Date()`"
+title: "Pilot data analysis"
 output:
-  xaringan::moon_reader:
-    lib_dir: libs
-    nature:
-      highlightStyle: github
-      highlightLines: true
-      countIncrementalSlides: false
+  html_document:
+    df_print: paged
 ---
 
-```{r setup, include=FALSE}
-options(htmltools.dir.version = FALSE)
-library(sp)
-library(leaflet)
+```{r}
 library(lmerTest)
@@
 source("RainCloudPlots.R")
-```
-
-# Doing research during a pandemic
-
-- No eye-tracking!
-- But lots of bored people sitting at home
-- What are language-related paradigms that we can do remotely?
-  - Surveys (not terribly interesting for many language researchers)
-  - Self-paced reading
-  - RSVP
-  - Lexical decision tasks
-
----
-
-# Is priming possible online?
-
-- Overt priming certainly is
-- But masked priming relies on very precise timing of the stimuli.
-- Ken Forster did it a long time ago with GIFs:
-
-  - 40 ms prime duration: 
-  ![40 ms prime](http://www.u.arizona.edu/~kforster/priming/mp_demo_1.gif)
-  - 100 ms prime duration: 
-  ![100 ms prime](http://www.u.arizona.edu/~kforster/priming/mp_demo_2.gif)
-
-- But a demo on a website and an online experiment are two very different things!
-
----
-
-# Using the three Ps (Psychopy, Pavlovia, and Prolific) to collect data
-
-- Psychopy is an experiment presentation software allowing precise display of stimuli
-  - It's written in Python, but there is now the option of translating the experiments into Javascript (PsychoJS) for online presentation.
-  - Pavlovia is a paid service that integrates with Psychopy and hosts the experiment code and the collected data
-  - Prolific is a participant recruitment service (like Mechanical Turk, but more research-focused and less US-centric)
-
----
-
-# Our experiment
-
-- Based on Gomez, Perea, & Ratcliff (2013)
-
-- Gomez et al. used the diffusion model to fit data from masked and unmasked prime presentation and found that masked and unmasked priming affect different model parameters:
-  - masked identity priming affects the $T_{er}$ parameter which represents encoding processes
-  - unmasked priming affects both $T_er$ and the drift rates parameter corresponding to the quality of information
-
-- If we can show that the data from an online experiment pattern with the masked priming data from Gomez et al.
-rather than the unmasked priming data, that demonstrates the reliability of the online masked priming paradigm.
-
----
-
-Design
-
-- Targets: 240 words and 240 nonwords
-- Conditions: 
-  - prime duration (33 vs. 50 ms)
-    - this corresponds to 2 vs. 3 refresh cycles at 60 Hz
-  - prime condition: identical vs. unrelated
-- 60 word/nonword stimuli per group
-
----
-
-Participants
-
-```{r participant_map, echo = FALSE, message=FALSE}
-
-participant_data <- read_csv("participant_data.csv")
-coordinates(participant_data) <- c("Location Longitude","Location Latitude")
-leaflet(participant_data) %>% addMarkers(label = .$`Confirm Prolific ID`) %>% addTiles()
-```
-
----
-
-# Results
-
-```{r main_code, echo = FALSE, warning=FALSE, message = FALSE}
 
@@
 ```
-
----
-# LMM for RT (words, correct responses)
+## LMM for RT (words, correct responses)
 ```{r lmms}
-lmm1 <- lmer(data = data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (Condition+PrimeDuration|source) + (PrimeDuration|Target))
+lmm1 <- lmer(data = data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))
 
@@
 ```
-
----
-# gLMM for accuracy (Words)
+gLMM for accuracy (Words)
 ```{r logistic_lmm}
-lmm_acc <- glmer(data = data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt < 1500), corr ~ Condition + PrimeDuration + (1|Target), family = binomial(link = "logit"))
+lmm_acc <- glmer(data = data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt < 1500), corr ~ Condition * PrimeDuration + (1|Target), family = binomial(link = "logit"))
 
@@
 ```
+
+Creepy: visualize participant locations from Qualtrics
+```{r participant_map}
+library(sp)
+library(leaflet)
+
+participant_data <- read_csv("participant_data.csv")
+coordinates(participant_data) <- c("Location Longitude","Location Latitude")
+leaflet(participant_data) %>% addMarkers(label = .$`Confirm Prolific ID`) %>% addTiles()
+```

### 2020-11-26 RainCloudPlots.R

@@ -1,0 +1,136 @@
+# Raincloud plot code adapted from https://github.com/gabrifc/raincloud-shiny
+
+
+## function to make drawing raincloud plots faster
+plot_raincloud <- function(data, x_column, y_column, fill_column = x_column, main_title = "Main Plot Title", y_label = "y axis", x_label = "x axis", scatter_plot = TRUE, box_plot = TRUE, violin_plot = TRUE, plot_mean = TRUE, flip = TRUE){
+  
+  my_plot <- ggplot(data, aes_string(x = x_column, y = y_column, fill = fill_column, color = fill_column)) +
+    ggtitle(main_title) +
+    ylab(y_label) +
+    xlab(x_label) +
+    theme_cowplot() +
+    scale_shape_identity() +
+    theme(legend.position = "none",
+          plot.title = element_text(size = 20),
+          axis.title = element_text(size = 15),
+          axis.text = element_text(size = 15),
+          axis.text.x = element_text(angle = 0, 
+                                     hjust = 0,
+                                     vjust = 0)) +
+    scale_colour_brewer(palette = "Set1") +
+    scale_fill_brewer(palette = "Set1")
+  if(scatter_plot) {
+    my_plot <- my_plot + geom_point(position = position_jitter(0.15), 
+                                    size = 0.3, 
+                                    alpha = 0.5, 
+                                    aes(shape = 16))
+  }
+  if(violin_plot){
+    my_plot <- my_plot + geom_flat_violin(position = position_nudge(x = 0.2, y = 0),
+                                          adjust = 2,
+                                          alpha = 0.6, 
+                                          trim = TRUE, 
+                                          scale = "width")
+  }
+  if(box_plot){
+    x_numeric <- as.numeric(unlist(data[,x_column]))
+    my_plot <- my_plot + geom_boxplot(aes_string(x = x_numeric + 0.2, y = y_column), 
+                                      notch = FALSE, 
+                                      width = 0.1, 
+                                      varwidth = FALSE, 
+                                      outlier.shape = NA, 
+                                      alpha = 0.3, 
+                                      colour = "black", 
+                                      show.legend = FALSE)
+  }
+  if(plot_mean){
+    my_plot <- my_plot + stat_summary(fun.min = mean, 
+                                      fun.max = mean,
+                                      geom = "errorbar",
+                                      width = 0.4,
[…]

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js

@@ -565,7 +565,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 121;
+  break_every = 1;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -576,7 +576,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 121;
+  break_every = 1;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
change break interval to 1 for testing

@@ -565,7 +565,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 1;
+  break_every = 11;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -576,7 +576,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 1;
+  break_every = 11;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
change break interval to 2 for testing

@@ -565,7 +565,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 11;
+  break_every = 2;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -576,7 +576,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 11;
+  break_every = 2;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
change break variable to trials.ThisN for testing

@@ -1554,7 +1554,7 @@ function BreakRoutineEachFrame(snapshot) {
     // exit the break routine immediately if we are not on a break trial
     // break trials occur every break_every trials (see Begin Experiment)
     
-    if ((trials.thisTrialN+1) % break_every != 0){
+    if ((trials.thisN+1) % break_every != 0){
         continueRoutine = false;
     }
     

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -1557,7 +1557,7 @@ function BreakRoutineEachFrame(snapshot) {
     // exit the break routine immediately if we are not on a break trial
     // break trials occur every break_every trials (see Begin Experiment)
     
-    if ((trials.thisTrialN+1) % break_every != 0){
+    if ((trials.thisN+1) % break_every != 0){
         continueRoutine = false;
     }
     

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
make new variable indicating whether there should be a break or not

@@ -1504,6 +1504,7 @@ function feedbackRoutineEnd(snapshot) {
 }
 
 
+var show_break;
 var _break_done_keyboard_allKeys;
 var BreakComponents;
 function BreakRoutineBegin(snapshot) {
@@ -1515,7 +1516,7 @@ function BreakRoutineBegin(snapshot) {
     // update component parameters for each repeat
     break_msg_top = (("BREAK\n\nYou have now completed " + round(((trials.thisTrialN / trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
-    
+    show_break = trials.thisTrialN % break_every == 0
     break_text.setText(break_msg);
     // setup some python lists for storing info about the break_done_touch
     break_done_touch.clicked_name = [];
@@ -1554,7 +1555,7 @@ function BreakRoutineEachFrame(snapshot) {
     // exit the break routine immediately if we are not on a break trial
     // break trials occur every break_every trials (see Begin Experiment)
     
-    if ((trials.thisN+1) % break_every != 0){
+    if (!show_break){
         continueRoutine = false;
     }
     

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -1508,6 +1508,7 @@ function feedbackRoutineEnd(snapshot) {
 }
 
 
+var show_break;
 var _break_done_keyboard_allKeys;
 var BreakComponents;
 function BreakRoutineBegin(snapshot) {
@@ -1519,7 +1520,7 @@ function BreakRoutineBegin(snapshot) {
     // update component parameters for each repeat
     break_msg_top = (("BREAK\n\nYou have now completed " + round(((trials.thisTrialN / trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
-    
+    show_break = trials.thisTrialN % break_every == 0
     break_text.setText(break_msg);
     // setup some python lists for storing info about the break_done_touch
     break_done_touch.clicked_name = [];
@@ -1557,7 +1558,7 @@ function BreakRoutineEachFrame(snapshot) {
     // exit the break routine immediately if we are not on a break trial
     // break trials occur every break_every trials (see Begin Experiment)
     
-    if ((trials.thisN+1) % break_every != 0){
+    if (!show_break){
         continueRoutine = false;
     }
     

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
add console logging

@@ -565,7 +565,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 2;
+  break_every = 11;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";
@@ -1517,6 +1517,8 @@ function BreakRoutineBegin(snapshot) {
     break_msg_top = (("BREAK\n\nYou have now completed " + round(((trials.thisTrialN / trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
     show_break = trials.thisTrialN % break_every == 0
+    console.log(trials.ThisTrialN)
+    console.log(show_break)
     break_text.setText(break_msg);
     // setup some python lists for storing info about the break_done_touch
     break_done_touch.clicked_name = [];

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -576,7 +576,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 2;
+  break_every = 11;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";
@@ -1521,6 +1521,8 @@ function BreakRoutineBegin(snapshot) {
     break_msg_top = (("BREAK\n\nYou have now completed " + round(((trials.thisTrialN / trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
     show_break = trials.thisTrialN % break_every == 0
+    console.log(trials.ThisTrialN)
+    console.log(show_break)
     break_text.setText(break_msg);
     // setup some python lists for storing info about the break_done_touch
     break_done_touch.clicked_name = [];

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
base breaks on trials.nRemaining now

@@ -97,7 +97,7 @@ var win;
 var event;
 var randint;
 var instructions_image;
-var TrialClock;
+var presentTrialClock;
 var fixation_mask;
 var prime_text;
 var target;
@@ -204,8 +204,8 @@ function experimentInit() {
     flipHoriz : false, flipVert : false,
     texRes : 128, interpolate : true, depth : -6.0 
   });
-  // Initialize components for Routine "Trial"
-  TrialClock = new util.Clock();
+  // Initialize components for Routine "presentTrial"
+  presentTrialClock = new util.Clock();
   fixation_mask = new visual.TextStim({
     win: psychoJS.window,
     name: 'fixation_mask',
@@ -416,8 +416,8 @@ function experimentInit() {
     flipHoriz : false, flipVert : false,
     texRes : 128, interpolate : true, depth : -6.0 
   });
-  // Initialize components for Routine "Trial"
-  TrialClock = new util.Clock();
+  // Initialize components for Routine "presentTrial"
+  presentTrialClock = new util.Clock();
   fixation_mask = new visual.TextStim({
     win: psychoJS.window,
     name: 'fixation_mask',
@@ -565,7 +565,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 11;
+  break_every = 2;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";
@@ -683,9 +683,9 @@ function practice_trialsLoopBegin(practice_trialsLoopScheduler) {
     const snapshot = practice_trials.getSnapshot();
 
     practice_trialsLoopScheduler.add(importConditions(snapshot));
-    practice_trialsLoopScheduler.add(TrialRoutineBegin(snapshot));
-    practice_trialsLoopScheduler.add(TrialRoutineEachFrame(snapshot));
-    practice_trialsLoopScheduler.add(TrialRoutineEnd(snapshot));
+    practice_trialsLoopScheduler.add(presentTrialRoutineBegin(snapshot));
+    practice_trialsLoopScheduler.add(presentTrialRoutineEachFrame(snapshot));
+    practice_trialsLoopScheduler.add(presentTrialRoutineEnd(snapshot));
     practice_trialsLoopScheduler.add(feedbackRoutineBegin(snapshot));
[…]

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -108,7 +108,7 @@ var win;
 var event;
 var randint;
 var instructions_image;
-var TrialClock;
+var presentTrialClock;
 var fixation_mask;
 var prime_text;
 var target;
@@ -215,8 +215,8 @@ function experimentInit() {
     flipHoriz : false, flipVert : false,
     texRes : 128, interpolate : true, depth : -6.0 
   });
-  // Initialize components for Routine "Trial"
-  TrialClock = new util.Clock();
+  // Initialize components for Routine "presentTrial"
+  presentTrialClock = new util.Clock();
   fixation_mask = new visual.TextStim({
     win: psychoJS.window,
     name: 'fixation_mask',
@@ -427,8 +427,8 @@ function experimentInit() {
     flipHoriz : false, flipVert : false,
     texRes : 128, interpolate : true, depth : -6.0 
   });
-  // Initialize components for Routine "Trial"
-  TrialClock = new util.Clock();
+  // Initialize components for Routine "presentTrial"
+  presentTrialClock = new util.Clock();
   fixation_mask = new visual.TextStim({
     win: psychoJS.window,
     name: 'fixation_mask',
@@ -576,7 +576,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 11;
+  break_every = 2;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";
@@ -692,9 +692,9 @@ function practice_trialsLoopBegin(practice_trialsLoopScheduler) {
   for (const thisPractice_trial of practice_trials) {
     const snapshot = practice_trials.getSnapshot();
     practice_trialsLoopScheduler.add(importConditions(snapshot));
-    practice_trialsLoopScheduler.add(TrialRoutineBegin(snapshot));
-    practice_trialsLoopScheduler.add(TrialRoutineEachFrame(snapshot));
-    practice_trialsLoopScheduler.add(TrialRoutineEnd(snapshot));
+    practice_trialsLoopScheduler.add(presentTrialRoutineBegin(snapshot));
+    practice_trialsLoopScheduler.add(presentTrialRoutineEachFrame(snapshot));
+    practice_trialsLoopScheduler.add(presentTrialRoutineEnd(snapshot));
     practice_trialsLoopScheduler.add(feedbackRoutineBegin(snapshot));
[…]

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
change name of trials loop to experiment_trials

@@ -44,10 +44,10 @@ const end_of_practice_trials_pagesLoopScheduler = new Scheduler(psychoJS);
 flowScheduler.add(end_of_practice_trials_pagesLoopBegin, end_of_practice_trials_pagesLoopScheduler);
 flowScheduler.add(end_of_practice_trials_pagesLoopScheduler);
 flowScheduler.add(end_of_practice_trials_pagesLoopEnd);
-const trialsLoopScheduler = new Scheduler(psychoJS);
-flowScheduler.add(trialsLoopBegin, trialsLoopScheduler);
-flowScheduler.add(trialsLoopScheduler);
-flowScheduler.add(trialsLoopEnd);
+const experiment_trialsLoopScheduler = new Scheduler(psychoJS);
+flowScheduler.add(experiment_trialsLoopBegin, experiment_trialsLoopScheduler);
+flowScheduler.add(experiment_trialsLoopScheduler);
+flowScheduler.add(experiment_trialsLoopEnd);
 flowScheduler.add(EndRoutineBegin());
 flowScheduler.add(EndRoutineEachFrame());
 flowScheduler.add(EndRoutineEnd());
@@ -738,42 +738,42 @@ function end_of_practice_trials_pagesLoopEnd() {
 }
 
 
-var trials;
-function trialsLoopBegin(trialsLoopScheduler) {
+var experiment_trials;
+function experiment_trialsLoopBegin(experiment_trialsLoopScheduler) {
   // set up handler to look after randomisation of conditions etc
-  trials = new TrialHandler({
+  experiment_trials = new TrialHandler({
     psychoJS: psychoJS,
     nReps: 1, method: TrialHandler.Method.RANDOM,
     extraInfo: expInfo, originPath: undefined,
     trialList: trial_list_file,
-    seed: undefined, name: 'trials'
+    seed: undefined, name: 'experiment_trials'
   });
-  psychoJS.experiment.addLoop(trials); // add the loop to the experiment
-  currentLoop = trials;  // we're now the current loop
+  psychoJS.experiment.addLoop(experiment_trials); // add the loop to the experiment
+  currentLoop = experiment_trials;  // we're now the current loop
 
   // Schedule all the trials in the trialList:
-  trials.forEach(function() {
-    const snapshot = trials.getSnapshot();
+  experiment_trials.forEach(function() {
+    const snapshot = experiment_trials.getSnapshot();
 
[…]

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -55,10 +55,10 @@ const end_of_practice_trials_pagesLoopScheduler = new Scheduler(psychoJS);
 flowScheduler.add(end_of_practice_trials_pagesLoopBegin, end_of_practice_trials_pagesLoopScheduler);
 flowScheduler.add(end_of_practice_trials_pagesLoopScheduler);
 flowScheduler.add(end_of_practice_trials_pagesLoopEnd);
-const trialsLoopScheduler = new Scheduler(psychoJS);
-flowScheduler.add(trialsLoopBegin, trialsLoopScheduler);
-flowScheduler.add(trialsLoopScheduler);
-flowScheduler.add(trialsLoopEnd);
+const experiment_trialsLoopScheduler = new Scheduler(psychoJS);
+flowScheduler.add(experiment_trialsLoopBegin, experiment_trialsLoopScheduler);
+flowScheduler.add(experiment_trialsLoopScheduler);
+flowScheduler.add(experiment_trialsLoopEnd);
 flowScheduler.add(EndRoutineBegin());
 flowScheduler.add(EndRoutineEachFrame());
 flowScheduler.add(EndRoutineEnd());
@@ -746,41 +746,41 @@ function end_of_practice_trials_pagesLoopEnd() {
 }
 
 
-var trials;
-function trialsLoopBegin(trialsLoopScheduler) {
+var experiment_trials;
+function experiment_trialsLoopBegin(experiment_trialsLoopScheduler) {
   // set up handler to look after randomisation of conditions etc
-  trials = new TrialHandler({
+  experiment_trials = new TrialHandler({
     psychoJS: psychoJS,
     nReps: 1, method: TrialHandler.Method.RANDOM,
     extraInfo: expInfo, originPath: undefined,
     trialList: trial_list_file,
-    seed: undefined, name: 'trials'
+    seed: undefined, name: 'experiment_trials'
   });
-  psychoJS.experiment.addLoop(trials); // add the loop to the experiment
-  currentLoop = trials;  // we're now the current loop
+  psychoJS.experiment.addLoop(experiment_trials); // add the loop to the experiment
+  currentLoop = experiment_trials;  // we're now the current loop
 
   // Schedule all the trials in the trialList:
-  for (const thisTrial of trials) {
-    const snapshot = trials.getSnapshot();
-    trialsLoopScheduler.add(importConditions(snapshot));
[…]

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
fix typo

@@ -1514,7 +1514,7 @@ function BreakRoutineBegin(snapshot) {
     BreakClock.reset(); // clock
     frameN = -1;
     // update component parameters for each repeat
-    break_msg_top = (("BREAK\n\nYou have now completed " + round(((experiment_trials.thisTrialN / trials.nTotal) * 100)).toString()) + "% of the experiment. ");
+    break_msg_top = (("BREAK\n\nYou have now completed " + round(((experiment_trials.thisTrialN / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
     show_break = experiment_trials.nRemaining % break_every == 0
     console.log(experiment_trials.ThisTrialN)

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -1518,7 +1518,7 @@ function BreakRoutineBegin(snapshot) {
     BreakClock.reset(); // clock
     frameN = -1;
     // update component parameters for each repeat
-    break_msg_top = (("BREAK\n\nYou have now completed " + round(((experiment_trials.thisTrialN / trials.nTotal) * 100)).toString()) + "% of the experiment. ");
+    break_msg_top = (("BREAK\n\nYou have now completed " + round(((experiment_trials.thisTrialN / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
     show_break = experiment_trials.nRemaining % break_every == 0
     console.log(experiment_trials.ThisTrialN)

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
fix typo

@@ -1517,7 +1517,7 @@ function BreakRoutineBegin(snapshot) {
     break_msg_top = (("BREAK\n\nYou have now completed " + round(((experiment_trials.thisTrialN / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
     show_break = experiment_trials.nRemaining % break_every == 0
-    console.log(experiment_trials.ThisTrialN)
+    console.log(experiment_trials.thisTrialN)
     console.log(experiment_trials.nRemaining)
     console.log(show_break)
     break_text.setText(break_msg);

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -1521,7 +1521,7 @@ function BreakRoutineBegin(snapshot) {
     break_msg_top = (("BREAK\n\nYou have now completed " + round(((experiment_trials.thisTrialN / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
     show_break = experiment_trials.nRemaining % break_every == 0
-    console.log(experiment_trials.ThisTrialN)
+    console.log(experiment_trials.thisTrialN)
     console.log(experiment_trials.nRemaining)
     console.log(show_break)
     break_text.setText(break_msg);

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
add new variable trials_completed_so_far and increment it manually

@@ -129,6 +129,7 @@ var break_msg_top;
 var break_msg_middle;
 var break_msg_bottom;
 var break_msg;
+var trials_presented_so_far;
 var break_text;
 var break_done_touch;
 var break_done_keyboard;
@@ -571,6 +572,7 @@ function experimentInit() {
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";
   break_msg = "";
   
+  trials_presented_so_far = 0
   break_text = new visual.TextStim({
     win: psychoJS.window,
     name: 'break_text',
@@ -1514,12 +1516,16 @@ function BreakRoutineBegin(snapshot) {
     BreakClock.reset(); // clock
     frameN = -1;
     // update component parameters for each repeat
-    break_msg_top = (("BREAK\n\nYou have now completed " + round(((experiment_trials.thisTrialN / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
+    trials_presented_so_far++
+    
+    break_msg_top = (("BREAK\n\nYou have now completed " + round(((trials_presented_so_far / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
-    show_break = experiment_trials.nRemaining % break_every == 0
-    console.log(experiment_trials.thisTrialN)
+    show_break = trials_presented_so_far % break_every == 0
+    console.log(trials_presented_so_far)
     console.log(experiment_trials.nRemaining)
     console.log(show_break)
+    
+    
     break_text.setText(break_msg);
     // setup some python lists for storing info about the break_done_touch
     break_done_touch.clicked_name = [];

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -140,6 +140,7 @@ var break_msg_top;
 var break_msg_middle;
 var break_msg_bottom;
 var break_msg;
+var trials_presented_so_far;
 var break_text;
 var break_done_touch;
 var break_done_keyboard;
@@ -582,6 +583,7 @@ function experimentInit() {
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";
   break_msg = "";
   
+  trials_presented_so_far = 0
   break_text = new visual.TextStim({
     win: psychoJS.window,
     name: 'break_text',
@@ -1518,12 +1520,16 @@ function BreakRoutineBegin(snapshot) {
     BreakClock.reset(); // clock
     frameN = -1;
     // update component parameters for each repeat
-    break_msg_top = (("BREAK\n\nYou have now completed " + round(((experiment_trials.thisTrialN / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
+    trials_presented_so_far++
+    
+    break_msg_top = (("BREAK\n\nYou have now completed " + round(((trials_presented_so_far / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
-    show_break = experiment_trials.nRemaining % break_every == 0
-    console.log(experiment_trials.thisTrialN)
+    show_break = trials_presented_so_far % break_every == 0
+    console.log(trials_presented_so_far)
     console.log(experiment_trials.nRemaining)
     console.log(show_break)
+    
+    
     break_text.setText(break_msg);
     // setup some python lists for storing info about the break_done_touch
     break_done_touch.clicked_name = [];

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
add new variable trials_presented_so_far and increment it manually. now set it to 121 as it should be

@@ -566,7 +566,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 2;
+  break_every = 120;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -577,7 +577,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 2;
+  break_every = 120;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
remove console log messages

@@ -566,7 +566,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 120;
+  break_every = 121;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -577,7 +577,7 @@ function experimentInit() {
   
   // Initialize components for Routine "Break"
   BreakClock = new util.Clock();
-  break_every = 120;
+  break_every = 121;
   break_msg_top = "";
   break_msg_middle = "Please take a short break.\n";
   break_msg_bottom = "When you are done, please press the space bar or touch the \"Continue\" button below to continue the experiment.";

### 2020-11-26 html/lexical_decision_task_MP_exp2-legacy-browsers.js
remove console log messages

@@ -1521,9 +1521,9 @@ function BreakRoutineBegin(snapshot) {
     break_msg_top = (("BREAK\n\nYou have now completed " + round(((trials_presented_so_far / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
     show_break = trials_presented_so_far % break_every == 0
-    console.log(trials_presented_so_far)
-    console.log(experiment_trials.nRemaining)
-    console.log(show_break)
+    //console.log(trials_presented_so_far)
+    //console.log(experiment_trials.nRemaining)
+    //console.log(show_break)
     
     
     break_text.setText(break_msg);

### 2020-11-26 html/lexical_decision_task_MP_exp2.js

@@ -1525,9 +1525,9 @@ function BreakRoutineBegin(snapshot) {
     break_msg_top = (("BREAK\n\nYou have now completed " + round(((trials_presented_so_far / experiment_trials.nTotal) * 100)).toString()) + "% of the experiment. ");
     break_msg = ((break_msg_top + break_msg_middle) + break_msg_bottom);
     show_break = trials_presented_so_far % break_every == 0
-    console.log(trials_presented_so_far)
-    console.log(experiment_trials.nRemaining)
-    console.log(show_break)
+    //console.log(trials_presented_so_far)
+    //console.log(experiment_trials.nRemaining)
+    //console.log(show_break)
     
     
     break_text.setText(break_msg);

### 2020-11-30 pilot_data_analysis.Rmd
add analysis files, set counterbalancing condition to 3

@@
 
+# explore counterbalancing condition
+counterbalancing <- fs::dir_ls(path = "./data", glob = "*.csv") %>%
+  map_dfr(read_csv, .id = "source", n_max = 1, col_type = cols(
+  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer()))
+
 csv_data <- fs::dir_ls(path = "./data", glob = "*.csv") %>%
@@
 
+csv_data$device <- ifelse(csv_data$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
+
 # get participants with correct responses
 
-accuracy_by_participant <- csv_data %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())
+accuracy_by_participant <- csv_data %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n()) %>% left_join(counterbalancing, by = "source")
 
 participants_to_include <- accuracy_by_participant %>% filter(N == 480 & acc > .8)
+
+participants_to_exclude <- accuracy_by_participant %>% filter(N != 480 | acc <= .8)
 
@@
 
-write_csv(data_to_include, path = "current_data.csv")
+write_csv(data_to_include, file = "current_data.csv")
 
@@
 ```
+
+Experimental plot by device
+
+```{r plot_by_device}
+plot_raincloud(data_to_include %>% filter(corr == 1 & rt < 1500), x_column = "Condition", y_column = "rt", x_label = "Condition", y_label = "RT in ms (correct responses)", main_title = "RT by condition and word type") +
+  # put labels on the mean for easier comparison
+  stat_summary(fun.data = function(x) {data.frame(label = format(mean(x), digits = 2), y = mean(x))}, 
+                                      geom = "text",
+                                      #width = 1,
+                                      position = position_nudge(x = 0.5, y = 0),
+                                      #size = 0.2,
+                                      color = "black") +
+  facet_grid(cols = vars(PrimeDuration), rows = vars(StimulusType, device), labeller = label_context)
+
+```
 ## LMM for RT (words, correct responses)
@@
 ```
+```{r experiment1_and_2_comparison}
+exp1 <- read_csv("Exp 1 data.csv")
+
+```
 

### 2020-11-30 html/lexical_decision_task_MP_exp2-legacy-browsers.js

@@ -19,6 +19,7 @@ psychoJS.openWindow({
 let expName = 'lexical_decision_task_MP_exp2';  // from the Builder filename that created this script
 let expInfo = {'participant': '999'};
 
+// Start code blocks for 'Before Experiment'
 // schedule the experiment:
 psychoJS.schedule(psychoJS.gui.DlgFromDict({
   dictionary: expInfo,
@@ -68,7 +69,7 @@ var frameDur;
 function updateInfo() {
   expInfo['date'] = util.MonotonicClock.getDateStr();  // add a simple timestamp
   expInfo['expName'] = expName;
-  expInfo['psychopyVersion'] = '2020.2.5';
+  expInfo['psychopyVersion'] = '2020.2.8';
   expInfo['OS'] = window.navigator.platform;
 
   // store frame rate of monitor if we can measure it successfully
@@ -247,7 +248,8 @@ function experimentInit() {
   fixation_height = 0.1;
   text_height = 0.1;
   arrow_keys_height = 0.05;
-  counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
+  // counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
+  counterbalancing_condition = 3;
   thisExp.addData("counterbalancing_condition", counterbalancing_condition);
   trial_list_file = (("trials_list" + counterbalancing_condition.toString()) + ".xlsx");
   mask_duration = 0.5;
@@ -459,7 +461,8 @@ function experimentInit() {
   fixation_height = 0.1;
   text_height = 0.1;
   arrow_keys_height = 0.05;
-  counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
+  // counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
+  counterbalancing_condition = 3;
   thisExp.addData("counterbalancing_condition", counterbalancing_condition);
   trial_list_file = (("trials_list" + counterbalancing_condition.toString()) + ".xlsx");
   mask_duration = 0.5;

### 2020-11-30 html/lexical_decision_task_MP_exp2.js

@@ -30,6 +30,7 @@ psychoJS.openWindow({
 let expName = 'lexical_decision_task_MP_exp2';  // from the Builder filename that created this script
 let expInfo = {'participant': '999'};
 
+// Start code blocks for 'Before Experiment'
 // schedule the experiment:
 psychoJS.schedule(psychoJS.gui.DlgFromDict({
   dictionary: expInfo,
@@ -79,7 +80,7 @@ var frameDur;
 function updateInfo() {
   expInfo['date'] = util.MonotonicClock.getDateStr();  // add a simple timestamp
   expInfo['expName'] = expName;
-  expInfo['psychopyVersion'] = '2020.2.5';
+  expInfo['psychopyVersion'] = '2020.2.8';
   expInfo['OS'] = window.navigator.platform;
 
   // store frame rate of monitor if we can measure it successfully
@@ -258,7 +259,8 @@ function experimentInit() {
   fixation_height = 0.1;
   text_height = 0.1;
   arrow_keys_height = 0.05;
-  counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
+  // counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
+  counterbalancing_condition = 3;
   thisExp.addData("counterbalancing_condition", counterbalancing_condition);
   trial_list_file = (("trials_list" + counterbalancing_condition.toString()) + ".xlsx");
   mask_duration = 0.5;
@@ -470,7 +472,8 @@ function experimentInit() {
   fixation_height = 0.1;
   text_height = 0.1;
   arrow_keys_height = 0.05;
-  counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
+  // counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
+  counterbalancing_condition = 3;
   thisExp.addData("counterbalancing_condition", counterbalancing_condition);
   trial_list_file = (("trials_list" + counterbalancing_condition.toString()) + ".xlsx");
   mask_duration = 0.5;

### 2020-12-01 html/lexical_decision_task_MP_exp2-legacy-browsers.js
change counterbalancing condition to 0

@@ -249,7 +249,7 @@ function experimentInit() {
   text_height = 0.1;
   arrow_keys_height = 0.05;
   // counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
-  counterbalancing_condition = 3;
+  counterbalancing_condition = 0;
   thisExp.addData("counterbalancing_condition", counterbalancing_condition);
   trial_list_file = (("trials_list" + counterbalancing_condition.toString()) + ".xlsx");
   mask_duration = 0.5;
@@ -462,7 +462,7 @@ function experimentInit() {
   text_height = 0.1;
   arrow_keys_height = 0.05;
   // counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
-  counterbalancing_condition = 3;
+  counterbalancing_condition = 0;
   thisExp.addData("counterbalancing_condition", counterbalancing_condition);
   trial_list_file = (("trials_list" + counterbalancing_condition.toString()) + ".xlsx");
   mask_duration = 0.5;

### 2020-12-01 html/lexical_decision_task_MP_exp2.js

@@ -260,7 +260,7 @@ function experimentInit() {
   text_height = 0.1;
   arrow_keys_height = 0.05;
   // counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
-  counterbalancing_condition = 3;
+  counterbalancing_condition = 0;
   thisExp.addData("counterbalancing_condition", counterbalancing_condition);
   trial_list_file = (("trials_list" + counterbalancing_condition.toString()) + ".xlsx");
   mask_duration = 0.5;
@@ -473,7 +473,7 @@ function experimentInit() {
   text_height = 0.1;
   arrow_keys_height = 0.05;
   // counterbalancing_condition = (Math.floor((Math.random() * ((3 - 0) + 1))) + 0);
-  counterbalancing_condition = 3;
+  counterbalancing_condition = 0;
   thisExp.addData("counterbalancing_condition", counterbalancing_condition);
   trial_list_file = (("trials_list" + counterbalancing_condition.toString()) + ".xlsx");
   mask_duration = 0.5;

### 2020-12-07 pilot_data_analysis.Rmd
Remove test data files

@@
 
+#participants_to_exclude[,1:3]
+
 participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
+
 paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows
+
+exclude_list_for_prolific <- str_extract(string = participants_to_exclude$source, pattern = "[a-z0-9]{24}") %>% paste0(collapse = "\n")
 

### 2021-01-04 Manuscript.Rmd
Make manuscript files

---
title             : "Effects of masked prime duration in an online lexical decision task"
shorttitle        : "Online lexical decision task"

author: 
  - name          : "Bernhard Angele"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, Faculty of Science and Technology, Talbot Campus, Fern Barrow, Poole BH12 5BB, UK"
    email         : "bangele@bournemouth.ac.uk"
  - name          : "Ana Baciero"
    affiliation   : "2,3"
  - name          : "Pablo Gomez"
    affiliation   : "3,4"
  - name          : "Manuel Perea Lara"
    affiliation   : "2,3"

affiliation:
  - id            : "1"
    institution   : "Bournemouth University"
  - id            : "2"
    institution   : Universitat de Valencia, Valencia, Spain
  - id            : "3"
    institution   : "Nebrija University, Madrid, Spain"
  - id            : "4"
    institution   : "California State University San Bernardino, Palm Desert Campus"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Masked priming is one of the most important paradigms in the study of visual word recognition and representation.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["bibliography.bib", "r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@gomezDiffusionModelAccount2013 performed an experiment

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-01-04 Manuscript.tex
Make manuscript files

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Effects of masked prime duration in an online lexical decision task},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Online lexical decision task}
\author{Bernhard Angele\textsuperscript{1,2}, Ana Baciero\textsuperscript{2,3}, Pablo Gomez\textsuperscript{3,4}, \& Manuel Perea Lara\textsuperscript{2,3}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Bournemouth University\\\textsuperscript{2} Universitat de Valencia, Valencia, Spain\\\textsuperscript{3} Nebrija University, Madrid, Spain\\\textsuperscript{4} California State University San Bernardino, Palm Desert Campus}
\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to Bernhard Angele, Department of Psychology, Faculty of Science and Technology, Talbot Campus, Fern Barrow, Poole BH12 5BB, UK. E-mail: bangele@bournemouth.ac.uk}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{Effects of masked prime duration in an online lexical decision task}

\date{}

\abstract{
Masked priming is one of the most important paradigms in the study of visual word recognition and representation.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

Gomez, Perea, and Ratcliff (2013) performed an experiment

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 4.0.3; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-gomezDiffusionModelAccount2013}{}%
Gomez, P., Perea, M., \& Ratcliff, R. (2013). A diffusion model account of masked versus unmasked priming: Are they qualitatively different? \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{39}(6), 1731--1740. \url{https://doi.org/10.1037/a0032333}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\endgroup

\end{document}

### 2021-01-04 pilot_data_analysis.Rmd
Make manuscript files

@@
 ```{r participant_map}
-library(sp)
-library(leaflet)
-
-participant_data <- read_csv("participant_data.csv")
-coordinates(participant_data) <- c("Location Longitude","Location Latitude")
-leaflet(participant_data) %>% addMarkers(label = .$`Confirm Prolific ID`) %>% addTiles()
+# library(sp)
+# library(leaflet)
+# 
+# participant_data <- read_csv("participant_data.csv")
+# coordinates(participant_data) <- c("Location Longitude","Location Latitude")
+# leaflet(participant_data) %>% addMarkers(label = .$`Confirm Prolific ID`) %>% addTiles()
 ```

### 2021-01-12 Manuscript.Rmd
Update manuscript, keep working on intro

@@
 
+Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important paradigms in the study of visual word recognition.
+Priming refers to the observation that the response to a target stimulus (e.g.
+responding that "DOCTOR" is a word in a lexical decision task or pronouncing the same stimulus in a naming task) is faster, more accurate, or both when it was preceded by a related stimulus (e.g.
+"nurse") compared to an unrelated stimulus (e.g.
+"horse").
+In masked priming, the prime stimulus ("nurse" or "horse") is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g.
+"#####") which is presented fora much longer duration (typically 500 ms).
+This forward mask ensures that participants are usually unaware of the prime [@forsterRepetitionPrimingFrequency1984].
+The masked priming paradigm has been used in a large number of studies over the last decades [for a review, see e.g.
+@kinoshitaMaskedPrimingState2004; @vandenbusscheMechanismsMaskedPriming2009], but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by @forsterDMDXWindowsDisplay2003.
+Given that, as of the time of this writing, researchers in a large part of the world are unable to perform psychology experiments in a laboratory due to the COVID-19 pandemic, with not much clarity about when laboratories will be able to reopen completely, it is an important consideration whether it may be possible to collect masked priming data remotely using online experiments.
+Even after the current exceptional situation, online data collection has many advantages, such as easy access to a much more diverse population than would be accessible at the typical university research laboratory, independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment, not time spent commuting, waiting for the experiment to start, etc.
+Researchers in decision making and economics have been using online paradigms for several decades now [e.g.
+@birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010], but cognitive and experimental psychology have been much slower in taking up online paradigms, often due to concerns about the validity of the results.
+Such concerns are not limited to cognitive studies [@austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times.
+In masked priming, it is critical for the onset of the mask, the prime, and the target to occur at the intended times.
+In particular, presenting the prime for too long will counteract the effect of the mask, making the prime consciously visible to the participant.
+There have been attempts to address these concerns.
+For example, a Web version of DMDX (webDMDX) was developed which showed promising results in a trial experiment [@witzelTestingViabilityWebDMDX2013].
+However, webDMDX was a self-contained Windows executable file that participants had to download and run rather than a "true" online experiment that could be run inside of a browser.
+A downside of this is that participants often are (and should be) understandably skeptical about downloading and running files from the Internet.
+Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
+
 @gomezDiffusionModelAccount2013 performed an experiment

### 2021-01-12 Manuscript.tex
Update manuscript, keep working on intro

@@
 
+Masked priming (Forster \& Davis, 1984) is one of the most important paradigms in the study of visual word recognition.
+Priming refers to the observation that the response to a target stimulus (e.g.~responding that \enquote{DOCTOR} is a word in a lexical decision task or pronouncing the same stimulus in a naming task) is faster, more accurate, or both when it was preceded by a related stimulus (e.g.~\enquote{nurse}) compared to an unrelated stimulus (e.g.~\enquote{horse}).
+In masked priming, the prime stimulus (\enquote{nurse} or \enquote{horse}) is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g.~\enquote{\#\#\#\#\#}) which is presented fora much longer duration (typically 500 ms).
+This forward mask ensures that participants are usually unaware of the prime (Forster \& Davis, 1984).
+The masked priming paradigm has been used in a large number of studies over the last decades (for a review, see e.g.~Kinoshita \& Lupker, 2004; Van den Bussche, Van den Noortgate, \& Reynvoet, 2009), but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by Forster and Forster (2003).
+Given that, as of the time of this writing, researchers in a large part of the world are unable to perform psychology experiments in a laboratory due to the COVID-19 pandemic, with not much clarity about when laboratories will be able to reopen completely, it is an important consideration whether it may be possible to collect masked priming data remotely using online experiments.
+Even after the current exceptional situation, online data collection has many advantages, such as easy access to a much more diverse population than would be accessible at the typical university research laboratory, independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment, not time spent commuting, waiting for the experiment to start, etc.
+Researchers in decision making and economics have been using online paradigms for several decades now (e.g.~Birnbaum \& Birnbaum, 2000; Paolacci, Chandler, \& Ipeirotis, 2010), but cognitive and experimental psychology have been much slower in taking up online paradigms, often due to concerns about the validity of the results.
+Such concerns are not limited to cognitive studies (Aust, Diedenhofen, Ullrich, \& Musch, 2013), but they are exacerbated by the reliance on precise presentation times.
+In masked priming, it is critical for the onset of the mask, the prime, and the target to occur at the intended times.
+In particular, presenting the prime for too long will counteract the effect of the mask, making the prime consciously visible to the participant.
+There have been attempts to address these concerns.
+For example, a Web version of DMDX (webDMDX) was developed which showed promising results in a trial experiment (Witzel, Cornelius, Witzel, Forster, \& Forster, 2013).
+However, webDMDX was a self-contained Windows executable file that participants had to download and run rather than a \enquote{true} online experiment that could be run inside of a browser.
+A downside of this is that participants often are (and should be) understandably skeptical about downloading and running files from the Internet.
+Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
+
 Gomez, Perea, and Ratcliff (2013) performed an experiment
@@
 
+\leavevmode\hypertarget{ref-austSeriousnessChecksAre2013}{}%
+Aust, F., Diedenhofen, B., Ullrich, S., \& Musch, J.
+(2013).
+Seriousness checks are useful to improve data validity in online research.
+\emph{Behavior Research Methods}, \emph{45}(2), 527--535.
+\url{https://doi.org/10.3758/s13428-012-0265-2}
+
+\leavevmode\hypertarget{ref-birnbaumPsychologicalExperimentsInternet2000a}{}%
+Birnbaum, M. H., \& Birnbaum, M. O. (2000). \emph{Psychological Experiments on the Internet}. Elsevier. Retrieved from \url{http://books.google.com?id=sw4NHyThFFkC}
+
+\leavevmode\hypertarget{ref-forsterRepetitionPrimingFrequency1984}{}%
+Forster, K.
+I., \& Davis, C.
+(1984).
+Repetition priming and frequency attenuation in lexical access.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{10}(4), 680--698.
+\url{https://doi.org/10.1037/0278-7393.10.4.680}
+
+\leavevmode\hypertarget{ref-forsterDMDXWindowsDisplay2003}{}%
+Forster, K. I., \& Forster, J. C. (2003). DMDX: A Windows display program with millisecond accuracy. \emph{Behavior Research Methods, Instruments, \& Computers}, \emph{35}(1), 116--124.
+
 \leavevmode\hypertarget{ref-gomezDiffusionModelAccount2013}{}%
@@
 
+\leavevmode\hypertarget{ref-kinoshitaMaskedPrimingState2004}{}%
+Kinoshita, S., \& Lupker, S. J. (2004). \emph{Masked Priming: The State of the Art}. Psychology Press. Retrieved from \url{http://books.google.com?id=VH55AgAAQBAJ}
+
+\leavevmode\hypertarget{ref-paolacciRunningExperimentsAmazon2010}{}%
+Paolacci, G., Chandler, J., \& Ipeirotis, P.
+G.
+(2010).
+\emph{Running Experiments on Amazon Mechanical Turk} (SSRN Scholarly Paper No.
+ID 1626226).
+Rochester, NY: Social Science Research Network.
+Retrieved from \url{https://papers.ssrn.com/abstract=1626226}
+
 \leavevmode\hypertarget{ref-R-base}{}%
 R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-vandenbusscheMechanismsMaskedPriming2009}{}%
+Van den Bussche, E., Van den Noortgate, W., \& Reynvoet, B.
+(2009).
+Mechanisms of masked priming: A meta-analysis.
+\emph{Psychological Bulletin}, \emph{135}(3), 452--477.
+\url{https://doi.org/10.1037/a0015329}
+
+\leavevmode\hypertarget{ref-witzelTestingViabilityWebDMDX2013}{}%
+Witzel, J., Cornelius, S., Witzel, N., Forster, K.
+I., \& Forster, J.
+C.
+(2013).
+Testing the viability of webDMDX for masked priming experiments.
+\emph{The Mental Lexicon}, \emph{8}(3), 421--449.
+\url{https://doi.org/10.1075/ml.8.3.07wit}
 

### 2021-03-01 Manuscript.Rmd
Major changes, new abstract

@@
 abstract: |
-  Masked priming is one of the most important paradigms in the study of visual word recognition and representation.
+  Masked priming is one of the most important paradigms in the study of visual word recognition, but it is usually thought to require a laboratory setup with a known monitor and keyboard.
+To investigate if this technique can be used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS [@peirce2019].
+In particular, we wanted to compare our online results to the data collected by @gomezDiffusionModelAccount2013, who compared masked and unmasked priming.
+Furthermore, we also tested the role of prime exposure duration effectively in an online experiment (33 vs.
+50 ms in Experiment 1 and 16 vs.
+33 ms in Experiment 2).
+  We found that our online data are indeed very similar to the masked priming data reported by @gomezDiffusionModelAccount2013.
+Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33 ms and no priming effect at 16 ms prime duration.
+  From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., Psychopy) can present stimuli and collect responses on standard consumer devices with enough precision.
+In sum, these findings provide us with confidence that masked priming can be used online, thus allowing us to reach populations that are hard to test in a laboratory.
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
+keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
 wordcount         : "X"
-
-bibliography      : ["bibliography.bib", "r-references.bib"]
 
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 output            : papaja::apa6_pdf
+bibliography: ["references.bib", "r-references.bib"]
 ---
@@
 In masked priming, the prime stimulus ("nurse" or "horse") is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g.
-"#####") which is presented fora much longer duration (typically 500 ms).
+"\#\#\#\#\#") which is presented fora much longer duration (typically 500 ms).
 This forward mask ensures that participants are usually unaware of the prime [@forsterRepetitionPrimingFrequency1984].
@@
 @kinoshitaMaskedPrimingState2004; @vandenbusscheMechanismsMaskedPriming2009], but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by @forsterDMDXWindowsDisplay2003.
+
 Given that, as of the time of this writing, researchers in a large part of the world are unable to perform psychology experiments in a laboratory due to the COVID-19 pandemic, with not much clarity about when laboratories will be able to reopen completely, it is an important consideration whether it may be possible to collect masked priming data remotely using online experiments.
@@
 For example, a Web version of DMDX (webDMDX) was developed which showed promising results in a trial experiment [@witzelTestingViabilityWebDMDX2013].
+
 However, webDMDX was a self-contained Windows executable file that participants had to download and run rather than a "true" online experiment that could be run inside of a browser.
@@
 Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
+As a consequence, the use of webDMDX has been rather limited so far.
+Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web.
+Most notably, the HTML5 standard now makes it possible to use Javascript in order to draw stimuli interactively and monitor participant responses with remarkable flexibility inside the browser.
+Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets [@reimersPresentationResponseTiming2015].
+There is now a variety of software packages taking advantage of the new capabilites to present experimental stimuli and collect data, both commercial, e.g.
+Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020] and open-source, e.g.
+jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of Psychopy 3, @peirce2019].
+
+Of course, despite the technological advances, there are still concerns about timing and measurement precision.
+While the Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (all stimulus data are usually downloaded before the start of the experiment to avoid delays), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
+Experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
+As @reimersPresentationResponseTiming2015 point out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
+If the results of the Web-based study are comparable to previous lab-based results, this suggests that whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
+
+The first approach has the advantage that differences in presentation timings can be objectively recorded and evaluated.
+A very thorough recent example of this approach is the "timing mega-study" by @bridges2020, who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
+The very similar study by @anwyl-irvine2020a compares only online packages and browsers with regard to timing.
+Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with "reasonable" precision, although the lab-based packages were slightly better in this regard.
+
+However, it
+
+In o
 
@@
 # Methods
+
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
@@
 ## Data analysis
+
 We used `r cite_r("r-references.bib")` for all our analyses.
@@
 
+```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
 
-<div id="refs" custom-style="Bibliography"></div>
 \endgroup

### 2021-03-01 Manuscript.tex
Major changes, new abstract

@@
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
+\usepackage{amsmath}
 \usepackage{ifxetex,ifluatex}
@@
   \usepackage{textcomp} % provide euro and other symbols
+  \usepackage{amssymb}
 \else % if luatex or xetex
@@
   pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdfkeywords={Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration},
   hidelinks,
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 E-mail: bangele@bournemouth.ac.uk}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
@@
 \fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \abstract{
-Masked priming is one of the most important paradigms in the study of visual word recognition and representation.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+Masked priming is one of the most important paradigms in the study of visual word recognition, but it is usually thought to require a laboratory setup with a known monitor and keyboard.
+To investigate if this technique can be used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS (Peirce et al., 2019).
+In particular, we wanted to compare our online results to the data collected by Gomez, Perea, and Ratcliff (2013), who compared masked and unmasked priming.
+Furthermore, we also tested the role of prime exposure duration effectively in an online experiment (33 vs.~50 ms in Experiment 1 and 16 vs.~33 ms in Experiment 2).
+We found that our online data are indeed very similar to the masked priming data reported by Gomez, Perea, and Ratcliff (2013).
+Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33 ms and no priming effect at 16 ms prime duration.
+From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., Psychopy) can present stimuli and collect responses on standard consumer devices with enough precision.
+In sum, these findings provide us with confidence that masked priming can be used online, thus allowing us to reach populations that are hard to test in a laboratory.
 }
@@
 Masked priming (Forster \& Davis, 1984) is one of the most important paradigms in the study of visual word recognition.
-Priming refers to the observation that the response to a target stimulus (e.g.~responding that \enquote{DOCTOR} is a word in a lexical decision task or pronouncing the same stimulus in a naming task) is faster, more accurate, or both when it was preceded by a related stimulus (e.g.~\enquote{nurse}) compared to an unrelated stimulus (e.g.~\enquote{horse}).
-In masked priming, the prime stimulus (\enquote{nurse} or \enquote{horse}) is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g.~\enquote{\#\#\#\#\#}) which is presented fora much longer duration (typically 500 ms).
+Priming refers to the observation that the response to a target stimulus (e.g.~responding that ``DOCTOR'' is a word in a lexical decision task or pronouncing the same stimulus in a naming task) is faster, more accurate, or both when it was preceded by a related stimulus (e.g.~``nurse'') compared to an unrelated stimulus (e.g.~``horse'').
+In masked priming, the prime stimulus (``nurse'' or ``horse'') is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g.~``\#\#\#\#\#'') which is presented fora much longer duration (typically 500 ms).
 This forward mask ensures that participants are usually unaware of the prime (Forster \& Davis, 1984).
-The masked priming paradigm has been used in a large number of studies over the last decades (for a review, see e.g.~Kinoshita \& Lupker, 2004; Van den Bussche, Van den Noortgate, \& Reynvoet, 2009), but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by Forster and Forster (2003).
+The masked priming paradigm has been used in a large number of studies over the last decades (for a review, see e.g.
+Kinoshita \& Lupker, 2004; Van den Bussche, Van den Noortgate, \& Reynvoet, 2009), but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by Forster and Forster (2003).
+
 Given that, as of the time of this writing, researchers in a large part of the world are unable to perform psychology experiments in a laboratory due to the COVID-19 pandemic, with not much clarity about when laboratories will be able to reopen completely, it is an important consideration whether it may be possible to collect masked priming data remotely using online experiments.
 Even after the current exceptional situation, online data collection has many advantages, such as easy access to a much more diverse population than would be accessible at the typical university research laboratory, independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment, not time spent commuting, waiting for the experiment to start, etc.
-Researchers in decision making and economics have been using online paradigms for several decades now (e.g.~Birnbaum \& Birnbaum, 2000; Paolacci, Chandler, \& Ipeirotis, 2010), but cognitive and experimental psychology have been much slower in taking up online paradigms, often due to concerns about the validity of the results.
+Researchers in decision making and economics have been using online paradigms for several decades now (e.g.
+Birnbaum \& Birnbaum, 2000; Paolacci, Chandler, \& Ipeirotis, 2010), but cognitive and experimental psychology have been much slower in taking up online paradigms, often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies (Aust, Diedenhofen, Ullrich, \& Musch, 2013), but they are exacerbated by the reliance on precise presentation times.
@@
 For example, a Web version of DMDX (webDMDX) was developed which showed promising results in a trial experiment (Witzel, Cornelius, Witzel, Forster, \& Forster, 2013).
-However, webDMDX was a self-contained Windows executable file that participants had to download and run rather than a \enquote{true} online experiment that could be run inside of a browser.
+
+However, webDMDX was a self-contained Windows executable file that participants had to download and run rather than a ``true'' online experiment that could be run inside of a browser.
 A downside of this is that participants often are (and should be) understandably skeptical about downloading and running files from the Internet.
 Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
+As a consequence, the use of webDMDX has been rather limited so far.
+Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web.
+Most notably, the HTML5 standard now makes it possible to use Javascript in order to draw stimuli interactively and monitor participant responses with remarkable flexibility inside the browser.
+Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets (Reimers \& Stewart, 2015).
+There is now a variety of software packages taking advantage of the new capabilites to present experimental stimuli and collect data, both commercial, e.g.~Gorilla (A.
+L.
+Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020) or Testable (Rezlescu, Danaila, Miron, \& Amariei, 2020) and open-source, e.g.~jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of Psychopy 3, Peirce et al., 2019).
+
+Of course, despite the technological advances, there are still concerns about timing and measurement precision.
+While the Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (all stimulus data are usually downloaded before the start of the experiment to avoid delays), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
+Experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
+As Reimers and Stewart (2015) point out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
+If the results of the Web-based study are comparable to previous lab-based results, this suggests that whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
+
+The first approach has the advantage that differences in presentation timings can be objectively recorded and evaluated.
+A very thorough recent example of this approach is the ``timing mega-study'' by Bridges, Pitiot, MacAskill, and Peirce (2020), who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
+The very similar study by A.
+Anwyl-Irvine, Dalmaijer, Hodges, and Evershed (2020) compares only online packages and browsers with regard to timing.
+Overall, Bridges, Pitiot, MacAskill, and Peirce (2020) found that online packages were capable of presenting visual stimuli with ``reasonable'' precision, although the lab-based packages were slightly better in this regard.
+
+However, it
+
+In o
 
@@
 
-We used R (Version 4.0.3; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020) for all our analyses.
+We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-package \emph{papaja} {[}Version 0.1.0.9942; Aust and Barth (2020){]} for all our analyses.
 
@@
 \hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-anwyl-irvine2020a}{}%
+Anwyl-Irvine, A., Dalmaijer, E.
+S., Hodges, N., \& Evershed, J.
+K.
+(2020).
+Realistic precision and accuracy of online experiment platforms, web browsers, and devices.
+\emph{Behavior Research Methods}.
+\url{https://doi.org/10.3758/s13428-020-01501-5}
+
+\leavevmode\hypertarget{ref-anwyl-irvine2020}{}%
+Anwyl-Irvine, A.
+L., Massonnié, J., Flitton, A., Kirkham, N., \& Evershed, J.
+K.
+(2020).
+Gorilla in our midst: An online behavioral experiment builder.
+\emph{Behavior Research Methods}, \emph{52}(1), 388--407.
+\url{https://doi.org/10.3758/s13428-019-01237-x}
+
 \leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
@@
 \leavevmode\hypertarget{ref-birnbaumPsychologicalExperimentsInternet2000a}{}%
-Birnbaum, M. H., \& Birnbaum, M. O. (2000). \emph{Psychological Experiments on the Internet}. Elsevier. Retrieved from \url{http://books.google.com?id=sw4NHyThFFkC}
+Birnbaum, M. H., \& Birnbaum, M. O. (2000). \emph{Psychological {Experiments} on the {Internet}}. {Elsevier}. Retrieved from \url{http://books.google.com?id=sw4NHyThFFkC}
+
+\leavevmode\hypertarget{ref-bridges2020}{}%
+Bridges, D., Pitiot, A., MacAskill, M.
+R., \& Peirce, J.
+W.
+(2020).
+The timing mega-study: comparing a range of experiment generators, both lab-based and online.
+\emph{PeerJ}, \emph{8}, e9414.
+\url{https://doi.org/10.7717/peerj.9414}
+
+\leavevmode\hypertarget{ref-deleeuw2015}{}%
+de Leeuw, J.
+R.
+(2015).
+jsPsych: A JavaScript library for creating behavioral experiments in a Web browser.
+\emph{Behavior Research Methods}, \emph{47}(1), 1--12.
+\url{https://doi.org/10.3758/s13428-014-0458-y}
 
@@
 \leavevmode\hypertarget{ref-forsterDMDXWindowsDisplay2003}{}%
-Forster, K. I., \& Forster, J. C. (2003). DMDX: A Windows display program with millisecond accuracy. \emph{Behavior Research Methods, Instruments, \& Computers}, \emph{35}(1), 116--124.
+Forster, K. I., \& Forster, J. C. (2003). {DMDX}: {A Windows} display program with millisecond accuracy. \emph{Behavior Research Methods, Instruments, \& Computers}, \emph{35}(1), 116--124.
 
@@
 (2013).
-A diffusion model account of masked versus unmasked priming: Are they qualitatively different?
+A diffusion model account of masked versus unmasked priming: {Are} they qualitatively different?
 \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{39}(6), 1731--1740.
@@
 \leavevmode\hypertarget{ref-kinoshitaMaskedPrimingState2004}{}%
-Kinoshita, S., \& Lupker, S. J. (2004). \emph{Masked Priming: The State of the Art}. Psychology Press. Retrieved from \url{http://books.google.com?id=VH55AgAAQBAJ}
+Kinoshita, S., \& Lupker, S. J. (2004). \emph{Masked {Priming}: {The State} of the {Art}}. {Psychology Press}. Retrieved from \url{http://books.google.com?id=VH55AgAAQBAJ}
 
@@
 (2010).
-\emph{Running Experiments on Amazon Mechanical Turk} (SSRN Scholarly Paper No.
+\emph{Running {Experiments} on {Amazon Mechanical Turk}} (SSRN Scholarly Paper No.
 ID 1626226).
-Rochester, NY: Social Science Research Network.
+{Rochester, NY}: {Social Science Research Network}.
 Retrieved from \url{https://papers.ssrn.com/abstract=1626226}
+
+\leavevmode\hypertarget{ref-peirce2019}{}%
+Peirce, J., Gray, J.
+R., Simpson, S., MacAskill, M., Höchenberger, R., Sogo, H., \ldots{} Lindeløv, J.
+K.
+(2019).
+PsychoPy2: Experiments in behavior made easy.
+\emph{Behavior Research Methods}, \emph{51}(1), 195--203.
+\url{https://doi.org/10.3758/s13428-018-01193-y}
 
@@
 
+\leavevmode\hypertarget{ref-reimersPresentationResponseTiming2015}{}%
+Reimers, S., \& Stewart, N.
+(2015).
+Presentation and response timing accuracy in {Adobe Flash} and {HTML5}/{JavaScript Web} experiments.
+\emph{Behavior Research Methods}, \emph{47}(2), 309--327.
+\url{https://doi.org/10.3758/s13428-014-0471-1}
+
+\leavevmode\hypertarget{ref-rezlescu2020}{}%
+Rezlescu, C., Danaila, I., Miron, A., \& Amariei, C.
+(2020).
+Chapter 13 - More time for science: Using Testable to create and share behavioral experiments faster, recruit better participants, and engage students in hands-on research.
+In B.
+L.
+Parkin (Ed.) (Vol.
+253, pp.
+243--262).
+Elsevier.
+\url{https://doi.org/10.1016/bs.pbr.2020.06.005}
+
 \leavevmode\hypertarget{ref-vandenbusscheMechanismsMaskedPriming2009}{}%
@@
 (2009).
-Mechanisms of masked priming: A meta-analysis.
+Mechanisms of masked priming: {A} meta-analysis.
 \emph{Psychological Bulletin}, \emph{135}(3), 452--477.
@@
 (2013).
-Testing the viability of webDMDX for masked priming experiments.
+Testing the viability of {webDMDX} for masked priming experiments.
 \emph{The Mental Lexicon}, \emph{8}(3), 421--449.
 \url{https://doi.org/10.1075/ml.8.3.07wit}
+
+\end{CSLReferences}
 

### 2021-03-06 Manuscript.Rmd
First draft of introduction

@@
 
-However, it
+This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
+If this is not possible, there is no point in moving forward to the second approach and replicating specific paradigms.
+However, it is of course impossible to test every possible device and configuration that participants might use.
+On the other hand, some of the differences in precision and accuracy between setups that can be observed using a photodiode may be too small to have an influence on actual participant performance.
+Therefore, we consider replication of previous lab-based effects a more important test of online paradigms than photodiode measurements.
+Based on the results by @bridges2020 and @anwyl-irvine2020a, we are satisfied that modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
+In order to establish whether masked priming studies can be successfully run sonline, the next step is now to follow the second approach and implement the masked priming paradigm in one of the online experiment packages tested by @bridges2020 and @anwyl-irvine2020a.
+After evaluating their results, we decided on Psychopy/PsychoJS [@peirce2019] as it combines relative ease of use with high precision and accuracy across the great majority of platforms.
 
-In o
+In the present study, we were particularly interested in manipulating the duration of the prime, as this is what determines whether the stimulus is consciously perceived or not (i.e., if it is masked).
+@gomezDiffusionModelAccount2013 performed an experiment in which they presented a prime either for 56 ms preceded by a mask or for 200 ms without a mask.
+They found qualitative differences between masked and unmasked priming, which they explained using the diffusion model [@ratcliff2004]: For masked priming, the priming effects for identical compared to unrelated primes were the same across all quantiles of the response time distribution.
+In the diffusion model, this corresponds to a shift in a change in the $T_{er}$ parameter, which corresponds to encoding processed.
+However, for unmasked priming, the identity priming effects were stronger in the upper quantiles of the RT distribution than in the lower quantiles.
+In the diffusion model, this corresponds to a shift in both the $T_{er}$ parameter and the drift rate, the parameter corresponding to the quality of information.
+This qualitative pattern can help us interpret our results as well.
 
-@gomezDiffusionModelAccount2013 performed an experiment
+Additionally, if the prime duration can be manipulated very precisely, we may able to see effects of small differences in prime durations.
+@ziegler2000 found that priming effects were smaller for lower prime durations and interpreted this as evidence for different levels of facilitation (due to phonological overlap) and inhibition (due to visual differences between prime and target).
 
-# Methods
+In order to test this, we presented masked primes of different durations in an online experiment and measured response times and accuracy.
+
+If it is possible to present masked primes reliably in an online experiment, our results should be similar to those observed by @gomezDiffusionModelAccount2013 in their masked priming condition for word trials:
+
+1: The priming effects should be approximately the same across quantiles in the reaction time distributions. 2: In terms of the Diffusion model, allowing
+
+a) the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
+
+b) allowing the non-decision parameter T_er to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one T_er parameter for all word stimuli regardless of priming condition).
+
+If it is not possible to achieve consistent presentation times in an online experiment, and the primes are effectively presented for longer durations than intended, we should see a pattern that resembles that observed by Gomez et al.
+(2013) for unmasked primes:
+
+1': The priming effects would increase in the higher quantiles in the reaction time distributions.
+
+2': In terms of the Diffusion model, both
+
+a) allowing the drift rate parameter for words to vary as a function of the priming condition should improve the model compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition, and
+
+b) allowing the non-decision parameter T_er to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one T_er parameter for all word stimuli regardless of priming condition.
+
+Finally, there is the (unlikely) possibility that there are no priming effects at all due to inconsistent stimulus presentation (for example, the frames with the prime are not displayed at all due to timing issues with the participant's device).
+In this case, we would expect to observe no difference in reaction time between the identical and the unrelated control priming condition for word stimuli.
+
+If the online experiment succeeds in not only presenting the primes fast enough to create masked priming effects, but also in manipulating the prime duration precisely enough that this affects reaction times and accuracy, we expect to find smaller effects for shorter prime presentations, analogous to @ziegler2000.
+
+# Method
 

### 2021-03-06 Manuscript.tex
First draft of introduction

@@
 
-However, it
+This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
+If this is not possible, there is no point in moving forward to the second approach and replicating specific paradigms.
+However, it is of course impossible to test every possible device and configuration that participants might use.
+On the other hand, some of the differences in precision and accuracy between setups that can be observed using a photodiode may be too small to have an influence on actual participant performance.
+Therefore, we consider replication of previous lab-based effects a more important test of online paradigms than photodiode measurements.
+Based on the results by Bridges, Pitiot, MacAskill, and Peirce (2020) and A.
+Anwyl-Irvine, Dalmaijer, Hodges, and Evershed (2020), we are satisfied that modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
+In order to establish whether masked priming studies can be successfully run sonline, the next step is now to follow the second approach and implement the masked priming paradigm in one of the online experiment packages tested by Bridges, Pitiot, MacAskill, and Peirce (2020) and A.
+Anwyl-Irvine, Dalmaijer, Hodges, and Evershed (2020).
+After evaluating their results, we decided on Psychopy/PsychoJS (Peirce et al., 2019) as it combines relative ease of use with high precision and accuracy across the great majority of platforms.
 
-In o
+In the present study, we were particularly interested in manipulating the duration of the prime, as this is what determines whether the stimulus is consciously perceived or not (i.e., if it is masked).
+Gomez, Perea, and Ratcliff (2013) performed an experiment in which they presented a prime either for 56 ms preceded by a mask or for 200 ms without a mask.
+They found qualitative differences between masked and unmasked priming, which they explained using the diffusion model (Ratcliff, Gomez, \& McKoon, 2004): For masked priming, the priming effects for identical compared to unrelated primes were the same across all quantiles of the response time distribution.
+In the diffusion model, this corresponds to a shift in a change in the \(T_{er}\) parameter, which corresponds to encoding processed.
+However, for unmasked priming, the identity priming effects were stronger in the upper quantiles of the RT distribution than in the lower quantiles.
+In the diffusion model, this corresponds to a shift in both the \(T_{er}\) parameter and the drift rate, the parameter corresponding to the quality of information.
+This qualitative pattern can help us interpret our results as well.
 
-Gomez, Perea, and Ratcliff (2013) performed an experiment
+Additionally, if the prime duration can be manipulated very precisely, we may able to see effects of small differences in prime durations.
+Ziegler, Ferrand, Jacobs, Rey, and Grainger (2000) found that priming effects were smaller for lower prime durations and interpreted this as evidence for different levels of facilitation (due to phonological overlap) and inhibition (due to visual differences between prime and target).
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+In order to test this, we presented masked primes of different durations in an online experiment and measured response times and accuracy.
+
+If it is possible to present masked primes reliably in an online experiment, our results should be similar to those observed by Gomez, Perea, and Ratcliff (2013) in their masked priming condition for word trials:
+
+1: The priming effects should be approximately the same across quantiles in the reaction time distributions. 2: In terms of the Diffusion model, allowing
+
+\begin{enumerate}
+\def\labelenumi{\alph{enumi})}
+\item
+  the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
+\item
+  allowing the non-decision parameter T\_er to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one T\_er parameter for all word stimuli regardless of priming condition).
+\end{enumerate}
+
+If it is not possible to achieve consistent presentation times in an online experiment, and the primes are effectively presented for longer durations than intended, we should see a pattern that resembles that observed by Gomez et al.~(2013) for unmasked primes:
+
+1': The priming effects would increase in the higher quantiles in the reaction time distributions.
+
+2': In terms of the Diffusion model, both
+
+\begin{enumerate}
+\def\labelenumi{\alph{enumi})}
+\item
+  allowing the drift rate parameter for words to vary as a function of the priming condition should improve the model compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition, and
+\item
+  allowing the non-decision parameter T\_er to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one T\_er parameter for all word stimuli regardless of priming condition.
+\end{enumerate}
+
+Finally, there is the (unlikely) possibility that there are no priming effects at all due to inconsistent stimulus presentation (for example, the frames with the prime are not displayed at all due to timing issues with the participant's device).
+In this case, we would expect to observe no difference in reaction time between the identical and the unrelated control priming condition for word stimuli.
+
+If the online experiment succeeds in not only presenting the primes fast enough to create masked priming effects, but also in manipulating the prime duration precisely enough that this affects reaction times and accuracy, we expect to find smaller effects for shorter prime presentations, analogous to Ziegler, Ferrand, Jacobs, Rey, and Grainger (2000).
+
+\hypertarget{method}{%
+\section{Method}\label{method}}
 
@@
 
+\leavevmode\hypertarget{ref-ratcliff2004}{}%
+Ratcliff, R., Gomez, P., \& McKoon, G.
+(2004).
+A diffusion model account of the lexical decision task.
+\emph{Psychological Review}, \emph{111}(1), 159--182.
+\url{https://doi.org/10.1037/0033-295X.111.1.159}
+
 \leavevmode\hypertarget{ref-reimersPresentationResponseTiming2015}{}%
@@
 
+\leavevmode\hypertarget{ref-ziegler2000}{}%
+Ziegler, J.
+C., Ferrand, L., Jacobs, A.
+M., Rey, A., \& Grainger, J.
+(2000).
+Visual and Phonological Codes in Letter and Word Recognition: Evidence from Incremental Priming.
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{53A}(3), 671--692.
+
 \end{CSLReferences}

### 2021-03-08 Manuscript_AB.Rmd
Update Manuscript AB.Rmd

--- 2021-03-06 Manuscript.Rmd
@@
 Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important paradigms in the study of visual word recognition.
-Priming refers to the observation that the response to a target stimulus (e.g.
-responding that "DOCTOR" is a word in a lexical decision task or pronouncing the same stimulus in a naming task) is faster, more accurate, or both when it was preceded by a related stimulus (e.g.
-"nurse") compared to an unrelated stimulus (e.g.
-"horse").
-In masked priming, the prime stimulus ("nurse" or "horse") is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g.
-"\#\#\#\#\#") which is presented fora much longer duration (typically 500 ms).
+Priming refers to the observation that the response to a target stimulus (e.g., responding that "DOCTOR" is a word in a lexical decision task or pronouncing the same stimulus in a naming task) is faster, more accurate, or both when it was preceded by a related stimulus (e.g., "nurse") compared to an unrelated stimulus (e.g., "horse").
+In masked priming, the prime stimulus ("nurse" or "horse") is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g., "\#\#\#\#\#") which is presented fora much longer duration (typically 500 ms).
 This forward mask ensures that participants are usually unaware of the prime [@forsterRepetitionPrimingFrequency1984].
-The masked priming paradigm has been used in a large number of studies over the last decades [for a review, see e.g.
-@kinoshitaMaskedPrimingState2004; @vandenbusscheMechanismsMaskedPriming2009], but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by @forsterDMDXWindowsDisplay2003.
+The masked priming paradigm has been used in a large number of studies over the last decades [for a review, see e.g., @kinoshitaMaskedPrimingState2004; @vandenbusscheMechanismsMaskedPriming2009], but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by @forsterDMDXWindowsDisplay2003.
 
@@
 Even after the current exceptional situation, online data collection has many advantages, such as easy access to a much more diverse population than would be accessible at the typical university research laboratory, independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment, not time spent commuting, waiting for the experiment to start, etc.
-Researchers in decision making and economics have been using online paradigms for several decades now [e.g.
-@birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010], but cognitive and experimental psychology have been much slower in taking up online paradigms, often due to concerns about the validity of the results.
+Researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010], but cognitive and experimental psychology have been much slower in taking up online paradigms, often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies [@austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times.
@@
 In particular, presenting the prime for too long will counteract the effect of the mask, making the prime consciously visible to the participant.
+
 There have been attempts to address these concerns.
 For example, a Web version of DMDX (webDMDX) was developed which showed promising results in a trial experiment [@witzelTestingViabilityWebDMDX2013].
-
 However, webDMDX was a self-contained Windows executable file that participants had to download and run rather than a "true" online experiment that could be run inside of a browser.
@@
 Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets [@reimersPresentationResponseTiming2015].
-There is now a variety of software packages taking advantage of the new capabilites to present experimental stimuli and collect data, both commercial, e.g.
-Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020] and open-source, e.g.
-jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of Psychopy 3, @peirce2019].
+There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, e.g., Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020] and open-source, e.g., jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of Psychopy 3, @peirce2019].
 
@@
 While the Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (all stimulus data are usually downloaded before the start of the experiment to avoid delays), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
-Experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
+Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
 As @reimersPresentationResponseTiming2015 point out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
@@
 Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with "reasonable" precision, although the lab-based packages were slightly better in this regard.
-
 This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
@@
 Based on the results by @bridges2020 and @anwyl-irvine2020a, we are satisfied that modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
-In order to establish whether masked priming studies can be successfully run sonline, the next step is now to follow the second approach and implement the masked priming paradigm in one of the online experiment packages tested by @bridges2020 and @anwyl-irvine2020a.
+To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm in one of the online experiment packages tested by @bridges2020 and @anwyl-irvine2020a.
 After evaluating their results, we decided on Psychopy/PsychoJS [@peirce2019] as it combines relative ease of use with high precision and accuracy across the great majority of platforms.
 
-In the present study, we were particularly interested in manipulating the duration of the prime, as this is what determines whether the stimulus is consciously perceived or not (i.e., if it is masked).
-@gomezDiffusionModelAccount2013 performed an experiment in which they presented a prime either for 56 ms preceded by a mask or for 200 ms without a mask.
-They found qualitative differences between masked and unmasked priming, which they explained using the diffusion model [@ratcliff2004]: For masked priming, the priming effects for identical compared to unrelated primes were the same across all quantiles of the response time distribution.
-In the diffusion model, this corresponds to a shift in a change in the $T_{er}$ parameter, which corresponds to encoding processed.
+In the present study, we were particularly interested in manipulating the duration of the prime, as this is what determines whether the stimulus is consciously perceived or not.
+Indeed, @gomezDiffusionModelAccount2013 performed an experiment in which they presented a prime either for 56 ms preceded by a mask or for 200 ms without a mask and found qualitative differences between masked and unmasked priming, which they explained using the diffusion model [@ratcliff2004]: For masked priming, the priming effects for identical compared to unrelated primes were the same across all quantiles of the response time distribution.
+In the diffusion model, this corresponds to a shift in a change in the $T_{er}$ parameter, which corresponds to encoding process.
 However, for unmasked priming, the identity priming effects were stronger in the upper quantiles of the RT distribution than in the lower quantiles.
-In the diffusion model, this corresponds to a shift in both the $T_{er}$ parameter and the drift rate, the parameter corresponding to the quality of information.
+In the diffusion model, this corresponds to a shift in both the $T_{er}$ parameter and the drift rate, the parameter corresponding to the quality of the information gathered.
 This qualitative pattern can help us interpret our results as well.
 
-Additionally, if the prime duration can be manipulated very precisely, we may able to see effects of small differences in prime durations.
+Additionally, if the prime duration can be manipulated very precisely, we may be able to see effects of small differences in prime durations.
 @ziegler2000 found that priming effects were smaller for lower prime durations and interpreted this as evidence for different levels of facilitation (due to phonological overlap) and inhibition (due to visual differences between prime and target).
-
 In order to test this, we presented masked primes of different durations in an online experiment and measured response times and accuracy.
@@
 
-1: The priming effects should be approximately the same across quantiles in the reaction time distributions. 2: In terms of the Diffusion model, allowing
+1: The priming effects should be approximately the same across quantiles in the reaction time distributions.
 
-a) the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
+2: In terms of the Diffusion model,
+
+a) allowing the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
 
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

### 2021-03-08 Manuscript.Rmd
Begin method

@@
 
-b) allowing the non-decision parameter T_er to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one T_er parameter for all word stimuli regardless of priming condition).
+b)  allowing the non-decision parameter $T_{er}$ to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one $T_{er}$ parameter for all word stimuli regardless of priming condition).
 
@@
 
-b) allowing the non-decision parameter T_er to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one T_er parameter for all word stimuli regardless of priming condition.
+b)  allowing the non-decision parameter $T_{er}$ to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one $T_{er}$ parameter for all word stimuli regardless of priming condition.
 
@@
 
-# Method
+# Experiment 1
+
+In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33 ms and 50 ms (roughly corresponding to two and three frames at a refresh rate of 60 Hz).
 
@@
 
-## Participants
+## Method
 
-## Material
+```{r load_exp1_data, message=FALSE, echo=FALSE}
+library(tidyverse)
+library(sp)
+library(rworldmap)
 
-## Procedure
+e1_all_participants <- read_csv("participant_data_exp1.csv")
 
-## Data analysis
+e1 <- read_csv(file = "Exp 1 data.csv")
+
+e1_actual_participants <- filter(e1_all_participants, PROLIFIC_PID %in% e1$participant & `What is your age?` != 99)
+
+participant_ages <- e1_actual_participants$`What is your age?`
+
+male_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow
+
+female_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow
+
+other_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
+
+NA_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
+```
+
+### Participants
+
+We collected data from `r e1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants aged from `r participant_ages %>% min` to `r participant_ages %>% max` (mean age: `r participant_ages %>% mean %>% round(2)`) recruited through Prolific [www.prolific.co, -@prolific2021].
+Of the participants, The experiment was only be shown to participants who have indicated that English is their first language in the Prolific screening questions.
+They were paid £1.25 for their participation (corresponding to £5/hour).
+Participants indicated that English was their first language before starting the experiment.
+
+### Material
+
+### Procedure
+
+### Data analysis
 
@@
 
-# Results
+## Results
 
-# Discussion
+## Discussion
+
+# General Discussion
 

### 2021-03-08 Manuscript.tex
Begin method

@@
 \item
-  allowing the non-decision parameter T\_er to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one T\_er parameter for all word stimuli regardless of priming condition).
+  allowing the non-decision parameter \(T_{er}\) to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one \(T_{er}\) parameter for all word stimuli regardless of priming condition).
 \end{enumerate}
@@
 \item
-  allowing the non-decision parameter T\_er to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one T\_er parameter for all word stimuli regardless of priming condition.
+  allowing the non-decision parameter \(T_{er}\) to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one \(T_{er}\) parameter for all word stimuli regardless of priming condition.
 \end{enumerate}
@@
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
+
+In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33 ms and 50 ms (roughly corresponding to two and three frames at a refresh rate of 60 Hz).
 
@@
 
+\hypertarget{method}{%
+\subsection{Method}\label{method}}
+
+\begin{verbatim}
+## Warning: package 'sp' was built under R version 4.0.4
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'rworldmap' was built under R version 4.0.4
+\end{verbatim}
+
 \hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsubsection{Participants}\label{participants}}
+
+We collected data from 78 participants aged from 18 to 99 (mean age: 31.94) recruited through Prolific (www.prolific.co, Prolific (2021)).
+The experiment was only be shown to participants who have indicated that English is their first language in the Prolific screening questions.
+They were paid £1.25 for their participation (corresponding to £5/hour).
+Participants indicated that English was their first language before starting the experiment.
 
 \hypertarget{material}{%
-\subsection{Material}\label{material}}
+\subsubsection{Material}\label{material}}
 
 \hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsubsection{Procedure}\label{procedure}}
 
 \hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+\subsubsection{Data analysis}\label{data-analysis}}
 
@@
 \hypertarget{results}{%
-\section{Results}\label{results}}
+\subsection{Results}\label{results}}
 
 \hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\subsection{Discussion}\label{discussion}}
+
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
 
@@
 
+\leavevmode\hypertarget{ref-prolific2021}{}%
+Prolific. (2021). Prolific \textbar{} online participant recruitment for surveys and market research. Retrieved from \url{https://www.prolific.co/}
+
 \leavevmode\hypertarget{ref-R-base}{}%

### 2021-03-08 Manuscript.tex
Participant information

@@
 Masked priming (Forster \& Davis, 1984) is one of the most important paradigms in the study of visual word recognition.
-Priming refers to the observation that the response to a target stimulus (e.g.~responding that ``DOCTOR'' is a word in a lexical decision task or pronouncing the same stimulus in a naming task) is faster, more accurate, or both when it was preceded by a related stimulus (e.g.~``nurse'') compared to an unrelated stimulus (e.g.~``horse'').
-In masked priming, the prime stimulus (``nurse'' or ``horse'') is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g.~``\#\#\#\#\#'') which is presented fora much longer duration (typically 500 ms).
+Priming refers to the observation that the response to a target stimulus (e.g., responding that ``DOCTOR'' is a word in a lexical decision task or pronouncing the same stimulus in a naming task) is faster, more accurate, or both when it was preceded by a related stimulus (e.g., ``nurse'') compared to an unrelated stimulus (e.g., ``horse'').
+In masked priming, the prime stimulus (``nurse'' or ``horse'') is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g., ``\#\#\#\#\#'') which is presented fora much longer duration (typically 500 ms).
 This forward mask ensures that participants are usually unaware of the prime (Forster \& Davis, 1984).
-The masked priming paradigm has been used in a large number of studies over the last decades (for a review, see e.g.
-Kinoshita \& Lupker, 2004; Van den Bussche, Van den Noortgate, \& Reynvoet, 2009), but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by Forster and Forster (2003).
+The masked priming paradigm has been used in a large number of studies over the last decades (for a review, see e.g., Kinoshita \& Lupker, 2004; Van den Bussche, Van den Noortgate, \& Reynvoet, 2009), but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by Forster and Forster (2003).
 
@@
 Even after the current exceptional situation, online data collection has many advantages, such as easy access to a much more diverse population than would be accessible at the typical university research laboratory, independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment, not time spent commuting, waiting for the experiment to start, etc.
-Researchers in decision making and economics have been using online paradigms for several decades now (e.g.
-Birnbaum \& Birnbaum, 2000; Paolacci, Chandler, \& Ipeirotis, 2010), but cognitive and experimental psychology have been much slower in taking up online paradigms, often due to concerns about the validity of the results.
+Researchers in decision making and economics have been using online paradigms for several decades now (e.g., Birnbaum \& Birnbaum, 2000; Paolacci, Chandler, \& Ipeirotis, 2010), but cognitive and experimental psychology have been much slower in taking up online paradigms, often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies (Aust, Diedenhofen, Ullrich, \& Musch, 2013), but they are exacerbated by the reliance on precise presentation times.
@@
 In particular, presenting the prime for too long will counteract the effect of the mask, making the prime consciously visible to the participant.
+
 There have been attempts to address these concerns.
 For example, a Web version of DMDX (webDMDX) was developed which showed promising results in a trial experiment (Witzel, Cornelius, Witzel, Forster, \& Forster, 2013).
-
 However, webDMDX was a self-contained Windows executable file that participants had to download and run rather than a ``true'' online experiment that could be run inside of a browser.
@@
 Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets (Reimers \& Stewart, 2015).
-There is now a variety of software packages taking advantage of the new capabilites to present experimental stimuli and collect data, both commercial, e.g.~Gorilla (A.
+There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, e.g., Gorilla (A.
 L.
-Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020) or Testable (Rezlescu, Danaila, Miron, \& Amariei, 2020) and open-source, e.g.~jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of Psychopy 3, Peirce et al., 2019).
+Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020) or Testable (Rezlescu, Danaila, Miron, \& Amariei, 2020) and open-source, e.g., jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of Psychopy 3, Peirce et al., 2019).
 
@@
 While the Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (all stimulus data are usually downloaded before the start of the experiment to avoid delays), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
-Experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
+Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
 As Reimers and Stewart (2015) point out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
@@
 Overall, Bridges, Pitiot, MacAskill, and Peirce (2020) found that online packages were capable of presenting visual stimuli with ``reasonable'' precision, although the lab-based packages were slightly better in this regard.
-
 This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
@@
 Anwyl-Irvine, Dalmaijer, Hodges, and Evershed (2020), we are satisfied that modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
-In order to establish whether masked priming studies can be successfully run sonline, the next step is now to follow the second approach and implement the masked priming paradigm in one of the online experiment packages tested by Bridges, Pitiot, MacAskill, and Peirce (2020) and A.
+To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm in one of the online experiment packages tested by Bridges, Pitiot, MacAskill, and Peirce (2020) and A.
 Anwyl-Irvine, Dalmaijer, Hodges, and Evershed (2020).
@@
 
-In the present study, we were particularly interested in manipulating the duration of the prime, as this is what determines whether the stimulus is consciously perceived or not (i.e., if it is masked).
-Gomez, Perea, and Ratcliff (2013) performed an experiment in which they presented a prime either for 56 ms preceded by a mask or for 200 ms without a mask.
-They found qualitative differences between masked and unmasked priming, which they explained using the diffusion model (Ratcliff, Gomez, \& McKoon, 2004): For masked priming, the priming effects for identical compared to unrelated primes were the same across all quantiles of the response time distribution.
-In the diffusion model, this corresponds to a shift in a change in the \(T_{er}\) parameter, which corresponds to encoding processed.
+In the present study, we were particularly interested in manipulating the duration of the prime, as this is what determines whether the stimulus is consciously perceived or not.
+Indeed, Gomez, Perea, and Ratcliff (2013) performed an experiment in which they presented a prime either for 56 ms preceded by a mask or for 200 ms without a mask and found qualitative differences between masked and unmasked priming, which they explained using the diffusion model (Ratcliff, Gomez, \& McKoon, 2004): For masked priming, the priming effects for identical compared to unrelated primes were the same across all quantiles of the response time distribution.
+In the diffusion model, this corresponds to a shift in a change in the \(T_{er}\) parameter, which corresponds to encoding process.
 However, for unmasked priming, the identity priming effects were stronger in the upper quantiles of the RT distribution than in the lower quantiles.
-In the diffusion model, this corresponds to a shift in both the \(T_{er}\) parameter and the drift rate, the parameter corresponding to the quality of information.
+In the diffusion model, this corresponds to a shift in both the \(T_{er}\) parameter and the drift rate, the parameter corresponding to the quality of the information gathered.
 This qualitative pattern can help us interpret our results as well.
 
-Additionally, if the prime duration can be manipulated very precisely, we may able to see effects of small differences in prime durations.
+Additionally, if the prime duration can be manipulated very precisely, we may be able to see effects of small differences in prime durations.
 Ziegler, Ferrand, Jacobs, Rey, and Grainger (2000) found that priming effects were smaller for lower prime durations and interpreted this as evidence for different levels of facilitation (due to phonological overlap) and inhibition (due to visual differences between prime and target).
-
 In order to test this, we presented masked primes of different durations in an online experiment and measured response times and accuracy.
@@
 
-1: The priming effects should be approximately the same across quantiles in the reaction time distributions. 2: In terms of the Diffusion model, allowing
+1: The priming effects should be approximately the same across quantiles in the reaction time distributions.
+
+2: In terms of the Diffusion model,
 
@@
 \item
-  the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
+  allowing the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
 \item
@@
 
-\hypertarget{experiment-1}{%
-\section{Experiment 1}\label{experiment-1}}
+\textless\textless\textless\textless\textless\textless\textless{} HEAD:Manuscript.Rmd
+\# Experiment 1
 
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
 
@@
 
-We collected data from 78 participants aged from 18 to 99 (mean age: 31.94) recruited through Prolific (www.prolific.co, Prolific (2021)).
-The experiment was only be shown to participants who have indicated that English is their first language in the Prolific screening questions.
-They were paid £1.25 for their participation (corresponding to £5/hour).
-Participants indicated that English was their first language before starting the experiment.
+We collected data from 77 participants aged from 18 to 71 (mean age: 31.08) recruited through Prolific (www.prolific.co, 2021).
+Of the participants, 41 identified as male, 37 identified as female, 0 identified as other, and 0 declined to identify their gender.
+The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions.
+Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour).
+All participants were naïve to the purpose of the experiment.
 

### 2021-03-12 Manuscript.Rmd
brms analyses

@@
 
-1: The priming effects should be approximately the same across quantiles in the reaction time distributions. 2: In terms of the Diffusion model, allowing
+1: The priming effects should be approximately the same across quantiles in the reaction time distributions.
 
-a)  the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
+2: In terms of the Diffusion model,
+
+a)  allowing the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
 
@@
 ```{r load_exp1_data, message=FALSE, echo=FALSE}
+library(xfun)
 library(tidyverse)
@@
 
-e1_actual_participants <- filter(e1_all_participants, PROLIFIC_PID %in% e1$participant & `What is your age?` != 99)
+# only consider participants who have actually participated in the whole experiment
+# also don't consider participants whose age is 99 (used for testing)
+# one participant is duplicate. Remove the first occurrence (likely incompatible device)
+
+e1_actual_participants <- filter(e1_all_participants, PROLIFIC_PID %in% e1$participant & `What is your age?` != 99 & `Response ID` != "R_sU4qJ6UCe9jRKs9")
 
@@
 
+# there aren't actually any of these, but will leave the code in just in calse
 other_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
 
-NA_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
+NA_participants_nr <- filter(e1_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow
+
+#coordinates(e1_actual_participants) <- c("Location Longitude","Location Latitude")
+
+# from https://stackoverflow.com/questions/14334970/convert-latitude-and-longitude-coordinates-to-country-name-in-r
+
+# The single argument to this function, points, is a data.frame in which:
+#   - column 1 contains the longitude in degrees
+#   - column 2 contains the latitude in degrees
+coords2country = function(points)
+{  
+  countriesSP <- getMap(resolution='low')
+  #countriesSP <- getMap(resolution='high') #you could use high res map from rworldxtra if you were concerned about detail
+
+  # convert our list of points to a SpatialPoints object
+
+  # pointsSP = SpatialPoints(points, proj4string=CRS(" +proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0"))
+
+  #setting CRS directly to that from rworldmap
+  pointsSP = SpatialPoints(points, proj4string=CRS(proj4string(countriesSP)))
+
+  # use 'over' to get indices of the Polygons object containing each point 
+  indices = over(pointsSP, countriesSP)
+
+  # return the ADMIN names of each country
+  indices$ADMIN  
+  #indices$ISO3 # returns the ISO3 code 
+  #indices$continent   # returns the continent (6 continent model)
+  #indices$REGION   # returns the continent (7 continent model)
+}
+
+participant_coords <- e1_actual_participants %>% select("Location Longitude", "Location Latitude")
+
+e1_actual_participants$country <- coords2country(participant_coords)
+
+e1_participant_countries <- table(e1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
 ```
@@
 We collected data from `r e1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants aged from `r participant_ages %>% min` to `r participant_ages %>% max` (mean age: `r participant_ages %>% mean %>% round(2)`) recruited through Prolific [www.prolific.co, -@prolific2021].
-Of the participants, The experiment was only be shown to participants who have indicated that English is their first language in the Prolific screening questions.
-They were paid £1.25 for their participation (corresponding to £5/hour).
-Participants indicated that English was their first language before starting the experiment.
+Of the participants, `r male_participants_nr` identified as male and `r female_participants_nr` identified as female.
+The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions.
+Based on their IP addresses, `r e1_participant_countries["United Kingdom"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in the UK, `r e1_participant_countries["United States of America"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` were based in the US, `r e1_participant_countries["Canada"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in Canada, and `r e1_participant_countries["Ireland"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in Ireland.
+Two participants could not be localized in this way.
+Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour).
+All participants were naïve to the purpose of the experiment.
 
-### Material
+### Materials
 
 ### Procedure
+
+Participants were able to sign up for the experiment on the Prolific website.
+On signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment [@qualtrics2020].
+After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual PsychoJS experiment was hosted.
+After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.
 
@@
 
+```{=html}
+<script src="https://hypothes.is/embed.js" async></script>
+```
 \newpage

### 2021-03-12 Manuscript.tex
brms analyses

@@
 
-\textless\textless\textless\textless\textless\textless\textless{} HEAD:Manuscript.Rmd
-\# Experiment 1
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
 
@@
 
-\begin{verbatim}
-## Warning: package 'sp' was built under R version 4.0.4
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'rworldmap' was built under R version 4.0.4
-\end{verbatim}
-
 \hypertarget{participants}{%
@@
 
-We collected data from 77 participants aged from 18 to 71 (mean age: 31.08) recruited through Prolific (www.prolific.co, 2021).
-Of the participants, 41 identified as male, 37 identified as female, 0 identified as other, and 0 declined to identify their gender.
+We collected data from 77 participants aged from 18 to 71 (mean age: 31.14) recruited through Prolific (www.prolific.co, 2021).
+Of the participants, 41 identified as male and 36 identified as female.
 The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions.
+Based on their IP addresses, 47 participants were based in the UK, 23 were based in the US, three participants were based in Canada, and two participants were based in Ireland.
+Two participants could not be localized in this way.
 Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour).
@@
 
-\hypertarget{material}{%
-\subsubsection{Material}\label{material}}
+\hypertarget{materials}{%
+\subsubsection{Materials}\label{materials}}
 
@@
 
-We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-package \emph{papaja} {[}Version 0.1.0.9942; Aust and Barth (2020){]} for all our analyses.
+We used R {[}Version 4.0.4; R Core Team (2020){]} and the R-packages \emph{dplyr} {[}Version 1.0.5; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9942; Aust and Barth (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{rworldmap} {[}Version 1.3.6; South (2011){]}, \emph{sp} {[}Version 1.4.5; Pebesma and Bivand (2005){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.1.0; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
+(2019){]} for all our analyses.
 
@@
 
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
 \leavevmode\hypertarget{ref-kinoshitaMaskedPrimingState2004}{}%
 Kinoshita, S., \& Lupker, S. J. (2004). \emph{Masked {Priming}: {The State} of the {Art}}. {Psychology Press}. Retrieved from \url{http://books.google.com?id=VH55AgAAQBAJ}
+
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
@@
 Retrieved from \url{https://papers.ssrn.com/abstract=1626226}
+
+\leavevmode\hypertarget{ref-R-sp}{}%
+Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. Retrieved from \url{https://CRAN.R-project.org/doc/Rnews/}
 
@@
 
+\leavevmode\hypertarget{ref-R-rworldmap}{}%
+South, A.
+(2011).
+Rworldmap: A new r package for mapping global data.
+\emph{The R Journal}, \emph{3}(1), 35--43.
+Retrieved from \url{http://journal.r-project.org/archive/2011-1/RJournal_2011-1_South.pdf}
+
 \leavevmode\hypertarget{ref-vandenbusscheMechanismsMaskedPriming2009}{}%
@@
 \url{https://doi.org/10.1037/a0015329}
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
 

### 2021-03-12 data_analysis_brms.Rmd
brms analyses

---
title: "Pilot data analysis"
output:
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r}
library(lmerTest)
library(tidyverse)
library(cowplot)
library(stargazer)
source("RainCloudPlots.R")

# explore counterbalancing condition
counterbalancing <- fs::dir_ls(path = "./data", glob = "*.csv") %>%
  map_dfr(read_csv, .id = "source", n_max = 1, col_type = cols(
  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer()))

exp1 <- read_csv("Exp 1 data.csv")
exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")

csv_data <- fs::dir_ls(path = "./data", glob = "*.csv") %>%
  map_dfr(read_csv, .id = "source", col_type = cols(
  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
  filter(!is.na(TrialID) & TrialID < 1000) %>%
  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)

csv_data$device <- ifelse(csv_data$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")

# get participants with correct responses

accuracy_by_participant <- csv_data %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n()) %>% left_join(counterbalancing, by = "source")

participants_to_include <- accuracy_by_participant %>% filter(N == 480 & acc > .8)

participants_to_exclude <- accuracy_by_participant %>% filter(N != 480 | acc <= .8)

#participants_to_exclude[,1:3]

participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")

paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows

exclude_list_for_prolific <- str_extract(string = participants_to_exclude$source, pattern = "[a-z0-9]{24}") %>% paste0(collapse = "\n")

# for now, we only have two participants with accuracy > .8 and a full data set

exp2_data_to_include <- csv_data %>% filter(source %in% participants_to_include$source) %>% mutate(StimulusType = StimulusType %>% factor, Condition = Condition %>% factor, PrimeDuration = PrimeDuration %>% factor, rt = rt * 1000)

exp1_data_to_include <- exp1 %>% mutate(StimulusType = StimulusType %>% factor, Condition = Condition %>% factor, PrimeDuration = PrimeDuration %>% factor)

write_csv(exp2_data_to_include, file = "exp2_current_data.csv")

exp1_data_summary_rt <- exp1_data_to_include %>% group_by(StimulusType, Condition, PrimeDuration) %>% summarise(M = mean(rt), SD = sd(rt), N = n())

exp2_data_summary_rt <- exp2_data_to_include %>% group_by(StimulusType, Condition, PrimeDuration) %>% summarise(M = mean(rt), SD = sd(rt), N = n())

# data above 1500 ms excluded

plot_raincloud(exp1_data_to_include %>% filter(corr == 1 & rt < 1500), x_column = "Condition", y_column = "rt", x_label = "Condition", y_label = "RT in ms (correct responses)", main_title = "RT by condition and word type (Experiment 1)") + 
  # put labels on the mean for easier comparison
  stat_summary(fun.data = function(x) {data.frame(label = format(mean(x), digits = 2), y = mean(x))}, 
                                      geom = "text",
                                      #width = 1,
                                      position = position_nudge(x = 0.5, y = 0),
                                      #size = 0.2,
                                      color = "black") +
  facet_grid(cols = vars(PrimeDuration), rows = vars(StimulusType), labeller = label_context)

plot_raincloud(exp2_data_to_include %>% filter(corr == 1 & rt < 1500), x_column = "Condition", y_column = "rt", x_label = "Condition", y_label = "RT in ms (correct responses)", main_title = "RT by condition and word type (Experiment 2)") + 
  # put labels on the mean for easier comparison
  stat_summary(fun.data = function(x) {data.frame(label = format(mean(x), digits = 2), y = mean(x))}, 
                                      geom = "text",
                                      #width = 1,
                                      position = position_nudge(x = 0.5, y = 0),
                                      #size = 0.2,
                                      color = "black") +
  facet_grid(cols = vars(PrimeDuration), rows = vars(StimulusType), labeller = label_context)

```

## LMM for RT (words, correct responses)

```{r lmm1}
contrasts(exp1_data_to_include$Condition) <- c(-1,1)
contrasts(exp1_data_to_include$PrimeDuration) <- c(-1,1)
lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))

summary(lmm_exp1)

```

```{r lmm2}
contrasts(exp2_data_to_include$Condition) <- c(-1,1)
contrasts(exp2_data_to_include$PrimeDuration) <- c(-1,1)

lmm_exp2 <- lmer(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))

summary(lmm_exp2)

```

gLMM for accuracy (Words)

```{r logistic_lmm_exp1}

lmm_acc_exp1 <- glmer(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt < 1500), corr ~ Condition * PrimeDuration + (1|Target), family = binomial(link = "logit"))

summary(lmm_acc_exp1)

```

```{r logistic_lmm_exp2}

lmm_acc_exp2 <- glmer(data = exp2_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt < 1500), corr ~ Condition * PrimeDuration + (1|Target), family = binomial(link = "logit"))

summary(lmm_acc_exp2)

```

BRMS analysis

```{r brms}
library(brms)
#ncores = parallel::detectCores()
# Mean RTs in each condition

prior_exp1 <- c(set_prior("normal(0,100)", class = "b", coef = "Condition1"),
            set_prior("normal(0,100)", class = "b", coef = "Condition1:PrimeDuration1"),
            set_prior("normal(0,100)", class = "b", coef = "PrimeDuration1"))

blmm_exp1 <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500, rt ~
Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
warmup = 1000,
iter = 5000,
chains = 4,
prior = prior_exp1,
family = exgaussian(),
inits = "random",
control = list(adapt_delta = 0.95),
cores = 4, backend = "cmdstanr", threads = threading(2))

#blmm_exp1_full <- update(blmm_exp1,
#                         warmup = 1000,
#                         iter = 5000, 
#                         chains = 4,
#                         prior = prior_exp1,
#                         family = exgaussian(),
#                         inits = "random",
#                         control = list(adapt_delta = 0.95),
#                         cores = 4, 
#                         backend = "cmdstanr", 
#                         threads = threading(2))

save(blmm_exp1, file = "blmm_exp1.RData")
```

### 2021-03-13 data_analysis_brms_old.Rmd
brms experiment 2 RT

--- 2021-03-12 data_analysis_brms.Rmd
@@
 
-blmm_exp1 <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500, rt ~
-Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
+blmm_exp2 <- brm(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), 
+                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                         warmup = 1000,
@@
 
-save(blmm_exp1, file = "blmm_exp1.RData")
+save(blmm_exp2, file = "blmm_exp2.RData")
 ```

### 2021-03-15 Manuscript_AB_MP.Rmd
Add files via upload

--- 2021-03-12 Manuscript.Rmd
@@
 ---
-title             : "Effects of masked prime duration in an online lexical decision task"
-shorttitle        : "Online lexical decision task"
+title             : |
+    | Can we use masked priming in an online setting?
+    | The effect of prime exposure duration in online masked priming lexical decision
+shorttitle        : "Online masked priming"
 
@@
   - name          : "Pablo Gomez"
-    affiliation   : "3,4"
+    affiliation   : "4"
   - name          : "Manuel Perea Lara"
-    affiliation   : "2,3"
+    affiliation   : "2,5"
 
@@
   - id            : "1"
-    institution   : "Bournemouth University"
+    institution   : "Bournemouth University, Bournemouth, UK"
   - id            : "2"
-    institution   : Universitat de Valencia, Valencia, Spain
+    institution   : "Universidad Antonio de Nebrija, Madrid, Spain"
   - id            : "3"
-    institution   : "Nebrija University, Madrid, Spain"
+    institution   : "DePaul University, Chicago, USA"
   - id            : "4"
-    institution   : "California State University San Bernardino, Palm Desert Campus"
+    institution   : "California State University San Bernardino, Palm Desert Campus, USA"
+  - id            : "5"
+    institution   : "Universitat de València, Valencia, Spain"
 
@@
 keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
-wordcount         : "X"
+wordcount         : "XXX"
 
@@
 
-Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important paradigms in the study of visual word recognition.
-Priming refers to the observation that the response to a target stimulus (e.g., responding that "DOCTOR" is a word in a lexical decision task or pronouncing the same stimulus in a naming task) is faster, more accurate, or both when it was preceded by a related stimulus (e.g., "nurse") compared to an unrelated stimulus (e.g., "horse").
-In masked priming, the prime stimulus ("nurse" or "horse") is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g., "\#\#\#\#\#") which is presented fora much longer duration (typically 500 ms).
-This forward mask ensures that participants are usually unaware of the prime [@forsterRepetitionPrimingFrequency1984].
-The masked priming paradigm has been used in a large number of studies over the last decades [for a review, see e.g., @kinoshitaMaskedPrimingState2004; @vandenbusscheMechanismsMaskedPriming2009], but so far, virtually all of these studies have been done in a laboratory setting, often using the DMDX software by @forsterDMDXWindowsDisplay2003.
+Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition[see @forster1998pros; @grainger2008cracking, for reviews].
+Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond (e.g., “is *DOCTOR* a word?”).
+It is measured as the difference in a dependent variable (e.g., response time [RT]) between two conditions (e.g., unrelated: *horse-DOCTOR*; related: *nurse-DOCTOR*).
+In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g., #####) for a much longer duration (typically 500 ms).
+The rationale of the procedure is to make participants unaware of the identity of the masked prime [@forsterRepetitionPrimingFrequency1984; @forster1998pros], thus minimizing the role of participants’ strategies.
+Indeed, masked priming experiments do not show the strategical effects that occur with visible, unmasked primes [e.g., @grossi2006relatedness; @perea2002does].
 
-Given that, as of the time of this writing, researchers in a large part of the world are unable to perform psychology experiments in a laboratory due to the COVID-19 pandemic, with not much clarity about when laboratories will be able to reopen completely, it is an important consideration whether it may be possible to collect masked priming data remotely using online experiments.
-Even after the current exceptional situation, online data collection has many advantages, such as easy access to a much more diverse population than would be accessible at the typical university research laboratory, independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment, not time spent commuting, waiting for the experiment to start, etc.
-Researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010], but cognitive and experimental psychology have been much slower in taking up online paradigms, often due to concerns about the validity of the results.
-Such concerns are not limited to cognitive studies [@austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times.
-In masked priming, it is critical for the onset of the mask, the prime, and the target to occur at the intended times.
-In particular, presenting the prime for too long will counteract the effect of the mask, making the prime consciously visible to the participant.
+The masked priming paradigm has been used in a large number of studies over the last decades.
+For instance, a search of the expression “masked priming” in Google Scholar in March 2021 produced nearly 10,000 hits.
+Virtually all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003).
+The issue we examine in the present paper is whether masked priming experiments can safely be conducted in an online setting.
+Even before the current exceptional situation due to the COVID pandemic, in which many labs around the world have been closed (or with minimal activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
+Indeed, researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010].
+
+However, cognitive psychologists have been much slower in taking up online paradigms [see  @vandeberg2012out; @eerland2013influence; @rodd2016impact; @cai2017accent, for some exceptions], often due to concerns about the validity of the results.
+Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013],
+but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
+Indeed, in the masked priming technique, it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
+In particular, presenting the masked prime for longer than intended would counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest.
 
 There have been attempts to address these concerns.
-For example, a Web version of DMDX (webDMDX) was developed which showed promising results in a trial experiment [@witzelTestingViabilityWebDMDX2013].
-However, webDMDX was a self-contained Windows executable file that participants had to download and run rather than a "true" online experiment that could be run inside of a browser.
-A downside of this is that participants often are (and should be) understandably skeptical about downloading and running files from the Internet.
+For example, a Web version of DMDX (webDMDX) was developed and showed promising results in a trial experiment [@witzelTestingViabilityWebDMDX2013].
+However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a “true” online programming script that could be run inside of a browser.
+A downside of this format is that participants often are (and should be) understandably skeptical about downloading and running executable files from the Internet.
 Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
-As a consequence, the use of webDMDX has been rather limited so far.
+As a consequence, the use of webDMDX has been rather limited so far (\color{red}CITE somebody who has employed it \color{black})
+
 Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web.
@@
 There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, e.g., Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020] and open-source, e.g., jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of Psychopy 3, @peirce2019].
+In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
+Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility to recruit participants for on-line experiments based on various specific characteristics set up by the experimenter not necessarily in the country’s lab (e.g., native French speakers, not older than 30 years old, not currently in college).
 
-Of course, despite the technological advances, there are still concerns about timing and measurement precision.
-While the Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (all stimulus data are usually downloaded before the start of the experiment to avoid delays), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
-Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
+Of course, despite the technological advances, many cognitive psychologists still have concerns about timing and measurement precision.
+While Javascript-based experiments run on the participants’ devices and thereby avoid any lag due to connection issues (e.g., to avoid delays, all stimuli are usually downloaded before the start of the experiment), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
+Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants’ preferences.
 As @reimersPresentationResponseTiming2015 point out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
@@
 The first approach has the advantage that differences in presentation timings can be objectively recorded and evaluated.
-A very thorough recent example of this approach is the "timing mega-study" by @bridges2020, who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
+A very thorough recent example of this approach is the “timing mega-study” by @bridges2020, who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
 The very similar study by @anwyl-irvine2020a compares only online packages and browsers with regard to timing.
-Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with "reasonable" precision, although the lab-based packages were slightly better in this regard.
+Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with “reasonable” precision, although the lab-based packages were slightly better in this regard.
 This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
@@
 On the other hand, some of the differences in precision and accuracy between setups that can be observed using a photodiode may be too small to have an influence on actual participant performance.
-Therefore, we consider replication of previous lab-based effects a more important test of online paradigms than photodiode measurements.
-Based on the results by @bridges2020 and @anwyl-irvine2020a, we are satisfied that modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
+
+Therefore, we consider replication of previous key lab-based effects a more important test of online paradigms than photodiode measurements.
+Based on the results by @bridges2020 and @anwyl-irvine2020a, modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
 To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm in one of the online experiment packages tested by @bridges2020 and @anwyl-irvine2020a.
 After evaluating their results, we decided on Psychopy/PsychoJS [@peirce2019] as it combines relative ease of use with high precision and accuracy across the great majority of platforms.
+\color{red} COMMENT: Was there something better (more precise)?
+It needs better rationale (we want to say it is the best).
+Possible reviewers’ comments:
 
-In the present study, we were particularly interested in manipulating the duration of the prime, as this is what determines whether the stimulus is consciously perceived or not.
-Indeed, @gomezDiffusionModelAccount2013 performed an experiment in which they presented a prime either for 56 ms preceded by a mask or for 200 ms without a mask and found qualitative differences between masked and unmasked priming, which they explained using the diffusion model [@ratcliff2004]: For masked priming, the priming effects for identical compared to unrelated primes were the same across all quantiles of the response time distribution.
-In the diffusion model, this corresponds to a shift in a change in the $T_{er}$ parameter, which corresponds to encoding process.
-However, for unmasked priming, the identity priming effects were stronger in the upper quantiles of the RT distribution than in the lower quantiles.
-In the diffusion model, this corresponds to a shift in both the $T_{er}$ parameter and the drift rate, the parameter corresponding to the quality of the information gathered.
-This qualitative pattern can help us interpret our results as well.
+    -	 Have you checked in different platforms?
+    -	 What does it mean “ease of use”?
+    -	 How precise is it? 
+\color{black}
 
-Additionally, if the prime duration can be manipulated very precisely, we may be able to see effects of small differences in prime durations.
-@ziegler2000 found that priming effects were smaller for lower prime durations and interpreted this as evidence for different levels of facilitation (due to phonological overlap) and inhibition (due to visual differences between prime and target).
-In order to test this, we presented masked primes of different durations in an online experiment and measured response times and accuracy.
+In the present study, we were interested in whether we could replicate, and extend, a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming reflects a savings effect.
+As first suggested by @forster1998pros, for a masked identity prime, “the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner”, whereas for an unrelated prime, “the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur” (p.
+213).
+Thus, according to the savings account, a target word like *DOCTOR* would enjoy an encoding advantage when preceded by an identity prime such as *doctor* than when preceded by an unrelated prime such as *pencil* (i.e., a head-start).
+One implication of such benefit is that the RT distributions of the unrelated and identity pairs should reflect a shift rather than a change in shape.
+Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony.
+Empirical evidence supporting this view has been obtained in several papers not only with skilled adults but also with developing readers [e.g., @gomezDiffusionModelAccount2013; @Gomez_2020; @Taikh_2020; @Yang_2021].
+Moreover, this pattern of results fits very well with the diffusion model [@ratcliff2004].
+This model proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution ($T_{er}$) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached.
+Importantly, in the decision process, the information gathered from the stimulus can vary in noise, depending on its quality, which modifies the rate at which information is accumulated (i.e., the *drift rate*).
+With regards to RTs from masked priming tasks, @gomezDiffusionModelAccount2013 found that the difference between identity and unrelated conditions could be accounted by a change in the $T_{er}$ parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)–note that changes in drift rate would necessarily produce a skewer RT distribution in the slower, unrelated condition.
 
-If it is possible to present masked primes reliably in an online experiment, our results should be similar to those observed by @gomezDiffusionModelAccount2013 in their masked priming condition for word trials:
+Critically, the above pattern is *specific* to masked priming.
+When primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles [i.e., a change in shape rather than a shift in RT distributions; see @gomezDiffusionModelAccount2013].
+Fits from the diffusion model show that this result corresponds to changes in both the $T_{er}$ parameter and the drift rate [see @gomezDiffusionModelAccount2013].
+Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word.
+Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.
+both encoding + information quality in unmasked priming.
 
-1: The priming effects should be approximately the same across quantiles in the reaction time distributions.
+In the present paper, we took advantage of the above marker to examine whether online masked priming studies follow the same pattern as in-lab masked priming studies.
+Specifically, we manipulated prime exposure duration in identity vs.
+unrelated primes: 33.3 vs.
+50 ms in Experiment 1, and 16.6 vs.
+33.3 ms in Experiment 2—note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA).
+The rationale of Experiment 1 is that if the actual exposure duration of the primes is the nominal exposure duration, then we would expect the typical shift between the identity and unrelated response time distributions, which according to the savings hypothesis [@forster1998pros] would be greater for 50-ms than for 33.3-ms exposure duration (i.e., the head-start would be greater for 50-ms identity primes than for 33.3-ms identity primes).
+This outcome would indicate that the on-line masked priming studies reproduce a characteristic signature of laboratory masked priming studies.
+Alternatively, if the actual exposure duration is greater than the nominal one (e.g., approximately 20-ms longer on average) then, the 50 ms primes could be consciously perceived.
+If this were the case, the effect of the prime could affect not only the encoding but also core decision processes (i.e., drift rate parameter), which would be reflected as a stronger priming effect in the upper quantiles (i.e., the two RT distributions would have a different shape).
+In this scenario, one should be very cautious when running online masked priming experiments—at least with the settings currently available.
 
-2: In terms of the Diffusion model,
+To further constraint the research questions, Experiment 2 was parallel to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms).
+Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]—in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
+Thus, if prime exposure durations in online masked priming correspond to the nominal ones, we would expect a sizeable priming effect at the 33.3 but only a residual priming effect at the 16.6 ms prime exposure duration.
+Alternatively, if we obtain a sizeable effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would indicate, again, that we should be wary of using the masked priming technique in online experiments.
+Keep in mind that we are using a software that has good control over the exposure duration (\color{red} CITE).
 
-a)  allowing the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
+ADD at some point:
 
-b)  allowing the non-decision parameter $T_{er}$ to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one $T_{er}$ parameter for all word stimuli regardless of priming condition).
-
-If it is not possible to achieve consistent presentation times in an online experiment, and the primes are effectively presented for longer durations than intended, we should see a pattern that resembles that observed by Gomez et al.
-(2013) for unmasked primes:
-
-1': The priming effects would increase in the higher quantiles in the reaction time distributions.
-
-2': In terms of the Diffusion model, both
-
-a)  allowing the drift rate parameter for words to vary as a function of the priming condition should improve the model compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition, and
-
-b)  allowing the non-decision parameter $T_{er}$ to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one $T_{er}$ parameter for all word stimuli regardless of priming condition.
-
-Finally, there is the (unlikely) possibility that there are no priming effects at all due to inconsistent stimulus presentation (for example, the frames with the prime are not displayed at all due to timing issues with the participant's device).
-In this case, we would expect to observe no difference in reaction time between the identical and the unrelated control priming condition for word stimuli.
-
-If the online experiment succeeds in not only presenting the primes fast enough to create masked priming effects, but also in manipulating the prime duration precisely enough that this affects reaction times and accuracy, we expect to find smaller effects for shorter prime presentations, analogous to @ziegler2000.
+    - Even with no control over many context variables, we obtain the effects (peerj:Parker)
+    - Hypotheses in a figure (as in Gomez & Perea, 2020).
+    - In addition:
+We conducted a simulation study on the impact of suboptimal response time accuracy on statistical power when varying the number of participants, the number of items/condition, and the degree of inaccuracy of the response device.
+\color{black}
 

### 2021-03-27 Manuscript_AB_MP.Rmd
Method section (beginning)

@@
   - id            : "5"
-    institution   : "Universitat de València, Valencia, Spain"
+    institution   : "Universitat de Valencia, Valencia, Spain"
 
@@
 library("papaja")
+library("tidyverse")
+library("brms")
 r_refs("r-references.bib")
@@
 Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition[see @forster1998pros; @grainger2008cracking, for reviews].
-Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond (e.g., “is *DOCTOR* a word?”).
+Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond (e.g., "is *DOCTOR* a word?").
 It is measured as the difference in a dependent variable (e.g., response time [RT]) between two conditions (e.g., unrelated: *horse-DOCTOR*; related: *nurse-DOCTOR*).
-In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g., #####) for a much longer duration (typically 500 ms).
-The rationale of the procedure is to make participants unaware of the identity of the masked prime [@forsterRepetitionPrimingFrequency1984; @forster1998pros], thus minimizing the role of participants’ strategies.
+In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a pattern mask (e.g., \#\#\#\#\#) for a much longer duration (typically 500 ms).
+The rationale of the procedure is to make participants unaware of the identity of the masked prime [@forsterRepetitionPrimingFrequency1984; @forster1998pros], thus minimizing the role of participants' strategies.
 Indeed, masked priming experiments do not show the strategical effects that occur with visible, unmasked primes [e.g., @grossi2006relatedness; @perea2002does].
@@
 The masked priming paradigm has been used in a large number of studies over the last decades.
-For instance, a search of the expression “masked priming” in Google Scholar in March 2021 produced nearly 10,000 hits.
+For instance, a search of the expression "masked priming" in Google Scholar in March 2021 produced nearly 10,000 hits.
 Virtually all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003).
@@
 However, cognitive psychologists have been much slower in taking up online paradigms [see @vandeberg2012out; @eerland2013influence; @rodd2016impact; @cai2017accent, for some exceptions], often due to concerns about the validity of the results.
-Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013],
-but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
+Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
 Indeed, in the masked priming technique, it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
@@
 For example, a Web version of DMDX (webDMDX) was developed and showed promising results in a trial experiment [@witzelTestingViabilityWebDMDX2013].
-However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a “true” online programming script that could be run inside of a browser.
+However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a "true" online programming script that could be run inside of a browser.
 A downside of this format is that participants often are (and should be) understandably skeptical about downloading and running executable files from the Internet.
@@
 In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
-Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility to recruit participants for on-line experiments based on various specific characteristics set up by the experimenter not necessarily in the country’s lab (e.g., native French speakers, not older than 30 years old, not currently in college).
+Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility to recruit participants for on-line experiments based on various specific characteristics set up by the experimenter not necessarily in the country's lab (e.g., native French speakers, not older than 30 years old, not currently in college).
 
 Of course, despite the technological advances, many cognitive psychologists still have concerns about timing and measurement precision.
-While Javascript-based experiments run on the participants’ devices and thereby avoid any lag due to connection issues (e.g., to avoid delays, all stimuli are usually downloaded before the start of the experiment), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
-Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants’ preferences.
+While Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (e.g., to avoid delays, all stimuli are usually downloaded before the start of the experiment), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
+Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
 As @reimersPresentationResponseTiming2015 point out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
@@
 The first approach has the advantage that differences in presentation timings can be objectively recorded and evaluated.
-A very thorough recent example of this approach is the “timing mega-study” by @bridges2020, who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
+A very thorough recent example of this approach is the "timing mega-study" by @bridges2020, who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
 The very similar study by @anwyl-irvine2020a compares only online packages and browsers with regard to timing.
-Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with “reasonable” precision, although the lab-based packages were slightly better in this regard.
+Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with "reasonable" precision, although the lab-based packages were slightly better in this regard.
 This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
@@
 It needs better rationale (we want to say it is the best).
-Possible reviewers’ comments:
+Possible reviewers' comments:
 
@@
     -    How precise is it?
+
 \color{black}
@@
 In the present study, we were interested in whether we could replicate, and extend, a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming reflects a savings effect.
-As first suggested by @forster1998pros, for a masked identity prime, “the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner”, whereas for an unrelated prime, “the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur” (p.
+As first suggested by @forster1998pros, for a masked identity prime, "the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner", whereas for an unrelated prime, "the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur" (p.
 213).
@@
 Importantly, in the decision process, the information gathered from the stimulus can vary in noise, depending on its quality, which modifies the rate at which information is accumulated (i.e., the *drift rate*).
-With regards to RTs from masked priming tasks, @gomezDiffusionModelAccount2013 found that the difference between identity and unrelated conditions could be accounted by a change in the $T_{er}$ parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)–note that changes in drift rate would necessarily produce a skewer RT distribution in the slower, unrelated condition.
+With regards to RTs from masked priming tasks, @gomezDiffusionModelAccount2013 found that the difference between identity and unrelated conditions could be accounted by a change in the $T_{er}$ parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a skewer RT distribution in the slower, unrelated condition.
 
@@
 50 ms in Experiment 1, and 16.6 vs.
-33.3 ms in Experiment 2—note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA).
+33.3 ms in Experiment 2---note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA).
 The rationale of Experiment 1 is that if the actual exposure duration of the primes is the nominal exposure duration, then we would expect the typical shift between the identity and unrelated response time distributions, which according to the savings hypothesis [@forster1998pros] would be greater for 50-ms than for 33.3-ms exposure duration (i.e., the head-start would be greater for 50-ms identity primes than for 33.3-ms identity primes).
@@
 If this were the case, the effect of the prime could affect not only the encoding but also core decision processes (i.e., drift rate parameter), which would be reflected as a stronger priming effect in the upper quantiles (i.e., the two RT distributions would have a different shape).
-In this scenario, one should be very cautious when running online masked priming experiments—at least with the settings currently available.
+In this scenario, one should be very cautious when running online masked priming experiments---at least with the settings currently available.
 
 To further constraint the research questions, Experiment 2 was parallel to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms).
-Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]—in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
+Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
 Thus, if prime exposure durations in online masked priming correspond to the nominal ones, we would expect a sizeable priming effect at the 33.3 but only a residual priming effect at the 16.6 ms prime exposure duration.
@@
     - In addition:
+
 We conducted a simulation study on the impact of suboptimal response time accuracy on statistical power when varying the number of participants, the number of items/condition, and the degree of inaccuracy of the response device.
@@
 All participants were naïve to the purpose of the experiment.
+Participants could use a desktop or laptop computer or a mobile device.
+Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
 
 ### Materials
+
+```{r load_trial_data, message=FALSE, echo=FALSE}
+library(readxl)
+
+trials <- read_xlsx(path = "html/resources/trials_list0.xlsx")
+
+word_statistics <- read_xlsx(path = "online_MaskedPriming_materials_v1.xlsx")
+
+word_statistics$Word_upper <- word_statistics$Word %>% toupper()
+
+trials_word_stats <- left_join(trials, word_statistics, by = c("Target" = "Word_upper"))
+```
+
+We selected 240 six-letter English words from the English Lexicon Project [@balota2007].
+The mean Zipf frequency based on the HAL corpus [@lund1996] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(Freq_HAL %>% log10)) %>% signif(2)` (range: `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(Freq_HAL %>% log10)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(Freq_HAL %>% log10)) %>% signif(2)`).
+The mean OLD20 [@yarkoni2008] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(OLD)) %>% signif(2)`(range:`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(OLD)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(OLD)) %>% signif(2)`).
+We also selected 240 matched, orthographically legal six-letter nonwords.
+For each target, we created an identical prime (e.g.`region`--`REGION`and`fainch`--`FAINCH`) and an unrelated prime consisting of another word from the list (e.g.`launch`--`REGION`and`miluer`--`FAINCH`).
+Appendix A contains a list of the items.
 
@@
 After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual PsychoJS experiment was hosted.
+In the experiment, all stimuli were presented in the center of the screen in black Courier New font on a white background.
+As we do not know the exact dimensions of each participant's screen, all stimulus sizes and positions were defined in Psychopy's "height" units, with the bottom left of a 16:10 aspect ratio screen being represented as (-.8, -.5) and the top right being (.8, .5).
+The height for all text stimuli was 0.1 units.
+Each trial began with a six-character pattern mask (`######`) set to be presented for 500 ms, followed first by the lowercase prime (e.g.
+`region`) set to be presented for either 33 or 50 ms, and then by the uppercase target (e.g.
+`REGION`).
+Participants were instructed to respond to the target stimulus as quickly as possible either by using the keyboard, if their device had one, and pressing the "Z" key if the target was not a valid English word or the "M" key if the target was a valid English word.
+Participants on a device without a keyboard were instructed to respond by touching one of two rectangular touch areas labeled "Z = Non-word" (presented at -0.4, -0.3) and "M = Word" (presented at 0.4, -0.3).
+The touch areas each had a width of 0.4 and a height of 0.2 and were presented in white with a black outline.
+If participants did not respond within two seconds of the target onset, a "Too slow!" feedback message was shown for 500 ms and the trial ended.
+The experimental trials were preceded by 16 practice trials during which participants also received feedback on the accuracy of their responses.
+No feedback apart from the trial timeout feedback was given during the experimental trials.
+Every 120 trials, participants were asked to take a short break before continuing the experiment.
 After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.
@@
 
-We used `r cite_r("r-references.bib")` for all our analyses.
+We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the *brms* package [@R-brms_a; @R-brms_b] in R [@R-base][^1].
+
+[^1]: The full list of software we used for our analyses is as follows: `r cite_r("r-references.bib")`.
 
@@
 
+We
+
+(ref:exp1-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 1 for words and nonwords and by prime duration and priming condition.
+
+```{r exp1_descriptive_rt_table, as.is = TRUE,echo=FALSE}
+#load raw Exp1 data
+exp1 <- read_csv("Exp 1 data.csv")
+exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
+
+exp1$StimulusType <- factor(exp1$StimulusType, levels = c("NW", "WORD"), labels = c("Nonword", "Word"))
+exp1$Condition <- factor(exp1$Condition, levels = c("ID", "UN"), labels = c("Identical", "Unrelated"))
+exp1$PrimeDuration <- factor(exp1$PrimeDuration, levels = c(33, 50), labels = c("33 ms", "50 ms"))
+
+exp1_descriptives_rt <- exp1 %>%
+  filter(rt > 250 & rt < 2000 & corr == 1) %>%
+  group_by(StimulusType, PrimeDuration, Condition) %>%
+  summarize(
+    Mean = mean(rt)
+    , Median = median(rt)
+    , SD = sd(rt)
+    , Min = min(rt)
+    , Max = max(rt)
+  )
+
+exp1_descriptives_corr <- exp1 %>%
+  filter(rt > 250 & rt < 2000) %>%
+  group_by(StimulusType, PrimeDuration, Condition) %>%
+  summarize(
+    Accuracy = mean(corr)
+  )
+
+exp1_descriptives_rt[, -1] <- printnum(exp1_descriptives_rt[, -1], digits = 0)
+
+exp1_descriptives_corr[, -1] <- printnum(exp1_descriptives_corr[, -1], digits = 2)
+
+colnames(exp1_descriptives_rt)[1:2] <- c("Stimulus Type", "Prime Duration")
+
+exp1_descriptives_rt$Accuracy <- exp1_descriptives_corr$Accuracy
+
+apa_table(
+  exp1_descriptives_rt
+  , caption = "(ref:exp1-descriptives-rt-table-caption)"
+  , note = "Trials with reaction times below 250 ms were excluded from the analysis. For the calculation of response times, incorrect responses were also removed."
+  , escape = TRUE
+)  
+```
+We
+
+(ref:exp1-blmm-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 1.
+
+```{r load_exp1_brms_data, echo=FALSE, as.is = TRUE}
+# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
+load("blmm_exp1_rt_new.RData")
+# model name is blmm_exp1_rt
+
+# adapted from a paper by Nalborczyk et al. (2019) -- https://osf.io/eancg/
+
+blmm_exp1_summary <- summary(blmm_exp1_rt)
+
+blmm_exp1_fixed_for_print <- blmm_exp1_summary$fixed
+
+parameter_names <- c(
+    "Intercept",
+    "Condition",
+    "Prime Duration",
+    "Condition:Prime Duration"
+    )
+
+blmm_exp1_fixed_for_print <- blmm_exp1_fixed_for_print %>% tibble(Parameter = parameter_names, .)
+
+colnames(blmm_exp1_fixed_for_print) <- c("mean","SE","lower bound","upper bound","Rhat", "Bulk ESS","Tail ESS")
+
+blmm_exp1_fixed_for_print <- blmm_exp1_fixed_for_print  %>%
+  dplyr::select(-ends_with("ESS"))
+
+write.csv(blmm_exp1_fixed_for_print, file = "Table_1.csv", row.names = FALSE)
+
+apa_table(
+    blmm_exp1_fixed_for_print,
+    placement = "H",
+    align = c("c", "c", "c", "c", "c"),
+    caption = "(ref:exp1-blmm-table-caption)",
+    note = NULL,
+    small = TRUE,
+    digits = 3,
+    escape = FALSE
+    )
+
+```
+
+# Experiment 2
+
+In the second experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 16 ms and 33 ms (roughly corresponding to one and two frames at a refresh rate of 60 Hz).
+
+## Method
+
+## Results
+
+We
+
+(ref:exp2-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 2 for words and nonwords and by prime duration and priming condition.
+
+```{r exp1_descriptive_rt_table, as.is = TRUE,echo=FALSE}
+#load raw Exp1 data
+exp2 <- read_csv("Exp 1 data.csv")
+exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
+
+exp1$StimulusType <- factor(exp1$StimulusType, levels = c("NW", "WORD"), labels = c("Nonword", "Word"))
+exp1$Condition <- factor(exp1$Condition, levels = c("ID", "UN"), labels = c("Identical", "Unrelated"))
+exp1$PrimeDuration <- factor(exp1$PrimeDuration, levels = c(33, 50), labels = c("33 ms", "50 ms"))
+
+exp1_descriptives_rt <- exp1 %>%
+  filter(rt > 250 & rt < 2000 & corr == 1) %>%
+  group_by(StimulusType, PrimeDuration, Condition) %>%
+  summarize(
+    Mean = mean(rt)
+    , Median = median(rt)
+    , SD = sd(rt)
+    , Min = min(rt)
+    , Max = max(rt)
+  )
+
+exp1_descriptives_corr <- exp1 %>%
+  filter(rt > 250 & rt < 2000) %>%
+  group_by(StimulusType, PrimeDuration, Condition) %>%
+  summarize(
+    Accuracy = mean(corr)
+  )
+
+exp1_descriptives_rt[, -1] <- printnum(exp1_descriptives_rt[, -1], digits = 0)
+
+exp1_descriptives_corr[, -1] <- printnum(exp1_descriptives_corr[, -1], digits = 2)
+
+colnames(exp1_descriptives_rt)[1:2] <- c("Stimulus Type", "Prime Duration")
+
+exp1_descriptives_rt$Accuracy <- exp1_descriptives_corr$Accuracy
+
+apa_table(
+  exp1_descriptives_rt
+  , caption = "(ref:exp2-descriptives-rt-table-caption)"
+  , note = "Trials with reaction times below 250 ms were excluded from the analysis. For the calculation of response times, incorrect responses were also removed."
+  , escape = TRUE
+)  
+```
+We
+
+(ref:exp1-blmm-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 1.
+
+```{r load_exp1_brms_data, echo=FALSE, as.is = TRUE}
+# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
+load("blmm_exp1_rt_new.RData")
+# model name is blmm_exp1_rt
+
+# adapted from a paper by Nalborczyk et al. (2019) -- https://osf.io/eancg/
+
+blmm_exp2_summary <- summary(blmm_exp2_rt)
+
+blmm_exp2_fixed_for_print <- blmm_exp2_summary$fixed
+
+parameter_names <- c(
+    "Intercept",
+    "Condition",
+    "Prime Duration",
+    "Condition:Prime Duration"
+    )
+
+blmm_exp1_fixed_for_print <- blmm_exp2_fixed_for_print %>% tibble(Parameter = parameter_names, .)
+
+colnames(blmm_exp2_fixed_for_print) <- c("mean","SE","lower bound","upper bound","Rhat", "Bulk ESS","Tail ESS")
+
+blmm_exp2_fixed_for_print <- blmm_exp2_fixed_for_print  %>%
+  dplyr::select(-ends_with("ESS"))
+
+write.csv(blmm_exp2_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
+
+apa_table(
+    blmm_exp1_fixed_for_print,
+    placement = "H",
+    align = c("c", "c", "c", "c", "c"),
+    caption = "(ref:exp2-blmm-table-caption)",
+    note = NULL,
+    small = TRUE,
+    digits = 3,
+    escape = FALSE
+    )
+
+```
 ## Discussion
+
+$\hat{R}$
 

### 2021-03-27 data_analysis_brms_updated.Rmd
Method section (beginning)

--- 2021-03-12 data_analysis_brms.Rmd
@@
 contrasts(exp1_data_to_include$PrimeDuration) <- c(-1,1)
-lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))
+lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))
 
@@
 
-lmm_exp2 <- lmer(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))
+lmm_exp2 <- lmer(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))
 
@@
 
-blmm_exp1 <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500, rt ~
-Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
+blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
+                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                         warmup = 1000,
@@
 
-#blmm_exp1_full <- update(blmm_exp1,
-#                         warmup = 1000,
-#                         iter = 5000, 
-#                         chains = 4,
-#                         prior = prior_exp1,
-#                         family = exgaussian(),
-#                         inits = "random",
-#                         control = list(adapt_delta = 0.95),
-#                         cores = 4, 
-#                         backend = "cmdstanr", 
-#                         threads = threading(2))
+save(blmm_exp1_rt, file = "blmm_exp1_rt_new.RData")
 
-save(blmm_exp1, file = "blmm_exp1.RData")
+blmm_exp1_acc <- brm(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
+                 formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
+                 warmup = 1000,
+                 iter = 5000,
+                 chains = 4,
+                 prior = prior_exp1,
+                 family = bernoulli(link = "logit"),
+                 inits = "random",
+                 control = list(adapt_delta = 0.95),
+                 cores = 4, backend = "cmdstanr", threads = threading(2))
+
+save(blmm_exp1_acc, file = "blmm_exp1_acc_new.RData")
+
+### Experiment 2
+
+blmm_exp2_rt <- brm(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
+                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
+                        warmup = 1000,
+                        iter = 5000,
+                        chains = 4,
+                        prior = prior_exp1,
+                        family = exgaussian(),
+                        inits = "random",
+                        control = list(adapt_delta = 0.95),
+                        cores = 4, backend = "cmdstanr", threads = threading(2))
+
+save(blmm_exp2_rt, file = "blmm_exp2_rt_new.RData")
+
+blmm_exp2_acc <- brm(data = exp2_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
+                 formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
+                 warmup = 1000,
+                 iter = 5000,
+                 chains = 4,
+                 prior = prior_exp1,
+                 family = bernoulli(link = "logit"),
+                 inits = "random",
+                 control = list(adapt_delta = 0.95),
+                 cores = 4, backend = "cmdstanr", threads = threading(2))
+
+save(blmm_exp2_acc, file = "blmm_exp2_acc_new.RData")
+
 ```

### 2021-04-02 Manuscript_intro_method_results.Rmd
Add method and results

--- 2021-03-27 Manuscript_AB_MP.Rmd
@@
 shorttitle        : "Online masked priming"
-
 author: 
@@
     affiliation   : "2,5"
+affiliation:
 
-affiliation:
   - id            : "1"
@@
     institution   : "Universitat de Valencia, Valencia, Spain"
-
 authornote: |
   Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
   Enter author note here.
@@
 wordcount         : "XXX"
-
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 draft             : no
-
 documentclass     : "apa6"
@@
 bibliography: ["references.bib", "r-references.bib"]
+editor_options: 
+  chunk_output_type: console
 ---
@@
 ```{r setup, include = FALSE}
-library("papaja")
 library("tidyverse")
 library("brms")
+library("bayestestR")
+library("see")
+library("papaja")
+
 r_refs("r-references.bib")
@@
 For instance, a search of the expression "masked priming" in Google Scholar in March 2021 produced nearly 10,000 hits.
-Virtually all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003).
+Virtually all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003.
 The issue we examine in the present paper is whether masked priming experiments can safely be conducted in an online setting.
@@
 To further constraint the research questions, Experiment 2 was parallel to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms).
-Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
+Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
 Thus, if prime exposure durations in online masked priming correspond to the nominal ones, we would expect a sizeable priming effect at the 33.3 but only a residual priming effect at the 16.6 ms prime exposure duration.
@@
 
-We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the two experiments.
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
@@
 
-```{r load_exp1_data, message=FALSE, echo=FALSE}
+```{r load_exp1_data, message=FALSE, echo=FALSE, warning=FALSE}
 library(xfun)
@@
 
-e1_all_participants <- read_csv("participant_data_exp1.csv")
+# Qualtrics survey data
+exp1_all_participants <- read_csv("participant_data_exp1.csv")
 
-e1 <- read_csv(file = "Exp 1 data.csv")
+# PsychoJS trial data
+exp1 <- fs::dir_ls(path = "./data_exp1", glob = "*.csv") %>%
+  map_dfr(read_csv, .id = "source", col_type = cols(
+  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
+  filter(!is.na(TrialID) & TrialID < 1000) %>%
+  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)
+
+exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
 
@@
 
-e1_actual_participants <- filter(e1_all_participants, PROLIFIC_PID %in% e1$participant & `What is your age?` != 99 & `Response ID` != "R_sU4qJ6UCe9jRKs9")
+exp1_actual_participants <- filter(exp1_all_participants, (PROLIFIC_PID %in% exp1$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & (`Response ID` != "R_sU4qJ6UCe9jRKs9"))
 
-participant_ages <- e1_actual_participants$`What is your age?`
+# get participants with more than 80% correct responses
 
-male_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow
+exp1_accuracy_by_participant <- exp1 %>% filter(participant %in% exp1_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())
 
-female_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow
+exp1_participants_to_include <- exp1_accuracy_by_participant %>% filter(N == 480 & acc >= .8)
 
-# there aren't actually any of these, but will leave the code in just in calse
-other_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
+exp1_participants_to_exclude <- exp1_accuracy_by_participant %>% filter(N != 480 | acc < .8)
 
-NA_participants_nr <- filter(e1_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow
+#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
 
-#coordinates(e1_actual_participants) <- c("Location Longitude","Location Latitude")
+exp1_data_to_include <- exp1 %>% filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33 ms", "50 ms")), rt = rt * 1000)
+
+# filter out any of the participants we eliminated from the Qualtrics file as well
+
+exp1_actual_participants <- filter(exp1_actual_participants, (PROLIFIC_PID %in% exp1_data_to_include$participant))
+
+exp1_participant_ages <- exp1_actual_participants$`What is your age?`
+
+exp1_male_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow
+
+exp1_female_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow
+
+# there aren't actually any of these, but will leave the code in just in case
+exp1_other_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
+
+exp1_NA_participants_nr <- filter(exp1_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow
+
+exp1_participant_coords <- exp1_actual_participants %>% select("Location Longitude", "Location Latitude")
+
+#coordinates(exp1_actual_participants) <- c("Location Longitude","Location Latitude")
 
@@
 
-participant_coords <- e1_actual_participants %>% select("Location Longitude", "Location Latitude")
+participant_coords <- exp1_actual_participants %>% select("Location Longitude", "Location Latitude")
 
-e1_actual_participants$country <- coords2country(participant_coords)
+exp1_actual_participants$country <- coords2country(participant_coords)
 
-e1_participant_countries <- table(e1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
+exp1_participant_countries <- table(exp1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
 ```
@@
 
-We collected data from `r e1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants aged from `r participant_ages %>% min` to `r participant_ages %>% max` (mean age: `r participant_ages %>% mean %>% round(2)`) recruited through Prolific [www.prolific.co, -@prolific2021].
-Of the participants, `r male_participants_nr` identified as male and `r female_participants_nr` identified as female.
+Participants were recruited through Prolific [www.prolific.co, -@prolific2021].
+The experiment was accessed by `r exp1_all_participants$PROLIFIC_PID %>% unique %>% length` participants.
+Out of these, `r exp1_accuracy_by_participant %>% nrow` provided experimental data.
+`r exp1_participants_to_exclude %>% filter(N != 480) %>% nrow %>% numbers_to_words() %>% str_to_sentence()` of these participants did not complete the experiment.
+A further `r exp1_participants_to_exclude %>% filter(N == 480 & acc < .8) %>% nrow %>% ifelse(.
+< 11, numbers_to_words(.), .)` were excluded because of low accuracy (less than .8).
+The remaining `r exp1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants were aged from `r exp1_participant_ages %>% min` to `r exp1_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
+Of the participants, `r exp1_male_participants_nr` identified as male and `r exp1_female_participants_nr` identified as female.
 The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions.
-Based on their IP addresses, `r e1_participant_countries["United Kingdom"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in the UK, `r e1_participant_countries["United States of America"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` were based in the US, `r e1_participant_countries["Canada"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in Canada, and `r e1_participant_countries["Ireland"] %>% ifelse(.
+Based on their IP addresses, `r exp1_participant_countries["United Kingdom"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in the UK, `r exp1_participant_countries["United States of America"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` were based in the US, `r exp1_participant_countries["Canada"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in Canada, and `r exp1_participant_countries["Ireland"] %>% ifelse(.
 < 11, numbers_to_words(.), .)` participants were based in Ireland.
@@
 Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
+
+#### Rationale for sample size and stopping rule
+
+@brysbaert2018 recommended that masked priming experiments should have at least 1,600 observations per condition.
+In order to account for potentially smaller effect sizes in an online experiment, we set a target of 3,000 observations per condition (12,000 observations total), which corresponds to a minimum of 50 participants given that there were 240 word stimuli in the experiment (see below).
+Our stopping rule was to keep collecting data until 3,000 valid observations were found.
+This goal was met and exceeded in our initial data collection with a budget of £200.
 
@@
 The mean Zipf frequency based on the HAL corpus [@lund1996] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(Freq_HAL %>% log10)) %>% signif(2)` (range: `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(Freq_HAL %>% log10)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(Freq_HAL %>% log10)) %>% signif(2)`).
-The mean OLD20 [@yarkoni2008] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(OLD)) %>% signif(2)`(range:`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(OLD)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(OLD)) %>% signif(2)`).
+The mean OLD20 [@yarkoni2008] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(OLD)) %>% signif(2)` (range: `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(OLD)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(OLD)) %>% signif(2)`).
 We also selected 240 matched, orthographically legal six-letter nonwords.
-For each target, we created an identical prime (e.g.`region`--`REGION`and`fainch`--`FAINCH`) and an unrelated prime consisting of another word from the list (e.g.`launch`--`REGION`and`miluer`--`FAINCH`).
+For each target, we created an identical prime (e.g.
+`region` --- `REGION` and `fainch` --- `FAINCH`) and an unrelated prime consisting of another word from the list (e.g.
+`launch` --- `REGION` and `miluer` --- `FAINCH`).
 Appendix A contains a list of the items.
@@
 On signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment [@qualtrics2020].
-After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual PsychoJS experiment was hosted.
+After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual lexical decision task was implemented in PsychoJS.
 In the experiment, all stimuli were presented in the center of the screen in black Courier New font on a white background.
@@
 We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the *brms* package [@R-brms_a; @R-brms_b] in R [@R-base][^1].
+We only analyzed trials where the target stimulus was a word.
+For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials).
+For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials).
+As the trials automatically ended after 2000 ms, there were no RTs longer than this.
+For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.
+identical) and prime duration (33 ms vs.
+50 ms) as well as their interaction as the fixed effects.
+For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -1 and unrelated was coded as 1.
+For priming duration, 33 ms was coded as -1 and 50 ms was coded as 1.
+We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items.
+We used the ex-Gaussian distribution to model response times and the Bernoulli distribution (with a logit link) to model response accuracy.
+We used the default priors suggested by *brms* except for the coefficients for the fixed effects, for which we applied weakly informative priors of $\beta \sim N(0,100)$ in order to rule out improbably large effect sizes.
+Each model was fitted using four chains with 5000 iterations each (1000 warmup iterations).
+We consider an effect as credible if the 95% credible interval (CrI) estimated from the posterior distribution does not contain zero.
 
@@
 
-We
+Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table \@ref(tab:exp1-descriptive-rt-table) (although note that we only analyzed the word trials).
 
@@
 
-```{r exp1_descriptive_rt_table, as.is = TRUE,echo=FALSE}
+```{r exp1-descriptive-rt-table, as.is = TRUE,echo=FALSE}
 #load raw Exp1 data
-exp1 <- read_csv("Exp 1 data.csv")
-exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
 
-exp1$StimulusType <- factor(exp1$StimulusType, levels = c("NW", "WORD"), labels = c("Nonword", "Word"))
-exp1$Condition <- factor(exp1$Condition, levels = c("ID", "UN"), labels = c("Identical", "Unrelated"))
-exp1$PrimeDuration <- factor(exp1$PrimeDuration, levels = c(33, 50), labels = c("33 ms", "50 ms"))
+#exp1 <- read_csv("Exp 1 data.csv")
 
-exp1_descriptives_rt <- exp1 %>%
+exp1_descriptives_rt <- exp1_data_to_include %>%
   filter(rt > 250 & rt < 2000 & corr == 1) %>%
@@
 
-exp1_descriptives_corr <- exp1 %>%
+exp1_descriptives_corr <- exp1_data_to_include %>%
   filter(rt > 250 & rt < 2000) %>%
@@
 ```
-We
 
-(ref:exp1-blmm-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 1.
+### Response times
 
-```{r load_exp1_brms_data, echo=FALSE, as.is = TRUE}
+Table \@ref(tab:exp1-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% credible interval (CrI) of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+
+(ref:exp1-blmm-table-caption) Posterior mean, standard error (SE), 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 1.
+
+```{r exp1-blmm-table, echo=FALSE, as.is = TRUE}
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
@@
 
-blmm_exp1_summary <- summary(blmm_exp1_rt)
+blmm_exp1_summary_rt <- summary(blmm_exp1_rt)
 
-blmm_exp1_fixed_for_print <- blmm_exp1_summary$fixed
+blmm_exp1_rt_fixed_for_print <- blmm_exp1_summary_rt$fixed
 
@@
 
-blmm_exp1_fixed_for_print <- blmm_exp1_fixed_for_print %>% tibble(Parameter = parameter_names, .)
-
-colnames(blmm_exp1_fixed_for_print) <- c("mean","SE","lower bound","upper bound","Rhat", "Bulk ESS","Tail ESS")
-
-blmm_exp1_fixed_for_print <- blmm_exp1_fixed_for_print  %>%
+blmm_exp1_rt_fixed_for_print <- blmm_exp1_rt_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
+  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
   dplyr::select(-ends_with("ESS"))
 
-write.csv(blmm_exp1_fixed_for_print, file = "Table_1.csv", row.names = FALSE)
+write.csv(blmm_exp1_rt_fixed_for_print, file = "Table_1.csv", row.names = FALSE)
 
 apa_table(
-    blmm_exp1_fixed_for_print,
+    blmm_exp1_rt_fixed_for_print,
     placement = "H",
@@
 
+The RT model indicates that response times were higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]) and higher in the 33 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
+The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+Figure \@ref(fig:exp1-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
+
+(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the parameters of the response time model in Experiment 1.
+
+```{r exp1-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)"}
+
+del_hdi_exp1_rt = hdi(blmm_exp1_rt, ci = c(0.5, 0.75, 0.89, 0.95))
+
+plot(del_hdi_exp1_rt) + scale_fill_flat() + theme_apa()
+```
+
+### Accuracy
+
+Table \@ref(tab:exp1-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% credible interval (CrI) of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+
+(ref:exp1-blmm-accuracy-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for response accuracy on word trials in Experiment 1.
+
+```{r exp1-acc-blmm-table, echo=FALSE, as.is = TRUE}
+
+load("blmm_exp1_acc_new.RData")
+
+blmm_exp1_summary_acc <- summary(blmm_exp1_acc)
+
+blmm_exp1_acc_fixed_for_print <- blmm_exp1_summary_acc$fixed
+
+parameter_names <- c(
+    "Intercept",
+    "Condition",
+    "Prime Duration",
+    "Condition:Prime Duration"
+    )
+
+blmm_exp1_acc_fixed_for_print <- blmm_exp1_acc_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
+  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
+  dplyr::select(-ends_with("ESS"))
+
+write.csv(blmm_exp1_acc_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
+
+apa_table(
+    blmm_exp1_acc_fixed_for_print,
+    placement = "H",
+    align = c("c", "c", "c", "c", "c"),
+    caption = "(ref:exp1-blmm-accuracy-table-caption)",
+    note = NULL,
+    small = TRUE,
+    digits = 3,
+    escape = FALSE
+    )
+
+```
+
+The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1","u-95% CI"]`]).
+The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp1_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
+The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+
+## Discussion
+
+The results from Experiment 1 show that we were able to replicate masked priming effects using an online experiment.
+The size of the effect is similar to that observed in previous studies.
+We also saw a clear difference between the 33 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices.
+Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.
+In order to further explore this, we perfomed a second experiment in which we set the prime to be displayed for an even shorter duration.
+As described above, a 16 ms prime duration should yield qualitatively different effects from the 33 and 50 ms durations used in Experiment 1.
+If it does not, this casts doubt on the timing accuracy in online experiments.
+
 # Experiment 2
@@
 
+```{r load-exp2-data, as.is = TRUE,echo=FALSE, warning=FALSE}
+#load raw Exp2 data
+
+exp2_all_participants <- read_csv("participant_data_exp2.csv")
+
+exp2 <- fs::dir_ls(path = "./data_exp2", glob = "*.csv") %>%
+  map_dfr(read_csv, .id = "source", col_type = cols(
+  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
+  filter(!is.na(TrialID) & TrialID < 1000) %>%
+  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)
+
+exp2$device <- ifelse(exp2$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
+
+# only consider participants who have actually participated in the whole experiment
+# also don't consider participants whose age is 99 (used for testing)
+# one participant is duplicate. Remove the first occurrence (likely incompatible device)
+
+exp2_actual_participants <- filter(exp2_all_participants, (PROLIFIC_PID %in% exp2$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & !(`Response ID` %in% c("R_2c2dVRNmGvI6CH9", "R_3ELutaT6GNe5mmR", "R_XX7jgUk2NbIi41j", "R_125QKzJfHwoGHaT")))
+
+# get participants with more than 80% correct responses
+
+exp2_accuracy_by_participant <- exp2 %>% filter(participant %in% exp2_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())
+
+exp2_participants_to_include <- exp2_accuracy_by_participant %>% filter(N == 480 & acc >= .8)
+
+exp2_participants_to_exclude <- exp2_accuracy_by_participant %>% filter(N != 480 | acc < .8)
+
+#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
+
+exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16 ms", "33 ms")), rt = rt * 1000)
+
+# filter out any of the participants we eliminated from the Qualtrics file as well
+
+exp2_actual_participants <- filter(exp2_actual_participants, (PROLIFIC_PID %in% exp2_data_to_include$participant))
+
+exp2_participant_ages <- exp2_actual_participants$`What is your age?`
+
+exp2_male_participants_nr <- filter(exp2_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow
+
+exp2_female_participants_nr <- filter(exp2_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow
+
+# there aren't actually any of these, but will leave the code in just in case
+exp2_other_participants_nr <- filter(exp2_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
+
+exp2_NA_participants_nr <- filter(exp2_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow
+
+exp2_participant_coords <- exp2_actual_participants %>% select("Location Longitude", "Location Latitude")
+
+# coords2country function definition in exp1 chunk above
+exp2_actual_participants$country <- coords2country(exp2_participant_coords)
+
+exp2_participant_countries <- table(exp2_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
+
+#paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows
+
+exclude_list_for_prolific <- str_extract(string = exp2_participants_to_exclude$source, pattern = "[a-z0-9]{24}") %>% paste0(collapse = "\n")
+
+```
+
+### Participants
+
+As in Experiment 1, participants were recruited through Prolific [www.prolific.co, -@prolific2021].
+The experiment was accessed by `r exp2_all_participants$PROLIFIC_PID %>% unique %>% length` participants.
+Out of these, `r exp2_accuracy_by_participant %>% nrow` provided experimental data.
+`r exp2_participants_to_exclude %>% filter(N != 480) %>% nrow %>% numbers_to_words() %>% str_to_sentence()` of these participants did not complete the experiment.
+A further `r exp2_participants_to_exclude %>% filter(N == 480 & acc < .8) %>% nrow %>% ifelse(.
+< 11, numbers_to_words(.), .)` were excluded because of low accuracy (less than .8).
+The remaining `r exp2_actual_participants$PROLIFIC_PID %>% unique %>% length` participants were aged from `r exp2_participant_ages %>% min` to `r exp2_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
+Of the participants, `r exp2_male_participants_nr` identified as male, `r exp2_female_participants_nr` identified as female, and `r exp2_other_participants_nr` identified as other.
+The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions.
+Based on their IP addresses, `r exp2_participant_countries["United Kingdom"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in the UK, `r exp2_participant_countries["United States of America"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` were based in the US, `r exp2_participant_countries["Canada"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in Canada, `r exp2_participant_countries["South Africa"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in South Africa, and one participant each was based in Hungary and Ireland.
+`r exp2_actual_participants$country %>% is.na %>% sum %>% numbers_to_words %>% str_to_sentence()` participants could not be localized in this way.
+As in Experiment 1, participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour).
+All participants were naïve to the purpose of the experiment.
+Participants could use a desktop or laptop computer or a mobile device.
+Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
+
+#### Rationale for sample size and stopping rule
+
+As in Experiment 1, our stopping rule was to keep collecting data until 3,000 valid observations were collected. This goal was met and exceeded in our initial data collection with a budget of £200.
+
+### Materials
+
+The materials were identical to those used in Experiment 1.
+
+### Procedure
+
+The procedure was identical to Experiment 1, the only difference being that the primes were set to be displayed for either 16 ms or 33 ms.
+
+### Data analysis
+
+We analyzed the data in the same way as in Experiment 1, again only analyzing trials where the target stimulus was a word.
+For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials).
+For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials).
+For priming duration, 16 ms was coded as -1 and 33 ms was coded as 1.
+Otherwise, the model specifications were identical to those in Experiment 1.
+
 ## Results
-
-We
 
@@
 
-```{r exp1_descriptive_rt_table, as.is = TRUE,echo=FALSE}
-#load raw Exp1 data
-exp2 <- read_csv("Exp 1 data.csv")
-exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
+```{r exp2-descriptive-rt-table, as.is = TRUE,echo=FALSE}
 
-exp1$StimulusType <- factor(exp1$StimulusType, levels = c("NW", "WORD"), labels = c("Nonword", "Word"))
-exp1$Condition <- factor(exp1$Condition, levels = c("ID", "UN"), labels = c("Identical", "Unrelated"))
-exp1$PrimeDuration <- factor(exp1$PrimeDuration, levels = c(33, 50), labels = c("33 ms", "50 ms"))
-
-exp1_descriptives_rt <- exp1 %>%
+exp2_descriptives_rt <- exp2_data_to_include %>%
   filter(rt > 250 & rt < 2000 & corr == 1) %>%
@@
 
-exp1_descriptives_corr <- exp1 %>%
+exp2_descriptives_corr <- exp2_data_to_include %>%
   filter(rt > 250 & rt < 2000) %>%
@@
 
-exp1_descriptives_rt[, -1] <- printnum(exp1_descriptives_rt[, -1], digits = 0)
+exp2_descriptives_rt[, -1] <- printnum(exp2_descriptives_rt[, -1], digits = 0)
 
-exp1_descriptives_corr[, -1] <- printnum(exp1_descriptives_corr[, -1], digits = 2)
+exp2_descriptives_corr[, -1] <- printnum(exp2_descriptives_corr[, -1], digits = 2)
 
-colnames(exp1_descriptives_rt)[1:2] <- c("Stimulus Type", "Prime Duration")
+colnames(exp2_descriptives_rt)[1:2] <- c("Stimulus Type", "Prime Duration")
 
-exp1_descriptives_rt$Accuracy <- exp1_descriptives_corr$Accuracy
+exp2_descriptives_rt$Accuracy <- exp2_descriptives_corr$Accuracy
 
 apa_table(
-  exp1_descriptives_rt
+  exp2_descriptives_rt
   , caption = "(ref:exp2-descriptives-rt-table-caption)"
@@
 ```
-We
 
-(ref:exp1-blmm-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 1.
+(ref:exp2-blmm-rt-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 2.
 
-```{r load_exp1_brms_data, echo=FALSE, as.is = TRUE}
+```{r load_exp2_brms_data, echo=FALSE, as.is = TRUE}
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
-load("blmm_exp1_rt_new.RData")
+load("blmm_exp2_rt_new.RData")
 # model name is blmm_exp1_rt
@@
 
-blmm_exp2_summary <- summary(blmm_exp2_rt)
+blmm_exp2_summary_rt <- summary(blmm_exp2_rt)
 
-blmm_exp2_fixed_for_print <- blmm_exp2_summary$fixed
+blmm_exp2_rt_fixed_for_print <- blmm_exp2_summary_rt$fixed
 
@@
 
-blmm_exp1_fixed_for_print <- blmm_exp2_fixed_for_print %>% tibble(Parameter = parameter_names, .)
-
-colnames(blmm_exp2_fixed_for_print) <- c("mean","SE","lower bound","upper bound","Rhat", "Bulk ESS","Tail ESS")
-
-blmm_exp2_fixed_for_print <- blmm_exp2_fixed_for_print  %>%
+blmm_exp2_rt_fixed_for_print <- blmm_exp2_rt_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
+  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
   dplyr::select(-ends_with("ESS"))
 
-write.csv(blmm_exp2_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
+write.csv(blmm_exp2_rt_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
 
 apa_table(
-    blmm_exp1_fixed_for_print,
+    blmm_exp2_rt_fixed_for_print,
     placement = "H",
     align = c("c", "c", "c", "c", "c"),
-    caption = "(ref:exp2-blmm-table-caption)",
+    caption = "(ref:exp2-blmm-rt-table-caption)",
     note = NULL,
@@
 ```
+
+The model indicates that response times were higher in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]), although across the two prime duration conditions, the effect was much smaller than in Experiment 1.
+Response times were also higher in the 16 ms than in the 33 ms prime duration condition (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]) although, as the interaction effect shows, this was mainly due to an absence of the priming effect in the 16 ms prime duration condition, as opposed to the 33 ms condition, which showed a robust priming effect (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+Figure \@ref(fig:exp2-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
+
+(ref:exp2-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the parameters of the response time model in Experiment 2.
+
+```{r exp2-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp2-brms-rt-plot-caption)"}
+
+del_hdi_exp2_rt = hdi(blmm_exp2_rt, ci = c(0.5, 0.75, 0.89, 0.95))
+# brms (like any other lm-like function) automatically adds a "1" to the parameter name (for the contrast)
+# get rid of the ones (and any other numbers) by using gsub 
+#del_hdi_exp2_rt$Parameter <- del_hdi_exp2_rt$Parameter %>% gsub(pattern = "[[:digit:]]", replacement = "")
+plot(del_hdi_exp2_rt) + scale_fill_flat() + theme_apa()
+```
+
+(ref:exp2-blmm-accuracy-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for response accuracy on word trials in Experiment 2.
+
+```{r exp2_acc_brms_table, echo=FALSE, as.is = TRUE}
+
+load("blmm_exp2_acc_new.RData")
+
+blmm_exp2_summary_acc <- summary(blmm_exp2_acc)
+
+blmm_exp2_acc_fixed_for_print <- blmm_exp2_summary_acc$fixed
+
+parameter_names <- c(
+    "Intercept",
+    "Condition",
+    "Prime Duration",
+    "Condition:Prime Duration"
+    )
+
+blmm_exp2_acc_fixed_for_print <- blmm_exp2_acc_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
+  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
+  dplyr::select(-ends_with("ESS"))
+
+write.csv(blmm_exp2_acc_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
+
+apa_table(
+    blmm_exp2_acc_fixed_for_print,
+    placement = "H",
+    align = c("c", "c", "c", "c", "c"),
+    caption = "(ref:exp2-blmm-accuracy-table-caption)",
+    note = NULL,
+    small = TRUE,
+    digits = 3,
+    escape = FALSE
+    )
+
+```
+
+The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1","u-95% CI"]`]).
+The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16 ms prime duration condition than in the 33 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp2_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
+The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33 ms condition, and reversed in the 16 ms condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]), although the effect in the 16 ms condition was very weak.
+
 ## Discussion
 
-$\hat{R}$
+In Experiment 2, we observed the pattern we expected from previous research: a robust priming effect in response time and accuracy in the 33 ms condition, but a very weak effect in the 16 ms condition.
+This suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
 
@@
 
-```{=html}
-<script src="https://hypothes.is/embed.js" async></script>
-```
+In this study, we
+
 \newpage

### 2021-04-02 data_analysis_brms_updated.Rmd
Add method and results

@@
 contrasts(exp1_data_to_include$PrimeDuration) <- c(-1,1)
-lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))
+lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))
+
+lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (Condition*PrimeDuration|source) + (Condition*PrimeDuration|Target))
 
@@
 
-lmm_acc_exp1 <- glmer(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt < 1500), corr ~ Condition * PrimeDuration + (1|Target), family = binomial(link = "logit"))
+lmm_acc_exp1 <- glmer(data = exp1_data_to_include %>% filter(rt > 250 & corr != -1 & StimulusType == "Word" & rt < 2000), corr ~ Condition * PrimeDuration + (1|Target), family = binomial(link = "logit"))
 
@@
 
-blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
+blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
+                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
+                        warmup = 1000,
+                        iter = 5000,
+                        chains = 4,
+                        prior = prior_exp1,
+                        family = exgaussian(),
+                        inits = "random",
+                        control = list(adapt_delta = 0.95),
+                        cores = 4, backend = "cmdstanr", threads = threading(2))
+
+blmm_exp1_rt_string <- make_stancode(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
                         rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
@@
 save(blmm_exp1_acc, file = "blmm_exp1_acc_new.RData")
+
+blmm_exp1_acc_string <- make_stancode(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
+                 formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
+                 warmup = 1000,
+                 iter = 5000,
+                 chains = 4,
+                 prior = prior_exp1,
+                 family = bernoulli(link = "logit"),
+                 inits = "random",
+                 control = list(adapt_delta = 0.95),
+                 cores = 4, backend = "cmdstanr", threads = threading(2))
 

### 2021-04-02 data_analysis_brms_distributional.R
Add new R script to try distributional analyses, remove old files

@@ -1,0 +1,211 @@
+library(lme4)
+library(tidyverse)
+library(brms)
+
+library(xfun)
+
+
+
+# Load Exp 1 data
+##################
+
+# Qualtrics survey data
+exp1_all_participants <- read_csv("participant_data_exp1.csv")
+
+# PsychoJS trial data
+exp1 <- fs::dir_ls(path = "./data_exp1", glob = "*.csv") %>%
+  map_dfr(read_csv, .id = "source", col_type = cols(
+    .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
+  filter(!is.na(TrialID) & TrialID < 1000) %>%
+  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)
+
+exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
+
+# only consider participants who have actually participated in the whole experiment
+# also don't consider participants whose age is 99 (used for testing)
+# one participant is duplicate. Remove the first occurrence (likely incompatible device)
+
+exp1_actual_participants <- filter(exp1_all_participants, (PROLIFIC_PID %in% exp1$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & (`Response ID` != "R_sU4qJ6UCe9jRKs9"))
+
+# get participants with more than 80% correct responses
+
+exp1_accuracy_by_participant <- exp1 %>% filter(participant %in% exp1_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())
+
+exp1_participants_to_include <- exp1_accuracy_by_participant %>% filter(N == 480 & acc >= .8)   
+
+exp1_participants_to_exclude <- exp1_accuracy_by_participant %>% filter(N != 480 | acc < .8)   
+
+#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}") 
+
[…]

### 2021-04-02 data_analysis_brms_distributional.R
Distributional analysis

@@ -113,8 +113,15 @@ library(brms)
 #ncores = parallel::detectCores()
 # Mean RTs in each condition
 
+
+prior_exp1 <- c(set_prior("normal(0,2500)", class = "b", coef = "", dpar = ""),
+                set_prior("normal(0,100)", class = "b", coef = "Condition1", dpar = ""),
+                set_prior("normal(0,100)", class = "b", coef = "Condition1:PrimeDuration1"),
+                set_prior("normal(0,100)", class = "b", coef = "PrimeDuration1"))
+
+
 blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
-                    bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition),
+                    bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration),
                     warmup = 10,
                     iter = 50,
                     chains = 4,
@@ -124,10 +131,8 @@ blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & Stim
                     control = list(adapt_delta = 0.95),
                     cores = 4, backend = "cmdstanr", threads = threading(2))
 
+save(blmm_exp1_rt_dist, file = "blmm_exp1_rt_dist.RData")
 
-prior_exp1 <- c(set_prior("normal(0,100)", class = "b", coef = "Condition1"),
-                set_prior("normal(0,100)", class = "b", coef = "Condition1:PrimeDuration1"),
-                set_prior("normal(0,100)", class = "b", coef = "PrimeDuration1"))
 
 blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
                     rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),

### 2021-04-20 EDA_OnlineMaskedPriming.Rmd
Create EDA_OnlineMaskedPriming.Rmd

---
title: "EDA"
author: "Ana Baciero"
date: "20/4/2021"
output: pdf_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(ggplot2)
library(papaja)

```

# Data sets:

## Experiment 1

```{r Experiment 1, include=FALSE}

# Qualtrics survey data
exp1_all_participants <- read_csv("participant_data_exp1.csv")

# PsychoJS trial data
exp1 <- fs::dir_ls(path = "./data_exp1", glob = "*.csv") %>%
  map_dfr(read_csv, .id = "source", col_type = cols(
    .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
  filter(!is.na(TrialID) & TrialID < 1000) %>%
  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)

exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")

# only consider participants who have actually participated in the whole experiment
# also don't consider participants whose age is 99 (used for testing)
# one participant is duplicate. Remove the first occurrence (likely incompatible device)

exp1_actual_participants <- filter(exp1_all_participants, (PROLIFIC_PID %in% exp1$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & (`Response ID` != "R_sU4qJ6UCe9jRKs9"))

# get participants with more than 80% correct responses

exp1_accuracy_by_participant <- exp1 %>% filter(participant %in% exp1_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())

exp1_participants_to_include <- exp1_accuracy_by_participant %>% filter(N == 480 & acc >= .8)

exp1_participants_to_exclude <- exp1_accuracy_by_participant %>% filter(N != 480 | acc < .8)

#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")

exp1_data_to_include <- exp1 %>% filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33 ms", "50 ms")), rt = rt * 1000)

```

```{r E1 Head, tidy=TRUE}

E1<- exp1_data_to_include%>%
  select(participant, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target, corr, rt)%>%
  mutate(participant=factor(participant),
         TrialID = factor(TrialID))

head(E1)
```

## Experiment 2

```{r Experiment 2, include=FALSE}

exp2_all_participants <- read_csv("participant_data_exp2.csv")

exp2 <- fs::dir_ls(path = "./data_exp2", glob = "*.csv") %>%
  map_dfr(read_csv, .id = "source", col_type = cols(
    .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
  filter(!is.na(TrialID) & TrialID < 1000) %>%
  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)

exp2$device <- ifelse(exp2$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")

# only consider participants who have actually participated in the whole experiment
# also don't consider participants whose age is 99 (used for testing)
# one participant is duplicate. Remove the first occurrence (likely incompatible device)

exp2_actual_participants <- filter(exp2_all_participants, (PROLIFIC_PID %in% exp2$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & !(`Response ID` %in% c("R_2c2dVRNmGvI6CH9", "R_3ELutaT6GNe5mmR", "R_XX7jgUk2NbIi41j", "R_125QKzJfHwoGHaT")))

# get participants with more than 80% correct responses

exp2_accuracy_by_participant <- exp2 %>% filter(participant %in% exp2_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())

exp2_participants_to_include <- exp2_accuracy_by_participant %>% filter(N == 480 & acc >= .8)

exp2_participants_to_exclude <- exp2_accuracy_by_participant %>% filter(N != 480 | acc < .8)

#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")

exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16 ms", "33 ms")), rt = rt * 1000)
```

```{r E2 Head, tidy=TRUE}

E2<- exp2_data_to_include%>%
  select(participant, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target, corr, rt)%>%
  mutate(participant=factor(participant),
         TrialID = factor(TrialID))

head(E2)

```

\newpage

# Delta Plots

```{r Deltas E1, message=FALSE, warning=FALSE}

quibble <- function(x, q = seq(.1, .9, .2)) {
  tibble(x = quantile(x, q), q = q)
}

E1 %>%
  group_by(participant, StimulusType, Condition, PrimeDuration,corr) %>%
  summarise(RT = list(quibble(rt, seq(.1, .9, .2)))) %>% 
  tidyr::unnest(RT) -> data.E1.quantiles

data.E1.quantiles %>%
  filter(corr==1) %>%
  select(-corr) %>%
  group_by(StimulusType,PrimeDuration,Condition,q) %>%
  summarize(RT=mean(x))%>%
  ungroup()-> vincentiles.E1

#Priming Effect (related vs. unrelated):

vincentiles.E1 %>%
  arrange(desc(Condition))%>%
  group_by(StimulusType,PrimeDuration,q) %>%
  summarize(MRT=mean(RT),
            Delta=diff(rev(RT)))%>%
  ungroup()%>%
ggplot(aes(y=Delta, x=MRT)) +
  geom_line()+
  geom_point()+
  ylim(-60, +60)+
  xlim(450, 950)+
  xlab("Mean RT per quantile")+
  ylab("Priming effect (delta)")+
  ggtitle("Experiment 1")+
  facet_wrap(~StimulusType + PrimeDuration)+
  theme_minimal()-> DeltaE1.PrimingEffect

DeltaE1.PrimingEffect

#Prime Duration Effect (33ms vs 50 ms):

vincentiles.E1 %>%
  group_by(StimulusType,Condition,q) %>%
 summarize(MRT=mean(RT),
            Delta=diff(rev(RT)))%>%
ggplot(aes(y=Delta, x=MRT)) +
  geom_line()+
  geom_point()+
  ylim(-60, +60)+
  xlim(450, 950)+
  xlab("Mean RT per quantile")+
  ylab("Prime duration effect (delta)")+
  ggtitle("Experiment 1")+
  facet_wrap(~StimulusType + Condition)+
  theme_minimal()-> DeltaE1.PrimeDurationEffect

DeltaE1.PrimeDurationEffect

```

```{r Deltas E2, message=FALSE, warning=FALSE}

E2 %>%
  group_by(participant, StimulusType, Condition, PrimeDuration,corr) %>%
  summarise(RT = list(quibble(rt, seq(.1, .9, .2)))) %>% 
  tidyr::unnest(RT) -> data.E2.quantiles

data.E2.quantiles %>%
  filter(corr==1) %>%
  select(-corr) %>%
  group_by(StimulusType,PrimeDuration,Condition,q) %>%
  summarize(RT=mean(x))%>%
  ungroup()-> vincentiles.E2

#Priming Effect (related vs. unrelated):

vincentiles.E2 %>%
  arrange(desc(Condition))%>%
  group_by(StimulusType,PrimeDuration,q) %>%
  summarize(MRT=mean(RT),
            Delta=diff(rev(RT)))%>%
  ungroup()%>%
ggplot(aes(y=Delta, x=MRT)) +
  geom_line()+
  geom_point()+
  ylim(-60, +60)+
  xlim(450, 950)+
  xlab("Mean RT per quantile")+
  ylab("Priming effect (delta)")+
  ggtitle("Experiment 2")+
  facet_wrap(~StimulusType + PrimeDuration)+
  theme_minimal() -> DeltaE2.PrimingEffect

DeltaE2.PrimingEffect

#Prime Duration Effect (33ms vs 50 ms):

vincentiles.E2 %>%
  group_by(StimulusType,Condition,q) %>%
 summarize(MRT=mean(RT),
            Delta=diff(rev(RT)))%>%
ggplot(aes(y=Delta, x=MRT)) +
  geom_line()+
  geom_point()+
  ylim(-60, +60)+
  xlim(450, 950)+
  xlab("Mean RT per quantile")+
  ylab("Prime duration effect (delta)")+
  ggtitle("Experiment 2")+
  facet_wrap(~StimulusType + Condition)+
  theme_minimal() -> DeltaE2.PrimeDurationEffect

DeltaE2.PrimeDurationEffect

```

\newpage

# CAF

```{r Experiment 1 CAF, message=FALSE, warning=FALSE}

E1 %>%
  group_by(participant, StimulusType, Condition, PrimeDuration) %>%
  mutate(Quantile = cut_number(rt, n = 10, labels = c(1,1,2,2,3,3,4,4,5,5))) %>%
  ungroup() %>%
  group_by(participant, StimulusType, Condition, PrimeDuration, Quantile) %>%
  summarize(Macc=mean(corr),
            Mrt=mean(rt)) %>%
  ungroup() -> data.caf.E1

data.caf.E1 %>%
  filter(StimulusType=="Word")%>%
  group_by(Condition, PrimeDuration, Quantile) %>%
    summarize(Macc2=mean(Macc),
            Mrt2=mean(Mrt)) %>%
  ggplot(aes(x=Mrt2, y=Macc2, )) +
geom_line(alpha=.3, size=1.2) +
  geom_point()+
  ylim(0.5, 1)+
  xlim(450, 1000)+
  facet_wrap(~PrimeDuration+Condition)+
  ggtitle("Accuracy as a function of RT in Experiment 1. Word data")+
  theme_minimal()+
  xlab("RT")+
  ylab("Accuracy") -> CAF.E1.W

CAF.E1.W

data.caf.E1 %>%
  filter(StimulusType=="Nonword")%>%
  group_by(Condition, PrimeDuration, Quantile) %>%
    summarize(Macc2=mean(Macc),
            Mrt2=mean(Mrt)) %>%
  ggplot(aes(x=Mrt2, y=Macc2, )) +
  geom_line(alpha=.3, size=1.2) +
  geom_point()+
  ylim(0.5, 1)+
  xlim(450, 1000)+
  facet_wrap(~PrimeDuration+Condition)+
  ggtitle("Accuracy as a function of RT in Experiment 1. Nonword data")+
  theme_minimal()+
  xlab("RT")+
  ylab("Accuracy") -> CAF.E1.NW

CAF.E1.NW

```

```{r Experiment 2 CAF, message=FALSE, warning=FALSE}

E2 %>%
  group_by(participant, StimulusType, Condition, PrimeDuration) %>%
  mutate(Quantile = cut_number(rt, n = 10, labels = c(1,1,2,2,3,3,4,4,5,5))) %>%
  ungroup() %>%
  group_by(participant, StimulusType, Condition, PrimeDuration, Quantile) %>%
  summarize(Macc=mean(corr),
            Mrt=mean(rt)) %>%
  ungroup() -> data.caf.E2

data.caf.E2 %>%
  filter(StimulusType=="Word")%>%
  group_by(Condition, PrimeDuration, Quantile) %>%
    summarize(Macc2=mean(Macc),
            Mrt2=mean(Mrt)) %>%
  ggplot(aes(x=Mrt2, y=Macc2, )) +
geom_line(alpha=.3, size=1.2) +
  geom_point()+
  ylim(0.5, 1)+
  xlim(450, 1000)+
  facet_wrap(~PrimeDuration+Condition)+
  ggtitle("Accuracy as a function of RT in Experiment 2. Word data")+
  theme_minimal()+
  xlab("RT")+
  ylab("Accuracy") -> CAF.E2.W

CAF.E2.W

data.caf.E2 %>%
  filter(StimulusType=="Nonword")%>%
  group_by(Condition, PrimeDuration, Quantile) %>%
    summarize(Macc2=mean(Macc),
            Mrt2=mean(Mrt)) %>%
  ggplot(aes(x=Mrt2, y=Macc2, )) +
  geom_line(alpha=.3, size=1.2) +
  geom_point()+
  ylim(0.5, 1)+
  xlim(450, 1000)+
  facet_wrap(~PrimeDuration+Condition)+
  ggtitle("Accuracy as a function of RT in Experiment 2. Nonword data")+
  theme_minimal()+
  xlab("RT")+
  ylab("Accuracy") -> CAF.E2.NW

CAF.E2.NW

```

### 2021-04-20 data_analysis_brms_distributional.R
updating data file locations

@@ -117,21 +117,30 @@ library(brms)
 prior_exp1 <- c(set_prior("normal(0,2500)", class = "b", coef = "", dpar = ""),
                 set_prior("normal(0,100)", class = "b", coef = "Condition1", dpar = ""),
                 set_prior("normal(0,100)", class = "b", coef = "Condition1:PrimeDuration1"),
+                set_prior("normal(0,100)", class = "b", coef = "PrimeDuration1"),
+                set_prior("normal(0,100)", class = "b", coef = "Condition1", dpar = ""),
+                set_prior("normal(0,100)", class = "b", coef = "Condition1:PrimeDuration1"),
                 set_prior("normal(0,100)", class = "b", coef = "PrimeDuration1"))
 
+prior_exp1 <- c(set_prior("normal(0,1000)", class = "b"),
+                set_prior("normal(0,2500)", class = "Intercept"),
+                set_prior("normal(0,1000)", class = "b", dpar = "beta"),
+                set_prior("normal(0,2500)", class = "Intercept", dpar = "beta"))
+
+#formula_exp1 <- bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target))
 
 blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
-                    bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration),
-                    warmup = 1000,
-                    iter = 5000,
+                    bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target)),
+                    warmup = 200,
+                    iter = 1000,
                     chains = 4,
-                    #prior = prior_exp1,
+                    prior = prior_exp1,
                     family = exgaussian(),
                     inits = "random",
-                    control = list(adapt_delta = 0.95),
[…]

### 2021-04-23 EDA_OnlineMaskedPriming.Rmd
add > 250 ms filter to EDA Rmd

@@
 
-exp1_data_to_include <- exp1 %>% filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33 ms", "50 ms")), rt = rt * 1000)
-
+exp1_data_to_include <- exp1 %>% 
+  filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% 
+  mutate(StimulusType = StimulusType %>% 
+           factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% 
+           factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33 ms", "50 ms")), rt = rt * 1000) %>% 
+  filter(rt > 250 & rt < 2000)
 ```
@@
 
-exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16 ms", "33 ms")), rt = rt * 1000)
+exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16 ms", "33 ms")), rt = rt * 1000) %>% filter(rt > 250 & rt < 2000)
+
 ```

### 2021-04-23 data_analysis_brms_distributional.R

@@ -131,8 +131,8 @@ prior_exp1 <- c(set_prior("normal(0,1000)", class = "b"),
 
 blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
                     bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target)),
-                    warmup = 200,
-                    iter = 1000,
+                    warmup = 1000,
+                    iter = 5000,
                     chains = 4,
                     prior = prior_exp1,
                     family = exgaussian(),
@@ -140,7 +140,7 @@ blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & Stim
                     control = list(adapt_delta = 0.8),
                     cores = 4, backend = "cmdstanr", threads = threading(2))
 
-save(blmm_exp1_rt_dist, file = "blmm_exp1_rt_dist_full_ranef.RData")
+save(blmm_exp1_rt_dist, file = "blmm_exp1_rt_dist_full_ranef_5000.RData")
 
 
 blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
@@ -213,6 +213,31 @@ blmm_exp2_rt <- brm(data = exp2_data_to_include %>% filter(corr == 1 & StimulusT
 
 save(blmm_exp2_rt, file = "blmm_exp2_rt_new.RData")
 
+blmm_exp2_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
+                         bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target)),
+                         warmup = 200,
+                         iter = 1000,
+                         chains = 4,
+                         prior = prior_exp1,
+                         family = exgaussian(),
+                         inits = "random",
+                         control = list(adapt_delta = 0.8),
[…]

### 2021-04-27 data_analysis_brms_distributional.R
Clean up data files, include new random effects models for beta

@@ -131,8 +131,8 @@ prior_exp1 <- c(set_prior("normal(0,1000)", class = "b"),
 
 blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
                     bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target)),
-                    warmup = 1000,
-                    iter = 5000,
+                    warmup = 200,
+                    iter = 1000,
                     chains = 4,
                     prior = prior_exp1,
                     family = exgaussian(),
@@ -140,7 +140,7 @@ blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & Stim
                     control = list(adapt_delta = 0.8),
                     cores = 4, backend = "cmdstanr", threads = threading(2))
 
-save(blmm_exp1_rt_dist, file = "blmm_exp1_rt_dist_full_ranef_5000.RData")
+save(blmm_exp1_rt_dist, file = "blmm_exp1_rt_dist_full_ranef.RData")
 
 
 blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
@@ -213,31 +213,6 @@ blmm_exp2_rt <- brm(data = exp2_data_to_include %>% filter(corr == 1 & StimulusT
 
 save(blmm_exp2_rt, file = "blmm_exp2_rt_new.RData")
 
-blmm_exp2_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
-                         bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target)),
-                         warmup = 200,
-                         iter = 1000,
-                         chains = 4,
-                         prior = prior_exp1,
-                         family = exgaussian(),
-                         inits = "random",
-                         control = list(adapt_delta = 0.8),
[…]

### 2021-04-27 data_analysis_brms_distributional.R
Update manuscripts

@@ -131,8 +131,8 @@ prior_exp1 <- c(set_prior("normal(0,1000)", class = "b"),
 
 blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
                     bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target)),
-                    warmup = 200,
-                    iter = 1000,
+                    warmup = 1000,
+                    iter = 5000,
                     chains = 4,
                     prior = prior_exp1,
                     family = exgaussian(),
@@ -140,7 +140,7 @@ blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & Stim
                     control = list(adapt_delta = 0.8),
                     cores = 4, backend = "cmdstanr", threads = threading(2))
 
-save(blmm_exp1_rt_dist, file = "blmm_exp1_rt_dist_full_ranef.RData")
+save(blmm_exp1_rt_dist, file = "blmm_exp1_rt_dist_full_ranef_5000.RData")
 
 
 blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
@@ -213,6 +213,31 @@ blmm_exp2_rt <- brm(data = exp2_data_to_include %>% filter(corr == 1 & StimulusT
 
 save(blmm_exp2_rt, file = "blmm_exp2_rt_new.RData")
 
+blmm_exp2_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
+                         bf(rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target), beta ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target)),
+                         warmup = 200,
+                         iter = 1000,
+                         chains = 4,
+                         prior = prior_exp1,
+                         family = exgaussian(),
+                         inits = "random",
+                         control = list(adapt_delta = 0.8),
[…]

### 2021-04-27 Lab meeting presentation April 2021.Rmd
Start presentation

--- 2020-11-26 Pilot_data_presentation.Rmd
@@
 ---
-title: "Online masked priming"
-subtitle: "Can we get the same quality data as in a laboratory study?"
-author: "Bernhard Angele, Pablo Gomez, & Manuel Perea"
-institute: "Bournemouth/Valencia/San Bernardino/The Internet"
+title: "Can we use masked priming in an online setting?"
+
+subtitle: "The effect of prime exposure duration in online masked priming lexical decision"
+author: "Bernhard Angele, Ana Baciero, Pablo Gomez, & Manuel Perea"
+institute: "Bournemouth University, Universidad Nebrija, DePaul University, California State University San Bernardino, Universitat de Valencia"
 date: "`r Sys.Date()`"
@@
   xaringan::moon_reader:
+    css: [default, metropolis, metropolis-fonts] 
     lib_dir: libs
@@
 ---
-
-```{r setup, include=FALSE}
-options(htmltools.dir.version = FALSE)
-library(sp)
-library(leaflet)
-library(lmerTest)
-library(tidyverse)
-library(cowplot)
-library(stargazer)
-source("RainCloudPlots.R")
-```
 
@@
 
-# Our experiment
+# Our study
 
@@
 
-Design
+# Design
+
+## Experiment 1
 
@@
 ---
+# Design
 
-Participants
+## Experiment 2
 
-```{r participant_map, echo = FALSE, message=FALSE}
-
-participant_data <- read_csv("participant_data.csv")
-coordinates(participant_data) <- c("Location Longitude","Location Latitude")
-leaflet(participant_data) %>% addMarkers(label = .$`Confirm Prolific ID`) %>% addTiles()
-```
+  - Like Experiment 1, but shorter prime duration condition (16 ms vs. 33 ms):
+    - Targets: same 240 words and 240 nonwords
+    - Conditions: 
+      - prime duration (16 vs. 33 ms)
+        - this corresponds to 1 vs. 2 refresh cycles at 60 Hz
+      - prime condition: identical vs. unrelated
+    - 60 word/nonword stimuli per group
 
 ---
-
 # Results
-
-```{r main_code, echo = FALSE, warning=FALSE, message = FALSE}
-
-csv_data <- fs::dir_ls(path = "./data", glob = "*.csv") %>%
-  map_dfr(read_csv, .id = "source", col_type = cols(
-  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
-  filter(!is.na(TrialID) & TrialID < 1000) %>%
-  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)
-
-# get participants with correct responses
-
-accuracy_by_participant <- csv_data %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())
-
-participants_to_include <- accuracy_by_participant %>% filter(N == 480 & acc > .8)
-
-participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
-paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows
-
-# for now, we only have two participants with accuracy > .8 and a full data set
-
-data_to_include <- csv_data %>% filter(source %in% participants_to_include$source) %>% mutate(StimulusType = StimulusType %>% factor, Condition = Condition %>% factor, PrimeDuration = PrimeDuration %>% factor, rt = rt * 1000)
-
-write_csv(data_to_include, path = "current_data.csv")
-
-data_summary_rt <- data_to_include %>% group_by(StimulusType, Condition, PrimeDuration) %>% summarise(M = mean(rt), SD = sd(rt), N = n())
-
-# data above 1500 ms excluded
-
-plot_raincloud(data_to_include %>% filter(corr == 1 & rt < 1500), x_column = "Condition", y_column = "rt", x_label = "Condition", y_label = "RT in ms (correct responses)", main_title = "RT by condition and word type") +
-  # put labels on the mean for easier comparison
-  stat_summary(fun.data = function(x) {data.frame(label = format(mean(x), digits = 2), y = mean(x))}, 
-                                      geom = "text",
-                                      #width = 1,
-                                      position = position_nudge(x = 0.5, y = 0),
-                                      #size = 0.2,
-                                      color = "black") +
-  facet_grid(cols = vars(PrimeDuration), rows = vars(StimulusType), labeller = label_context)
-
-```
-
----
-# LMM for RT (words, correct responses)
-```{r lmms}
-lmm1 <- lmer(data = data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (Condition+PrimeDuration|source) + (PrimeDuration|Target))
-
-summary(lmm1)
-
-```
-
----
-# gLMM for accuracy (Words)
-```{r logistic_lmm}
-lmm_acc <- glmer(data = data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt < 1500), corr ~ Condition + PrimeDuration + (1|Target), family = binomial(link = "logit"))
-
-summary(lmm_acc)
-
-```

### 2021-04-27 Lab meeting presentation April 2021 Results.Rmd

--- 2021-03-15 Manuscript_AB_MP.Rmd
@@
 ---
-title             : |
-    | Can we use masked priming in an online setting?
-    | The effect of prime exposure duration in online masked priming lexical decision
-shorttitle        : "Online masked priming"
+title: "Can we use masked priming in an online setting?"
 
-author: 
-  - name          : "Bernhard Angele"
-    affiliation   : "1,2"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Psychology, Faculty of Science and Technology, Talbot Campus, Fern Barrow, Poole BH12 5BB, UK"
-    email         : "bangele@bournemouth.ac.uk"
-  - name          : "Ana Baciero"
-    affiliation   : "2,3"
-  - name          : "Pablo Gomez"
-    affiliation   : "4"
-  - name          : "Manuel Perea Lara"
-    affiliation   : "2,5"
-
-affiliation:
-  - id            : "1"
-    institution   : "Bournemouth University, Bournemouth, UK"
-  - id            : "2"
-    institution   : "Universidad Antonio de Nebrija, Madrid, Spain"
-  - id            : "3"
-    institution   : "DePaul University, Chicago, USA"
-  - id            : "4"
-    institution   : "California State University San Bernardino, Palm Desert Campus, USA"
-  - id            : "5"
-    institution   : "Universitat de València, Valencia, Spain"
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  Masked priming is one of the most important paradigms in the study of visual word recognition, but it is usually thought to require a laboratory setup with a known monitor and keyboard.
-To investigate if this technique can be used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS [@peirce2019].
-In particular, we wanted to compare our online results to the data collected by @gomezDiffusionModelAccount2013, who compared masked and unmasked priming.
-Furthermore, we also tested the role of prime exposure duration effectively in an online experiment (33 vs.
-50 ms in Experiment 1 and 16 vs.
-33 ms in Experiment 2).
-  We found that our online data are indeed very similar to the masked priming data reported by @gomezDiffusionModelAccount2013.
-Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33 ms and no priming effect at 16 ms prime duration.
-  From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., Psychopy) can present stimuli and collect responses on standard consumer devices with enough precision.
-In sum, these findings provide us with confidence that masked priming can be used online, thus allowing us to reach populations that are hard to test in a laboratory.
-
-keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
-wordcount         : "XXX"
-
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-bibliography: ["references.bib", "r-references.bib"]
+subtitle: "The effect of prime exposure duration in online masked priming lexical decision"
+author: "Bernhard Angele, Ana Baciero, Pablo Gomez, & Manuel Perea"
+institute: "Bournemouth University, Universidad Nebrija, DePaul University, California State University San Bernardino, Universitat de Valencia"
+date: "`r Sys.Date()`"
+output:
+  xaringan::moon_reader:
+    css: [default, metropolis, metropolis-fonts] 
+    lib_dir: libs
+    nature:
+      highlightStyle: github
+      highlightLines: true
+      countIncrementalSlides: false
 ---
 
-```{r setup, include = FALSE}
-library("papaja")
-r_refs("r-references.bib")
+# Doing research during a pandemic
 
-```
+- No eye-tracking!
+- But lots of bored people sitting at home
+- What are language-related paradigms that we can do remotely?
+  - Surveys (not terribly interesting for many language researchers)
+  - Self-paced reading
+  - RSVP
+  - Lexical decision tasks
 
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+---
 
-Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition[see @forster1998pros; @grainger2008cracking, for reviews].
-Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond (e.g., “is *DOCTOR* a word?”).
-It is measured as the difference in a dependent variable (e.g., response time [RT]) between two conditions (e.g., unrelated: *horse-DOCTOR*; related: *nurse-DOCTOR*).
-In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a mask (e.g., #####) for a much longer duration (typically 500 ms).
-The rationale of the procedure is to make participants unaware of the identity of the masked prime [@forsterRepetitionPrimingFrequency1984; @forster1998pros], thus minimizing the role of participants’ strategies.
-Indeed, masked priming experiments do not show the strategical effects that occur with visible, unmasked primes [e.g., @grossi2006relatedness; @perea2002does].
+# Is priming possible online?
 
-The masked priming paradigm has been used in a large number of studies over the last decades.
-For instance, a search of the expression “masked priming” in Google Scholar in March 2021 produced nearly 10,000 hits.
-Virtually all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003).
-The issue we examine in the present paper is whether masked priming experiments can safely be conducted in an online setting.
-Even before the current exceptional situation due to the COVID pandemic, in which many labs around the world have been closed (or with minimal activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
-Indeed, researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010].
+- Overt priming certainly is
+- But masked priming relies on very precise timing of the stimuli.
+- Ken Forster did it a long time ago with GIFs:
 
-However, cognitive psychologists have been much slower in taking up online paradigms [see  @vandeberg2012out; @eerland2013influence; @rodd2016impact; @cai2017accent, for some exceptions], often due to concerns about the validity of the results.
-Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013],
-but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
-Indeed, in the masked priming technique, it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
-In particular, presenting the masked prime for longer than intended would counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest.
+  - 40 ms prime duration: 
+  ![40 ms prime](http://www.u.arizona.edu/~kforster/priming/mp_demo_1.gif)
+  - 100 ms prime duration: 
+  ![100 ms prime](http://www.u.arizona.edu/~kforster/priming/mp_demo_2.gif)
 
-There have been attempts to address these concerns.
-For example, a Web version of DMDX (webDMDX) was developed and showed promising results in a trial experiment [@witzelTestingViabilityWebDMDX2013].
-However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a “true” online programming script that could be run inside of a browser.
-A downside of this format is that participants often are (and should be) understandably skeptical about downloading and running executable files from the Internet.
-Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
-As a consequence, the use of webDMDX has been rather limited so far (\color{red}CITE somebody who has employed it \color{black})
+- But a demo on a website and an online experiment are two very different things!
 
-Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web.
-Most notably, the HTML5 standard now makes it possible to use Javascript in order to draw stimuli interactively and monitor participant responses with remarkable flexibility inside the browser.
-Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets [@reimersPresentationResponseTiming2015].
-There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, e.g., Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020] and open-source, e.g., jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of Psychopy 3, @peirce2019].
-In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
-Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility to recruit participants for on-line experiments based on various specific characteristics set up by the experimenter not necessarily in the country’s lab (e.g., native French speakers, not older than 30 years old, not currently in college).
+---
 
-Of course, despite the technological advances, many cognitive psychologists still have concerns about timing and measurement precision.
-While Javascript-based experiments run on the participants’ devices and thereby avoid any lag due to connection issues (e.g., to avoid delays, all stimuli are usually downloaded before the start of the experiment), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
-Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants’ preferences.
-As @reimersPresentationResponseTiming2015 point out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
-If the results of the Web-based study are comparable to previous lab-based results, this suggests that whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
+# Using the three Ps (Psychopy, Pavlovia, and Prolific) to collect data
 
-The first approach has the advantage that differences in presentation timings can be objectively recorded and evaluated.
-A very thorough recent example of this approach is the “timing mega-study” by @bridges2020, who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
-The very similar study by @anwyl-irvine2020a compares only online packages and browsers with regard to timing.
-Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with “reasonable” precision, although the lab-based packages were slightly better in this regard.
-This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
-If this is not possible, there is no point in moving forward to the second approach and replicating specific paradigms.
-However, it is of course impossible to test every possible device and configuration that participants might use.
-On the other hand, some of the differences in precision and accuracy between setups that can be observed using a photodiode may be too small to have an influence on actual participant performance.
+- Psychopy is an experiment presentation software allowing precise display of stimuli
+  - It's written in Python, but there is now the option of translating the experiments into Javascript (PsychoJS) for online presentation.
+  - Pavlovia is a paid service that integrates with Psychopy and hosts the experiment code and the collected data
+  - Prolific is a participant recruitment service (like Mechanical Turk, but more research-focused and less US-centric)
 
-Therefore, we consider replication of previous key lab-based effects a more important test of online paradigms than photodiode measurements.
-Based on the results by @bridges2020 and @anwyl-irvine2020a, modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
-To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm in one of the online experiment packages tested by @bridges2020 and @anwyl-irvine2020a.
-After evaluating their results, we decided on Psychopy/PsychoJS [@peirce2019] as it combines relative ease of use with high precision and accuracy across the great majority of platforms.
-\color{red} COMMENT: Was there something better (more precise)?
-It needs better rationale (we want to say it is the best).
-Possible reviewers’ comments:
+---
 
-    -	 Have you checked in different platforms?
-    -	 What does it mean “ease of use”?
-    -	 How precise is it? 
-\color{black}
+# Our study
 
-In the present study, we were interested in whether we could replicate, and extend, a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming reflects a savings effect.
-As first suggested by @forster1998pros, for a masked identity prime, “the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner”, whereas for an unrelated prime, “the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur” (p.
-213).
-Thus, according to the savings account, a target word like *DOCTOR* would enjoy an encoding advantage when preceded by an identity prime such as *doctor* than when preceded by an unrelated prime such as *pencil* (i.e., a head-start).
-One implication of such benefit is that the RT distributions of the unrelated and identity pairs should reflect a shift rather than a change in shape.
-Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony.
-Empirical evidence supporting this view has been obtained in several papers not only with skilled adults but also with developing readers [e.g., @gomezDiffusionModelAccount2013; @Gomez_2020; @Taikh_2020; @Yang_2021].
-Moreover, this pattern of results fits very well with the diffusion model [@ratcliff2004].
-This model proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution ($T_{er}$) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached.
-Importantly, in the decision process, the information gathered from the stimulus can vary in noise, depending on its quality, which modifies the rate at which information is accumulated (i.e., the *drift rate*).
-With regards to RTs from masked priming tasks, @gomezDiffusionModelAccount2013 found that the difference between identity and unrelated conditions could be accounted by a change in the $T_{er}$ parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)–note that changes in drift rate would necessarily produce a skewer RT distribution in the slower, unrelated condition.
+- Based on Gomez, Perea, & Ratcliff (2013)
 
-Critically, the above pattern is *specific* to masked priming.
-When primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles [i.e., a change in shape rather than a shift in RT distributions; see @gomezDiffusionModelAccount2013].
-Fits from the diffusion model show that this result corresponds to changes in both the $T_{er}$ parameter and the drift rate [see @gomezDiffusionModelAccount2013].
-Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word.
-Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.
-both encoding + information quality in unmasked priming.
+- Gomez et al. used the diffusion model to fit data from masked and unmasked prime presentation and found that masked and unmasked priming affect different model parameters:
+  - masked identity priming affects the $T_{er}$ parameter which represents encoding processes
+  - unmasked priming affects both $T_er$ and the drift rates parameter corresponding to the quality of information
 
-In the present paper, we took advantage of the above marker to examine whether online masked priming studies follow the same pattern as in-lab masked priming studies.
-Specifically, we manipulated prime exposure duration in identity vs.
-unrelated primes: 33.3 vs.
-50 ms in Experiment 1, and 16.6 vs.
-33.3 ms in Experiment 2—note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA).
-The rationale of Experiment 1 is that if the actual exposure duration of the primes is the nominal exposure duration, then we would expect the typical shift between the identity and unrelated response time distributions, which according to the savings hypothesis [@forster1998pros] would be greater for 50-ms than for 33.3-ms exposure duration (i.e., the head-start would be greater for 50-ms identity primes than for 33.3-ms identity primes).
-This outcome would indicate that the on-line masked priming studies reproduce a characteristic signature of laboratory masked priming studies.
-Alternatively, if the actual exposure duration is greater than the nominal one (e.g., approximately 20-ms longer on average) then, the 50 ms primes could be consciously perceived.
-If this were the case, the effect of the prime could affect not only the encoding but also core decision processes (i.e., drift rate parameter), which would be reflected as a stronger priming effect in the upper quantiles (i.e., the two RT distributions would have a different shape).
-In this scenario, one should be very cautious when running online masked priming experiments—at least with the settings currently available.
+- If we can show that the data from an online experiment pattern with the masked priming data from Gomez et al.
+rather than the unmasked priming data, that demonstrates the reliability of the online masked priming paradigm.
 
-To further constraint the research questions, Experiment 2 was parallel to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms).
-Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]—in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
-Thus, if prime exposure durations in online masked priming correspond to the nominal ones, we would expect a sizeable priming effect at the 33.3 but only a residual priming effect at the 16.6 ms prime exposure duration.
-Alternatively, if we obtain a sizeable effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would indicate, again, that we should be wary of using the masked priming technique in online experiments.
-Keep in mind that we are using a software that has good control over the exposure duration (\color{red} CITE).
-
-ADD at some point:
-
-    - Even with no control over many context variables, we obtain the effects (peerj:Parker)
-    - Hypotheses in a figure (as in Gomez & Perea, 2020).
-    - In addition:
-We conducted a simulation study on the impact of suboptimal response time accuracy on statistical power when varying the number of participants, the number of items/condition, and the degree of inaccuracy of the response device.
-\color{black}
+---
 
@@
 
-In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33 ms and 50 ms (roughly corresponding to two and three frames at a refresh rate of 60 Hz).
+## Design
 
-We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+- Targets: 240 words and 240 nonwords
+- Conditions: 
+  - prime duration (33 vs. 50 ms)
+    - this corresponds to 2 vs. 3 refresh cycles at 60 Hz
+  - prime condition: identical vs. unrelated
+- 60 word/nonword stimuli per group
 
-## Method
+## Participants
 
-```{r load_exp1_data, message=FALSE, echo=FALSE}
+```{r load_exp1_data, message=FALSE, echo=FALSE, warning=FALSE}
 library(xfun)
@@
 
-participant_coords <- e1_actual_participants %>% select("Location Longitude", "Location Latitude")
+participant_coords <- exp1_actual_participants %>% select("Location Longitude", "Location Latitude")
 
-e1_actual_participants$country <- coords2country(participant_coords)
+exp1_actual_participants$country <- coords2country(participant_coords)
 
-e1_participant_countries <- table(e1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
+exp1_participant_countries <- table(exp1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
 ```
 
-### Participants
+## Participants
 
-We collected data from `r e1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants aged from `r participant_ages %>% min` to `r participant_ages %>% max` (mean age: `r participant_ages %>% mean %>% round(2)`) recruited through Prolific [www.prolific.co, -@prolific2021].
-Of the participants, `r male_participants_nr` identified as male and `r female_participants_nr` identified as female.
+- `r exp1_all_participants$PROLIFIC_PID %>% unique %>% length` Prolific participants, with `r exp1_accuracy_by_participant %>% nrow` with `r exp1_actual_participants$PROLIFIC_PID %>% unique %>% length` completing the experiment.
+- Participants (`r exp1_male_participants_nr` male, `r exp1_female_participants_nr` female) were aged from `r exp1_participant_ages %>% min` to `r exp1_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
+Of the participants,  identified as male and `r exp1_female_participants_nr` identified as female.
 The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions.
-Based on their IP addresses, `r e1_participant_countries["United Kingdom"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in the UK, `r e1_participant_countries["United States of America"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` were based in the US, `r e1_participant_countries["Canada"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in Canada, and `r e1_participant_countries["Ireland"] %>% ifelse(.
+Based on their IP addresses, `r exp1_participant_countries["United Kingdom"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in the UK, `r exp1_participant_countries["United States of America"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` were based in the US, `r exp1_participant_countries["Canada"] %>% ifelse(.
+< 11, numbers_to_words(.), .)` participants were based in Canada, and `r exp1_participant_countries["Ireland"] %>% ifelse(.
 < 11, numbers_to_words(.), .)` participants were based in Ireland.
@@
 All participants were naïve to the purpose of the experiment.
+Participants could use a desktop or laptop computer or a mobile device.
+Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
 
-### Materials
+---
+# Design
 
-### Procedure
+## Experiment 2
 
-Participants were able to sign up for the experiment on the Prolific website.
-On signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment [@qualtrics2020].
-After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual PsychoJS experiment was hosted.
-After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.
+  - Like Experiment 1, but shorter prime duration condition (16 ms vs. 33 ms):
+    - Targets: same 240 words and 240 nonwords
+    - Conditions: 
+      - prime duration (16 vs. 33 ms)
+        - this corresponds to 1 vs. 2 refresh cycles at 60 Hz
+      - prime condition: identical vs. unrelated
+    - 60 word/nonword stimuli per group
 
-### Data analysis
-
-We used `r cite_r("r-references.bib")` for all our analyses.
-
-## Results
-
-## Discussion
-
-# General Discussion
-
-```{=html}
-<script src="https://hypothes.is/embed.js" async></script>
-```
-\newpage
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
-
-\endgroup
+---
+# Results

### 2021-04-28 Lab meeting presentation April 2021.Rmd

@@
 title: "Can we use masked priming in an online setting?"
+subtitle: "The effect of prime exposure duration in online masked priming lexical decision"
 
-subtitle: "The effect of prime exposure duration in online masked priming lexical decision"
 author: "Bernhard Angele, Ana Baciero, Pablo Gomez, & Manuel Perea"
-institute: "Bournemouth University, Universidad Nebrija, DePaul University, California State University San Bernardino, Universitat de Valencia"
-date: "`r Sys.Date()`"
+
 output:
@@
 
-# Doing research during a pandemic
+# Masked priming paradigm
 
-- No eye-tracking!
-- But lots of bored people sitting at home
-- What are language-related paradigms that we can do remotely?
-  - Surveys (not terribly interesting for many language researchers)
+-  One of the most important techniques to study early letter/word processes
+
+![Trial diagram](MaskedPrimingDiagram.PNG)
+
+<small>(Forster & Davis, 1984)
+
+---
+
+# Is masked priming possible online?
+
+<br>
+
+- Technology improvements + current situation have made online studies flourish
+
+<br>
+
+- Different paradigms are easily implemented in online settings:
+
+  - Surveys
   - Self-paced reading
@@
 
----
+<br>
 
-# Is priming possible online?
+- But masked priming relies on very precise timing of the stimuli
 
-- Overt priming certainly is
-- But masked priming relies on very precise timing of the stimuli.
-- Ken Forster did it a long time ago with GIFs:
-
-  - 40 ms prime duration: 
-  ![40 ms prime](http://www.u.arizona.edu/~kforster/priming/mp_demo_1.gif)
-  - 100 ms prime duration: 
-  ![100 ms prime](http://www.u.arizona.edu/~kforster/priming/mp_demo_2.gif)
-
-- But a demo on a website and an online experiment are two very different things!
+  - Issue: use of different devices to present the stimuli and record responses
 
@@
 
-# Using the three Ps (Psychopy, Pavlovia, and Prolific) to collect data
+# Here
 
-- Psychopy is an experiment presentation software allowing precise display of stimuli
-  - It's written in Python, but there is now the option of translating the experiments into Javascript (PsychoJS) for online presentation.
-  - Pavlovia is a paid service that integrates with Psychopy and hosts the experiment code and the collected data
-  - Prolific is a participant recruitment service (like Mechanical Turk, but more research-focused and less US-centric)
+<br>
+<center>
+<big>
+**Is it possible to do masked priming experiments online?**
+
+<br>
 
@@
 
-# Our study
+# But before diving into our study...
 
-- Based on Gomez, Perea, & Ratcliff (2013)
+<br>
 
-- Gomez et al. used the diffusion model to fit data from masked and unmasked prime presentation and found that masked and unmasked priming affect different model parameters:
-  - masked identity priming affects the $T_{er}$ parameter which represents encoding processes
-  - unmasked priming affects both $T_er$ and the drift rates parameter corresponding to the quality of information
+- A key phenomenon in laboratory masked priming lexical decision is that asked identity priming reflects a *savings effect*:
+  - Lexical entry evaluation begins sooner for identity primes than for unrelated primes.
 
-- If we can show that the data from an online experiment pattern with the masked priming data from Gomez et al.
-rather than the unmasked priming data, that demonstrates the reliability of the online masked priming paradigm.
+    >- RT distributions of the unrelated and identity pairs reflect a shift rather than a change in shape.
+
+<br>
+
+- Additionally, such shift should be similar in magnitude to the prime-target stimulus-onset asynchrony
+
+---
+# Model fits of observed data
+
+<br>
+
+- Gomez, Perea, & Ratcliff (2013) diffusion model fits:
+
+  -  Masked identity priming affects the $T_{er}$ parameter (encoding processes)
+
+  -  Unmasked priming affects both $T_{er}$ and the drift rates parameter (quality of information)
 
@@
 
-# Design
+# Research question
+
+<br>
+<br>
+
+Could we replicate these findings using an online setup?
+
+<br>
+
+- If we can show that the data from an online experiment pattern with the masked priming data from Gomez et al.
+rather than the unmasked priming data, that would show the reliability of the online masked priming paradigm.
+
+---
+
+# Popular online data collection method
+
+<br>
+
+- Integration of 3 pieces of software: *The three Ps*
+
+  - **Psychopy**: experiment presentation software that allows precise display of stimuli
+
+  - **Pavlovia**: paid service that hosts the experiment code and the collected data
+
+  - **Prolific**: participant recruitment service (like Mechanical Turk, but more research-focused and less US-centric)
+
+---
+
+# The present study
+
+<br>
+
+- We used said data collection method to examine whether online masked priming studies follow the same pattern as in-lab masked priming studies, manipulating:
+
+  - Prime condition:
+
+    >- Identity vs. Unrelated
+
+  - Prime exposure duration:
+
+    >- 33.3 vs. 50 ms (Experiment 1)
+    >- 16.6 vs. 33.3 ms (Experiment 2)
+
+---
+
+# Experimental Design
 
@@
 
+<br>
+
 - Targets: 240 words and 240 nonwords
+
+<br>
+
 - Conditions:
+
   - prime duration (33 vs. 50 ms)
-    - this corresponds to 2 vs. 3 refresh cycles at 60 Hz
+    >- Corresponding to 2 vs. 3 refresh cycles at 60 Hz
+
   - prime condition: identical vs. unrelated
+
+<br>
+
 - 60 word/nonword stimuli per group
@@
 ---
-# Design
+# Experimental Design
 
@@
 
-  - Like Experiment 1, but shorter prime duration condition (16 ms vs. 33 ms):
-    - Targets: same 240 words and 240 nonwords
+<br>
+
+- Targets: 240 words and 240 nonwords
+
+<br>
+
 - Conditions:
-      - prime duration (16 vs. 33 ms)
-        - this corresponds to 1 vs. 2 refresh cycles at 60 Hz
+
+  - prime duration (16 vs. 33.3 ms)
+    >- Corresponding to 1 vs. 2 refresh cycles at 60 Hz
+
   - prime condition: identical vs. unrelated
+
+<br>
+
 - 60 word/nonword stimuli per group
@@
 # Results
+<br>
+
+---
+# EDA: Experiment 1
+<br>
+
+![Trial diagram](DeltaE1_PrimingEffect.png)
+---
+# EDA: Experiment 2
+<br>
+
+![Trial diagram](DeltaE2_PrimingEffect.png)
+---
+# Inferentials
+<br>
+
+---
+# Conclusions
+<br>

### 2021-04-28 Lab meeting presentation April 2021.Rmd
Add raincloud plots

@@
 ---
+
+```{r setup, echo=FALSE, message=FALSE}
+library(tidyverse)
+# for finding out where the participants were
+library(xfun)
+library(sp)
+library(rworldmap)
+# for the analyses
+library(brms)
+# for the plots
+library(cowplot)
+library(stargazer)
+source("RainCloudPlots.R")
+```
 
@@
 
-# Experimental Design
+# Experiment 1
 
-## Experiment 1
+## Experimental Design
 
@@
 - 60 word/nonword stimuli per group
+---
+
+# Experiment 1: Participants
+
+```{r load_exp1_data, message=FALSE, echo=FALSE, warning=FALSE}
+
+# Qualtrics survey data
+exp1_all_participants <- read_csv("participant_data_exp1.csv")
+
+# PsychoJS trial data
+exp1 <- fs::dir_ls(path = "./data_exp1", glob = "*.csv") %>%
+  map_dfr(read_csv, .id = "source", col_type = cols(
+  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
+  filter(!is.na(TrialID) & TrialID < 1000) %>%
+  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)
+
+exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
+
+# only consider participants who have actually participated in the whole experiment
+# also don't consider participants whose age is 99 (used for testing)
+# one participant is duplicate. Remove the first occurrence (likely incompatible device)
+
+exp1_actual_participants <- filter(exp1_all_participants, (PROLIFIC_PID %in% exp1$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & (`Response ID` != "R_sU4qJ6UCe9jRKs9"))
+
+# get participants with more than 80% correct responses
+
+exp1_accuracy_by_participant <- exp1 %>% filter(participant %in% exp1_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())
+
+exp1_participants_to_include <- exp1_accuracy_by_participant %>% filter(N == 480 & acc >= .8)
+
+exp1_participants_to_exclude <- exp1_accuracy_by_participant %>% filter(N != 480 | acc < .8)
+
+#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
+
+exp1_data_to_include <- exp1 %>% filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33 ms", "50 ms")), rt = rt * 1000)
+
+# filter out any of the participants we eliminated from the Qualtrics file as well
+
+exp1_actual_participants <- filter(exp1_actual_participants, (PROLIFIC_PID %in% exp1_data_to_include$participant))
+
+exp1_participant_ages <- exp1_actual_participants$`What is your age?`
+
+exp1_male_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow
+
+exp1_female_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow
+
+# there aren't actually any of these, but will leave the code in just in case
+exp1_other_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
+
+exp1_NA_participants_nr <- filter(exp1_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow
+
+exp1_participant_coords <- exp1_actual_participants %>% select("Location Longitude", "Location Latitude")
+
+#coordinates(exp1_actual_participants) <- c("Location Longitude","Location Latitude")
+
+# from https://stackoverflow.com/questions/14334970/convert-latitude-and-longitude-coordinates-to-country-name-in-r
+
+# The single argument to this function, points, is a data.frame in which:
+#   - column 1 contains the longitude in degrees
+#   - column 2 contains the latitude in degrees
+coords2country = function(points)
+{  
+  countriesSP <- getMap(resolution='low')
+  #countriesSP <- getMap(resolution='high') #you could use high res map from rworldxtra if you were concerned about detail
+
+  # convert our list of points to a SpatialPoints object
+
+  # pointsSP = SpatialPoints(points, proj4string=CRS(" +proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0"))
+
+  #setting CRS directly to that from rworldmap
+  pointsSP = SpatialPoints(points, proj4string=CRS(proj4string(countriesSP)))
+
+  # use 'over' to get indices of the Polygons object containing each point 
+  indices = over(pointsSP, countriesSP)
+
+  # return the ADMIN names of each country
+  indices$ADMIN  
+  #indices$ISO3 # returns the ISO3 code 
+  #indices$continent   # returns the continent (6 continent model)
+  #indices$REGION   # returns the continent (7 continent model)
+}
+
+participant_coords <- exp1_actual_participants %>% select("Location Longitude", "Location Latitude")
+
+exp1_actual_participants$country <- coords2country(participant_coords)
+
+exp1_participant_countries <- table(exp1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
+```
+
+- `r exp1_all_participants$PROLIFIC_PID %>% unique %>% length` Prolific participants, with `r exp1_actual_participants$PROLIFIC_PID %>% unique %>% length` actually completing the experiment with an accuracy of > .8.
+- `r exp1_male_participants_nr` male and `r exp1_female_participants_nr` female participants 
+- Aged from `r exp1_participant_ages %>% min` to `r exp1_participant_ages %>% max` (mean: `r exp1_participant_ages %>% mean %>% round(2)`). 
+- Only shown to participants who indicated that English was their first language in the Prolific screening questions.
+- Participant countries (according to Qualtrics and based on the IP Addresses, only including participants who could be localized)
+
+```{r participant_location_table, as.is = TRUE, echo = FALSE}
+knitr::kable(exp1_participant_countries %>% t, format = "html")
+
+```
+- Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour). 
+- Participants could use a desktop or laptop computer or a mobile device.
+  - But not Safari (issues with PsychoJS)
 
 ---
-# Experimental Design
+# Experiment 1: Results
 
-## Experiment 2
+```{r raincloud_exp1, echo=FALSE}
+plot_raincloud(exp1_data_to_include %>% filter(corr == 1 & rt < 1500), x_column = "Condition", y_column = "rt", x_label = "Condition", y_label = "RT in ms (correct responses)", main_title = "RT by condition and word type") +
+  # put labels on the mean for easier comparison
+  stat_summary(fun.data = function(x) {data.frame(label = format(mean(x), digits = 2), y = mean(x))}, 
+                                      geom = "text",
+                                      #width = 1,
+                                      position = position_nudge(x = 0.5, y = 0),
+                                      #size = 0.2,
+                                      color = "black") +
+  facet_grid(cols = vars(PrimeDuration), rows = vars(StimulusType), labeller = label_context)
+```
+
+---
+# Experiment 1: EDA
+<br>
+
+![Trial diagram](DeltaE1_PrimingEffect.png)
+
+---
+# Experiment 2
+
+## Experimental Design
 
@@
 ---
-# Results
-<br>
+# Experiment 2: Participants
+
+```{r load-exp2-data, as.is = TRUE,echo=FALSE, warning=FALSE}
+#load raw Exp2 data
+
+exp2_all_participants <- read_csv("participant_data_exp2.csv")
+
+exp2 <- fs::dir_ls(path = "./data_exp2", glob = "*.csv") %>%
+  map_dfr(read_csv, .id = "source", col_type = cols(
+  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
+  filter(!is.na(TrialID) & TrialID < 1000) %>%
+  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)
+
+exp2$device <- ifelse(exp2$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
+
+# only consider participants who have actually participated in the whole experiment
+# also don't consider participants whose age is 99 (used for testing)
+# one participant is duplicate. Remove the first occurrence (likely incompatible device)
+
+exp2_actual_participants <- filter(exp2_all_participants, (PROLIFIC_PID %in% exp2$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & !(`Response ID` %in% c("R_2c2dVRNmGvI6CH9", "R_3ELutaT6GNe5mmR", "R_XX7jgUk2NbIi41j", "R_125QKzJfHwoGHaT")))
+
+# get participants with more than 80% correct responses
+
+exp2_accuracy_by_participant <- exp2 %>% filter(participant %in% exp2_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())
+
+exp2_participants_to_include <- exp2_accuracy_by_participant %>% filter(N == 480 & acc >= .8)
+
+exp2_participants_to_exclude <- exp2_accuracy_by_participant %>% filter(N != 480 | acc < .8)
+
+#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
+
+exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16 ms", "33 ms")), rt = rt * 1000)
+
+# filter out any of the participants we eliminated from the Qualtrics file as well
+
+exp2_actual_participants <- filter(exp2_actual_participants, (PROLIFIC_PID %in% exp2_data_to_include$participant))
+
+exp2_participant_ages <- exp2_actual_participants$`What is your age?`
+
+exp2_male_participants_nr <- filter(exp2_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow
+
+exp2_female_participants_nr <- filter(exp2_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow
+
+# there aren't actually any of these, but will leave the code in just in case
+exp2_other_participants_nr <- filter(exp2_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
+
+exp2_NA_participants_nr <- filter(exp2_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow
+
+exp2_participant_coords <- exp2_actual_participants %>% select("Location Longitude", "Location Latitude")
+
+# coords2country function definition in exp1 chunk above
+exp2_actual_participants$country <- coords2country(exp2_participant_coords)
+
+exp2_participant_countries <- table(exp2_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
+
+#paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows
+
+exclude_list_for_prolific <- str_extract(string = exp2_participants_to_exclude$source, pattern = "[a-z0-9]{24}") %>% paste0(collapse = "\n")
+
+```
+
+- `r exp2_all_participants$PROLIFIC_PID %>% unique %>% length` Prolific participants, with `r exp2_actual_participants$PROLIFIC_PID %>% unique %>% length` actually completing the experiment with an accuracy of > .8.
+- `r exp2_male_participants_nr` male and `r exp2_female_participants_nr` female participants 
+- Aged from `r exp2_participant_ages %>% min` to `r exp2_participant_ages %>% max` (mean: `r exp2_participant_ages %>% mean %>% round(2)`). 
+- Only shown to participants who indicated that English was their first language in the Prolific screening questions.
+- Participant countries (according to Qualtrics and based on the IP Addresses, only including participants who could be localized)
+
+```{r participant_location_table_exp2, as.is = TRUE, echo = FALSE}
+knitr::kable(exp2_participant_countries %>% t, format = "html")
+
+```
 
 ---
-# EDA: Experiment 1
-<br>
+# Experiment 2: Results
 
-![Trial diagram](DeltaE1_PrimingEffect.png)
+```{r raincloud_exp2, echo=FALSE}
+plot_raincloud(exp2_data_to_include %>% filter(corr == 1 & rt < 1500), x_column = "Condition", y_column = "rt", x_label = "Condition", y_label = "RT in ms (correct responses)", main_title = "RT by condition and word type") +
+  # put labels on the mean for easier comparison
+  stat_summary(fun.data = function(x) {data.frame(label = format(mean(x), digits = 2), y = mean(x))}, 
+                                      geom = "text",
+                                      #width = 1,
+                                      position = position_nudge(x = 0.5, y = 0),
+                                      #size = 0.2,
+                                      color = "black") +
+  facet_grid(cols = vars(PrimeDuration), rows = vars(StimulusType), labeller = label_context)
+```
+
 ---
-# EDA: Experiment 2
+# Experiment 2: EDA
 <br>

### 2021-05-05 Lab meeting presentation April 2021 Results.Rmd
Added general discussion, edited introduction

@@
 - `r exp1_all_participants$PROLIFIC_PID %>% unique %>% length` Prolific participants, with `r exp1_accuracy_by_participant %>% nrow` with `r exp1_actual_participants$PROLIFIC_PID %>% unique %>% length` completing the experiment.
-- Participants (`r exp1_male_participants_nr` male, `r exp1_female_participants_nr` female) were aged from `r exp1_participant_ages %>% min` to `r exp1_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
+- Participants (`r exp1_male_participants_nr` male, `r exp1_female_participants_nr` female) were aged from `r exp1_participant_ages %>% min` to `r exp1_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`)s.
 Of the participants,  identified as male and `r exp1_female_participants_nr` identified as female.

### 2021-05-05 Manuscript_intro_method_results.Rmd
Added general discussion, edited introduction

@@
 One implication of such benefit is that the RT distributions of the unrelated and identity pairs should reflect a shift rather than a change in shape.
-Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony.
+Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony (SOA).
 Empirical evidence supporting this view has been obtained in several papers not only with skilled adults but also with developing readers [e.g., @gomezDiffusionModelAccount2013; @Gomez_2020; @Taikh_2020; @Yang_2021].
@@
 33.3 ms in Experiment 2---note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA).
-The rationale of Experiment 1 is that if the actual exposure duration of the primes is the nominal exposure duration, then we would expect the typical shift between the identity and unrelated response time distributions, which according to the savings hypothesis [@forster1998pros] would be greater for 50-ms than for 33.3-ms exposure duration (i.e., the head-start would be greater for 50-ms identity primes than for 33.3-ms identity primes).
+The rationale of Experiment 1 is that if the actual exposure duration of the primes is the nominal exposure duration, then we would expect the typical shift between the identity and unrelated response time distributions, which according to the savings hypothesis [@forster1998pros] would be greater for 50 ms than for 33.3 ms exposure duration (i.e., the head-start would be greater for 50 ms identity primes than for 33.3 ms identity primes).
 This outcome would indicate that the on-line masked priming studies reproduce a characteristic signature of laboratory masked priming studies.
-Alternatively, if the actual exposure duration is greater than the nominal one (e.g., approximately 20-ms longer on average) then, the 50 ms primes could be consciously perceived.
-If this were the case, the effect of the prime could affect not only the encoding but also core decision processes (i.e., drift rate parameter), which would be reflected as a stronger priming effect in the upper quantiles (i.e., the two RT distributions would have a different shape).
-In this scenario, one should be very cautious when running online masked priming experiments---at least with the settings currently available.
+Alternatively, if the online presentation conditions lead to a greater actual exposure duration on the participant's device compared to that specified in our experiment, (e.g., prime durations are approximately 20 ms longer on average than programmed) then the 50 ms primes may no longer be masked, but may rather be consciously perceived.
+If this is the case, the prime could affect not only the encoding, but also core decision processes (i.e., the drift rate), which would be reflected as a stronger priming effect in the higher quantiles of the distribution (i.e., the two RT distributions would have a different shape).
+In this scenario, one should be very cautious when running online masked priming experiments---at least with the typical software and hardware currently available.
 
-To further constraint the research questions, Experiment 2 was parallel to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms).
+To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms).
 Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
-Thus, if prime exposure durations in online masked priming correspond to the nominal ones, we would expect a sizeable priming effect at the 33.3 but only a residual priming effect at the 16.6 ms prime exposure duration.
-Alternatively, if we obtain a sizeable effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would indicate, again, that we should be wary of using the masked priming technique in online experiments.
+Thus, if the size of the priming effect is roughly similar to the prime exposure duration, we would expect a much larger priming effect at the 33.3 ms prime exposure duration than at the 16.6 ms prime exposure duration.
+If we do observe a large effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments.
 Keep in mind that we are using a software that has good control over the exposure duration (\color{red} CITE).
@@
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
-load("blmm_exp1_rt_new.RData")
+load("blmm_exp1_rt_dist_full_ranef_5000.RData")
 # model name is blmm_exp1_rt
@@
 
-blmm_exp1_summary_rt <- summary(blmm_exp1_rt)
+blmm_exp1_summary_rt <- summary(blmm_exp1_rt_dist)
 
@@
 parameter_names <- c(
-    "Intercept",
-    "Condition",
-    "Prime Duration",
-    "Condition:Prime Duration"
+    "Intercept ($\\mu$)",
+    "Intercept ($\\beta$)",
+    "Condition ($\\mu$)",
+    "Prime Duration ($\\mu$)",
+    "Condition:Prime Duration ($\\mu$)",
+    "Condition ($\\beta$)",
+    "Prime Duration ($\\beta$)",
+    "Condition:Prime Duration ($\\beta$)"
     )
@@
     caption = "(ref:exp1-blmm-table-caption)",
-    note = NULL,
+    note = "$\\beta$ is the scale parameter (the inverse of the rate parameter $\\lambda$) of the ex-Gaussian distribution.",
     small = TRUE,
@@
 
-load("blmm_exp1_acc_new.RData")
+load("blmm_exp1_acc_new_10000.RData")
 
@@
 We also saw a clear difference between the 33 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices.
+We did not observe an effect of either the priming condition or the prime exposure duration on the shape parameter $\beta$ of the exponential distribution, suggesting, according to the savings hypothesis by @forster1998pros, that only encoding processes were affected.
+
 Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.
-In order to further explore this, we perfomed a second experiment in which we set the prime to be displayed for an even shorter duration.
-As described above, a 16 ms prime duration should yield qualitatively different effects from the 33 and 50 ms durations used in Experiment 1.
+In order to further explore this, we performed a second experiment in which we set the prime to be displayed for an even shorter duration.
+As described above, a 16.6 ms prime duration should yield qualitatively different effects from the 33.3 and 50 ms durations used in Experiment 1.
 If it does not, this casts doubt on the timing accuracy in online experiments.
@@
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
-load("blmm_exp2_rt_new.RData")
-# model name is blmm_exp1_rt
+load("blmm_exp2_rt_dist.RData")
+# model name is blmm_exp2_rt
 
@@
 
-blmm_exp2_summary_rt <- summary(blmm_exp2_rt)
+blmm_exp2_summary_rt <- summary(blmm_exp2_rt_dist)
 
@@
     caption = "(ref:exp2-blmm-rt-table-caption)",
-    note = NULL,
+    note = "$\\beta$ is the scale parameter (the inverse of the rate parameter $\\lambda$) of the ex-Gaussian distribution.",
     small = TRUE,
@@
 
-load("blmm_exp2_acc_new.RData")
+load("blmm_exp2_acc_new_10000.RData")
 
@@
 
-In Experiment 2, we observed the pattern we expected from previous research: a robust priming effect in response time and accuracy in the 33 ms condition, but a very weak effect in the 16 ms condition.
+In Experiment 2, we observed the pattern we expected from previous research: In the the mean $\mu$ of the Gaussian distribution, we saw a robust priming effect in response time and accuracy in the 33 ms condition, but a very weak effect in the 16 ms condition.
 This suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
+Again, we did not observe an effect of either the priming condition or the prime exposure duration on the shape parameter $\beta$ of the exponential distribution.
 
@@
 
-In this study, we
+In this study, we set out to test whether using an online, browser-based experiment software, we could replicate the masked priming effect both qualitatively and quantitatively, i.e., in terms of effect sizes.
+Our results show that this is the case: not only did we observe results comparable to the lab-based studies in the literature, we also observed the effect sizes predicted by Forster's [-@forster1998pros] savings hypothesis: Our data show a shift in the mean of the Gaussian distribution, but no change in the shape parameter $\beta$ of the exponential distribution, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision making processes.
+
+We also found that the size of the priming effect was directly influenced by the prime exposure duration.
+This indicates that the experimental software was able to control the display timing of the prime accurately.
+Accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, but are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade.
+The fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of Psychopy.
+
+Our results open the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
+Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible.
+For example, many people in developing countries may not have computers at home, but they do have smartphones.
+Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant.
+Deploying experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
+
+In conclusion, our results give us confidence that high-quality behavioral data can be collected online using Javascript-based experiment platforms.
+We hope that future research takes advantage of these new methods in order to make research faster, more inclusive, and more efficient.
 

### 2021-05-06 Manuscript_intro_method_results_AB.Rmd
Create Manuscript_intro_method_results_AB.Rmd

--- 2021-05-05 Manuscript_intro_method_results.Rmd
@@
     affiliation   : "4"
-  - name          : "Manuel Perea Lara"
+  - name          : "Manuel Perea"
     affiliation   : "2,5"
@@
 draft             : no
-documentclass     : "apa6"
+csl               : "apa.csl"
+documentclass     : "apa7"
 classoption       : "man"
@@
 library("papaja")
+library(ggplot2)
+library(patchwork)
 
@@
 
-Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition[see @forster1998pros; @grainger2008cracking, for reviews].
+Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition[see @forster1998pros; and @grainger2008cracking, for reviews].
 Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond (e.g., "is *DOCTOR* a word?").
@@
 
-However, cognitive psychologists have been much slower in taking up online paradigms [see @vandeberg2012out; @eerland2013influence; @rodd2016impact; @cai2017accent, for some exceptions], often due to concerns about the validity of the results.
+However, cognitive psychologists have been much slower in taking up online paradigms [see @cai2017accent;@eerland2013influence; @rodd2016impact; @vandeberg2012out , for some exceptions], often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
@@
 Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
-As a consequence, the use of webDMDX has been rather limited so far (\color{red}CITE somebody who has employed it \color{black})
+As a consequence, the use of webDMDX in masked priming experiments has been rather limited so far [see @Alluhaybi_2020; @Dubey_2018 for exceptions].
 
@@
 Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets [@reimersPresentationResponseTiming2015].
-There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, e.g., Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020] and open-source, e.g., jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of Psychopy 3, @peirce2019].
+There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020], and open-source such as jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of Psychopy 3, @peirce2019].
 In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
@@
 On the other hand, some of the differences in precision and accuracy between setups that can be observed using a photodiode may be too small to have an influence on actual participant performance.
-
 Therefore, we consider replication of previous key lab-based effects a more important test of online paradigms than photodiode measurements.
 Based on the results by @bridges2020 and @anwyl-irvine2020a, modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
-To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm in one of the online experiment packages tested by @bridges2020 and @anwyl-irvine2020a.
-After evaluating their results, we decided on Psychopy/PsychoJS [@peirce2019] as it combines relative ease of use with high precision and accuracy across the great majority of platforms.
-\color{red} COMMENT: Was there something better (more precise)?
-It needs better rationale (we want to say it is the best).
-Possible reviewers' comments:
+To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study.
+Importantly, we will do so using Psychopy/PsychoJS [@peirce2019] as it showed high precision and accuracy across the great majority of platforms [@bridges2020; @anwyl-irvine2020a], in addition to being an open-source software.
 
-    -    Have you checked in different platforms?
-    -    What does it mean “ease of use”?
-    -    How precise is it?
-
-\color{black}
-
-In the present study, we were interested in whether we could replicate, and extend, a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming reflects a savings effect.
+Specifically, in this study we were interested in whether we could replicate, and extend, a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming reflects a savings effect.
 As first suggested by @forster1998pros, for a masked identity prime, "the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner", whereas for an unrelated prime, "the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur" (p.
@@
 If we do observe a large effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments.
-Keep in mind that we are using a software that has good control over the exposure duration (\color{red} CITE).
+Keep in mind that we are using a software that has good control over the exposure duration [@bridges2020; @anwyl-irvine2020a].All in all, replicating the results observed in controlled laoboratory masked primiming studies would provide some grounds to the validity of online masked priming tasks,even with no control over many variables (e.g., the devices in which the experiment is run, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
 
-ADD at some point:
+\color{red}ADD at some point:
 
-    - Even with no control over many context variables, we obtain the effects (peerj:Parker)
     - Hypotheses in a figure (as in Gomez & Perea, 2020).
-    - In addition:
 
-We conducted a simulation study on the impact of suboptimal response time accuracy on statistical power when varying the number of participants, the number of items/condition, and the degree of inaccuracy of the response device.
 \color{black}
+
+The study was pre-registered on the Open Science Framework (OSF) prior to data collection.
+The registration form, together with the materials, data files, and R scripts can be found at https://osf.io/d2txs/.
 
@@
 A further `r exp1_participants_to_exclude %>% filter(N == 480 & acc < .8) %>% nrow %>% ifelse(.
-< 11, numbers_to_words(.), .)` were excluded because of low accuracy (less than .8).
-The remaining `r exp1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants were aged from `r exp1_participant_ages %>% min` to `r exp1_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
-Of the participants, `r exp1_male_participants_nr` identified as male and `r exp1_female_participants_nr` identified as female.
-The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions.
+< 11, numbers_to_words(.), .)` were excluded because of low accuracy (less than .8, which was the pre-registered criterion).
+In the end, we analyzed the data from `r exp1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants (`r exp1_female_participants_nr` female), aged from `r exp1_participant_ages %>% min` to `r exp1_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
+All these participants indicated that English was their first language in the Prolific screening questions.
 Based on their IP addresses, `r exp1_participant_countries["United Kingdom"] %>% ifelse(.
@@
 Two participants could not be localized in this way.
-Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour).
-All participants were naïve to the purpose of the experiment.
-Participants could use a desktop or laptop computer or a mobile device.
+All participants were naïve to the purpose of the experiment and received £1.25 for their participation (corresponding to £5/hour).
+Participants could use either a desktop/laptop computer or a mobile device.
 Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
@@
 For each target, we created an identical prime (e.g.
-`region` --- `REGION` and `fainch` --- `FAINCH`) and an unrelated prime consisting of another word from the list (e.g.
-`launch` --- `REGION` and `miluer` --- `FAINCH`).
+*region --- REGION* and *fainch --- FAINCH*) and an unrelated prime consisting of another word from the list (e.g.
+*launch --- REGION* and *miluer --- FAINCH*).
 Appendix A contains a list of the items.
@@
 The height for all text stimuli was 0.1 units.
-Each trial began with a six-character pattern mask (`######`) set to be presented for 500 ms, followed first by the lowercase prime (e.g.
-`region`) set to be presented for either 33 or 50 ms, and then by the uppercase target (e.g.
-`REGION`).
+Each trial began with a six-character pattern mask (*######*) set to be presented for 500 ms, followed first by the lowercase prime (e.g.
+*region*) set to be presented for either 33 or 50 ms, and then by the uppercase target (e.g.
+*REGION*).
 Participants were instructed to respond to the target stimulus as quickly as possible either by using the keyboard, if their device had one, and pressing the "Z" key if the target was not a valid English word or the "M" key if the target was a valid English word.
@@
 We consider an effect as credible if the 95% credible interval (CrI) estimated from the posterior distribution does not contain zero.
+
+In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.
 
@@
 
-plot(del_hdi_exp1_rt) + scale_fill_flat() + theme_apa()
+plot(del_hdi_exp1_rt) +
+  scale_fill_flat() + theme_apa()
+
+#scale_fill_manual(values = c("dodgerblue4","dodgerblue3","dodgerblue2","deepskyblue1", "lightskyblue"), labels = c("50%", "75%", "85%", "95%", "100%"))+
+
+```
+
+To better visualize the data, we computed the delta plots for the effect of Priming (see Panel A in Figure \@ref(fig:Deltas_E1_Words)), as well as for the effect of Prime Duration (see Panel B in Figure \@ref(fig:Deltas_E1_Words)).
+These delta plots are residual quantile plots that show the size of the effect for the .1, .3, .5, .7, and .9 response time quantiles.
+
+(ref:Deltas_E1_Words-caption) Delta in Experiment 1...EXPLAIN.
+
+```{r Deltas_E1_Words, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)"}
+
+E1<- exp1_data_to_include%>% 
+  filter(rt > 250 & rt < 2000)%>%
+  select(participant, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target, corr, rt)%>%
+  mutate(participant=factor(participant),
+         TrialID = factor(TrialID))
+
+quibble <- function(x, q = seq(.1, .9, .2)) {
+  tibble(x = quantile(x, q), q = q)
+}
+
+E1 %>%
+  group_by(participant, StimulusType, Condition, PrimeDuration,corr) %>%
+  summarise(RT = list(quibble(rt, seq(.1, .9, .2)))) %>% 
+  tidyr::unnest(RT) -> data.E1.quantiles
+
+data.E1.quantiles %>%
+  filter(corr==1) %>%
+  select(-corr) %>%
+  group_by(StimulusType,PrimeDuration,Condition,q) %>%
+  summarize(RT=mean(x))%>%
+  ungroup()-> vincentiles.E1
+
+#Priming Effect (unrelated - identity):
+
+vincentiles.E1 %>%
+  filter(StimulusType == "Word")%>%
+  arrange(desc(Condition))%>%
+  group_by(PrimeDuration,q) %>%
+  summarize(MRT=mean(RT),
+            Delta=diff(rev(RT)))%>%
+  ungroup()%>%
+ggplot(aes(y=Delta, x=MRT)) +
+  geom_line(size = .75)+
+  geom_point(size = 2)+
+  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
+  ylim(-60, +60)+
+  xlim(450, 850)+
+  xlab("Mean RT per quantile")+
+  ylab("Effect (in ms)")+
+  ggtitle("Priming Effect")+
+  facet_wrap(~PrimeDuration)+
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12),
+        axis.text=element_text(size=10),
+        axis.title=element_text(size=10))-> DeltaE1.PrimingEffect.W
+
+#Prime Duration Effect (33ms - 50 ms):
+
+vincentiles.E1 %>%
+  filter(StimulusType == "Word")%>%
+  group_by(Condition,q) %>%
+  summarize(MRT=mean(RT),
+            Delta=diff(rev(RT)))%>%
+  ggplot(aes(y=Delta, x=MRT)) +
+  geom_line(size = .75)+
+  geom_point(size = 2)+
+  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
+  ylim(-60, +60)+
+  xlim(450, 850)+
+  xlab("Mean RT per quantile")+
+  ylab("Effect (in ms)")+
+  ggtitle("Prime duration effect")+
+  facet_wrap(~ Condition)+
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12),
+        axis.text=element_text(size=10),
+        axis.title=element_text(size=10))-> DeltaE1.PrimeDurationEffect.W
+
+cowplot::plot_grid(DeltaE1.PrimingEffect.W,
+                   DeltaE1.PrimeDurationEffect.W,
+                   ncol = 1,
+                   labels = c("A", "B"))+
+  plot_annotation(title = "Experiment 1: 33 vs. 50 ms",
+                  theme = theme(plot.title = element_text(size = 14)))
+
 ```
@@
 A further `r exp2_participants_to_exclude %>% filter(N == 480 & acc < .8) %>% nrow %>% ifelse(.
-< 11, numbers_to_words(.), .)` were excluded because of low accuracy (less than .8).
+< 11, numbers_to_words(.), .)` were excluded because of low accuracy (again, less than .8).
 The remaining `r exp2_actual_participants$PROLIFIC_PID %>% unique %>% length` participants were aged from `r exp2_participant_ages %>% min` to `r exp2_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
 Of the participants, `r exp2_male_participants_nr` identified as male, `r exp2_female_participants_nr` identified as female, and `r exp2_other_participants_nr` identified as other.
-The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions.
+All these participants indicated that English was their first language in the Prolific screening questions.
 Based on their IP addresses, `r exp2_participant_countries["United Kingdom"] %>% ifelse(.
@@
 `r exp2_actual_participants$country %>% is.na %>% sum %>% numbers_to_words %>% str_to_sentence()` participants could not be localized in this way.
-As in Experiment 1, participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour).
-All participants were naïve to the purpose of the experiment.
-Participants could use a desktop or laptop computer or a mobile device.
+As in Experiment 1, all participants were naïve to the purpose of the experiment, and received £1.25 for their participation (corresponding to £5/hour).
+Participants could use either a desktop/laptop computer or a mobile device.
 Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
@@
 Otherwise, the model specifications were identical to those in Experiment 1.
+W
 
@@
 
+We also created the delta plots for the effect of Priming (see Panel A in Figure \@ref(fig:Deltas_E2_Words)), as well as for the effect of Prime Duration (see Panel B in Figure \@ref(fig:Deltas_E2_Words)).
+
+(ref:Deltas_E2_Words-caption) Delta in Experiment 2...EXPLAIN.
+
+```{r Deltas_E2_Words, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)"}
+
+E2<- exp2_data_to_include%>% 
+  filter(rt > 250 & rt < 2000)%>%
+  select(participant, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target, corr, rt)%>%
+  mutate(participant=factor(participant),
+         TrialID = factor(TrialID))
+
+E2 %>%
+  group_by(participant, StimulusType, Condition, PrimeDuration,corr) %>%
+  summarise(RT = list(quibble(rt, seq(.1, .9, .2)))) %>% 
+  tidyr::unnest(RT) -> data.E2.quantiles
+
+data.E2.quantiles %>%
+  filter(corr==1) %>%
+  select(-corr) %>%
+  group_by(StimulusType,PrimeDuration,Condition,q) %>%
+  summarize(RT=mean(x))%>%
+  ungroup()-> vincentiles.E2
+
+#Priming Effect (unrelated - identity):
+
+vincentiles.E2 %>%
+  filter(StimulusType == "Word")%>%
+  arrange(desc(Condition))%>%
+  group_by(PrimeDuration,q) %>%
+  summarize(MRT=mean(RT),
+            Delta=diff(rev(RT)))%>%
+  ungroup()%>%
+ggplot(aes(y=Delta, x=MRT)) +
+  geom_line(size = .75)+
+  geom_point(size = 2)+
+  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
+  ylim(-60, +60)+
+  xlim(450, 850)+
+  xlab("Mean RT per quantile")+
+  ylab("Effect (in ms)")+
+  ggtitle("Priming Effect")+
+  facet_wrap(~PrimeDuration)+
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12),
+        axis.text=element_text(size=10),
+        axis.title=element_text(size=10))-> DeltaE2.PrimingEffect.W
+
+#Prime Duration Effect (16ms - 33 ms):
+
+vincentiles.E2 %>%
+  filter(StimulusType == "Word")%>%
+  group_by(Condition,q) %>%
+  summarize(MRT=mean(RT),
+            Delta=diff(rev(RT)))%>%
+  ggplot(aes(y=Delta, x=MRT)) +
+  geom_line(size = .75)+
+  geom_point(size = 2)+
+  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
+  ylim(-60, +60)+
+  xlim(450, 850)+
+  xlab("Mean RT per quantile")+
+  ylab("Effect (in ms)")+
+  ggtitle("Prime duration effect")+
+  facet_wrap(~ Condition)+
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12),
+        axis.text=element_text(size=10),
+        axis.title=element_text(size=10))-> DeltaE2.PrimeDurationEffect.W
+
+cowplot::plot_grid(DeltaE2.PrimingEffect.W,
+                   DeltaE2.PrimeDurationEffect.W,
+                   ncol = 1,
+                   labels = c("A", "B"))+
+  plot_annotation(title = "Experiment 2: 16 vs. 33 ms",
+                  theme = theme(plot.title = element_text(size = 14)))
+
+```
+
 ## Discussion

### 2021-05-06 Manuscript_intro_method_results_AB.Rmd
Added Onedrive links

@@
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
+
 load("blmm_exp1_rt_dist_full_ranef_5000.RData")
-# model name is blmm_exp1_rt
+# This file does not fit on GitHub
+# Download it at https://1drv.ms/u/s!ApE7JQmoH0baocARuxg21SFrS4riyg?e=8ZgbHA
+# model name is blmm_exp1_rt_dist
 
@@
 load("blmm_exp1_acc_new_10000.RData")
+
+# This file does not fit on GitHub
+# Download it at https://1drv.ms/u/s!ApE7JQmoH0baobQPat43HR3ixhuqww?e=VySttd
 
@@
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
-load("blmm_exp2_rt_dist.RData")
+load("blmm_exp2_rt_dist_full_ranef_5000.RData")
+# this file doesn't fit on GitHub
+# download it at https://1drv.ms/u/s!ApE7JQmoH0baocIO3qh2TNb_TlqvlA?e=q3vJml
 # model name is blmm_exp2_rt
@@
 load("blmm_exp2_acc_new_10000.RData")
+
+# This file doesn't fit on GitHub
+# Download it at https://1drv.ms/u/s!ApE7JQmoH0baobF4qRyXSfOymglf_g?e=0JGhre
 

### 2021-05-06 Manuscript_intro_method_results_AB.Rmd
new variable name for hdi plots
Changes to get the AB.Rmd to knit

@@
 csl               : "apa.csl"
-documentclass     : "apa7"
+documentclass     : "apa6"
 classoption       : "man"
@@
 library("papaja")
-library(ggplot2)
 library(patchwork)
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(error = TRUE)
 ```
@@
 
-del_hdi_exp1_rt = hdi(blmm_exp1_rt, ci = c(0.5, 0.75, 0.89, 0.95))
+del_hdi_exp1_rt = hdi(blmm_exp1_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
 
@@
   group_by(StimulusType, PrimeDuration, Condition) %>%
-  summarize(
+  summarize(a
     Mean = mean(rt)
@@
 
-del_hdi_exp2_rt = hdi(blmm_exp2_rt, ci = c(0.5, 0.75, 0.89, 0.95))
+#del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
 # brms (like any other lm-like function) automatically adds a "1" to the parameter name (for the contrast)
@@
 #del_hdi_exp2_rt$Parameter <- del_hdi_exp2_rt$Parameter %>% gsub(pattern = "[[:digit:]]", replacement = "")
-plot(del_hdi_exp2_rt) + scale_fill_flat() + theme_apa()
+#plot(del_hdi_exp2_rt_dist) + scale_fill_flat() + theme_apa()
 ```

### 2021-05-06 Manuscript_intro_method_results_AB.Rmd
Fix typo

@@
   group_by(StimulusType, PrimeDuration, Condition) %>%
-  summarize(a
+  summarize(
     Mean = mean(rt)

### 2021-05-06 Manuscript_intro_method_results_AB.Rmd
Update Manuscript_intro_method_results_AB.Rmd

@@
 
-\color{red}ADD at some point:
-
-    - Hypotheses in a figure (as in Gomez & Perea, 2020).
-
-\color{black}
+\color{red} ADD: Hypotheses -> Model -> Data in a figure. \color{black}
 
@@
 
-#### Rationale for sample size and stopping rule
-
-@brysbaert2018 recommended that masked priming experiments should have at least 1,600 observations per condition.
+***Rationale for sample size and stopping rule.*** @brysbaert2018 recommended that masked priming experiments should have at least 1,600 observations per condition.
 In order to account for potentially smaller effect sizes in an online experiment, we set a target of 3,000 observations per condition (12,000 observations total), which corresponds to a minimum of 50 participants given that there were 240 word stimuli in the experiment (see below).
@@
 We consider an effect as credible if the 95% credible interval (CrI) estimated from the posterior distribution does not contain zero.
-
 In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.
@@
 
-(ref:exp1-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 1 for words and nonwords and by prime duration and priming condition.
+(ref:exp1-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 1 for each condition.
 
-```{r exp1-descriptive-rt-table, as.is = TRUE,echo=FALSE}
+```{r exp1-descriptive-rt-table, as.is = TRUE,echo=FALSE, warning=FALSE, message=FALSE}
 #load raw Exp1 data
@@
   , caption = "(ref:exp1-descriptives-rt-table-caption)"
-  , note = "Trials with reaction times below 250 ms were excluded from the analysis. For the calculation of response times, incorrect responses were also removed."
   , escape = TRUE
@@
 
-```{r exp1-blmm-table, echo=FALSE, as.is = TRUE}
+```{r exp1-blmm-table, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
@@
 
-(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the parameters of the response time model in Experiment 1.
+(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 1.
 
-```{r exp1-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)"}
+```{r exp1-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)", warning=FALSE, message=FALSE}
 
@@
 
-plot(del_hdi_exp1_rt) +
-  scale_fill_flat() + theme_apa()
+del_hdi_exp1_rt%>%
+  filter(!grepl("beta",Parameter)) -> posteriorsToPlot
 
-#scale_fill_manual(values = c("dodgerblue4","dodgerblue3","dodgerblue2","deepskyblue1", "lightskyblue"), labels = c("50%", "75%", "85%", "95%", "100%"))+
+plot(posteriorsToPlot) +
+  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
+  ylab("")+
+  theme_apa() -> Plot_post_E1
+
+Plot_post_E1
 
@@
 
-To better visualize the data, we computed the delta plots for the effect of Priming (see Panel A in Figure \@ref(fig:Deltas_E1_Words)), as well as for the effect of Prime Duration (see Panel B in Figure \@ref(fig:Deltas_E1_Words)).
+To better visualize the data, we computed the delta plots for the effect of Priming (see Panel A in
+Figure \@ref(fig:Deltas_E1_Words) ), as well as for the effect of Prime Duration (see Panel B in Figure \@ref(fig:Deltas_E1_Words) ).
 These delta plots are residual quantile plots that show the size of the effect for the .1, .3, .5, .7, and .9 response time quantiles.
 
-(ref:Deltas_E1_Words-caption) Delta in Experiment 1...EXPLAIN.
-
-```{r Deltas_E1_Words, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)"}
+```{r Deltas_E1_Words, echo=FALSE, cache=TRUE, fig.cap = "Delta in Experiment 1...EXPLAIN.", message=FALSE, warning=FALSE}
 
@@
 
-```{r exp1-acc-blmm-table, echo=FALSE, as.is = TRUE}
+```{r exp1-acc-blmm-table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
 
@@
 
-#### Rationale for sample size and stopping rule
-
-As in Experiment 1, our stopping rule was to keep collecting data until 3,000 valid observations were collected. This goal was met and exceeded in our initial data collection with a budget of £200.
+***Rationale for sample size and stopping rule.*** As in Experiment 1, our stopping rule was to keep collecting data until 3,000 valid observations were collected.
+This goal was met and exceeded in our initial data collection with a budget of £200.
 
@@
 Otherwise, the model specifications were identical to those in Experiment 1.
-W
+SAY SOMETHING ABOUT THE DELTAS
 
@@
 
+The model indicates that response times were higher in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]), although across the two prime duration conditions, the effect was much smaller than in Experiment 1.
+Response times were also higher in the 16 ms than in the 33 ms prime duration condition (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]) although, as the interaction effect shows, this was mainly due to an absence of the priming effect in the 16 ms prime duration condition, as opposed to the 33 ms condition, which showed a robust priming effect (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+Figure \@ref(fig:exp2-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
+
 (ref:exp2-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 2 for words and nonwords and by prime duration and priming condition.
 
-```{r exp2-descriptive-rt-table, as.is = TRUE,echo=FALSE}
+```{r exp2-descriptive-rt-table, as.is = TRUE,echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r load_exp2_brms_data, echo=FALSE, as.is = TRUE}
+```{r load_exp2_brms_data, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
@@
 
-The model indicates that response times were higher in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]), although across the two prime duration conditions, the effect was much smaller than in Experiment 1.
-Response times were also higher in the 16 ms than in the 33 ms prime duration condition (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]) although, as the interaction effect shows, this was mainly due to an absence of the priming effect in the 16 ms prime duration condition, as opposed to the 33 ms condition, which showed a robust priming effect (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-Figure \@ref(fig:exp2-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
+(ref:exp2-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 2.
 
-(ref:exp2-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the parameters of the response time model in Experiment 2.
+```{r exp2-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp2-brms-rt-plot-caption)", message=FALSE, warning=FALSE}
 
-```{r exp2-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp2-brms-rt-plot-caption)"}
+del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
 
-#del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
-# brms (like any other lm-like function) automatically adds a "1" to the parameter name (for the contrast)
-# get rid of the ones (and any other numbers) by using gsub 
-#del_hdi_exp2_rt$Parameter <- del_hdi_exp2_rt$Parameter %>% gsub(pattern = "[[:digit:]]", replacement = "")
-#plot(del_hdi_exp2_rt_dist) + scale_fill_flat() + theme_apa()
+del_hdi_exp2_rt%>%
+  filter(!grepl("beta",Parameter)) -> posteriorsToPlotE2
+
+plot(posteriorsToPlotE2) +
+  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
+  ylab("")+
+  theme_apa() -> Plot_post_E2
+
+Plot_post_E2
+
 ```
@@
 
-```{r exp2_acc_brms_table, echo=FALSE, as.is = TRUE}
+```{r exp2_acc_brms_table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
 

### 2021-05-11 Manuscript_intro_method_results_AB.Rmd
Update Manuscript_intro_method_results_AB.Rmd

@@
 If we do observe a large effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments.
-Keep in mind that we are using a software that has good control over the exposure duration [@bridges2020; @anwyl-irvine2020a].All in all, replicating the results observed in controlled laoboratory masked primiming studies would provide some grounds to the validity of online masked priming tasks,even with no control over many variables (e.g., the devices in which the experiment is run, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
-
-\color{red} ADD: Hypotheses -> Model -> Data in a figure. \color{black}
+Keep in mind that we are using a software that has good control over the exposure duration [@bridges2020; @anwyl-irvine2020a].
+Figure \ref{fig:hyp-mod-dat-figure} displays the link between all these verbal hypotheses, the process model that corresponds to each of them, and their predictions in the response time distributions.
+
+```{r hyp-mod-dat-figure, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE, fig.height=3.4, fig.cap = "Add caption"}
+suppressMessages(library("tidyverse"))
+
+#pdf("Fig1_ModelsToData.pdf", height = 3)
+
+par(mfrow=c(1,3))
+tdp   <- .386
+sd.dp <- .100
+
+nsims <- 1000000
+
+slope.gray  <- 0.00001
+slope.blue   <- rnorm(nsims, 3, .6)
+slope.yellow <- rnorm(nsims, 3, .6)
+
+sim.trials.blue<-matrix(ncol=4, nrow=nsims)
+sim.trials.yellow<-matrix(ncol=4, nrow=nsims)
+
+sim.trials.blue[,1]    <-  rep(tdp+.05, nsims)
+sim.trials.yellow[,1]  <-  rep(tdp+.05, nsims)
+
+sim.trials.blue[ ,2]   <- (slope.gray * sim.trials.blue[,1])
+sim.trials.yellow[ ,2] <- (slope.gray * sim.trials.yellow[,1])
+
+sim.trials.blue[ ,3]   <- (sim.trials.blue[,2] - slope.blue * sim.trials.blue[,1])
+sim.trials.yellow[ ,3] <- (sim.trials.yellow[,2] - slope.yellow * sim.trials.yellow[,1])
+
+sim.trials.blue[ ,4]   <- (1 - sim.trials.blue[,3]) / slope.blue
+sim.trials.yellow[ ,4] <- (1 - sim.trials.yellow[,3]) / slope.yellow
+
+nlines<- 1000
+sample.blue <- sample(1:nsims,nlines)
+sample.yellow <- sample(1:nsims,nlines)
+
+plot(c(rep(0,nlines),sim.trials.blue[sample.blue,1]), c(rep(.02,nlines),.02+sim.trials.blue[sample.blue,2]), type="l", col=alpha("dodgerblue2",alpha = .5), ylim = c(0,1.7), xlim=c(0,1.2), bty="n",yaxt='n', xlab="RT (sec)", ylab="", lwd=3)
+
+lines(c(rep(0,nlines),sim.trials.yellow[sample.yellow,1]), c(rep(0,nlines),sim.trials.yellow[sample.yellow,2]), type="l", col=alpha("deeppink2",alpha = .5), lwd=3)
+
+for(i in 1:nlines){
+    lines(c(sim.trials.blue[sample.blue[i],1], sim.trials.blue[sample.blue[i],4]), c(sim.trials.blue[sample.blue[i],2], 1), col=alpha("dodgerblue2",alpha = .005),lwd=2)
+
+    lines(c(sim.trials.yellow[sample.yellow[i],1], sim.trials.yellow[sample.yellow[i],4]), c(sim.trials.yellow[sample.yellow[i],2], 1), col=alpha("deeppink2",alpha = .005), lwd=2)
+}
+
+lines(density(sim.trials.yellow[,4], from=.4,to=1.5)$x,(density(sim.trials.yellow[,4],, from=.4,to=1.5)$y)/20+1, col=alpha("deeppink2",alpha = 1), lwd=1)
+lines(density(sim.trials.blue[,4], from=.4,to=1.5)$x,(density(sim.trials.blue[,4], from=.4,to=1.5)$y)/20+1, col=alpha("dodgerblue2",alpha = .3),lwd=4)
+
+lines(c(0, 1), c(1,1), lwd=1.5)
+
+lines(c(tdp, tdp), c(0,1), lty=2)
+lines(c(tdp+.05, tdp+.05), c(0,1), lty=2)
+
+text("Evidence\naccumulations",x = .88, y=.4,cex=.8)
+text("Encoding",x = .2, y=.4,cex=.8)
+title("Null Effect")
+
+###########################################################################
+
+tdp   <- .386
+sd.dp <- .100
+
+nsims <- 1000000
+
+slope.gray  <- 0.00001
+slope.blue   <- rnorm(nsims, 3, .6)
+slope.yellow <- rnorm(nsims, 3, .6)
+
+sim.trials.blue<-matrix(ncol=4, nrow=nsims)
+sim.trials.yellow<-matrix(ncol=4, nrow=nsims)
+
+sim.trials.blue[,1]    <-  rep(tdp, nsims)
+sim.trials.yellow[,1]  <-  rep(tdp+.05, nsims)
+
+sim.trials.blue[ ,2]   <- (slope.gray * sim.trials.blue[,1])
+sim.trials.yellow[ ,2] <- (slope.gray * sim.trials.yellow[,1])
+
+sim.trials.blue[ ,3]   <- (sim.trials.blue[,2] - slope.blue * sim.trials.blue[,1])
+sim.trials.yellow[ ,3] <- (sim.trials.yellow[,2] - slope.yellow * sim.trials.yellow[,1])
+
+sim.trials.blue[ ,4]   <- (1 - sim.trials.blue[,3]) / slope.blue
+sim.trials.yellow[ ,4] <- (1 - sim.trials.yellow[,3]) / slope.yellow
+
+nlines<- 1000
+sample.blue <- sample(1:nsims,nlines)
+sample.yellow <- sample(1:nsims,nlines)
+
+plot(c(rep(0,nlines),sim.trials.blue[sample.blue,1]), c(rep(.02,nlines),.02+sim.trials.blue[sample.blue,2]), type="l", col=alpha("dodgerblue2",alpha = .5), ylim = c(0,1.7), xlim=c(0,1.2), bty="n",yaxt='n', xlab="RT (sec)", ylab="", lwd=3)
+
+lines(c(rep(0,nlines),sim.trials.yellow[sample.yellow,1]), c(rep(0,nlines),sim.trials.yellow[sample.yellow,2]), type="l", col=alpha("deeppink2",alpha = .5), lwd=3)
+
+for(i in 1:nlines){
+    lines(c(sim.trials.blue[sample.blue[i],1], sim.trials.blue[sample.blue[i],4]), c(sim.trials.blue[sample.blue[i],2], 1), col=alpha("dodgerblue2",alpha = .006),lwd=2)
+
+    lines(c(sim.trials.yellow[sample.yellow[i],1], sim.trials.yellow[sample.yellow[i],4]), c(sim.trials.yellow[sample.yellow[i],2], 1), col=alpha("deeppink2",alpha = .006), lwd=2)
+
+}
+
+lines(density(sim.trials.yellow[,4], from=.4,to=1.5)$x,(density(sim.trials.yellow[,4],, from=.4,to=1.5)$y)/20+1, col=alpha("deeppink2",alpha = .7), lwd=2)
+lines(density(sim.trials.blue[,4], from=.4,to=1.5)$x,(density(sim.trials.blue[,4], from=.4,to=1.5)$y)/20+1, col=alpha("dodgerblue2",alpha = .7),lwd=2)
+
+lines(c(0, 1), c(1,1), lwd=1.5)
+
+lines(c(tdp, tdp), c(0,1), lty=2)
+lines(c(tdp+.05, tdp+.05), c(0,1), lty=2)
+
+text("Evidence\naccumulations",x = .88, y=.4,cex=.8)
+text("Encoding",x = .2, y=.4,cex=.8)
+
+title("Effect in\nencoding")
+
+#############################################################################
+
+tdp   <- .386
+sd.dp <- .100
+
+nsims <- 1000000
+
+slope.gray  <- 0.00001 
+slope.blue   <- rnorm(nsims, 3.8, .6)
+slope.yellow <- rnorm(nsims, 3, .6)
+
+sim.trials.blue<-matrix(ncol=4, nrow=nsims)
+sim.trials.yellow<-matrix(ncol=4, nrow=nsims)
+
+sim.trials.blue[,1]    <-  rep(tdp, nsims)
+sim.trials.yellow[,1]  <-  rep(tdp+.05, nsims)
+
+sim.trials.blue[ ,2]   <- (slope.gray * sim.trials.blue[,1])
+sim.trials.yellow[ ,2] <- (slope.gray * sim.trials.yellow[,1])
+
+sim.trials.blue[ ,3]   <- (sim.trials.blue[,2] - slope.blue * sim.trials.blue[,1])
+sim.trials.yellow[ ,3] <- (sim.trials.yellow[,2] - slope.yellow * sim.trials.yellow[,1])
+
+sim.trials.blue[ ,4]   <- (1 - sim.trials.blue[,3]) / slope.blue
+sim.trials.yellow[ ,4] <- (1 - sim.trials.yellow[,3]) / slope.yellow
+
+nlines<- 1000
+
+sample.blue <- sample(1:nsims,nlines)
+sample.yellow <- sample(1:nsims,nlines)
+
+plot(c(rep(0,nlines),sim.trials.blue[sample.blue,1]), c(rep(.02,nlines),.02+sim.trials.blue[sample.blue,2]), type="l", col=alpha("dodgerblue2",alpha = .5), ylim = c(0,1.7), xlim=c(0,1.2), bty="n",yaxt='n', xlab="RT (sec)", ylab="", lwd=3)
+
+lines(c(rep(0,nlines),sim.trials.yellow[sample.yellow,1]), c(rep(0,nlines),sim.trials.yellow[sample.yellow,2]), type="l", col=alpha("deeppink2",alpha = .5), lwd=3)
+
+for(i in 1:nlines){
+    lines(c(sim.trials.blue[sample.blue[i],1], sim.trials.blue[sample.blue[i],4]), c(sim.trials.blue[sample.blue[i],2], 1), col=alpha("dodgerblue2",alpha = .006),lwd=2)
+
+    lines(c(sim.trials.yellow[sample.yellow[i],1], sim.trials.yellow[sample.yellow[i],4]), c(sim.trials.yellow[sample.yellow[i],2], 1), col=alpha("deeppink2",alpha = .006), lwd=2)
+
+}
+
+lines(density(sim.trials.yellow[,4], from=.4,to=1.5)$x,(density(sim.trials.yellow[,4],, from=.4,to=1.5)$y)/20+1, col=alpha("deeppink2",alpha = .7), lwd=2)
+lines(density(sim.trials.blue[,4], from=.4,to=1.5)$x,(density(sim.trials.blue[,4], from=.4,to=1.5)$y)/20+1, col=alpha("dodgerblue2",alpha = .7),lwd=2)
+
+lines(c(0, 1), c(1,1), lwd=1.5)
+
+lines(c(tdp, tdp), c(0,1), lty=2)
+lines(c(tdp+.05, tdp+.05), c(0,1), lty=2)
+
+text("Evidence\naccumulations",x = .88, y=.4,cex=.8)
+text("Encoding",x = .2, y=.4,cex=.8)
+
+title("Effect in encoding and \nevidence accumulation")
+
+#dev.off()
+
+```
+
+All in all, replicating the results observed in controlled laoboratory masked primiming studies would provide some grounds to the validity of online masked priming tasks,even with no control over many variables (e.g., the devices in which the experiment is run, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
 
@@
 *REGION*).
-Participants were instructed to respond to the target stimulus as quickly as possible either by using the keyboard, if their device had one, and pressing the "Z" key if the target was not a valid English word or the "M" key if the target was a valid English word.
+Participants were instructed to respond to the target stimulus as quickly as possible either by using the keyboard, if their device had one, by pressing the "Z" key if the target was not a valid English word or the "M" key if the target was a valid English word.
 Participants on a device without a keyboard were instructed to respond by touching one of two rectangular touch areas labeled "Z = Non-word" (presented at -0.4, -0.3) and "M = Word" (presented at 0.4, -0.3).
@@
 We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items.
-We used the ex-Gaussian distribution to model response times and the Bernoulli distribution (with a logit link) to model response accuracy.
+We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component $\mu$ and the scale parameter of the exponential component $\beta$ (equalling the inverse of the rate parameter $\lambda$) being allowed to vary between conditions.
+To model response accuracy, we used the Bernoulli distribution with a logit link.
 We used the default priors suggested by *brms* except for the coefficients for the fixed effects, for which we applied weakly informative priors of $\beta \sim N(0,100)$ in order to rule out improbably large effect sizes.
-Each model was fitted using four chains with 5000 iterations each (1000 warmup iterations).
+Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warmup iterations for the accuracy models).
 We consider an effect as credible if the 95% credible interval (CrI) estimated from the posterior distribution does not contain zero.
@@
     "Intercept ($\\beta$)",
-    "Condition ($\\mu$)",
+    "Relatedness ($\\mu$)",
     "Prime Duration ($\\mu$)",
-    "Condition:Prime Duration ($\\mu$)",
-    "Condition ($\\beta$)",
+    "Relatedness:Prime Duration ($\\mu$)",
+    "Relatedness ($\\beta$)",
     "Prime Duration ($\\beta$)",
-    "Condition:Prime Duration ($\\beta$)"
+    "Relatedness:Prime Duration ($\\beta$)"
     )
@@
 
-The RT model indicates that response times were higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]) and higher in the 33 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
-The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-Figure \@ref(fig:exp1-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
-
-(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 1.
+The RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]).
+For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
+However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33 ms condition, but only a negligible effect in the 16 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+Once again, the shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1","u-95% CI"]`]).
+However, the 50 ms prime exposure duration (*b* = `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]) seems to be associated with a slightly lower $\beta$, i.e., a slightly weaker right skew of the distribution, than the 33 ms condition.
+On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]).
+
+<!---  Figure \@ref(fig:exp1-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
+
+(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 1. -->
 
@@
 
-del_hdi_exp1_rt = hdi(blmm_exp1_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
-
-del_hdi_exp1_rt%>%
-  filter(!grepl("beta",Parameter)) -> posteriorsToPlot
-
-plot(posteriorsToPlot) +
-  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
-  ylab("")+
-  theme_apa() -> Plot_post_E1
-
-Plot_post_E1
-
-```
-
-To better visualize the data, we computed the delta plots for the effect of Priming (see Panel A in
-Figure \@ref(fig:Deltas_E1_Words) ), as well as for the effect of Prime Duration (see Panel B in Figure \@ref(fig:Deltas_E1_Words) ).
-These delta plots are residual quantile plots that show the size of the effect for the .1, .3, .5, .7, and .9 response time quantiles.
-
-```{r Deltas_E1_Words, echo=FALSE, cache=TRUE, fig.cap = "Delta in Experiment 1...EXPLAIN.", message=FALSE, warning=FALSE}
+# del_hdi_exp1_rt = hdi(blmm_exp1_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
+# 
+# del_hdi_exp1_rt%>%
+#   filter(!grepl("beta",Parameter)) -> posteriorsToPlot
+# 
+# plot(posteriorsToPlot) +
+#   scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
+#   ylab("")+
+#   theme_apa() -> Plot_post_E1
+# 
+# Plot_post_E1
+
+```
+
+These results can be visualized in the delta plots depicted in Figure \ref{fig:deltas-e1-words}.
+Delta plots are residual quantile plots that show the distributional differences between conditions [@de1994conditional].
+As can be seen in Panel A, there is a priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33ms one.
+There is an increase of said effect for the longest responses (quantile .9) in the 33ms prime duration condition that can be understood by looking at Panel B of the same figure.
+In this panel, we show the size of the prime duration effect (computed as the difference in response times between responses to the 50 ms condition and responses to the 33 ms condition) across RT quantiles.
+While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition generated an effect only for very long responses.
+
+```{r deltas-e1-words, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE, cache=TRUE, fig.cap = "Add caption 2"}
 
@@
 ggplot(aes(y=Delta, x=MRT)) +
-  geom_line(size = .75)+
-  geom_point(size = 2)+
+  geom_line(size = .7)+
+  geom_point(size = 1.7)+
   geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
@@
   theme(plot.title = element_text(size = 12),
-        axis.text=element_text(size=10),
-        axis.title=element_text(size=10))-> DeltaE1.PrimingEffect.W
+        axis.text=element_text(size=9),
+        axis.title=element_text(size=9))-> DeltaE1.PrimingEffect.W
 
@@
   ggplot(aes(y=Delta, x=MRT)) +
-  geom_line(size = .75)+
-  geom_point(size = 2)+
+  geom_line(size = .7)+
+  geom_point(size = 1.7)+
   geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
@@
   theme(plot.title = element_text(size = 12),
-        axis.text=element_text(size=10),
-        axis.title=element_text(size=10))-> DeltaE1.PrimeDurationEffect.W
+        axis.text=element_text(size=9),
+        axis.title=element_text(size=9))-> DeltaE1.PrimeDurationEffect.W
 
@@
                    labels = c("A", "B"))+
-  plot_annotation(title = "Experiment 1: 33 vs. 50 ms",
-                  theme = theme(plot.title = element_text(size = 14)))
+  plot_annotation(theme = theme(plot.title = element_text(size = 14)))
 
@@
 We also saw a clear difference between the 33 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices.
-We did not observe an effect of either the priming condition or the prime exposure duration on the shape parameter $\beta$ of the exponential distribution, suggesting, according to the savings hypothesis by @forster1998pros, that only encoding processes were affected.
+While the shape of the distribution changed slightly between the 33.3 ms and the 50 ms prime exposure durations, we did not observe an effect of the prime relatedness condition on the shape parameter $\beta$ of the exponential distribution, suggesting, according to the savings hypothesis by @forster1998pros, that only encoding processes were affected by the relatedness manipulation.
 
@@
 Otherwise, the model specifications were identical to those in Experiment 1.
-SAY SOMETHING ABOUT THE DELTAS
-
-## Results
-
-The model indicates that response times were higher in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]), although across the two prime duration conditions, the effect was much smaller than in Experiment 1.
-Response times were also higher in the 16 ms than in the 33 ms prime duration condition (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]) although, as the interaction effect shows, this was mainly due to an absence of the priming effect in the 16 ms prime duration condition, as opposed to the 33 ms condition, which showed a robust priming effect (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-Figure \@ref(fig:exp2-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
 
@@
 
+## Results
+
+### Response times
+
+As in Experiment 1, the RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]) and higher in the 33 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
+The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1","u-95% CI"]`]), prime exposure duration (*b* = `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]), or their interaction (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
+
+<!--- Figure \@ref(fig:exp2-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
+
  (ref:exp2-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 2.
+-->
 
@@
 
-del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
-
-del_hdi_exp2_rt%>%
-  filter(!grepl("beta",Parameter)) -> posteriorsToPlotE2
-
-plot(posteriorsToPlotE2) +
-  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
-  ylab("")+
-  theme_apa() -> Plot_post_E2
-
-Plot_post_E2
-
-```
-
-(ref:exp2-blmm-accuracy-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for response accuracy on word trials in Experiment 2.
-
-```{r exp2_acc_brms_table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
-
-load("blmm_exp2_acc_new_10000.RData")
-
-# This file doesn't fit on GitHub
-# Download it at https://1drv.ms/u/s!ApE7JQmoH0baobF4qRyXSfOymglf_g?e=0JGhre
-
-blmm_exp2_summary_acc <- summary(blmm_exp2_acc)
-
-blmm_exp2_acc_fixed_for_print <- blmm_exp2_summary_acc$fixed
-
-parameter_names <- c(
-    "Intercept",
-    "Condition",
-    "Prime Duration",
-    "Condition:Prime Duration"
-    )
-
-blmm_exp2_acc_fixed_for_print <- blmm_exp2_acc_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
-  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
-  dplyr::select(-ends_with("ESS"))
-
-write.csv(blmm_exp2_acc_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
-
-apa_table(
-    blmm_exp2_acc_fixed_for_print,
-    placement = "H",
-    align = c("c", "c", "c", "c", "c"),
-    caption = "(ref:exp2-blmm-accuracy-table-caption)",
-    note = NULL,
-    small = TRUE,
-    digits = 3,
-    escape = FALSE
-    )
-
-```
-
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1","u-95% CI"]`]).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16 ms prime duration condition than in the 33 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp2_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
-The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33 ms condition, and reversed in the 16 ms condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]), although the effect in the 16 ms condition was very weak.
-
-We also created the delta plots for the effect of Priming (see Panel A in Figure \@ref(fig:Deltas_E2_Words)), as well as for the effect of Prime Duration (see Panel B in Figure \@ref(fig:Deltas_E2_Words)).
-
-(ref:Deltas_E2_Words-caption) Delta in Experiment 2...EXPLAIN.
-
-```{r Deltas_E2_Words, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)"}
+#del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
+
+#del_hdi_exp2_rt%>%
+#  filter(!grepl("beta",Parameter)) -> posteriorsToPlotE2
+
+#plot(posteriorsToPlotE2) +
+#  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
+#  ylab("")+
+#  theme_apa() -> Plot_post_E2
+
+#Plot_post_E2
+
+```
+
+We also created the delta plots of data from Experiment 2 (see Figure \ref{fig:deltas-e2-words}).
+Panel A, shows there is no priming effect for the 16 ms condition, but a consistent effect across quantiles for the 33ms condition (parallel to the one found in Experiment 1).
+Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight a slight hindering for unrelated primes.
+
+```{r deltas-e2-words, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.cap = "Add caption 3"}
 
 E2<- exp2_data_to_include%>%
-  filter(rt > 250 & rt < 2000)%>%
   select(participant, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target, corr, rt)%>%
@@
 
+#pdf("Fig_deltasE2.pdf", height = 5)
+
 cowplot::plot_grid(DeltaE2.PrimingEffect.W,
@@
                    labels = c("A", "B"))+
-  plot_annotation(title = "Experiment 2: 16 vs. 33 ms",
-                  theme = theme(plot.title = element_text(size = 14)))
-
-```
+  plot_annotation(theme = theme(plot.title = element_text(size = 14)))
+
+```
+
+### Accuracy
+
+(ref:exp2-blmm-accuracy-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for response accuracy on word trials in Experiment 2.
+
+```{r exp2_acc_brms_table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
+
+load("blmm_exp2_acc_new_10000.RData")
+
+# This file doesn't fit on GitHub
+# Download it at https://1drv.ms/u/s!ApE7JQmoH0baobF4qRyXSfOymglf_g?e=0JGhre
+
+blmm_exp2_summary_acc <- summary(blmm_exp2_acc)
+
+blmm_exp2_acc_fixed_for_print <- blmm_exp2_summary_acc$fixed
+
+parameter_names <- c(
+    "Intercept",
+    "Condition",
+    "Prime Duration",
+    "Condition:Prime Duration"
+    )
+
+blmm_exp2_acc_fixed_for_print <- blmm_exp2_acc_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
+  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
+  dplyr::select(-ends_with("ESS"))
+
+write.csv(blmm_exp2_acc_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
+
+apa_table(
+    blmm_exp2_acc_fixed_for_print,
+    placement = "H",
+    align = c("c", "c", "c", "c", "c"),
+    caption = "(ref:exp2-blmm-accuracy-table-caption)",
+    note = NULL,
+    small = TRUE,
+    digits = 3,
+    escape = FALSE
+    )
+
+```
+
+The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1","u-95% CI"]`]).
+The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16 ms prime duration condition than in the 33 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp2_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
+The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33 ms condition, and reversed in the 16 ms condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]), although the effect in the 16 ms condition was very weak.
 
@@
 This suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
-Again, we did not observe an effect of either the priming condition or the prime exposure duration on the shape parameter $\beta$ of the exponential distribution.
+Again, we did not observe an effect of the prime relatedness condition on the shape parameter $\beta$ of the exponential distribution, and, unlike in Experiment 1, there was no evidence for a difference in the shape of the distribution between the 16.7 and 33.3 ms prime duration conditions.
 

### 2021-05-13 Manuscript_intro_method_results_AB_MP.Rmd
Create Manuscript_intro_method_results_AB_MP.Rmd

--- 2021-05-11 Manuscript_intro_method_results_AB.Rmd
@@
     affiliation   : "2,3"
-  - name          : "Pablo Gomez"
+  - name          : "Pablo Gómez"
     affiliation   : "4"
@@
   - id            : "5"
-    institution   : "Universitat de Valencia, Valencia, Spain"
+    institution   : "Universitat de València, Valencia, Spain"
 authornote: |
@@
 From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., Psychopy) can present stimuli and collect responses on standard consumer devices with enough precision.
-In sum, these findings provide us with confidence that masked priming can be used online, thus allowing us to reach populations that are hard to test in a laboratory.
+In sum, these findings provide us with confidence that masked priming can be used online, thus allowing us to reach populations that are difficult to test in a laboratory.
 
@@
 
-Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition[see @forster1998pros; and @grainger2008cracking, for reviews].
+Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition [see @forster1998pros; and @grainger2008cracking, for reviews].
 Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond (e.g., "is *DOCTOR* a word?").
@@
 The masked priming paradigm has been used in a large number of studies over the last decades.
-For instance, a search of the expression "masked priming" in Google Scholar in March 2021 produced nearly 10,000 hits.
+For instance, a search of the expression "masked priming" in Google Scholar in May 2021 produced more than 10,000 hits.
 Virtually all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003.
-The issue we examine in the present paper is whether masked priming experiments can safely be conducted in an online setting.
-Even before the current exceptional situation due to the COVID pandemic, in which many labs around the world have been closed (or with minimal activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
+The issue we examine in the present paper is whether masked priming experiments can be safely conducted in an online setting.
+Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or with minimal activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
 Indeed, researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010].
 
-However, cognitive psychologists have been much slower in taking up online paradigms [see @cai2017accent;@eerland2013influence; @rodd2016impact; @vandeberg2012out , for some exceptions], often due to concerns about the validity of the results.
+However, cognitive psychologists have been much slower in taking up online paradigms [see @cai2017accent;@eerland2013influence; @rodd2016impact; @vandeberg2012out, for some exceptions], often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
@@
 There have been attempts to address these concerns.
-For example, a Web version of DMDX (webDMDX) was developed and showed promising results in a trial experiment [@witzelTestingViabilityWebDMDX2013].
+For example, @witzelTestingViabilityWebDMDX2013 developed a Web version of DMDX (webDMDX) showing  promising results in a trial experiment.
 However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a "true" online programming script that could be run inside of a browser.
@@
 Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
-As a consequence, the use of webDMDX in masked priming experiments has been rather limited so far [see @Alluhaybi_2020; @Dubey_2018 for exceptions].
+As a consequence, the use of webDMDX in masked priming experiments has been rather limited so far [see @Alluhaybi_2020; @Dubey_2018, for exceptions].
 
@@
 To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study.
-Importantly, we will do so using Psychopy/PsychoJS [@peirce2019] as it showed high precision and accuracy across the great majority of platforms [@bridges2020; @anwyl-irvine2020a], in addition to being an open-source software.
+Importantly, we will do so using PsychoPy/PsychoJS [@peirce2019] as it showed high precision and accuracy across the great majority of platforms [@bridges2020; @anwyl-irvine2020a], in addition to being an open-source software.
 
@@
 This outcome would indicate that the on-line masked priming studies reproduce a characteristic signature of laboratory masked priming studies.
-Alternatively, if the online presentation conditions lead to a greater actual exposure duration on the participant's device compared to that specified in our experiment, (e.g., prime durations are approximately 20 ms longer on average than programmed) then the 50 ms primes may no longer be masked, but may rather be consciously perceived.
+Alternatively, if the online presentation conditions lead to a greater actual exposure duration on the participant's device compared to that specified in our experiment, (e.g., prime durations are approximately 20 ms longer on average than programmed) then the 50 ms primes may no longer be adequately masked, but may rather be consciously perceived.
 If this is the case, the prime could affect not only the encoding, but also core decision processes (i.e., the drift rate), which would be reflected as a stronger priming effect in the higher quantiles of the distribution (i.e., the two RT distributions would have a different shape).
@@
 To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms).
-Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
+Similar prime exposure durations have shown very weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime duration of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
 Thus, if the size of the priming effect is roughly similar to the prime exposure duration, we would expect a much larger priming effect at the 33.3 ms prime exposure duration than at the 16.6 ms prime exposure duration.
 If we do observe a large effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments.
-Keep in mind that we are using a software that has good control over the exposure duration [@bridges2020; @anwyl-irvine2020a].
+Keep in mind that we are using a software that has very good control over the exposure duration [@bridges2020; @anwyl-irvine2020a].
 Figure \ref{fig:hyp-mod-dat-figure} displays the link between all these verbal hypotheses, the process model that corresponds to each of them, and their predictions in the response time distributions.
@@
 
-All in all, replicating the results observed in controlled laoboratory masked primiming studies would provide some grounds to the validity of online masked priming tasks,even with no control over many variables (e.g., the devices in which the experiment is run, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
+All in all, replicating the results observed in controlled laboratory masked priming studies would provide some grounds to the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
+Furthermore, the present experiments go beyond an online replication: they allow us to test not only masked priming effects across conditions (identity vs.
+unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) [e.g., JACOBS ET AL 1995 AÑADIR].
+Thus, the within-subject manipulation of prime exposure duration allows us to obtain the whole picture of priming effects--also including the examination of potential inhibitory effects of unrelated primes.
 
@@
 
-In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33 ms and 50 ms (roughly corresponding to two and three frames at a refresh rate of 60 Hz).
+In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33 ms and 50 ms (roughly corresponding to two and three frames, respectively, at a refresh rate of 60 Hz).
 
@@
 Delta plots are residual quantile plots that show the distributional differences between conditions [@de1994conditional].
-As can be seen in Panel A, there is a priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33ms one.
-There is an increase of said effect for the longest responses (quantile .9) in the 33ms prime duration condition that can be understood by looking at Panel B of the same figure.
+As can be seen in Panel A, there is an identity priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33ms one.
+We also found a slight increase of priming effects for the longest responses (quantile .9) in the 33ms prime duration condition.
+This apparent anomaly can be understood better by looking at Panel B of the same figure.
 In this panel, we show the size of the prime duration effect (computed as the difference in response times between responses to the 50 ms condition and responses to the 33 ms condition) across RT quantiles.
-While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition generated an effect only for very long responses.
+While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition virtually the same response times in the 33 and 50 ms conditions, except for a small increase at the 50 ms prime duration for the very long responses.
 
@@
 
-The results from Experiment 1 show that we were able to replicate masked priming effects using an online experiment.
+The results from Experiment 1 reveal that we were able to replicate benchmark masked priming effects using an online experiment.
 The size of the effect is similar to that observed in previous studies.
@@
 Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.
-In order to further explore this, we performed a second experiment in which we set the prime to be displayed for an even shorter duration.
-As described above, a 16.6 ms prime duration should yield qualitatively different effects from the 33.3 and 50 ms durations used in Experiment 1.
+In order to further explore this question, we performed a second experiment in which we set the prime to be displayed for an even shorter duration.
+As described in the Introducion, a 16.6 ms prime exposure duration should yield a negligible priming effect [@Tzur_2007; @ziegler2000) so the pattern should be qualitatively different effects from the 33.3 and 50 ms durations used in Experiment 1.
 If it does not, this casts doubt on the timing accuracy in online experiments.
@@
 Panel A, shows there is no priming effect for the 16 ms condition, but a consistent effect across quantiles for the 33ms condition (parallel to the one found in Experiment 1).
-Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight a slight hindering for unrelated primes.
+Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight hindering for unrelated primes.
 
@@
 
-In Experiment 2, we observed the pattern we expected from previous research: In the the mean $\mu$ of the Gaussian distribution, we saw a robust priming effect in response time and accuracy in the 33 ms condition, but a very weak effect in the 16 ms condition.
-This suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
-Again, we did not observe an effect of the prime relatedness condition on the shape parameter $\beta$ of the exponential distribution, and, unlike in Experiment 1, there was no evidence for a difference in the shape of the distribution between the 16.7 and 33.3 ms prime duration conditions.
+In Experiment 2, we found the pattern we expected from previous research: In the the mean $\mu$ of the Gaussian distribution, we observed  a robust identity priming effect in response time and accuracy in the 33 ms prime exposure duration, but a very weak effect in the 16 ms prime exposure duration.
+This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
+Again, we did not observe an effect of the prime relatedness on the shape parameter $\beta$ of the exponential distribution.
+Importantly, there was no evidence for a difference in the shape of the distribution between the 16.7 and 33.3 ms prime duration duration.
 
@@
 
-In this study, we set out to test whether using an online, browser-based experiment software, we could replicate the masked priming effect both qualitatively and quantitatively, i.e., in terms of effect sizes.
-Our results show that this is the case: not only did we observe results comparable to the lab-based studies in the literature, we also observed the effect sizes predicted by Forster's [-@forster1998pros] savings hypothesis: Our data show a shift in the mean of the Gaussian distribution, but no change in the shape parameter $\beta$ of the exponential distribution, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision making processes.
+In this study, we set out to test whether using an online, browser-based experiment software, we could replicate benchmark masked priming effects both qualitatively (i.e., shift in the RT distributions) and quantitatively (i.e., effect sizes).
+Our results show that this is the case: not only did we observe effects comparable to the lab-based studies in the literature, we also observed the effect sizes predicted by Forster's [-@forster1998pros] savings hypothesis: Our data show a shift in the mean of the Gaussian distribution, but no change in the shape parameter $\beta$ of the exponential distribution, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision making processes.
 
@@
 
-Our results open the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
+Novelty---prime duration JACOBS.... citar a Rodd que es una de las líderes en estudios online bla blabla...
+
+Thus, our results open the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
 Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible.

### 2021-05-13 MaskedPriming_complete_ms.Rmd
Create MaskedPriming_complete_ms.Rmd

--- 2021-05-13 Manuscript_intro_method_results_AB_MP.Rmd
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-  Enter author note here.
+  \color{red}This research has been partly supported by Grants...\color{black}
 
@@
   Masked priming is one of the most important paradigms in the study of visual word recognition, but it is usually thought to require a laboratory setup with a known monitor and keyboard.
-To investigate if this technique can be used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS [@peirce2019].
-In particular, we wanted to compare our online results to the data collected by @gomezDiffusionModelAccount2013, who compared masked and unmasked priming.
-Furthermore, we also tested the role of prime exposure duration effectively in an online experiment (33 vs.
-50 ms in Experiment 1 and 16 vs.
-33 ms in Experiment 2).
+To test if this technique can be used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS [@peirce2019].
+Importantly, we also tested the role of prime exposure duration effectively in an online experiment (33.3 vs.
+50 ms in Experiment 1 and 16.7 vs.
+33.3 ms in Experiment 2).
 We found that our online data are indeed very similar to the masked priming data reported by @gomezDiffusionModelAccount2013.
-Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33 ms and no priming effect at 16 ms prime duration.
-From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., Psychopy) can present stimuli and collect responses on standard consumer devices with enough precision.
+Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33.3 ms and no priming effect at 16.7 ms prime duration.
+From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., PsychoPy) can present stimuli and collect responses on standard end user devices with enough precision.
 In sum, these findings provide us with confidence that masked priming can be used online, thus allowing us to reach populations that are difficult to test in a laboratory.
@@
 keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
-wordcount         : "XXX"
+wordcount         : "XXXXX"
 floatsintext      : yes
@@
 For instance, a search of the expression "masked priming" in Google Scholar in May 2021 produced more than 10,000 hits.
-Virtually all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003.
+Nearly all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003.
 The issue we examine in the present paper is whether masked priming experiments can be safely conducted in an online setting.
@@
 
-However, cognitive psychologists have been much slower in taking up online paradigms [see @cai2017accent;@eerland2013influence; @rodd2016impact; @vandeberg2012out, for some exceptions], often due to concerns about the validity of the results.
+However, cognitive psychologists have been much slower in taking up online paradigms [see @brysbaert2016impact; @cai2017accent;@eerland2013influence; @rodd2016impact, for some exceptions], often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
-Indeed, in the masked priming technique, it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
-In particular, presenting the masked prime for longer than intended would counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest.
+Furthermore, in the masked priming technique, it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
+For instance, presenting the masked prime for longer than intended (e.g., 83 ms instead of the nominal 50 ms) would counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest.
 
 There have been attempts to address these concerns.
-For example, @witzelTestingViabilityWebDMDX2013 developed a Web version of DMDX (webDMDX) showing  promising results in a trial experiment.
+@witzelTestingViabilityWebDMDX2013 developed a Web version of DMDX (webDMDX) showing  promising results in a trial experiment.
 However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a "true" online programming script that could be run inside of a browser.
@@
 Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets [@reimersPresentationResponseTiming2015].
-There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020], and open-source such as jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of Psychopy 3, @peirce2019].
+There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020], and open-source such as jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of PsychoPy 3, @peirce2019].
 In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
@@
 
-Specifically, in this study we were interested in whether we could replicate, and extend, a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming reflects a savings effect.
+Specifically, in this study we were interested in whether we could replicate, and extend, a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming is commonly described as a savings effect.
 As first suggested by @forster1998pros, for a masked identity prime, "the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner", whereas for an unrelated prime, "the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur" (p.
@@
 unrelated primes: 33.3 vs.
-50 ms in Experiment 1, and 16.6 vs.
+50 ms in Experiment 1, and 16.7 vs.
 33.3 ms in Experiment 2---note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA).
@@
 This outcome would indicate that the on-line masked priming studies reproduce a characteristic signature of laboratory masked priming studies.
-Alternatively, if the online presentation conditions lead to a greater actual exposure duration on the participant's device compared to that specified in our experiment, (e.g., prime durations are approximately 20 ms longer on average than programmed) then the 50 ms primes may no longer be adequately masked, but may rather be consciously perceived.
+Alternatively, if the online presentation conditions lead to a greater actual exposure duration on the participant's device compared to that specified in our experiment (e.g.,if prime durations were, on average, 20 ms longer than intended), then the 50 ms primes may no longer be adequately masked, but may rather be consciously perceived.
 If this is the case, the prime could affect not only the encoding, but also core decision processes (i.e., the drift rate), which would be reflected as a stronger priming effect in the higher quantiles of the distribution (i.e., the two RT distributions would have a different shape).
@@
 
-To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms).
-Similar prime exposure durations have shown very weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime duration of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen.
-Thus, if the size of the priming effect is roughly similar to the prime exposure duration, we would expect a much larger priming effect at the 33.3 ms prime exposure duration than at the 16.6 ms prime exposure duration.
-If we do observe a large effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments.
+To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.7 ms).
+Similar prime exposure durations have shown very weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime duration of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16.7 ms when using a very high level of contrast in the computer screen.
+Thus, if the size of the priming effect is roughly similar to the prime exposure duration, we would expect a much larger priming effect at the 33.3 ms prime exposure duration than at the 16.7 ms prime exposure duration.
+If we do observe a large effect at the 16.7 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments.
 Keep in mind that we are using a software that has very good control over the exposure duration [@bridges2020; @anwyl-irvine2020a].
-Figure \ref{fig:hyp-mod-dat-figure} displays the link between all these verbal hypotheses, the process model that corresponds to each of them, and their predictions in the response time distributions.
-
-```{r hyp-mod-dat-figure, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE, fig.height=3.4, fig.cap = "Add caption"}
+Figure \ref{fig:hyp-mod-dat-figure} displays the link between all these verbal hypotheses, the process model that corresponds to each of them, and their predictions in the RT distributions.
+
+All in all, replicating the results observed in controlled laboratory masked priming studies would provide some grounds to the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
+Furthermore, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.
+unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) [e.g.,@Jacobs_1995].
+Thus, the within-subject manipulation of prime exposure duration allows us to obtain the whole picture of priming effects--also including the examination of potential inhibitory effects of unrelated primes.
+
+```{r hyp-mod-dat-figure, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE, fig.height=3.4, fig.cap = "Mapping from hypotheses to data via evidence accumulation models.
+The bottom part of each graph represents sample paths, and the top part shows the cumulative density functions.
+From left to right: *Null Effect* - there are no differences between the conditions; *Effect in Encoding* - the difference between the conditions is on the encoding time, hence the RT distributions are shifted; and *Effect of Encoding and Evidence Accumulation* - the differences between the conditions is on the rate of evidence accumulation, thus increasing the effect size for longer RTs (right-tail of the distribution)."}
+
 suppressMessages(library("tidyverse"))
@@
 
-text("Evidence\naccumulations",x = .88, y=.4,cex=.8)
+text("Evidence\naccumulation",x = .88, y=.4,cex=.8)
 text("Encoding",x = .2, y=.4,cex=.8)
@@
 
-text("Evidence\naccumulations",x = .88, y=.4,cex=.8)
+text("Evidence\naccumulation",x = .88, y=.4,cex=.8)
 text("Encoding",x = .2, y=.4,cex=.8)
 
-title("Effect in\nencoding")
+title("Effect in\nEncoding")
 
@@
 
-text("Evidence\naccumulations",x = .88, y=.4,cex=.8)
+text("Evidence\naccumulation",x = .88, y=.4,cex=.8)
 text("Encoding",x = .2, y=.4,cex=.8)
 
-title("Effect in encoding and \nevidence accumulation")
+title("Effect in Encoding and \nEvidence Accumulation")
 
@@
 ```
-
-All in all, replicating the results observed in controlled laboratory masked priming studies would provide some grounds to the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
-Furthermore, the present experiments go beyond an online replication: they allow us to test not only masked priming effects across conditions (identity vs.
-unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) [e.g., JACOBS ET AL 1995 AÑADIR].
-Thus, the within-subject manipulation of prime exposure duration allows us to obtain the whole picture of priming effects--also including the examination of potential inhibitory effects of unrelated primes.
 
@@
 
-In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33 ms and 50 ms (roughly corresponding to two and three frames, respectively, at a refresh rate of 60 Hz).
+In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33.3 ms and 50 ms (roughly corresponding to two and three frames, respectively, at a refresh rate of 60 Hz).
 
@@
 
-exp1_data_to_include <- exp1 %>% filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33 ms", "50 ms")), rt = rt * 1000)
+exp1_data_to_include <- exp1 %>% filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Relatedness = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identity", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33.3 ms", "50 ms")), rt = rt * 1000)
 
@@
 In the experiment, all stimuli were presented in the center of the screen in black Courier New font on a white background.
-As we do not know the exact dimensions of each participant's screen, all stimulus sizes and positions were defined in Psychopy's "height" units, with the bottom left of a 16:10 aspect ratio screen being represented as (-.8, -.5) and the top right being (.8, .5).
+As we do not know the exact dimensions of each participant's screen, all stimulus sizes and positions were defined in PsychoPy's "height" units, with the bottom left of a 16:10 aspect ratio screen being represented as (-.8, -.5) and the top right being (.8, .5).
 The height for all text stimuli was 0.1 units.
 Each trial began with a six-character pattern mask (*######*) set to be presented for 500 ms, followed first by the lowercase prime (e.g.
-*region*) set to be presented for either 33 or 50 ms, and then by the uppercase target (e.g.
+*region*) set to be presented for either 33.3 or 50 ms, and then by the uppercase target (e.g.
 *REGION*).
-Participants were instructed to respond to the target stimulus as quickly as possible either by using the keyboard, if their device had one, by pressing the "Z" key if the target was not a valid English word or the "M" key if the target was a valid English word.
+Participants were instructed to respond to the target stimulus as quickly as possible by pressing the "Z" key of their keyboard (if their device had one) if the target was not a valid English word or the "M" key if the target was a valid English word.
 Participants on a device without a keyboard were instructed to respond by touching one of two rectangular touch areas labeled "Z = Non-word" (presented at -0.4, -0.3) and "M = Word" (presented at 0.4, -0.3).
@@
 For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.
-identical) and prime duration (33 ms vs.
+identical) and prime duration (33.3 ms vs.
 50 ms) as well as their interaction as the fixed effects.
-For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -1 and unrelated was coded as 1.
-For priming duration, 33 ms was coded as -1 and 50 ms was coded as 1.
+For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -0.5 and unrelated was coded as 0.5.
+For priming duration, 33.3 ms was coded as -0.5 and 50 ms was coded as 0.5.
 We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items.
@@
 Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warmup iterations for the accuracy models).
-We consider an effect as credible if the 95% credible interval (CrI) estimated from the posterior distribution does not contain zero.
+We consider an effect as credible if the 95% Credible Interval (CrI) estimated from the posterior distribution does not contain zero.
 In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.
@@
 
-(ref:exp1-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 1 for each condition.
+(ref:exp1-descriptives-rt-table-caption) Mean, Median, Standard Deviation (SD), range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 1 for each condition.
+
+\newpage
 
@@
   filter(rt > 250 & rt < 2000 & corr == 1) %>%
-  group_by(StimulusType, PrimeDuration, Condition) %>%
+  group_by(StimulusType, PrimeDuration, Relatedness) %>%
   summarize(
@@
   filter(rt > 250 & rt < 2000) %>%
-  group_by(StimulusType, PrimeDuration, Condition) %>%
+  group_by(StimulusType, PrimeDuration, Relatedness) %>%
   summarize(
@@
 
-Table \@ref(tab:exp1-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% credible interval (CrI) of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-(ref:exp1-blmm-table-caption) Posterior mean, standard error (SE), 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 1.
-
-```{r exp1-blmm-table, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
+Table \@ref(tab:exp1-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+
+```{r exp1-models-rt, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
+
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
@@
 blmm_exp1_summary_rt <- summary(blmm_exp1_rt_dist)
+
+```
+
+The RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
+The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1","u-95% CI"]`]).
+However, the 50 ms prime exposure duration (*b* = `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]) seems to be associated with a slightly lower $\beta$, i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition.
+On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]).
+
+(ref:exp1-blmm-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for the fixed effects of the model fitted for correct word RTs in Experiment 1.
+
+```{r exp1-blmm-table, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
 
@@
 
-The RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]).
-For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
-However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33 ms condition, but only a negligible effect in the 16 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-Once again, the shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1","u-95% CI"]`]).
-However, the 50 ms prime exposure duration (*b* = `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]) seems to be associated with a slightly lower $\beta$, i.e., a slightly weaker right skew of the distribution, than the 33 ms condition.
-On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]).
-
-<!---  Figure \@ref(fig:exp1-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
-
-(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 1. -->
-
-```{r exp1-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)", warning=FALSE, message=FALSE}
-
-# del_hdi_exp1_rt = hdi(blmm_exp1_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
-# 
-# del_hdi_exp1_rt%>%
-#   filter(!grepl("beta",Parameter)) -> posteriorsToPlot
-# 
-# plot(posteriorsToPlot) +
-#   scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
-#   ylab("")+
-#   theme_apa() -> Plot_post_E1
-# 
-# Plot_post_E1
-
-```
-
 These results can be visualized in the delta plots depicted in Figure \ref{fig:deltas-e1-words}.
 Delta plots are residual quantile plots that show the distributional differences between conditions [@de1994conditional].
-As can be seen in Panel A, there is an identity priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33ms one.
-We also found a slight increase of priming effects for the longest responses (quantile .9) in the 33ms prime duration condition.
+As can be seen in Panel A, there is an identity priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33.3 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33.3 ms one.
+We also found a slight increase of priming effects for the longest responses (quantile .9) in the 33.3 ms prime duration condition.
 This apparent anomaly can be understood better by looking at Panel B of the same figure.
-In this panel, we show the size of the prime duration effect (computed as the difference in response times between responses to the 50 ms condition and responses to the 33 ms condition) across RT quantiles.
-While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition virtually the same response times in the 33 and 50 ms conditions, except for a small increase at the 50 ms prime duration for the very long responses.
-
-```{r deltas-e1-words, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE, cache=TRUE, fig.cap = "Add caption 2"}
+In this panel, we show the size of the prime duration effect (computed as the difference in response times between responses to the 50 ms condition and responses to the 33.3 ms condition) across RT quantiles.
+While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition yielded virtually the same response times in the 33.3 and 50 ms conditions, except for a small increase at the 50 ms prime duration for the very long responses (i.e., .9 quantile).
+
+```{r deltas-e1-words, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE, cache=TRUE, fig.cap = "Delta plots depicting the magnitude of the effect over time in Experiment 1.
+Each dot represents the mean RT at the .1, .3, .5, .7 and .9 quantiles.
+*Panel A)* Difference of RTs between  unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right).
+*Panel B)* Difference of RTs between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions."}
 
@@
   filter(rt > 250 & rt < 2000)%>%
-  select(participant, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target, corr, rt)%>%
+  select(participant, TrialID, StimulusType, Relatedness, PrimeDuration, Prime, Target, corr, rt)%>%
   mutate(participant=factor(participant),
@@
 E1 %>%
-  group_by(participant, StimulusType, Condition, PrimeDuration,corr) %>%
+  group_by(participant, StimulusType, Relatedness, PrimeDuration,corr) %>%
   summarise(RT = list(quibble(rt, seq(.1, .9, .2)))) %>% 
@@
   select(-corr) %>%
-  group_by(StimulusType,PrimeDuration,Condition,q) %>%
+  group_by(StimulusType,PrimeDuration,Relatedness,q) %>%
   summarize(RT=mean(x))%>%
@@
   filter(StimulusType == "Word")%>%
-  arrange(desc(Condition))%>%
+  arrange(desc(Relatedness))%>%
   group_by(PrimeDuration,q) %>%
@@
   filter(StimulusType == "Word")%>%
-  group_by(Condition,q) %>%
+  group_by(Relatedness,q) %>%
   summarize(MRT=mean(RT),
@@
   ylab("Effect (in ms)")+
-  ggtitle("Prime duration effect")+
-  facet_wrap(~ Condition)+
+  ggtitle("Prime Duration Effect")+
+  facet_wrap(~ Relatedness)+
   theme_minimal()+
@@
 
-Table \@ref(tab:exp1-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% credible interval (CrI) of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-(ref:exp1-blmm-accuracy-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for response accuracy on word trials in Experiment 1.
-
-```{r exp1-acc-blmm-table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
+Table \@ref(tab:exp1-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+
+```{r exp1-models-acc, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
 
@@
 # Download it at https://1drv.ms/u/s!ApE7JQmoH0baobQPat43HR3ixhuqww?e=VySttd
+# Relatedness = Condition
 
 blmm_exp1_summary_acc <- summary(blmm_exp1_acc)
+
+```
+
+The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1","u-95% CI"]`]).
+The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp1_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
+The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33.3 ms condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+
+(ref:exp1-blmm-accuracy-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for the fixed effects of the model fitted for response accuracy on word trials in Experiment 1.
+
+```{r exp1-acc-blmm-table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
 
@@
     "Intercept",
-    "Condition",
+    "Relatedness",
     "Prime Duration",
-    "Condition:Prime Duration"
+    "Relatedness:Prime Duration"
     )
@@
 
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1","u-95% CI"]`]).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp1_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
-The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-
 ## Discussion
@@
 The results from Experiment 1 reveal that we were able to replicate benchmark masked priming effects using an online experiment.
-The size of the effect is similar to that observed in previous studies.
-We also saw a clear difference between the 33 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices.
+The size of the effect is similar to that observed in previous studies [e.g., @gomezDiffusionModelAccount2013; \color{red}PEREA; LUPKER...\color{black}].
+In addition, we also saw a clear difference between the 33.3 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices.
 While the shape of the distribution changed slightly between the 33.3 ms and the 50 ms prime exposure durations, we did not observe an effect of the prime relatedness condition on the shape parameter $\beta$ of the exponential distribution, suggesting, according to the savings hypothesis by @forster1998pros, that only encoding processes were affected by the relatedness manipulation.
-
-Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.
+Moreover, as can be observed in Figure \ref{fig:deltas-e1-words} the effect magnitude was close to the stimulus-onset asynchrony [see also @Perea_2018].
+
+Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.Indeed, to better define the priming effect, one needs a baseline that serves as a reference point [i.e., a minimum intensity priming condition; see @Jacobs_1995].
 In order to further explore this question, we performed a second experiment in which we set the prime to be displayed for an even shorter duration.
-As described in the Introducion, a 16.6 ms prime exposure duration should yield a negligible priming effect [@Tzur_2007; @ziegler2000) so the pattern should be qualitatively different effects from the 33.3 and 50 ms durations used in Experiment 1.
+As described in the Introduction, a 16.7 ms prime exposure duration should yield a negligible priming effect [@Tzur_2007; @ziegler2000] so the pattern should be qualitatively different effects from the 33.3 and 50 ms durations used in Experiment 1.
 If it does not, this casts doubt on the timing accuracy in online experiments.
+In this experiment, we also include the 33.3 ms prime duration condition to not only have a better scheme to compare the two experiments, but also to be able to test the within-condition effect [@Jacobs_1995]---assuming the 16.7 ms prime duration serves as a baseline.
 
@@
 
-In the second experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 16 ms and 33 ms (roughly corresponding to one and two frames at a refresh rate of 60 Hz).
+In the second experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 16.7 ms and 33.3 ms (roughly corresponding to one and two frames at a refresh rate of 60 Hz).
 
@@
 
-exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16 ms", "33 ms")), rt = rt * 1000)
+exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Relatedness = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identity", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16.7 ms", "33.3 ms")), rt = rt * 1000)
 
@@
 The remaining `r exp2_actual_participants$PROLIFIC_PID %>% unique %>% length` participants were aged from `r exp2_participant_ages %>% min` to `r exp2_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
-Of the participants, `r exp2_male_participants_nr` identified as male, `r exp2_female_participants_nr` identified as female, and `r exp2_other_participants_nr` identified as other.
+Of the participants, `r exp2_male_participants_nr` identified as male, and `r exp2_female_participants_nr` identified as female.
 All these participants indicated that English was their first language in the Prolific screening questions.
@@
 
-The procedure was identical to Experiment 1, the only difference being that the primes were set to be displayed for either 16 ms or 33 ms.
+The procedure was identical to Experiment 1, the only difference being that the primes were set to be displayed for either 16.7 ms or 33.3 ms.
 
@@
 For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials).
-For priming duration, 16 ms was coded as -1 and 33 ms was coded as 1.
+For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5.
 Otherwise, the model specifications were identical to those in Experiment 1.
 
-(ref:exp2-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 2 for words and nonwords and by prime duration and priming condition.
+## Results
+
+Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table \@ref(tab:exp2-descriptive-rt-table).
+
+(ref:exp2-descriptives-rt-table-caption) Mean, Median, Standard Deviation (SD), and range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 2 for all conditions.
 
@@
   , caption = "(ref:exp2-descriptives-rt-table-caption)"
-  , note = "Trials with reaction times below 250 ms were excluded from the analysis. For the calculation of response times, incorrect responses were also removed."
   , escape = TRUE
@@
 
-(ref:exp2-blmm-rt-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 2.
-
-```{r load_exp2_brms_data, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
-# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
+### Response times
+
+```{r exp2-models-rt, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
+
+# We fitted the models in a separate file to make sure that knitting the manuscript doesn't take too long
 load("blmm_exp2_rt_dist_full_ranef_5000.RData")
+
 # this file doesn't fit on GitHub
 # download it at https://1drv.ms/u/s!ApE7JQmoH0baocIO3qh2TNb_TlqvlA?e=q3vJml
+
 # model name is blmm_exp2_rt
@@
 blmm_exp2_summary_rt <- summary(blmm_exp2_rt_dist)
+
+```
+
+As in Experiment 1, the RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]).
+For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
+However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1","u-95% CI"]`]), prime exposure duration (*b* = `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]), or their interaction (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
+Table \@ref(tab:exp2-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+
+(ref:exp2-blmm-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for the fixed effects of the model fitted for correct word RTs in Experiment 2.
+
+```{r exp2-blmm-table, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
 
@@
 
-## Results
-
-### Response times
-
-As in Experiment 1, the RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]) and higher in the 33 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
-The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1","u-95% CI"]`]), prime exposure duration (*b* = `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]), or their interaction (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
-
-<!--- Figure \@ref(fig:exp2-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
-
- (ref:exp2-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 2.
--->
-
-```{r exp2-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp2-brms-rt-plot-caption)", message=FALSE, warning=FALSE}
-
-#del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
-
-#del_hdi_exp2_rt%>%
-#  filter(!grepl("beta",Parameter)) -> posteriorsToPlotE2
-
-#plot(posteriorsToPlotE2) +
-#  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
-#  ylab("")+
-#  theme_apa() -> Plot_post_E2
-
-#Plot_post_E2
-
-```
-
 We also created the delta plots of data from Experiment 2 (see Figure \ref{fig:deltas-e2-words}).
-Panel A, shows there is no priming effect for the 16 ms condition, but a consistent effect across quantiles for the 33ms condition (parallel to the one found in Experiment 1).
+Panel A, shows there is no priming effect for the 16.7 ms condition, but a consistent effect across quantiles for the 33.3 ms condition (parallel to the one found in Experiment 1).
 Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight hindering for unrelated primes.
 
-```{r deltas-e2-words, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.cap = "Add caption 3"}
+\newpage
+
+```{r deltas-e2-words, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.cap = "Delta plots depicting the magnitude of the effect over time in Experiment 2."}
 
 E2<- exp2_data_to_include%>%
-  select(participant, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target, corr, rt)%>%
+  select(participant, TrialID, StimulusType, Relatedness, PrimeDuration, Prime, Target, corr, rt)%>%
   mutate(participant=factor(participant),
@@
 E2 %>%
-  group_by(participant, StimulusType, Condition, PrimeDuration,corr) %>%
+  group_by(participant, StimulusType, Relatedness, PrimeDuration,corr) %>%
   summarise(RT = list(quibble(rt, seq(.1, .9, .2)))) %>% 
@@
 
-(ref:exp2-blmm-accuracy-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for response accuracy on word trials in Experiment 2.
-
-```{r exp2_acc_brms_table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
+```{r exp2-models-acc, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
 
@@
 
+```
+
+The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1","u-95% CI"]`]).
+The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16.7 ms prime duration condition than in the 33.3 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp2_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
+The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33.3 ms condition, and reversed in the 16.7 ms condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]), although the effect in the 16.7 ms condition was very weak.
+Table \@ref(tab:exp2-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, indicating that the model was fitted successfully as they are all close to 1.
+
+(ref:exp2-blmm-accuracy-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for fixed effects of the model fitted for response accuracy on word trials in Experiment 2.
+
+```{r exp2-acc-blmm-table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
+
 blmm_exp2_acc_fixed_for_print <- blmm_exp2_summary_acc$fixed
@@
 
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1","u-95% CI"]`]).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16 ms prime duration condition than in the 33 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp2_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
-The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33 ms condition, and reversed in the 16 ms condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]), although the effect in the 16 ms condition was very weak.
-
 ## Discussion
 
-In Experiment 2, we found the pattern we expected from previous research: In the the mean $\mu$ of the Gaussian distribution, we observed  a robust identity priming effect in response time and accuracy in the 33 ms prime exposure duration, but a very weak effect in the 16 ms prime exposure duration.
+In Experiment 2, we found the pattern we expected from previous research: In the mean $\mu$ of the Gaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration [@Tzur_2007; @ziegler2000].
 This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
-Again, we did not observe an effect of the prime relatedness on the shape parameter $\beta$ of the exponential distribution.
-Importantly, there was no evidence for a difference in the shape of the distribution between the 16.7 and 33.3 ms prime duration duration.
+In addition, we did not observe an effect of the prime relatedness on the shape parameter $\beta$ of the exponential distribution.
+Thus, indicating there was no evidence for a difference in the shape of the distribution between the 16.7 and 33.3 ms prime duration.
+Moreover, the magnitude of the effect was close to the magnitude of the prime-target stimulus-onset asynchrony, as can be seen in the delta plots in Figure \ref{fig:deltas-e2-words} [see @Perea_2018].
+Hence, we replicated again the commonly observed savings effect [@forster1998pros].
+Critically, because the 16.7 ms prime duration condition yielded virtually no priming effects, it serves a within-condition baseline that allows us to qualify the priming effect [@Jacobs_1995] in this case for trials that had a 33.3 ms prime duration.
+Specifically, our findings show a small inhibitory effect for unrelated primes, and a slight facilitatory effect for identity primes.
+\color{red} AS OBSERVED IN OTHER STUDIES… \color{black}
 
@@
 
-In this study, we set out to test whether using an online, browser-based experiment software, we could replicate benchmark masked priming effects both qualitatively (i.e., shift in the RT distributions) and quantitatively (i.e., effect sizes).
-Our results show that this is the case: not only did we observe effects comparable to the lab-based studies in the literature, we also observed the effect sizes predicted by Forster's [-@forster1998pros] savings hypothesis: Our data show a shift in the mean of the Gaussian distribution, but no change in the shape parameter $\beta$ of the exponential distribution, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision making processes.
-
-We also found that the size of the priming effect was directly influenced by the prime exposure duration.
-This indicates that the experimental software was able to control the display timing of the prime accurately.
-Accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, but are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade.
-The fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of Psychopy.
-
-Novelty---prime duration JACOBS.... citar a Rodd que es una de las líderes en estudios online bla blabla...
-
-Thus, our results open the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
+In this study, we set out to test whether we could replicate benchmark masked priming effects both qualitatively (i.e., shift in the RT distributions) and quantitatively (i.e., effect sizes) using an online, browser-based experiment software.
+\color{red} EXPLAIN A BIT WHAT WE DID \color{black}
+
+Our results indicate that main masked priming effects obtained in the lab-based studies can also be obtained in online-based studies.
+We observed the effect sizes predicted by Forster's [-@forster1998pros] savings hypothesis: Our data show a shift in the mean of the Gaussian distribution, but no change in the shape parameter $\beta$ of the exponential distribution, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes.
+Furthermore, the size of the priming effect was not only directly influenced by the prime duration, suggesting the experimental software was able to control the display timing of the prime accurately, but also of a similar magnitude to the prime duration [within the range reported in previous studies, e.g., 35-47 ms for a 50 ms prime duration in @Perea_2018].
+
+While accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, they are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade.
+The fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy.
+Furthermore, our results not only replicate findings in previous masked priming laboratory studies, but also extend previous work showing the validity of on-line studies measuring response times [e.g., @brysbaert2016impact; @cai2017accent; @eerland2013influence; @rodd2016impact] to the masked priming technique.
+Thus, the present study opens the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
 Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible.
-For example, many people in developing countries may not have computers at home, but they do have smartphones.
+For instance, people from different countries and/or cultures, from different age groups, bilinguals/ multilinguals, even from those who do not have computers at home, but they do have smartphones.
 Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant.
-Deploying experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
-
-In conclusion, our results give us confidence that high-quality behavioral data can be collected online using Javascript-based experiment platforms.
+Additionally, deploying experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
+
+In conclusion, our results give us confidence that high-quality behavioral data using the masked priming paradigm can be collected online using Javascript-based experiment platforms.
 We hope that future research takes advantage of these new methods in order to make research faster, more inclusive, and more efficient.

### 2021-05-13 Manuscript_intro_method_results_AB.Rmd
Revert "Update Manuscript_intro_method_results_AB.Rmd"
This reverts commit d0a88038b11c79e9fd36fd3ec8bce3d54ebcd782.

--- 2021-05-06 Manuscript_intro_method_results_AB.Rmd
@@
 
-The RT model indicates that response times were higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]) and higher in the 33 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
-The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-Figure \@ref(fig:exp1-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
+The RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]).
+For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
+However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33 ms condition, but only a negligible effect in the 16 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+Once again, the shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1","u-95% CI"]`]).
+However, the 50 ms prime exposure duration (*b* = `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]) seems to be associated with a slightly lower $\beta$, i.e., a slightly weaker right skew of the distribution, than the 33 ms condition.
+On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]).
 
-(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 1.
+<!---  Figure \@ref(fig:exp1-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
+
+(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 1. -->
 
@@
 
-del_hdi_exp1_rt = hdi(blmm_exp1_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
-
-del_hdi_exp1_rt%>%
-  filter(!grepl("beta",Parameter)) -> posteriorsToPlot
-
-plot(posteriorsToPlot) +
-  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
-  ylab("")+
-  theme_apa() -> Plot_post_E1
-
-Plot_post_E1
+# del_hdi_exp1_rt = hdi(blmm_exp1_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
+# 
+# del_hdi_exp1_rt%>%
+#   filter(!grepl("beta",Parameter)) -> posteriorsToPlot
+# 
+# plot(posteriorsToPlot) +
+#   scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
+#   ylab("")+
+#   theme_apa() -> Plot_post_E1
+# 
+# Plot_post_E1
 
@@
 
-## Results
-
-The model indicates that response times were higher in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]), although across the two prime duration conditions, the effect was much smaller than in Experiment 1.
-Response times were also higher in the 16 ms than in the 33 ms prime duration condition (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]) although, as the interaction effect shows, this was mainly due to an absence of the priming effect in the 16 ms prime duration condition, as opposed to the 33 ms condition, which showed a robust priming effect (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-Figure \@ref(fig:exp2-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
-
 (ref:exp2-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 2 for words and nonwords and by prime duration and priming condition.
@@
 
+## Results
+
+As in Experiment 1, the RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]) and higher in the 33 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
+The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1","u-95% CI"]`]), prime exposure duration (*b* = `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]), or their interaction (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
+
+<!--- Figure \@ref(fig:exp2-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.
+
  (ref:exp2-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 2.
+-->
 
@@
 
-del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
+#del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
 
-del_hdi_exp2_rt%>%
-  filter(!grepl("beta",Parameter)) -> posteriorsToPlotE2
+#del_hdi_exp2_rt%>%
+#  filter(!grepl("beta",Parameter)) -> posteriorsToPlotE2
 
-plot(posteriorsToPlotE2) +
-  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
-  ylab("")+
-  theme_apa() -> Plot_post_E2
+#plot(posteriorsToPlotE2) +
+#  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
+#  ylab("")+
+#  theme_apa() -> Plot_post_E2
 
-Plot_post_E2
+#Plot_post_E2
 

### 2021-05-14 MaskedPriming_complete_ms.Rmd
Update MaskedPriming_complete_ms.Rmd

@@
 title             : |
-    | Can we use masked priming in an online setting?
-    | The effect of prime exposure duration in online masked priming lexical decision
+    | Does online masked priming passes the Turing test?
+    | The effects of prime exposure duration on masked identity priming
 shorttitle        : "Online masked priming"
@@
 authornote: |
-  \color{red}This research has been partly supported by Grants...\color{black}
+
+  This research has been partly supported by Grant PSI2017-86210-P  from  the  Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), \color{red} and...
+PABLO, BERNHARD  \color{black}
 
@@
   Masked priming is one of the most important paradigms in the study of visual word recognition, but it is usually thought to require a laboratory setup with a known monitor and keyboard.
-To test if this technique can be used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS [@peirce2019].
-Importantly, we also tested the role of prime exposure duration effectively in an online experiment (33.3 vs.
+To test if this technique can be safely used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS [@peirce2019].
+Importantly, we also tested the role of prime exposure duration (33.3 vs.
 50 ms in Experiment 1 and 16.7 vs.
-33.3 ms in Experiment 2).
+33.3 ms in Experiment 2), thus allowing us to examine both across conditions and within-conditions effects.
 We found that our online data are indeed very similar to the masked priming data reported by @gomezDiffusionModelAccount2013.
@@
 From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., PsychoPy) can present stimuli and collect responses on standard end user devices with enough precision.
-In sum, these findings provide us with confidence that masked priming can be used online, thus allowing us to reach populations that are difficult to test in a laboratory.
+These findings provide us with confidence that masked priming can be used online, thus allowing us not only to run less time-consuming experiments, but also to reach populations that are difficult to test in a laboratory.
 
@@
 
-Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition [see @forster1998pros; and @grainger2008cracking, for reviews].
+Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition [see @forster1998pros; @grainger2008cracking, for reviews].
 Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond (e.g., "is *DOCTOR* a word?").
@@
 Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
-Furthermore, in the masked priming technique, it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
-For instance, presenting the masked prime for longer than intended (e.g., 83 ms instead of the nominal 50 ms) would counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest.
+Furthermore, this concerns are even more central in the masked priming technique, where it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
+For instance, presenting the masked prime for longer than intended (e.g., 83 ms or longer instead of the nominal 50 ms) could counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest [see @Zimmerman_2012].
 
@@
 Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
-As @reimersPresentationResponseTiming2015 point out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
+As @reimersPresentationResponseTiming2015 pointed out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
 If the results of the Web-based study are comparable to previous lab-based results, this suggests that whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
@@
 The very similar study by @anwyl-irvine2020a compares only online packages and browsers with regard to timing.
-Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with "reasonable" precision, although the lab-based packages were slightly better in this regard.
+Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with reasonable precision, although the lab-based packages were slightly better in this regard.
 This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
@@
 
-To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.7 ms).
-Similar prime exposure durations have shown very weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime duration of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16.7 ms when using a very high level of contrast in the computer screen.
+To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for replacing the 50 ms prime exposure duration with a very short prime exposure duration, namely, 16.7 ms.
+Similar extremely brief prime exposure durations have shown very weak masked priming lexical decision experiments in a laboratory setting: less than 5 ms for a prime duration of 14 ms [@ziegler2000] and less than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16.7 ms when using a very high level of contrast in the computer screen.
 Thus, if the size of the priming effect is roughly similar to the prime exposure duration, we would expect a much larger priming effect at the 33.3 ms prime exposure duration than at the 16.7 ms prime exposure duration.
@@
 
-All in all, replicating the results observed in controlled laboratory masked priming studies would provide some grounds to the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
-Furthermore, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.
-unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) [e.g.,@Jacobs_1995].
-Thus, the within-subject manipulation of prime exposure duration allows us to obtain the whole picture of priming effects--also including the examination of potential inhibitory effects of unrelated primes.
+All in all, replicating the results observed in controlled laboratory masked priming studies would provide some grounds to the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
+Importantly, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.
+unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) [see @Jacobs_1995; @ziegler2000, for advantages of within-condition comparisons].
+Thus, the within-subject manipulation of prime exposure duration in both experiments allows us to obtain a comprehensive picture of masked identity priming effects--also including the examination of potential inhibitory effects of unrelated primes.
 
@@
 trials_word_stats <- left_join(trials, word_statistics, by = c("Target" = "Word_upper"))
+
 ```
@@
 *region --- REGION* and *fainch --- FAINCH*) and an unrelated prime consisting of another word from the list (e.g.
-*launch --- REGION* and *miluer --- FAINCH*).
-Appendix A contains a list of the items.
+*launch --- REGION* and *miluer --- FAINCH*)[^1].Unrelated primes were orthographically were paired with the targets by rearranging the order of identity primes (controling for neighbors; see @Perea_2018).
+Appendix A contains a list of the target items, and all counterbalanced lists can be found in the on-line repository.
+
+[^1]: Someone could argue that, for word targets, the unrelated primes were words, whereas for nonword targets, they were pseudowords.
+However, as shown by @Fern_ndez_L_pez_2019, the lexical status of the unrelated prime does not affect lexical decision times.
 
@@
 
-We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the *brms* package [@R-brms_a; @R-brms_b] in R [@R-base][^1].
+We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the *brms* package [@R-brms_a; @R-brms_b] in R [@R-base][^2].
 We only analyzed trials where the target stimulus was a word.
@@
 
-[^1]: The full list of software we used for our analyses is as follows: `r cite_r("r-references.bib")`.
+[^2]: The full list of software we used for our analyses is as follows: `r cite_r("r-references.bib")`.
 
@@
 (ref:exp1-descriptives-rt-table-caption) Mean, Median, Standard Deviation (SD), range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 1 for each condition.
-
-\newpage
 
@@
 
+\newpage
+
 ### Response times
@@
 The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1","u-95% CI"]`]).
-However, the 50 ms prime exposure duration (*b* = `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]) seems to be associated with a slightly lower $\beta$, i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition.
+However, the 50 ms prime exposure duration seems to be associated with a slightly lower $\beta$, i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]).
 On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]).
@@
 These results can be visualized in the delta plots depicted in Figure \ref{fig:deltas-e1-words}.
-Delta plots are residual quantile plots that show the distributional differences between conditions [@de1994conditional].
+Delta plots are residual quantile plots that show the distributional differences between conditions [see @de1994conditional].
 As can be seen in Panel A, there is an identity priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33.3 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33.3 ms one.
@@
 In this panel, we show the size of the prime duration effect (computed as the difference in response times between responses to the 50 ms condition and responses to the 33.3 ms condition) across RT quantiles.
-While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition yielded virtually the same response times in the 33.3 and 50 ms conditions, except for a small increase at the 50 ms prime duration for the very long responses (i.e., .9 quantile).
+While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition yielded virtually the same response times in the 33.3 and 50 ms conditions, except for a small increase at the 50 ms prime duration for the very long responses (i.e., .9 quantile)--we prefer not to over-interpret this latter finding with the slowest responses, as it did not appear in Experiment 2.
 
@@
 The results from Experiment 1 reveal that we were able to replicate benchmark masked priming effects using an online experiment.
-The size of the effect is similar to that observed in previous studies [e.g., @gomezDiffusionModelAccount2013; \color{red}PEREA; LUPKER...\color{black}].
+The size and shape of the effect is similar to that observed in previous studies [e.g., @gomezDiffusionModelAccount2013; @Perea_2018; @Taikh_2020; @Yang_2021].
 In addition, we also saw a clear difference between the 33.3 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices.
@@
 
-Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.Indeed, to better define the priming effect, one needs a baseline that serves as a reference point [i.e., a minimum intensity priming condition; see @Jacobs_1995].
+Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.
+Indeed, to better define the priming effect, one needs a baseline that serves as a reference point [i.e., an analog of the minimum "intensity" priming condition; see @Jacobs_1995].
 In order to further explore this question, we performed a second experiment in which we set the prime to be displayed for an even shorter duration.
-As described in the Introduction, a 16.7 ms prime exposure duration should yield a negligible priming effect [@Tzur_2007; @ziegler2000] so the pattern should be qualitatively different effects from the 33.3 and 50 ms durations used in Experiment 1.
-If it does not, this casts doubt on the timing accuracy in online experiments.
-In this experiment, we also include the 33.3 ms prime duration condition to not only have a better scheme to compare the two experiments, but also to be able to test the within-condition effect [@Jacobs_1995]---assuming the 16.7 ms prime duration serves as a baseline.
+As described in the Introduction, a 16.7 ms prime exposure duration should yield a negligible priming effect [@Tzur_2007; @ziegler2000] so the pattern should be qualitatively different from the 33.3 and 50 ms durations used in Experiment 1.
+If it does not, this would cast doubt on the timing accuracy in online experiments.
+In this experiment, we also include the 33.3 ms prime duration condition to not only have a better scheme to compare the two experiments, but also to be able to test the within-condition effects [@Jacobs_1995]---assuming the 16.7 ms prime duration serves as a baseline.
 
@@
 
+### Response times
+
+```{r exp2-models-rt, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
+
+# We fitted the models in a separate file to make sure that knitting the manuscript doesn't take too long
+load("blmm_exp2_rt_dist_full_ranef_5000.RData")
+
+# this file doesn't fit on GitHub
+# download it at https://1drv.ms/u/s!ApE7JQmoH0baocIO3qh2TNb_TlqvlA?e=q3vJml
+
+# model name is blmm_exp2_rt
+
+# adapted from a paper by Nalborczyk et al. (2019) -- https://osf.io/eancg/
+
+blmm_exp2_summary_rt <- summary(blmm_exp2_rt_dist)
+
+```
+
+As in Experiment 1, the RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]).
+For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
+However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
+The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1","u-95% CI"]`]), prime exposure duration (*b* = `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]), or their interaction (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
+
+Table \@ref(tab:exp2-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+
+\newpage
+
 (ref:exp2-descriptives-rt-table-caption) Mean, Median, Standard Deviation (SD), and range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 2 for all conditions.
+
+(ref:exp2-blmm-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for the fixed effects of the model fitted for correct word RTs in Experiment 2.
 
@@
 
-### Response times
-
-```{r exp2-models-rt, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
-
-# We fitted the models in a separate file to make sure that knitting the manuscript doesn't take too long
-load("blmm_exp2_rt_dist_full_ranef_5000.RData")
-
-# this file doesn't fit on GitHub
-# download it at https://1drv.ms/u/s!ApE7JQmoH0baocIO3qh2TNb_TlqvlA?e=q3vJml
-
-# model name is blmm_exp2_rt
-
-# adapted from a paper by Nalborczyk et al. (2019) -- https://osf.io/eancg/
-
-blmm_exp2_summary_rt <- summary(blmm_exp2_rt_dist)
-
-```
-
-As in Experiment 1, the RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]).
-For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
-However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1","u-95% CI"]`]), prime exposure duration (*b* = `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]), or their interaction (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
-Table \@ref(tab:exp2-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-(ref:exp2-blmm-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for the fixed effects of the model fitted for correct word RTs in Experiment 2.
-
-```{r exp2-blmm-table, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
+```{r exp2-blmm-table, as.is = TRUE,echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight hindering for unrelated primes.
-
-\newpage
 
@@
 This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
-In addition, we did not observe an effect of the prime relatedness on the shape parameter $\beta$ of the exponential distribution.
-Thus, indicating there was no evidence for a difference in the shape of the distribution between the 16.7 and 33.3 ms prime duration.
-Moreover, the magnitude of the effect was close to the magnitude of the prime-target stimulus-onset asynchrony, as can be seen in the delta plots in Figure \ref{fig:deltas-e2-words} [see @Perea_2018].
+In addition, we did not observe an effect of the prime relatedness on the shape parameter $\beta$ of the exponential distribution [i.e., the effect corresponded to a shift of the RT distributions, as shown in in-lab studies; e.g., @Taikh_2020; @Yang_2021].
+Moreover, the magnitude of the priming effect at the 33.3 ms prime exposure duration was close to the magnitude of the prime-target stimulus-onset asynchrony, as can be seen in the delta plots in Figure \ref{fig:deltas-e2-words} [see @gomezDiffusionModelAccount2013; @Perea_2018].
 Hence, we replicated again the commonly observed savings effect [@forster1998pros].
-Critically, because the 16.7 ms prime duration condition yielded virtually no priming effects, it serves a within-condition baseline that allows us to qualify the priming effect [@Jacobs_1995] in this case for trials that had a 33.3 ms prime duration.
-Specifically, our findings show a small inhibitory effect for unrelated primes, and a slight facilitatory effect for identity primes.
-\color{red} AS OBSERVED IN OTHER STUDIES… \color{black}
+
+Critically, because the 16.7 ms prime duration condition yielded virtually no priming effects, this very short prime exposure duration serves as a within-condition baseline that allows us to qualify the facilitative vs.
+inhibitory nature of masked priming effects [@Jacobs_1995; @ziegler2000].
+Specifically, when compared to the baseline, our findings at the 33.3 ms prime duration show a combination of a slight facilitatory effect for identity primes and a small inhibitory effect for unrelated primes.
 
@@
 
-In this study, we set out to test whether we could replicate benchmark masked priming effects both qualitatively (i.e., shift in the RT distributions) and quantitatively (i.e., effect sizes) using an online, browser-based experiment software.
+In this study, we set out to test whether we could obtain benchmark masked  priming effects both qualitatively (i.e., shift in the RT distributions) and quantitatively (i.e., effect sizes) using an online, browser-based experiment software.
+To that end, we conducted two online masked identity priming experiments (e.g., *region --- REGION* vs.
+*launch --- REGION*) in which we  manipulated prime exposure duration (33.3 vs.
+50 ms in Experiment 1; 16.7 vs.
+33 ms in Experiment 2).
 \color{red} EXPLAIN A BIT WHAT WE DID \color{black}
 
-Our results indicate that main masked priming effects obtained in the lab-based studies can also be obtained in online-based studies.
+The results of our online-based experiments replicated and extended benchmarks masked identity priming effects previous in the lab-based studies.
 We observed the effect sizes predicted by Forster's [-@forster1998pros] savings hypothesis: Our data show a shift in the mean of the Gaussian distribution, but no change in the shape parameter $\beta$ of the exponential distribution, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes.
 Furthermore, the size of the priming effect was not only directly influenced by the prime duration, suggesting the experimental software was able to control the display timing of the prime accurately, but also of a similar magnitude to the prime duration [within the range reported in previous studies, e.g., 35-47 ms for a 50 ms prime duration in @Perea_2018].
+Importantly, the use of a within-condition baseline revealed that the identity priming effects at the 33 ms prime exposure duration were a combination of some small facilitation from identity primes and some small inhibition from unrelated primes [see @Jacobs_1995, for evidence with a psychophysical experiment].
+Likewise, the greater identity priming effects at the 50 ms rather than at the 33.3 ms prime exposure duration were essentially due to the facilitation from the identity pairs.
 
 While accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, they are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade.
-The fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy.
-Furthermore, our results not only replicate findings in previous masked priming laboratory studies, but also extend previous work showing the validity of on-line studies measuring response times [e.g., @brysbaert2016impact; @cai2017accent; @eerland2013influence; @rodd2016impact] to the masked priming technique.
+Similarly, unlike in-lab conditions, were the contrast of the computer screens can be measured and kept constants, there is no such a guarantee in the monitors of online participnts--note that the manipulation of contrast in the @Tzur_2007 experiments used extreme values.
+Thus, the fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy.
+
+Furthermore, our results extend previous work showing the validity of on-line studies measuring response times [e.g., @brysbaert2016impact; @cai2017accent; @eerland2013influence; @rodd2016impact, to cite a few instances] to the masked priming technique.
 Thus, the present study opens the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
 Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible.
-For instance, people from different countries and/or cultures, from different age groups, bilinguals/ multilinguals, even from those who do not have computers at home, but they do have smartphones.
+For instance, people from different countries and/or cultures, from different age groups, bilinguals/multilinguals, even from those who do not have computers at home, but they do have smartphones.
 Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant.
-Additionally, deploying experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
+Additionally, deploying masked priming experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
 
@@
 
+\newpage
+
+# Appendix A
+
+## Words:
+```{r}
+trials%>%
+  filter(StimulusType=="WORD")%>%
+  pull(Target)%>%
+  noquote()->Word_targets
+
+Word_targets
+
+```
+
+## Non-Words:
+
+```{r}
+
+trials%>%
+  filter(StimulusType=="NW")%>%
+  pull(Target)%>%
+  noquote()->NonWord_targets
+
+NonWord_targets
+
+```
+
 \endgroup

### 2021-05-19 MaskedPriming_complete_mspg.Rmd
Create MaskedPriming_complete_mspg.Rmd

--- 2021-05-14 MaskedPriming_complete_ms.Rmd
@@
 
+  We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.
   This research has been partly supported by Grant PSI2017-86210-P  from  the  Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), \color{red} and...
-PABLO, BERNHARD  \color{black}
-
+PABLO?
+\color{black}
 abstract: |
@@
 keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
-wordcount         : "XXXXX"
+wordcount         : "7863"
 floatsintext      : yes
@@
 Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition [see @forster1998pros; @grainger2008cracking, for reviews].
-Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond (e.g., "is *DOCTOR* a word?").
-It is measured as the difference in a dependent variable (e.g., response time [RT]) between two conditions (e.g., unrelated: *horse-DOCTOR*; related: *nurse-DOCTOR*).
+Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond to (e.g., "is *DOCTOR* a word?").
+Priming effects are measured as the difference in a dependent variable (e.g., response time [RT]) between two conditions (e.g., unrelated: *horse-DOCTOR*; related: *nurse-DOCTOR*).
 In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a pattern mask (e.g., \#\#\#\#\#) for a much longer duration (typically 500 ms).
@@
 Nearly all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003.
-The issue we examine in the present paper is whether masked priming experiments can be safely conducted in an online setting.
-Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or with minimal activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
+The issue we examine in the present paper is whether masked priming experiments can be conducted in an online setting without significant changes in the pattern of results.
+Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
 Indeed, researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010].
 
-However, cognitive psychologists have been much slower in taking up online paradigms [see @brysbaert2016impact; @cai2017accent;@eerland2013influence; @rodd2016impact, for some exceptions], often due to concerns about the validity of the results.
+Cognitive psychologists have been much slower that their behavioral economics coleagues in taking up online paradigms [see @brysbaert2016impact; @cai2017accent;@eerland2013influence;@Dufau_2011; @rodd2016impact, for some exceptions], often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
-Furthermore, this concerns are even more central in the masked priming technique, where it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
+Furthermore, these concerns are even more central in the masked priming technique, where it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
 For instance, presenting the masked prime for longer than intended (e.g., 83 ms or longer instead of the nominal 50 ms) could counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest [see @Zimmerman_2012].
@@
 In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
-Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility to recruit participants for on-line experiments based on various specific characteristics set up by the experimenter not necessarily in the country's lab (e.g., native French speakers, not older than 30 years old, not currently in college).
+Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility of recruiting participants for on-line experiments based on various specific characteristics set up by the experimenters regardless of their location (e.g., native French speakers, not older than 30 years old, not currently in college).
 
@@
 
-Specifically, in this study we were interested in whether we could replicate, and extend, a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming is commonly described as a savings effect.
+Specifically, in this study we were interested in whether we could replicate and extend a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming is commonly described as a savings effect.
 As first suggested by @forster1998pros, for a masked identity prime, "the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner", whereas for an unrelated prime, "the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur" (p.
@@
 
+\color{green} I don't love the prior paragrpah.
+My main concenrn is that the savings account could have been also implemented as a headstart that boosts the drift rate.
+The Ter model is just one implementation of the hard start hypothesis  \color{black}
+
 Critically, the above pattern is *specific* to masked priming.
-When primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles [i.e., a change in shape rather than a shift in RT distributions; see @gomezDiffusionModelAccount2013].
+In fact, the most common pattern of results in latency based tasks is that conditions that produce longer latencies will also produce larger variance.
+This patter is evident in priming as well when primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles [i.e., a change in shape rather than a shift in RT distributions; see @gomezDiffusionModelAccount2013].
 Fits from the diffusion model show that this result corresponds to changes in both the $T_{er}$ parameter and the drift rate [see @gomezDiffusionModelAccount2013].
@@
 Participants were able to sign up for the experiment on the Prolific website.
-On signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment [@qualtrics2020].
+Upon signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment [@qualtrics2020].
 After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual lexical decision task was implemented in PsychoJS.
@@
 
-Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table \@ref(tab:exp1-descriptive-rt-table) (although note that we only analyzed the word trials).
+Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table~\@ref(tab:exp1-descriptive-rt-table) (although note that we only analyzed the word trials).
 
@@
 
-Table \@ref(tab:exp1-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+Table~\@ref(tab:exp1-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
 
@@
 
-Table \@ref(tab:exp1-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+Table~\@ref(tab:exp1-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
 
@@
 
-We analyzed the data in the same way as in Experiment 1, again only analyzing trials where the target stimulus was a word.
+We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word.
 For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials).
@@
 
-Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table \@ref(tab:exp2-descriptive-rt-table).
+Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table~\@ref(tab:exp2-descriptive-rt-table).
 
@@
 We also created the delta plots of data from Experiment 2 (see Figure \ref{fig:deltas-e2-words}).
-Panel A, shows there is no priming effect for the 16.7 ms condition, but a consistent effect across quantiles for the 33.3 ms condition (parallel to the one found in Experiment 1).
+Panel A, shows there is no priming effect for the 16.7 ms condition, in contrast with a consistent effect across quantiles for the 33.3 ms condition (parallel to the one found in Experiment 1).
 Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight hindering for unrelated primes.
@@
 
-In Experiment 2, we found the pattern we expected from previous research: In the mean $\mu$ of the Gaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration [@Tzur_2007; @ziegler2000].
+In Experiment 2, we found the pattern we expected from previous research: In the mean $\mu$ of the exGaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration [@Tzur_2007; @ziegler2000].
 This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
@@
 Hence, we replicated again the commonly observed savings effect [@forster1998pros].
+
+\color{green}I changed gaussian to exgaussian above, is that correct? \color{black}
 
@@
 33 ms in Experiment 2).
-\color{red} EXPLAIN A BIT WHAT WE DID \color{black}
-
 The results of our online-based experiments replicated and extended benchmarks masked identity priming effects previous in the lab-based studies.

### 2021-05-19 MaskedPriming_complete_mspg.Rmd
Implemented Pablo's changes

@@
   We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.
-  This research has been partly supported by Grant PSI2017-86210-P  from  the  Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), \color{red} and...
-PABLO?
-\color{black}
+  This research has been partly supported by Grant PSI2017-86210-P from  the  Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).
 abstract: |
@@
 
-Cognitive psychologists have been much slower that their behavioral economics coleagues in taking up online paradigms [see @brysbaert2016impact; @cai2017accent;@eerland2013influence;@Dufau_2011; @rodd2016impact, for some exceptions], often due to concerns about the validity of the results.
+Cognitive psychologists have been much slower that their behavioral economics coleagues in taking up online paradigms [see @brysbaert2016impact; @cai2017accent;@eerland2013influence; @rodd2016impact, for some exceptions], often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
@@
 Empirical evidence supporting this view has been obtained in several papers not only with skilled adults but also with developing readers [e.g., @gomezDiffusionModelAccount2013; @Gomez_2020; @Taikh_2020; @Yang_2021].
-Moreover, this pattern of results fits very well with the diffusion model [@ratcliff2004].
-This model proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution ($T_{er}$) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached.
+@gomezDiffusionModelAccount2013 proposed an implementation of this hypothesis within the diffusion model [@ratcliff2004].
+This implementation proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution ($T_{er}$) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached.
 Importantly, in the decision process, the information gathered from the stimulus can vary in noise, depending on its quality, which modifies the rate at which information is accumulated (i.e., the *drift rate*).
-With regards to RTs from masked priming tasks, @gomezDiffusionModelAccount2013 found that the difference between identity and unrelated conditions could be accounted by a change in the $T_{er}$ parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a skewer RT distribution in the slower, unrelated condition.
-
-\color{green} I don't love the prior paragrpah.
-My main concenrn is that the savings account could have been also implemented as a headstart that boosts the drift rate.
-The Ter model is just one implementation of the hard start hypothesis  \color{black}
+With regards to RTs from masked priming tasks, @gomezDiffusionModelAccount2013 found that the difference between identity and unrelated conditions could be accounted for by a change in the $T_{er}$ parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a more skewed RT distribution in the slower, unrelated condition.
 
@@
 
-In Experiment 2, we found the pattern we expected from previous research: In the mean $\mu$ of the exGaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration [@Tzur_2007; @ziegler2000].
+In Experiment 2, we found the pattern we expected from previous research: In the mean $\mu$ of the Gaussian component of the ex-Gaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration [@Tzur_2007; @ziegler2000].
 This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
-In addition, we did not observe an effect of the prime relatedness on the shape parameter $\beta$ of the exponential distribution [i.e., the effect corresponded to a shift of the RT distributions, as shown in in-lab studies; e.g., @Taikh_2020; @Yang_2021].
+In addition, we did not observe an effect of the prime relatedness on the shape parameter $\beta$ of the exponential component [i.e., the effect corresponded to a shift of the RT distributions, as shown in in-lab studies; e.g., @Taikh_2020; @Yang_2021].
 Moreover, the magnitude of the priming effect at the 33.3 ms prime exposure duration was close to the magnitude of the prime-target stimulus-onset asynchrony, as can be seen in the delta plots in Figure \ref{fig:deltas-e2-words} [see @gomezDiffusionModelAccount2013; @Perea_2018].
 Hence, we replicated again the commonly observed savings effect [@forster1998pros].
-
-\color{green}I changed gaussian to exgaussian above, is that correct? \color{black}
 

### 2021-05-19 MaskedPriming_complete_mspg.Rmd
Update MaskedPriming_complete_mspg.Rmd

@@
     | The effects of prime exposure duration on masked identity priming
+
 shorttitle        : "Online masked priming"
+
 author: 
@@
     affiliation   : "2,5"
+
 affiliation:
@@
     institution   : "Universitat de València, Valencia, Spain"
+
+note: "\\clearpage"
+
 authornote: |
@@
   We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.
+
   This research has been partly supported by Grant PSI2017-86210-P from  the  Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).
+
 abstract: |
@@
 keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
-wordcount         : "7863"
+wordcount         : "7916"
 floatsintext      : yes
@@
 
+The study was pre-registered on the Open Science Framework (OSF) prior to data collection.
+The registration form, together with the materials, data files, and R scripts can be found at https://osf.io/d2txs/.
+
+\newpage
+
 ```{r hyp-mod-dat-figure, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE, fig.height=3.4, fig.cap = "Mapping from hypotheses to data via evidence accumulation models.
@@
 ```
-
-The study was pre-registered on the Open Science Framework (OSF) prior to data collection.
-The registration form, together with the materials, data files, and R scripts can be found at https://osf.io/d2txs/.
 

### 2021-05-19 MaskedPriming_complete_mspg.Rmd
Update MaskedPriming_complete_mspg.Rmd

@@
 33.3 ms in Experiment 2), thus allowing us to examine both across conditions and within-conditions effects.
-We found that our online data are indeed very similar to the masked priming data reported by @gomezDiffusionModelAccount2013.
+We found that our online data are indeed very similar to the masked priming data previously reported in the masked priming literature.
 Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33.3 ms and no priming effect at 16.7 ms prime duration.
@@
 
-Cognitive psychologists have been much slower that their behavioral economics coleagues in taking up online paradigms [see @brysbaert2016impact; @cai2017accent;@eerland2013influence; @rodd2016impact, for some exceptions], often due to concerns about the validity of the results.
+Cognitive psychologists have been much slower that their behavioral economics colleagues in taking up online paradigms [see @brysbaert2016impact; @cai2017accent; @Dufau_2011; @eerland2013influence; @rodd2016impact, for some exceptions], often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
@@
 
-Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table~\@ref(tab:exp1-descriptive-rt-table) (although note that we only analyzed the word trials).
+Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table \@ref(tab:exp1-descriptive-rt-table) (although note that we only analyzed the word trials).
 
@@
 
-Table~\@ref(tab:exp1-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+Table \@ref(tab:exp1-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
 
@@
 
-Table~\@ref(tab:exp1-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+Table \@ref(tab:exp1-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
 
@@
 
-Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table~\@ref(tab:exp2-descriptive-rt-table).
+Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table \@ref(tab:exp2-descriptive-rt-table).
 
@@
     align = c("c", "c", "c", "c", "c"),
-    caption = "(ref:exp2-blmm-rt-table-caption)",
+    caption = "(ref:exp2-blmm-table-caption)",
     note = "$\\beta$ is the scale parameter (the inverse of the rate parameter $\\lambda$) of the ex-Gaussian distribution.",
@@
 
-Furthermore, our results extend previous work showing the validity of on-line studies measuring response times [e.g., @brysbaert2016impact; @cai2017accent; @eerland2013influence; @rodd2016impact, to cite a few instances] to the masked priming technique.
+Furthermore, our results extend previous work showing the validity of on-line studies measuring response times [e.g., @brysbaert2016impact; @cai2017accent; @Dufau_2011; @eerland2013influence; @rodd2016impact, to cite a few instances] to the masked priming technique.
 Thus, the present study opens the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.

### 2021-05-19 MaskedPriming_complete_mspg.Rmd
Proofreading and changes

@@
 title             : |
-    | Does online masked priming passes the Turing test?
+    | Does online masked priming pass the test?
     | The effects of prime exposure duration on masked identity priming
@@
 As @reimersPresentationResponseTiming2015 pointed out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
-If the results of the Web-based study are comparable to previous lab-based results, this suggests that whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
+If the results of the Web-based study are comparable to previous lab-based results, this suggests that, whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
 
@@
 Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony (SOA).
-Empirical evidence supporting this view has been obtained in several papers not only with skilled adults but also with developing readers [e.g., @gomezDiffusionModelAccount2013; @Gomez_2020; @Taikh_2020; @Yang_2021].
+Empirical evidence supporting this view has been obtained in several studies not only with skilled adults but also with developing readers [e.g., @gomezDiffusionModelAccount2013; @Gomez_2020; @Taikh_2020; @Yang_2021].
 @gomezDiffusionModelAccount2013 proposed an implementation of this hypothesis within the diffusion model [@ratcliff2004].
@@
 
-Critically, the above pattern is *specific* to masked priming.
+Critically, the above pattern is specific to *masked* priming.
 In fact, the most common pattern of results in latency based tasks is that conditions that produce longer latencies will also produce larger variance.
-This patter is evident in priming as well when primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles [i.e., a change in shape rather than a shift in RT distributions; see @gomezDiffusionModelAccount2013].
-Fits from the diffusion model show that this result corresponds to changes in both the $T_{er}$ parameter and the drift rate [see @gomezDiffusionModelAccount2013].
-Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word.
+This pattern is evident in priming as well---when primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles [i.e., a change in shape rather than a shift in RT distributions; see @gomezDiffusionModelAccount2013].
+Fits from the diffusion model show that this result corresponds to changes in both the $T_{er}$ parameter and the drift rate.
+Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word, unlike in masked priming.
 Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.
@@
 
-[^1]: Someone could argue that, for word targets, the unrelated primes were words, whereas for nonword targets, they were pseudowords.
+[^1]: Note that the lexical status of the unrelated prime differed depending on the target type: for word targets, the unrelated primes were words, whereas for nonword targets, they were pseudowords.
 However, as shown by @Fern_ndez_L_pez_2019, the lexical status of the unrelated prime does not affect lexical decision times.
@@
 
-The RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
+The RT model indicates that the mean of the Gaussian component $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
 The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1","u-95% CI"]`]).
+The shape parameter of the exponential component $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1","u-95% CI"]`]).
 However, the 50 ms prime exposure duration seems to be associated with a slightly lower $\beta$, i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]).
@@
 Each dot represents the mean RT at the .1, .3, .5, .7 and .9 quantiles.
-*Panel A)* Difference of RTs between  unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right).
-*Panel B)* Difference of RTs between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions."}
+*Panel A)* Difference in RT between unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right).
+*Panel B)* Difference in RT between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions."}
 
@@
 While the shape of the distribution changed slightly between the 33.3 ms and the 50 ms prime exposure durations, we did not observe an effect of the prime relatedness condition on the shape parameter $\beta$ of the exponential distribution, suggesting, according to the savings hypothesis by @forster1998pros, that only encoding processes were affected by the relatedness manipulation.
-Moreover, as can be observed in Figure \ref{fig:deltas-e1-words} the effect magnitude was close to the stimulus-onset asynchrony [see also @Perea_2018].
+Moreover, as can be observed in Figure \ref{fig:deltas-e1-words}, the effect magnitude was close to the stimulus-onset asynchrony [see also @Perea_2018].
 
@@
 
-As in Experiment 1, the RT model indicates that the mean of the normal distribution $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]).
+As in Experiment 1, the RT model indicates that the mean of the Gaussian component $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]).
 For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
 However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-The shape parameter of the exponential distribution $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1","u-95% CI"]`]), prime exposure duration (*b* = `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]), or their interaction (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
+The shape parameter of the exponential component $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1","u-95% CI"]`]), prime exposure duration (*b* = `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]), or their interaction (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
 
@@
 The results of our online-based experiments replicated and extended benchmarks masked identity priming effects previous in the lab-based studies.
-We observed the effect sizes predicted by Forster's [-@forster1998pros] savings hypothesis: Our data show a shift in the mean of the Gaussian distribution, but no change in the shape parameter $\beta$ of the exponential distribution, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes.
+We observed the effect sizes predicted by Forster's [-@forster1998pros] savings hypothesis: Our data show a shift in the mean of the Gaussian component of the ex-Gaussian distribution, but no change in the shape parameter $\beta$ of the exponential component, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes.
 Furthermore, the size of the priming effect was not only directly influenced by the prime duration, suggesting the experimental software was able to control the display timing of the prime accurately, but also of a similar magnitude to the prime duration [within the range reported in previous studies, e.g., 35-47 ms for a 50 ms prime duration in @Perea_2018].
@@
 While accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, they are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade.
-Similarly, unlike in-lab conditions, were the contrast of the computer screens can be measured and kept constants, there is no such a guarantee in the monitors of online participnts--note that the manipulation of contrast in the @Tzur_2007 experiments used extreme values.
-Thus, the fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy.
+Similarly, unlike in-lab conditions, where the contrast of the computer screens can be measured and kept constant, there is no such a guarantee for the screens used by online participants---note that @Tzur_2007 were only able to observe strong effects for short prime exposure durations when using extreme contrast values.
+Thus, the fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy, PsychoJS.
 
@@
 Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible.
-For instance, people from different countries and/or cultures, from different age groups, bilinguals/multilinguals, even from those who do not have computers at home, but they do have smartphones.
+For instance, online participants can be people from different countries and/or cultures, from different age groups, bilinguals/multilinguals, even those who do not own a computer, only a smartphone.
 Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant.

### 2021-05-19 MaskedPriming_complete_mspg.Rmd
Update MaskedPriming_complete_mspg.Rmd

@@
     | The effects of prime exposure duration on masked identity priming
-
 shorttitle        : "Online masked priming"
-
 author:
+
   - name          : "Bernhard Angele"
@@
     affiliation   : "2,5"
-
 affiliation:
@@
     institution   : "Universitat de València, Valencia, Spain"
-
 note: "\\clearpage"
-
 authornote: |

### 2021-05-27 MaskedPriming_complete_mspg.Rmd
update OSF link in manuscript

@@
 The study was pre-registered on the Open Science Framework (OSF) prior to data collection.
-The registration form, together with the materials, data files, and R scripts can be found at https://osf.io/d2txs/.
+The registration form, together with the materials, data files, and R scripts can be found at https://osf.io/57rzq/.
 
@@
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+
+The study was pre-registered on OSF.
+The pre-registration form, stimuli used in the experiment, scripts to run the experiment, data files, and data analyses are presented in the following OSF link: https://osf.io/fdtv5/
 
@@
 load("blmm_exp1_rt_dist_full_ranef_5000.RData")
-# This file does not fit on GitHub
-# Download it at https://1drv.ms/u/s!ApE7JQmoH0baocARuxg21SFrS4riyg?e=8ZgbHA
+# 
 # model name is blmm_exp1_rt_dist
@@
 
-# This file does not fit on GitHub
-# Download it at https://1drv.ms/u/s!ApE7JQmoH0baobQPat43HR3ixhuqww?e=VySttd
 # Relatedness = Condition

### 2021-05-27 MaskedPriming_complete_mspg.Rmd
Add OSF links in author statement

@@
   This research has been partly supported by Grant PSI2017-86210-P from  the  Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).
+
+  This study was pre-registered on the Open Science Framework (OSF) prior to data collection.
+The registration form for Experiment 1, together with the materials, data files, and R scripts can be found at [https://osf.io/57rzq/].
+The registration form for Experiment 2 can be found at [https://osf.io/957s8].
 
@@
 Thus, the within-subject manipulation of prime exposure duration in both experiments allows us to obtain a comprehensive picture of masked identity priming effects--also including the examination of potential inhibitory effects of unrelated primes.
-
-The study was pre-registered on the Open Science Framework (OSF) prior to data collection.
-The registration form, together with the materials, data files, and R scripts can be found at https://osf.io/57rzq/.
 

### 2021-05-27 MaskedPriming_complete_mspg.Rmd
Added OSF information to the Method sections

@@
 ```
+
+The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at [https://osf.io/57rzq/].
 
@@
 
+The pre-registration form for Experiment 2 can be found at [https://osf.io/957s8]. The materials, data files, and R scripts can be found at [https://osf.io/57rzq/]
+
 ## Method

### 2021-05-27 MaskedPriming_complete_mspg.Rmd
Added citations to megastudies

--- 2021-05-27 MaskedPriming_complete_mspg.Rmd
@@
 Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.
-both encoding + information quality in unmasked priming.
+both encoding and information quality in unmasked priming.
 
@@
 
-All in all, replicating the results observed in controlled laboratory masked priming studies would provide some grounds to the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
+All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
+This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms [e.g., @aguasvivas2020; @brysbaert2021a; @mandera2020; @brysbaert2016impact].
+So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries [e.g., @adelman2014].
 Importantly, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.
@@
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
-
-The study was pre-registered on OSF.
-The pre-registration form, stimuli used in the experiment, scripts to run the experiment, data files, and data analyses are presented in the following OSF link: https://osf.io/fdtv5/
 
@@
 ```
+
+The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at <https://osf.io/57rzq/>.
 
@@
 The height for all text stimuli was 0.1 units.
-Each trial began with a six-character pattern mask (*######*) set to be presented for 500 ms, followed first by the lowercase prime (e.g.
+Each trial began with a six-character pattern mask (*\#\#\#\#\#\#*) set to be presented for 500 ms, followed first by the lowercase prime (e.g.
 *region*) set to be presented for either 33.3 or 50 ms, and then by the uppercase target (e.g.
@@
 
+The pre-registration form for Experiment 2 can be found at [<https://osf.io/957s8>]. The materials, data files, and R scripts can be found at [<https://osf.io/57rzq/>]
+
 ## Method
@@
 Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant.
-Additionally, deploying masked priming experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
+This opens up the possibility of masked-priming crowdsourced megastudies.
+In general, deploying masked priming experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
 
@@
 ## Words:
+
 ```{r}

### 2021-09-21 MaskedPriming_revision.Rmd
Add revision and revision cover letter

--- 2021-05-27 MaskedPriming_complete_mspg.Rmd
@@
 The registration form for Experiment 2 can be found at [https://osf.io/957s8].
-
 abstract: |
@@
 ```{r setup, include = FALSE}
-library("tidyverse")
-library("brms")
-library("bayestestR")
+library(tidyverse)
 library("see")
@@
 library(patchwork)
+library(xfun)
+library(sp)
+library(rworldmap)
+library("brms")
+library("bayestestR")
 
@@
 ```{r load_exp1_data, message=FALSE, echo=FALSE, warning=FALSE}
-library(xfun)
-library(tidyverse)
-library(sp)
-library(rworldmap)
 
@@
 We only analyzed trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials).
-As the trials automatically ended after 2000 ms, there were no RTs longer than this.
+For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as incorrect responses (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt >= 1800 | corr == 0))/nrow(.)}*100` % of trials).
+For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt >= 1800))/nrow(.)}*100` % of trials).
 For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.
@@
 We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items.
-We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component $\mu$ and the scale parameter of the exponential component $\beta$ (equalling the inverse of the rate parameter $\lambda$) being allowed to vary between conditions.
+We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component $\mu$ and the scale parameter of the exponential component $\beta$ (equaling the inverse of the rate parameter $\lambda$) being allowed to vary between conditions.
 To model response accuracy, we used the Bernoulli distribution with a logit link.
 We used the default priors suggested by *brms* except for the coefficients for the fixed effects, for which we applied weakly informative priors of $\beta \sim N(0,100)$ in order to rule out improbably large effect sizes.
-Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warmup iterations for the accuracy models).
+Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warm-up iterations for the accuracy models).
 We consider an effect as credible if the 95% Credible Interval (CrI) estimated from the posterior distribution does not contain zero.
@@
 exp1_descriptives_rt <- exp1_data_to_include %>%
-  filter(rt > 250 & rt < 2000 & corr == 1) %>%
+  filter(rt > 250 & rt <= 1800 & corr == 1) %>%
   group_by(StimulusType, PrimeDuration, Relatedness) %>%
@@
 exp1_descriptives_corr <- exp1_data_to_include %>%
-  filter(rt > 250 & rt < 2000) %>%
+  filter(rt > 250 & rt <= 1800) %>%
   group_by(StimulusType, PrimeDuration, Relatedness) %>%
@@
 
-load("blmm_exp1_rt_dist_full_ranef_5000.RData")
+load("blmm_exp1_rt_dist_revision.RData")
 # 
@@
 E1<- exp1_data_to_include%>% 
-  filter(rt > 250 & rt < 2000)%>%
+  filter(rt > 250 & rt <= 1800)%>%
   select(participant, TrialID, StimulusType, Relatedness, PrimeDuration, Prime, Target, corr, rt)%>%
@@
 
-load("blmm_exp1_acc_new_10000.RData")
+load("blmm_exp1_acc_revision.RData")
 
@@
 We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials).
+For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as those with incorrect responses (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 1800 | corr == 0))/nrow(.)}*100` % of trials).
+For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 1800))/nrow(.)}*100` % of trials).
 For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5.
@@
 # We fitted the models in a separate file to make sure that knitting the manuscript doesn't take too long
-load("blmm_exp2_rt_dist_full_ranef_5000.RData")
+load("blmm_exp2_rt_dist_revision.RData")
 
@@
 exp2_descriptives_rt <- exp2_data_to_include %>%
-  filter(rt > 250 & rt < 2000 & corr == 1) %>%
+  filter(rt > 250 & rt <= 1800 & corr == 1) %>%
   group_by(StimulusType, PrimeDuration, Relatedness) %>%
@@
 exp2_descriptives_corr <- exp2_data_to_include %>%
-  filter(rt > 250 & rt < 2000) %>%
+  filter(rt > 250 & rt <= 1800) %>%
   group_by(StimulusType, PrimeDuration, Relatedness) %>%
@@
 
-load("blmm_exp2_acc_new_10000.RData")
+load("blmm_exp2_acc_revision.RData")
 

### 2021-09-21 final_data_analyses_brms_distributional.R

@@ -143,90 +143,6 @@ blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & Stim
 
 save(blmm_exp1_rt_dist, file = "blmm_exp1_rt_dist_full_ranef_5000_2.RData")
 
-
-blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 1800), 
-                    rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
-                    warmup = 1000,
-                    iter = 5000,
-                    chains = 4,
-                    prior = prior_exp1,
-                    family = exgaussian(),
-                    inits = "random",
-                    control = list(adapt_delta = 0.95),
-                    cores = 4, backend = "cmdstanr", threads = threading(4))
-
-save(blmm_exp1_rt, file = "blmm_exp1_rt_new2_5000.RData")
-
-blmm_exp1_rt_string <- make_stancode(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 1800), 
-                                     rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
-                                     warmup = 1000,
-                                     iter = 5000,
-                                     chains = 4,
-                                     prior = prior_exp1,
-                                     family = exgaussian(),
-                                     inits = "random",
-                                     control = list(adapt_delta = 0.95),
-                                     cores = 4, backend = "cmdstanr", threads = threading(4))
-
-
-
-
-
-
-
-blmm_exp1_acc <- brm(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "Word" & rt > 250 & rt < 1800), 
-                     formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
-                     warmup = 1000,
-                     iter = 5000,
-                     chains = 4,
-                     prior = prior_exp1,
-                     family = bernoulli(link = "logit"),
-                     inits = "random",
-                     control = list(adapt_delta = 0.95),
-                     cores = 4, backend = "cmdstanr", threads = threading(4))
-
-save(blmm_exp1_acc, file = "blmm_exp1_acc_new2_5000.RData")
-
-
[…]

### 2021-09-21 MaskedPriming_revision.tex
Add revision and revision cover letter

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Bernhard Angele1,2, Ana Baciero2,3, Pablo Gómez4, \& Manuel Perea2,5},
  pdflang={en-EN},
  pdfkeywords={Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Online masked priming}
\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 7916}
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Does online masked priming pass the test?\\
The effects of prime exposure duration on masked identity priming}
\author{Bernhard Angele\textsuperscript{1,2}, Ana Baciero\textsuperscript{2,3}, Pablo Gómez\textsuperscript{4}, \& Manuel Perea\textsuperscript{2,5}}
\date{}

\note{

\clearpage

}

\authornote{

We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.

This research has been partly supported by Grant PSI2017-86210-P from the Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).

This study was pre-registered on the Open Science Framework (OSF) prior to data collection. The registration form for Experiment 1, together with the materials, data files, and R scripts can be found at {[}\url{https://osf.io/57rzq/}{]}. The registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}.

Correspondence concerning this article should be addressed to Bernhard Angele, Department of Psychology, Faculty of Science and Technology, Talbot Campus, Fern Barrow, Poole BH12 5BB, UK. E-mail: \href{mailto:bangele@bournemouth.ac.uk}{\nolinkurl{bangele@bournemouth.ac.uk}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Bournemouth University, Bournemouth, UK\\\textsuperscript{2} Universidad Antonio de Nebrija, Madrid, Spain\\\textsuperscript{3} DePaul University, Chicago, USA\\\textsuperscript{4} California State University San Bernardino, Palm Desert Campus, USA\\\textsuperscript{5} Universitat de València, Valencia, Spain}

\abstract{
Masked priming is one of the most important paradigms in the study of visual word recognition, but it is usually thought to require a laboratory setup with a known monitor and keyboard. To test if this technique can be safely used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS (Peirce et al., 2019). Importantly, we also tested the role of prime exposure duration (33.3 vs.~50 ms in Experiment 1 and 16.7 vs.~33.3 ms in Experiment 2), thus allowing us to examine both across conditions and within-conditions effects. We found that our online data are indeed very similar to the masked priming data previously reported in the masked priming literature. Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33.3 ms and no priming effect at 16.7 ms prime duration. From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., PsychoPy) can present stimuli and collect responses on standard end user devices with enough precision. These findings provide us with confidence that masked priming can be used online, thus allowing us not only to run less time-consuming experiments, but also to reach populations that are difficult to test in a laboratory.
}

\begin{document}
\maketitle

Masked priming (Forster \& Davis, 1984) is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition (see Forster, 1998; Grainger, 2008, for reviews). Priming refers to the influence of a prime stimulus (e.g., \emph{nurse}, \emph{horse}) on a subsequently presented stimulus that the participant has to respond to (e.g., ``is \emph{DOCTOR} a word?''). Priming effects are measured as the difference in a dependent variable (e.g., response time {[}RT{]}) between two conditions (e.g., unrelated: \emph{horse-DOCTOR}; related: \emph{nurse-DOCTOR}). In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a pattern mask (e.g., \#\#\#\#\#) for a much longer duration (typically 500 ms). The rationale of the procedure is to make participants unaware of the identity of the masked prime (Forster, 1998; Forster \& Davis, 1984), thus minimizing the role of participants' strategies. Indeed, masked priming experiments do not show the strategical effects that occur with visible, unmasked primes (e.g., Grossi, 2006; Perea \& Rosa, 2002).

The masked priming paradigm has been used in a large number of studies over the last decades. For instance, a search of the expression ``masked priming'' in Google Scholar in May 2021 produced more than 10,000 hits. Nearly all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by Forster and Forster (2003). The issue we examine in the present paper is whether masked priming experiments can be conducted in an online setting without significant changes in the pattern of results. Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc. Indeed, researchers in decision making and economics have been using online paradigms for several decades now (e.g., Birnbaum \& Birnbaum, 2000; Paolacci et al., 2010).

Cognitive psychologists have been much slower that their behavioral economics colleagues in taking up online paradigms (see Brysbaert et al., 2016; Cai et al., 2017; Dufau et al., 2011; Eerland et al., 2013; Rodd et al., 2016, for some exceptions), often due to concerns about the validity of the results. Such concerns are not limited to cognitive studies (see Aust et al., 2013), but they are exacerbated by the reliance on precise presentation times in cognitive psychology. Furthermore, these concerns are even more central in the masked priming technique, where it is critical for the onset of the mask, the prime, and the target to occur at the nominal times. For instance, presenting the masked prime for longer than intended (e.g., 83 ms or longer instead of the nominal 50 ms) could counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest (see Zimmerman \& Gomez, 2012).

There have been attempts to address these concerns. Witzel et al. (2013) developed a Web version of DMDX (webDMDX) showing promising results in a trial experiment. However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a ``true'' online programming script that could be run inside of a browser. A downside of this format is that participants often are (and should be) understandably skeptical about downloading and running executable files from the Internet. Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer. As a consequence, the use of webDMDX in masked priming experiments has been rather limited so far (see Alluhaybi \& Witzel, 2020; Dubey et al., 2018, for exceptions).

Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web. Most notably, the HTML5 standard now makes it possible to use Javascript in order to draw stimuli interactively and monitor participant responses with remarkable flexibility inside the browser. Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets (Reimers \& Stewart, 2015). There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla (Anwyl-Irvine, Massonni, et al., 2020) or Testable (Rezlescu et al., 2020), and open-source such as jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of PsychoPy 3, Peirce et al., 2019). In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds. Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility of recruiting participants for on-line experiments based on various specific characteristics set up by the experimenters regardless of their location (e.g., native French speakers, not older than 30 years old, not currently in college).

Of course, despite the technological advances, many cognitive psychologists still have concerns about timing and measurement precision. While Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (e.g., to avoid delays, all stimuli are usually downloaded before the start of the experiment), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices. Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences. As Reimers and Stewart (2015) pointed out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm. If the results of the Web-based study are comparable to previous lab-based results, this suggests that, whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.

The first approach has the advantage that differences in presentation timings can be objectively recorded and evaluated. A very thorough recent example of this approach is the ``timing mega-study'' by Bridges et al. (2020), who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers. The very similar study by Anwyl-Irvine, Dalmaijer, et al. (2020) compares only online packages and browsers with regard to timing. Overall, Bridges et al. (2020) found that online packages were capable of presenting visual stimuli with reasonable precision, although the lab-based packages were slightly better in this regard. This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all. If this is not possible, there is no point in moving forward to the second approach and replicating specific paradigms. However, it is of course impossible to test every possible device and configuration that participants might use. On the other hand, some of the differences in precision and accuracy between setups that can be observed using a photodiode may be too small to have an influence on actual participant performance. Therefore, we consider replication of previous key lab-based effects a more important test of online paradigms than photodiode measurements. Based on the results by Bridges et al. (2020) and Anwyl-Irvine, Dalmaijer, et al. (2020), modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation. To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study. Importantly, we will do so using PsychoPy/PsychoJS (Peirce et al., 2019) as it showed high precision and accuracy across the great majority of platforms (Anwyl-Irvine, Dalmaijer, et al., 2020; Bridges et al., 2020), in addition to being an open-source software.

Specifically, in this study we were interested in whether we could replicate and extend a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming is commonly described as a savings effect. As first suggested by Forster (1998), for a masked identity prime, ``the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner,'' whereas for an unrelated prime, ``the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur'' (p.~213). Thus, according to the savings account, a target word like \emph{DOCTOR} would enjoy an encoding advantage when preceded by an identity prime such as \emph{doctor} than when preceded by an unrelated prime such as \emph{pencil} (i.e., a head-start). One implication of such benefit is that the RT distributions of the unrelated and identity pairs should reflect a shift rather than a change in shape. Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony (SOA). Empirical evidence supporting this view has been obtained in several studies not only with skilled adults but also with developing readers (e.g., Gomez et al., 2013; Gomez \& Perea, 2020; Taikh \& Lupker, 2020; Yang et al., 2021). Gomez et al. (2013) proposed an implementation of this hypothesis within the diffusion model (Ratcliff et al., 2004). This implementation proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution (\(T_{er}\)) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached. Importantly, in the decision process, the information gathered from the stimulus can vary in noise, depending on its quality, which modifies the rate at which information is accumulated (i.e., the \emph{drift rate}). With regards to RTs from masked priming tasks, Gomez et al. (2013) found that the difference between identity and unrelated conditions could be accounted for by a change in the \(T_{er}\) parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a more skewed RT distribution in the slower, unrelated condition.

Critically, the above pattern is specific to \emph{masked} priming. In fact, the most common pattern of results in latency based tasks is that conditions that produce longer latencies will also produce larger variance. This pattern is evident in priming as well---when primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles (i.e., a change in shape rather than a shift in RT distributions; see Gomez et al., 2013). Fits from the diffusion model show that this result corresponds to changes in both the \(T_{er}\) parameter and the drift rate. Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word, unlike in masked priming. Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.~both encoding and information quality in unmasked priming.

In the present paper, we took advantage of the above marker to examine whether online masked priming studies follow the same pattern as in-lab masked priming studies. Specifically, we manipulated prime exposure duration in identity vs.~unrelated primes: 33.3 vs.~50 ms in Experiment 1, and 16.7 vs.~33.3 ms in Experiment 2---note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA). The rationale of Experiment 1 is that if the actual exposure duration of the primes is the nominal exposure duration, then we would expect the typical shift between the identity and unrelated response time distributions, which according to the savings hypothesis (Forster, 1998) would be greater for 50 ms than for 33.3 ms exposure duration (i.e., the head-start would be greater for 50 ms identity primes than for 33.3 ms identity primes). This outcome would indicate that the on-line masked priming studies reproduce a characteristic signature of laboratory masked priming studies. Alternatively, if the online presentation conditions lead to a greater actual exposure duration on the participant's device compared to that specified in our experiment (e.g.,if prime durations were, on average, 20 ms longer than intended), then the 50 ms primes may no longer be adequately masked, but may rather be consciously perceived. If this is the case, the prime could affect not only the encoding, but also core decision processes (i.e., the drift rate), which would be reflected as a stronger priming effect in the higher quantiles of the distribution (i.e., the two RT distributions would have a different shape). In this scenario, one should be very cautious when running online masked priming experiments---at least with the typical software and hardware currently available.

To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for replacing the 50 ms prime exposure duration with a very short prime exposure duration, namely, 16.7 ms. Similar extremely brief prime exposure durations have shown very weak masked priming lexical decision experiments in a laboratory setting: less than 5 ms for a prime duration of 14 ms (Ziegler et al., 2000) and less than 9 ms for a prime duration of 20 ms (Tzur \& Frost, 2007)---in the Tzur and Frost (2007) experiment, this difference increased to 16.7 ms when using a very high level of contrast in the computer screen. Thus, if the size of the priming effect is roughly similar to the prime exposure duration, we would expect a much larger priming effect at the 33.3 ms prime exposure duration than at the 16.7 ms prime exposure duration. If we do observe a large effect at the 16.7 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments. Keep in mind that we are using a software that has very good control over the exposure duration (Anwyl-Irvine, Dalmaijer, et al., 2020; Bridges et al., 2020). Figure \ref{fig:hyp-mod-dat-figure} displays the link between all these verbal hypotheses, the process model that corresponds to each of them, and their predictions in the RT distributions.

All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli (e.g., Parker et al., 2021). This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms (e.g., Aguasvivas et al., 2020; Brysbaert et al., 2021; Brysbaert et al., 2016; Mandera et al., 2020). So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries (e.g., Adelman et al., 2014). Importantly, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.~unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) (see Jacobs et al., 1995; Ziegler et al., 2000, for advantages of within-condition comparisons). Thus, the within-subject manipulation of prime exposure duration in both experiments allows us to obtain a comprehensive picture of masked identity priming effects--also including the examination of potential inhibitory effects of unrelated primes.

\newpage

\begin{figure}
\centering
\includegraphics{MaskedPriming_revision_files/figure-latex/hyp-mod-dat-figure-1.pdf}
\caption{\label{fig:hyp-mod-dat-figure}Mapping from hypotheses to data via evidence accumulation models. The bottom part of each graph represents sample paths, and the top part shows the cumulative density functions. From left to right: \emph{Null Effect} - there are no differences between the conditions; \emph{Effect in Encoding} - the difference between the conditions is on the encoding time, hence the RT distributions are shifted; and \emph{Effect of Encoding and Evidence Accumulation} - the differences between the conditions is on the rate of evidence accumulation, thus increasing the effect size for longer RTs (right-tail of the distribution).}
\end{figure}

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33.3 ms and 50 ms (roughly corresponding to two and three frames, respectively, at a refresh rate of 60 Hz).

We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the two experiments.

\hypertarget{method}{%
\subsection{Method}\label{method}}

The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at \url{https://osf.io/57rzq/}.

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

Participants were recruited through Prolific (www.prolific.co, 2021). The experiment was accessed by 101 participants. Out of these, 89 provided experimental data. Two of these participants did not complete the experiment. A further ten were excluded because of low accuracy (less than .8, which was the pre-registered criterion). In the end, we analyzed the data from 77 participants (36 female), aged from 18 to 71 (mean age: 31.14). All these participants indicated that English was their first language in the Prolific screening questions. Based on their IP addresses, 47 participants were based in the UK, 23 were based in the US, three participants were based in Canada, and two participants were based in Ireland. Two participants could not be localized in this way. All participants were naïve to the purpose of the experiment and received £1.25 for their participation (corresponding to £5/hour). Participants could use either a desktop/laptop computer or a mobile device. Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.

\textbf{\emph{Rationale for sample size and stopping rule.}} Brysbaert and Stevens (2018) recommended that masked priming experiments should have at least 1,600 observations per condition. In order to account for potentially smaller effect sizes in an online experiment, we set a target of 3,000 observations per condition (12,000 observations total), which corresponds to a minimum of 50 participants given that there were 240 word stimuli in the experiment (see below). Our stopping rule was to keep collecting data until 3,000 valid observations were found. This goal was met and exceeded in our initial data collection with a budget of £200.

\hypertarget{materials}{%
\subsubsection{Materials}\label{materials}}

We selected 240 six-letter English words from the English Lexicon Project (Balota et al., 2007). The mean Zipf frequency based on the HAL corpus (Lund \& Burgess, 1996) was 3.8 (range: 1.9--5.5). The mean OLD20 (Yarkoni et al., 2008) was 2.1 (range: 1.4--3). We also selected 240 matched, orthographically legal six-letter nonwords. For each target, we created an identical prime (e.g.~\emph{region --- REGION} and \emph{fainch --- FAINCH}) and an unrelated prime consisting of another word from the list (e.g.~\emph{launch --- REGION} and \emph{miluer --- FAINCH})\footnote{Note that the lexical status of the unrelated prime differed depending on the target type: for word targets, the unrelated primes were words, whereas for nonword targets, they were pseudowords. However, as shown by Fernández-López et al. (2019), the lexical status of the unrelated prime does not affect lexical decision times.}.Unrelated primes were orthographically were paired with the targets by rearranging the order of identity primes (controling for neighbors; see Perea et al. (2018)). Appendix A contains a list of the target items, and all counterbalanced lists can be found in the on-line repository.

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

Participants were able to sign up for the experiment on the Prolific website. Upon signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment (Qualtrics, 2020). After indicating their agreement to participate, participants were forwarded to Pavlovia (Pavlovia, 2020), where the actual lexical decision task was implemented in PsychoJS. In the experiment, all stimuli were presented in the center of the screen in black Courier New font on a white background. As we do not know the exact dimensions of each participant's screen, all stimulus sizes and positions were defined in PsychoPy's ``height'' units, with the bottom left of a 16:10 aspect ratio screen being represented as (-.8, -.5) and the top right being (.8, .5). The height for all text stimuli was 0.1 units. Each trial began with a six-character pattern mask (\emph{\#\#\#\#\#\#}) set to be presented for 500 ms, followed first by the lowercase prime (e.g.~\emph{region}) set to be presented for either 33.3 or 50 ms, and then by the uppercase target (e.g.~\emph{REGION}). Participants were instructed to respond to the target stimulus as quickly as possible by pressing the ``Z'' key of their keyboard (if their device had one) if the target was not a valid English word or the ``M'' key if the target was a valid English word. Participants on a device without a keyboard were instructed to respond by touching one of two rectangular touch areas labeled ``Z = Non-word'' (presented at -0.4, -0.3) and ``M = Word'' (presented at 0.4, -0.3). The touch areas each had a width of 0.4 and a height of 0.2 and were presented in white with a black outline. If participants did not respond within two seconds of the target onset, a ``Too slow!'' feedback message was shown for 500 ms and the trial ended. The experimental trials were preceded by 16 practice trials during which participants also received feedback on the accuracy of their responses. No feedback apart from the trial timeout feedback was given during the experimental trials. Every 120 trials, participants were asked to take a short break before continuing the experiment. After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.

\hypertarget{data-analysis}{%
\subsubsection{Data analysis}\label{data-analysis}}

We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.10.5; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.7; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.3; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.3; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.25; Xie, 2021).}. We only analyzed trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as incorrect responses (5.84 \% of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.36 \% of trials). For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.~identical) and prime duration (33.3 ms vs.~50 ms) as well as their interaction as the fixed effects. For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -0.5 and unrelated was coded as 0.5. For priming duration, 33.3 ms was coded as -0.5 and 50 ms was coded as 0.5. We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items. We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component \(\mu\) and the scale parameter of the exponential component \(\beta\) (equaling the inverse of the rate parameter \(\lambda\)) being allowed to vary between conditions. To model response accuracy, we used the Bernoulli distribution with a logit link. We used the default priors suggested by \emph{brms} except for the coefficients for the fixed effects, for which we applied weakly informative priors of \(\beta \sim N(0,100)\) in order to rule out improbably large effect sizes. Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warm-up iterations for the accuracy models). We consider an effect as credible if the 95\% Credible Interval (CrI) estimated from the posterior distribution does not contain zero. In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.

\hypertarget{results}{%
\subsection{Results}\label{results}}

Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table \ref{tab:exp1-descriptive-rt-table} (although note that we only analyzed the word trials).

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp1-descriptive-rt-table}Mean, Median, Standard Deviation (SD), range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 1 for each condition.}

\begin{tabular}{lllllllll}
\toprule
Stimulus Type & \multicolumn{1}{c}{Prime Duration} & \multicolumn{1}{c}{Relatedness} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Accuracy}\\
\midrule
Nonword & 33.3 ms & Identity & 700 & 665 & 187 & 263 & 1,776 & 0.91\\
Nonword & 33.3 ms & Unrelated & 702 & 664 & 188 & 256 & 1,770 & 0.92\\
Nonword & 50 ms & Identity & 700 & 658 & 189 & 256 & 1,760 & 0.91\\
Nonword & 50 ms & Unrelated & 699 & 657 & 185 & 251 & 1,796 & 0.93\\
Word & 33.3 ms & Identity & 630 & 599 & 164 & 254 & 1,796 & 0.94\\
Word & 33.3 ms & Unrelated & 652 & 619 & 166 & 254 & 1,783 & 0.93\\
Word & 50 ms & Identity & 608 & 575 & 161 & 265 & 1,784 & 0.96\\
Word & 50 ms & Unrelated & 649 & 620 & 158 & 294 & 1,710 & 0.93\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\hypertarget{response-times}{%
\subsubsection{Response times}\label{response-times}}

Table \ref{tab:exp1-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.

The RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 31.55, 95\% CrI {[}27.16, 35.92{]}), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (\emph{b} = -10.96, 95\% CrI {[}-14.83, -7.11{]}). The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = 19.31, 95\% CrI {[}11.39, 27.09{]}). The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.07{]}). However, the 50 ms prime exposure duration seems to be associated with a slightly lower \(\beta\), i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (\emph{b} = -0.07, 95\% CrI {[}-0.12, -0.03{]}). On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (\emph{b} = 0.03, 95\% CrI {[}-0.05, 0.12{]}).

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp1-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for correct word RTs in Experiment 1.}

\small{

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept ($\mu$) & 633.707 & 8.815 & 617.142 & 651.175 & 1.006\\
Intercept ($\beta$) & 4.686 & 0.042 & 4.601 & 4.768 & 1.001\\
Relatedness ($\mu$) & 31.551 & 2.228 & 27.162 & 35.915 & 1.000\\
Prime Duration ($\mu$) & -10.959 & 1.947 & -14.825 & -7.105 & 1.000\\
Relatedness:Prime Duration ($\mu$) & 19.306 & 4.026 & 11.388 & 27.094 & 1.000\\
Relatedness ($\beta$) & 0.031 & 0.022 & -0.011 & 0.073 & 1.000\\
Prime Duration ($\beta$) & -0.074 & 0.024 & -0.120 & -0.028 & 1.000\\
Relatedness:Prime Duration ($\beta$) & 0.031 & 0.042 & -0.051 & 0.115 & 1.000\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $\beta$ is the scale parameter (the inverse of the rate parameter $\lambda$) of the ex-Gaussian distribution.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

These results can be visualized in the delta plots depicted in Figure \ref{fig:deltas-e1-words}. Delta plots are residual quantile plots that show the distributional differences between conditions (see De Jong et al., 1994). As can be seen in Panel A, there is an identity priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33.3 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33.3 ms one. We also found a slight increase of priming effects for the longest responses (quantile .9) in the 33.3 ms prime duration condition. This apparent anomaly can be understood better by looking at Panel B of the same figure. In this panel, we show the size of the prime duration effect (computed as the difference in response times between responses to the 50 ms condition and responses to the 33.3 ms condition) across RT quantiles. While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition yielded virtually the same response times in the 33.3 and 50 ms conditions, except for a small increase at the 50 ms prime duration for the very long responses (i.e., .9 quantile)--we prefer not to over-interpret this latter finding with the slowest responses, as it did not appear in Experiment 2.

\begin{figure}
\centering
\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e1-words-1.pdf}
\caption{\label{fig:deltas-e1-words}Delta plots depicting the magnitude of the effect over time in Experiment 1. Each dot represents the mean RT at the .1, .3, .5, .7 and .9 quantiles. \emph{Panel A)} Difference in RT between unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right). \emph{Panel B)} Difference in RT between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions.}
\end{figure}

\hypertarget{accuracy}{%
\subsubsection{Accuracy}\label{accuracy}}

Table \ref{tab:exp1-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.

The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.50, 95\% CrI {[}-0.72, -0.31{]}). The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = 0.19, 95\% CrI {[}-0.02, 0.42{]}). The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = -0.53, 95\% CrI {[}-0.94, -0.14{]}).

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp1-acc-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for response accuracy on word trials in Experiment 1.}

\small{

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept & 3.458 & 0.122 & 3.224 & 3.705 & 1.000\\
Relatedness & -0.503 & 0.105 & -0.720 & -0.305 & 1.000\\
Prime Duration & 0.192 & 0.110 & -0.016 & 0.417 & 1.000\\
Relatedness:Prime Duration & -0.530 & 0.206 & -0.944 & -0.138 & 1.000\\
\bottomrule
\end{tabular}

}

\end{threeparttable}
\end{center}

\end{table}

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

The results from Experiment 1 reveal that we were able to replicate benchmark masked priming effects using an online experiment. The size and shape of the effect is similar to that observed in previous studies (e.g., Gomez et al., 2013; Perea et al., 2018; Taikh \& Lupker, 2020; Yang et al., 2021). In addition, we also saw a clear difference between the 33.3 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices. While the shape of the distribution changed slightly between the 33.3 ms and the 50 ms prime exposure durations, we did not observe an effect of the prime relatedness condition on the shape parameter \(\beta\) of the exponential distribution, suggesting, according to the savings hypothesis by Forster (1998), that only encoding processes were affected by the relatedness manipulation. Moreover, as can be observed in Figure \ref{fig:deltas-e1-words}, the effect magnitude was close to the stimulus-onset asynchrony (see also Perea et al., 2018).

Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different. Indeed, to better define the priming effect, one needs a baseline that serves as a reference point (i.e., an analog of the minimum {``intensity''} priming condition; see Jacobs et al., 1995). In order to further explore this question, we performed a second experiment in which we set the prime to be displayed for an even shorter duration. As described in the Introduction, a 16.7 ms prime exposure duration should yield a negligible priming effect (Tzur \& Frost, 2007; Ziegler et al., 2000) so the pattern should be qualitatively different from the 33.3 and 50 ms durations used in Experiment 1. If it does not, this would cast doubt on the timing accuracy in online experiments. In this experiment, we also include the 33.3 ms prime duration condition to not only have a better scheme to compare the two experiments, but also to be able to test the within-condition effects (Jacobs et al., 1995)---assuming the 16.7 ms prime duration serves as a baseline.

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

In the second experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 16.7 ms and 33.3 ms (roughly corresponding to one and two frames at a refresh rate of 60 Hz).

The pre-registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}. The materials, data files, and R scripts can be found at {[}\url{https://osf.io/57rzq/}{]}

\hypertarget{method-1}{%
\subsection{Method}\label{method-1}}

\hypertarget{participants-1}{%
\subsubsection{Participants}\label{participants-1}}

As in Experiment 1, participants were recruited through Prolific (www.prolific.co, 2021). The experiment was accessed by 102 participants. Out of these, 87 provided experimental data. One of these participants did not complete the experiment. A further seven were excluded because of low accuracy (again, less than .8). The remaining 79 participants were aged from 18 to 69 (mean age: 31.14). Of the participants, 40 identified as male, and 39 identified as female. All these participants indicated that English was their first language in the Prolific screening questions. Based on their IP addresses, 56 participants were based in the UK, 14 were based in the US, two participants were based in Canada, two participants were based in South Africa, and one participant each was based in Hungary and Ireland. Three participants could not be localized in this way. As in Experiment 1, all participants were naïve to the purpose of the experiment, and received £1.25 for their participation (corresponding to £5/hour). Participants could use either a desktop/laptop computer or a mobile device. Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.

\textbf{\emph{Rationale for sample size and stopping rule.}} As in Experiment 1, our stopping rule was to keep collecting data until 3,000 valid observations were collected. This goal was met and exceeded in our initial data collection with a budget of £200.

\hypertarget{materials-1}{%
\subsubsection{Materials}\label{materials-1}}

The materials were identical to those used in Experiment 1.

\hypertarget{procedure-1}{%
\subsubsection{Procedure}\label{procedure-1}}

The procedure was identical to Experiment 1, the only difference being that the primes were set to be displayed for either 16.7 ms or 33.3 ms.

\hypertarget{data-analysis-1}{%
\subsubsection{Data analysis}\label{data-analysis-1}}

We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as those with incorrect responses (4.93 \% of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.15 \% of trials). For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5. Otherwise, the model specifications were identical to those in Experiment 1.

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table \ref{tab:exp2-descriptive-rt-table}.

\hypertarget{response-times-1}{%
\subsubsection{Response times}\label{response-times-1}}

As in Experiment 1, the RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 8.53, 95\% CrI {[}5.07, 12.11{]}). For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (\emph{b} = -3.60, 95\% CrI {[}-7.22, -0.03{]}). However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (\emph{b} = 15.17, 95\% CrI {[}8.52, 21.73{]}). The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.02, 0.07{]}), prime exposure duration (\emph{b} = 0.01, 95\% CrI {[}-0.03, 0.05{]}), or their interaction (\emph{b} = -0.03, 95\% CrI {[}-0.12, 0.05{]}), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.

Table \ref{tab:exp2-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.

\newpage

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp2-descriptive-rt-table}Mean, Median, Standard Deviation (SD), and range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 2 for all conditions.}

\begin{tabular}{lllllllll}
\toprule
Stimulus Type & \multicolumn{1}{c}{Prime Duration} & \multicolumn{1}{c}{Relatedness} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Accuracy}\\
\midrule
Nonword & 16.7 ms & Identity & 719 & 680 & 185 & 330 & 1,787 & 0.93\\
Nonword & 16.7 ms & Unrelated & 717 & 677 & 183 & 284 & 1,799 & 0.94\\
Nonword & 33.3 ms & Identity & 717 & 668 & 193 & 351 & 1,787 & 0.94\\
Nonword & 33.3 ms & Unrelated & 715 & 672 & 188 & 281 & 1,789 & 0.94\\
Word & 16.7 ms & Identity & 659 & 625 & 160 & 311 & 1,785 & 0.94\\
Word & 16.7 ms & Unrelated & 661 & 623 & 165 & 308 & 1,796 & 0.95\\
Word & 33.3 ms & Identity & 649 & 618 & 154 & 280 & 1,657 & 0.96\\
Word & 33.3 ms & Unrelated & 667 & 633 & 162 & 269 & 1,701 & 0.94\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp2-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for correct word RTs in Experiment 2.}

\small{

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept ($\mu$) & 656.975 & 9.036 & 639.056 & 674.711 & 1.003\\
Intercept ($\beta$) & 4.658 & 0.043 & 4.573 & 4.741 & 1.003\\
Relatedness ($\mu$) & 8.529 & 1.795 & 5.065 & 12.106 & 1.000\\
Prime Duration ($\mu$) & -3.602 & 1.813 & -7.216 & -0.033 & 1.000\\
Relatedness:Prime Duration ($\mu$) & 15.166 & 3.390 & 8.517 & 21.727 & 1.000\\
Relatedness ($\beta$) & 0.028 & 0.023 & -0.016 & 0.073 & 1.000\\
Prime Duration ($\beta$) & 0.011 & 0.021 & -0.031 & 0.053 & 1.000\\
Relatedness:Prime Duration ($\beta$) & -0.034 & 0.043 & -0.119 & 0.049 & 1.000\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $\beta$ is the scale parameter (the inverse of the rate parameter $\lambda$) of the ex-Gaussian distribution.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

We also created the delta plots of data from Experiment 2 (see Figure \ref{fig:deltas-e2-words}). Panel A, shows there is no priming effect for the 16.7 ms condition, in contrast with a consistent effect across quantiles for the 33.3 ms condition (parallel to the one found in Experiment 1). Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight hindering for unrelated primes.

\begin{figure}
\centering
\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e2-words-1.pdf}
\caption{\label{fig:deltas-e2-words}Delta plots depicting the magnitude of the effect over time in Experiment 2.}
\end{figure}

\hypertarget{accuracy-1}{%
\subsubsection{Accuracy}\label{accuracy-1}}

The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.22, 95\% CrI {[}-0.43, 0.00{]}). The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16.7 ms prime duration condition than in the 33.3 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = -0.05, 95\% CrI {[}-0.31, 0.18{]}). The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33.3 ms condition, and reversed in the 16.7 ms condition (\emph{b} = -0.71, 95\% CrI {[}-1.16, -0.30{]}), although the effect in the 16.7 ms condition was very weak. Table \ref{tab:exp2-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, indicating that the model was fitted successfully as they are all close to 1.

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp2-acc-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for fixed effects of the model fitted for response accuracy on word trials in Experiment 2.}

\small{

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept & 3.734 & 0.135 & 3.476 & 4.007 & 1.000\\
Relatedness & -0.217 & 0.109 & -0.434 & -0.004 & 1.000\\
Prime Duration & -0.055 & 0.126 & -0.306 & 0.184 & 1.000\\
Relatedness:Prime Duration & -0.710 & 0.218 & -1.157 & -0.305 & 1.000\\
\bottomrule
\end{tabular}

}

\end{threeparttable}
\end{center}

\end{table}

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}

In Experiment 2, we found the pattern we expected from previous research: In the mean \(\mu\) of the Gaussian component of the ex-Gaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration (Tzur \& Frost, 2007; Ziegler et al., 2000). This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script. In addition, we did not observe an effect of the prime relatedness on the shape parameter \(\beta\) of the exponential component (i.e., the effect corresponded to a shift of the RT distributions, as shown in in-lab studies; e.g., Taikh \& Lupker, 2020; Yang et al., 2021). Moreover, the magnitude of the priming effect at the 33.3 ms prime exposure duration was close to the magnitude of the prime-target stimulus-onset asynchrony, as can be seen in the delta plots in Figure \ref{fig:deltas-e2-words} (see Gomez et al., 2013; Perea et al., 2018). Hence, we replicated again the commonly observed savings effect (Forster, 1998).

Critically, because the 16.7 ms prime duration condition yielded virtually no priming effects, this very short prime exposure duration serves as a within-condition baseline that allows us to qualify the facilitative vs.~inhibitory nature of masked priming effects (Jacobs et al., 1995; Ziegler et al., 2000). Specifically, when compared to the baseline, our findings at the 33.3 ms prime duration show a combination of a slight facilitatory effect for identity primes and a small inhibitory effect for unrelated primes.

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

In this study, we set out to test whether we could obtain benchmark masked priming effects both qualitatively (i.e., shift in the RT distributions) and quantitatively (i.e., effect sizes) using an online, browser-based experiment software. To that end, we conducted two online masked identity priming experiments (e.g., \emph{region --- REGION} vs.~\emph{launch --- REGION}) in which we manipulated prime exposure duration (33.3 vs.~50 ms in Experiment 1; 16.7 vs.~33 ms in Experiment 2). The results of our online-based experiments replicated and extended benchmarks masked identity priming effects previous in the lab-based studies. We observed the effect sizes predicted by Forster's (1998) savings hypothesis: Our data show a shift in the mean of the Gaussian component of the ex-Gaussian distribution, but no change in the shape parameter \(\beta\) of the exponential component, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes. Furthermore, the size of the priming effect was not only directly influenced by the prime duration, suggesting the experimental software was able to control the display timing of the prime accurately, but also of a similar magnitude to the prime duration (within the range reported in previous studies, e.g., 35-47 ms for a 50 ms prime duration in Perea et al., 2018). Importantly, the use of a within-condition baseline revealed that the identity priming effects at the 33 ms prime exposure duration were a combination of some small facilitation from identity primes and some small inhibition from unrelated primes (see Jacobs et al., 1995, for evidence with a psychophysical experiment). Likewise, the greater identity priming effects at the 50 ms rather than at the 33.3 ms prime exposure duration were essentially due to the facilitation from the identity pairs.

While accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, they are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade. Similarly, unlike in-lab conditions, where the contrast of the computer screens can be measured and kept constant, there is no such a guarantee for the screens used by online participants---note that Tzur and Frost (2007) were only able to observe strong effects for short prime exposure durations when using extreme contrast values. Thus, the fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy, PsychoJS.

Furthermore, our results extend previous work showing the validity of on-line studies measuring response times (e.g., Brysbaert et al., 2016; Cai et al., 2017; Dufau et al., 2011; Eerland et al., 2013; Rodd et al., 2016, to cite a few instances) to the masked priming technique. Thus, the present study opens the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition. Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible. For instance, online participants can be people from different countries and/or cultures, from different age groups, bilinguals/multilinguals, even those who do not own a computer, only a smartphone. Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant. This opens up the possibility of masked-priming crowdsourced megastudies. In general, deploying masked priming experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.

In conclusion, our results give us confidence that high-quality behavioral data using the masked priming paradigm can be collected online using Javascript-based experiment platforms. We hope that future research takes advantage of these new methods in order to make research faster, more inclusive, and more efficient.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-adelman2014}{}%
Adelman, J. S., Johnson, R. L., McCormick, S. F., McKague, M., Kinoshita, S., Bowers, J. S., Perry, J. R., Lupker, S. J., Forster, K. I., Cortese, M. J., Scaltritti, M., Aschenbrenner, A. J., Coane, J. H., White, L., Yap, M. J., Davis, C., Kim, J., \& Davis, C. J. (2014). A behavioral database for masked form priming. \emph{Behavior Research Methods}, \emph{46}(4), 1052--1067. \url{https://doi.org/10.3758/s13428-013-0442-y}

\leavevmode\hypertarget{ref-aguasvivas2020}{}%
Aguasvivas, J., Carreiras, M., Brysbaert, M., Mandera, P., Keuleers, E., \& Duñabeitia, J. A. (2020). How do Spanish speakers read words? Insights from a crowdsourced lexical decision megastudy. \emph{Behavior Research Methods}, \emph{52}(5), 1867--1882. \url{https://doi.org/10.3758/s13428-020-01357-9}

\leavevmode\hypertarget{ref-Alluhaybi_2020}{}%
Alluhaybi, I., \& Witzel, J. (2020). Letter connectedness and arabic visual word recognition. \emph{Quarterly Journal of Experimental Psychology}, \emph{73}(10), 1660--1674. \url{https://doi.org/10.1177/1747021820926155}

\leavevmode\hypertarget{ref-anwyl-irvine2020a}{}%
Anwyl-Irvine, A., Dalmaijer, E. S., Hodges, N., \& Evershed, J. K. (2020). Realistic precision and accuracy of online experiment platforms, web browsers, and devices. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-020-01501-5}

\leavevmode\hypertarget{ref-anwyl-irvine2020}{}%
Anwyl-Irvine, A., Massonni, J., Flitton, A., Kirkham, N., \& Evershed, J. K. (2020). orilla in our midst: An online behavioral experiment builder. \emph{Behavior Research Methods}, \emph{52}(1), 388--407. \url{https://doi.org/10.3758/s13428-019-01237-x}

\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-austSeriousnessChecksAre2013}{}%
Aust, F., Diedenhofen, B., Ullrich, S., \& Musch, J. (2013). Seriousness checks are useful to improve data validity in online research. \emph{Behavior Research Methods}, \emph{45}(2), 527--535. \url{https://doi.org/10.3758/s13428-012-0265-2}

\leavevmode\hypertarget{ref-balota2007}{}%
Balota, D. A., Yap, M. J., Hutchison, K. A., Cortese, M. J., Kessler, B., Loftis, B., Neely, J. H., Nelson, D. L., Simpson, G. B., \& Treiman, R. (2007). The English Lexicon Project. \emph{Behavior Research Methods}, \emph{39}(3), 445--459. \url{https://doi.org/10.3758/BF03193014}

\leavevmode\hypertarget{ref-R-tinylabels}{}%
Barth, M. (2021). \emph{{tinylabels}: Lightweight variable labels}. \url{https://github.com/mariusbarth/tinylabels}

\leavevmode\hypertarget{ref-birnbaumPsychologicalExperimentsInternet2000a}{}%
Birnbaum, M. H., \& Birnbaum, M. O. (2000). \emph{Psychological {Experiments} on the {Internet}}. {Elsevier}. \url{http://books.google.com?id=sw4NHyThFFkC}

\leavevmode\hypertarget{ref-bridges2020}{}%
Bridges, D., Pitiot, A., MacAskill, M. R., \& Peirce, J. W. (2020). The timing mega-study: comparing a range of experiment generators, both lab-based and online. \emph{PeerJ}, \emph{8}, e9414. \url{https://doi.org/10.7717/peerj.9414}

\leavevmode\hypertarget{ref-brysbaert2021a}{}%
Brysbaert, M., Keuleers, E., \& Mandera, P. (2021). Which words do English non-native speakers know? New supernational levels based on yes/no decision. \emph{Second Language Research}, \emph{37}(2), 207--231. \url{https://doi.org/10.1177/0267658320934526}

\leavevmode\hypertarget{ref-brysbaert2018}{}%
Brysbaert, M., \& Stevens, M. (2018). Power Analysis and Effect Size in Mixed Effects Models: A Tutorial. \emph{Journal of Cognition}, \emph{1}(1), 9. \url{https://doi.org/10.5334/joc.10}

\leavevmode\hypertarget{ref-brysbaert2016impact}{}%
Brysbaert, M., Stevens, M., Mandera, P., \& Keuleers, E. (2016). The impact of word prevalence on lexical decision times: Evidence from the dutch lexicon project 2. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{42}(3), 441.

\leavevmode\hypertarget{ref-R-brms_a}{}%
Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}

\leavevmode\hypertarget{ref-R-brms_b}{}%
Bürkner, P.-C. (2018). Advanced {Bayesian} multilevel modeling with the {R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://doi.org/10.32614/RJ-2018-017}

\leavevmode\hypertarget{ref-cai2017accent}{}%
Cai, Z. G., Gilbert, R. A., Davis, M. H., Gaskell, M. G., Farrar, L., Adler, S., \& Rodd, J. M. (2017). \emph{Accent modulates access to word meaning: Evidence for a speaker-model account of spoken word recognition}. \url{https://doi.org/10.31234/osf.io/5x3tb}

\leavevmode\hypertarget{ref-de1994conditional}{}%
De Jong, R., Liang, C.-C., \& Lauber, E. (1994). Conditional and unconditional automaticity: A dual-process model of effects of spatial stimulus-response correspondence. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{20}(4), 731.

\leavevmode\hypertarget{ref-deleeuw2015}{}%
de Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating behavioral experiments in a Web browser. \emph{Behavior Research Methods}, \emph{47}(1), 1--12. \url{https://doi.org/10.3758/s13428-014-0458-y}

\leavevmode\hypertarget{ref-Dubey_2018}{}%
Dubey, N., Witzel, N., \& Witzel, J. (2018). Script differences and masked translation priming: Evidence from hindi-english bilinguals. \emph{Quarterly Journal of Experimental Psychology}, \emph{71}(11), 2421--2438. \url{https://doi.org/10.1177/1747021817743241}

\leavevmode\hypertarget{ref-Dufau_2011}{}%
Dufau, S., Duñabeitia, J. A., Moret-Tatay, C., McGonigal, A., Peeters, D., Alario, F.-X., Balota, D. A., Brysbaert, M., Carreiras, M., Ferrand, L., Ktori, M., Perea, M., Rastle, K., Sasburg, O., Yap, M. J., Ziegler, J. C., \& Grainger, J. (2011). Smart phone, smart science: How the use of smartphones can revolutionize research in cognitive science. \emph{{PLoS} {ONE}}, \emph{6}(9), e24974. \url{https://doi.org/10.1371/journal.pone.0024974}

\leavevmode\hypertarget{ref-R-Rcpp_b}{}%
Eddelbuettel, D., \& Balamuta, J. J. (2018). {Extending extit{R} with extit{C++}: A Brief Introduction to extit{Rcpp}}. \emph{The American Statistician}, \emph{72}(1), 28--36. \url{https://doi.org/10.1080/00031305.2017.1375990}

\leavevmode\hypertarget{ref-R-Rcpp_a}{}%
Eddelbuettel, D., \& François, R. (2011). {Rcpp}: Seamless {R} and {C++} integration. \emph{Journal of Statistical Software}, \emph{40}(8), 1--18. \url{https://doi.org/10.18637/jss.v040.i08}

\leavevmode\hypertarget{ref-eerland2013influence}{}%
Eerland, A., Engelen, J. A. A., \& Zwaan, R. A. (2013). The influence of direct and indirect speech on mental representations. \emph{{PLoS} {ONE}}, \emph{8}(6), e65480. \url{https://doi.org/10.1371/journal.pone.0065480}

\leavevmode\hypertarget{ref-Fern_ndez_L_pez_2019}{}%
Fernández-López, M., Marcet, A., \& Perea, M. (2019). Can response congruency effects be obtained in masked priming lexical decision? \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{45}(9), 1683--1702. \url{https://doi.org/10.1037/xlm0000666}

\leavevmode\hypertarget{ref-forster1998pros}{}%
Forster, K. (1998). The pros and cons of masked priming. \emph{Journal of Psycholinguistic Research}, \emph{27}(2), 203--233.

\leavevmode\hypertarget{ref-forsterRepetitionPrimingFrequency1984}{}%
Forster, K., \& Davis, C. (1984). Repetition priming and frequency attenuation in lexical access. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{10}(4), 680--698. \url{https://doi.org/10.1037/0278-7393.10.4.680}

\leavevmode\hypertarget{ref-forsterDMDXWindowsDisplay2003}{}%
Forster, K., \& Forster, J. (2003). {DMDX}: {A Windows} display program with millisecond accuracy. \emph{Behavior Research Methods, Instruments, \& Computers}, \emph{35}(1), 116--124.

\leavevmode\hypertarget{ref-Gomez_2020}{}%
Gomez, P., \& Perea, M. (2020). Masked identity priming reflects an encoding advantage in developing readers. \emph{Journal of Experimental Child Psychology}, \emph{199}, 104911. \url{https://doi.org/10.1016/j.jecp.2020.104911}

\leavevmode\hypertarget{ref-gomezDiffusionModelAccount2013}{}%
Gomez, P., Perea, M., \& Ratcliff, R. (2013). A diffusion model account of masked versus unmasked priming: {Are} they qualitatively different? \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{39}(6), 1731--1740. \url{https://doi.org/10.1037/a0032333}

\leavevmode\hypertarget{ref-grainger2008cracking}{}%
Grainger, J. (2008). Cracking the orthographic code: An introduction. \emph{Language and Cognitive Processes}, \emph{23}(1), 1--35. \url{https://doi.org/10.1080/01690960701578013}

\leavevmode\hypertarget{ref-grossi2006relatedness}{}%
Grossi, G. (2006). Relatedness proportion effects on masked associative priming: An {ERP} study. \emph{Psychophysiology}, \emph{43}(1), 21--30. \url{https://doi.org/10.1111/j.1469-8986.2006.00383.x}

\leavevmode\hypertarget{ref-R-purrr}{}%
Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. \url{https://CRAN.R-project.org/package=purrr}

\leavevmode\hypertarget{ref-Jacobs_1995}{}%
Jacobs, A. M., Grainger, J., \& Ferrand, L. (1995). The incremental priming technique: A method for determining within-condition priming effects. \emph{Perception {\&} Psychophysics}, \emph{57}(8), 1101--1110. \url{https://doi.org/10.3758/bf03208367}

\leavevmode\hypertarget{ref-lund1996}{}%
Lund, K., \& Burgess, C. (1996). Producing high-dimensional semantic spaces from lexical co-occurrence. \emph{Behavior Research Methods, Instruments, \& Computers}, \emph{28}(2), 203--208. \url{https://doi.org/10.3758/BF03204766}

\leavevmode\hypertarget{ref-R-see}{}%
Lüdecke, D., Ben-Shachar, M. S., Waggoner, P., \& Makowski, D. (2020). See: Visualisation toolbox for 'easystats' and extra geoms, themes and color palettes for 'ggplot2'. \emph{CRAN}. \url{https://doi.org/10.5281/zenodo.3952153}

\leavevmode\hypertarget{ref-R-bayestestR}{}%
Makowski, D., Ben-Shachar, M. S., \& Lüdecke, D. (2019). bayestestR: Describing effects and their uncertainty, existence and significance within the bayesian framework. \emph{Journal of Open Source Software}, \emph{4}(40), 1541. \url{https://doi.org/10.21105/joss.01541}

\leavevmode\hypertarget{ref-mandera2020}{}%
Mandera, P., Keuleers, E., \& Brysbaert, M. (2020). Recognition times for 62 thousand English words: Data from the English Crowdsourcing Project. \emph{Behavior Research Methods}, \emph{52}(2), 741--760. \url{https://doi.org/10.3758/s13428-019-01272-8}

\leavevmode\hypertarget{ref-R-tibble}{}%
Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. \url{https://CRAN.R-project.org/package=tibble}

\leavevmode\hypertarget{ref-paolacciRunningExperimentsAmazon2010}{}%
Paolacci, G., Chandler, J., \& Ipeirotis, P. G. (2010). \emph{Running {Experiments} on {Amazon Mechanical Turk}} (SSRN Scholarly Paper ID 1626226). {Social Science Research Network}. \url{https://papers.ssrn.com/abstract=1626226}

\leavevmode\hypertarget{ref-Parker_2021}{}%
Parker, A., Egan, C., Grant, J. H., Harte, S., Hudson, B. T., \& Woodhead, Z. V. J. (2021). The role of orthographic neighbourhood effects in lateralized lexical decision: A replication study and meta-analysis. \emph{{PeerJ}}, \emph{9}, e11266. \url{https://doi.org/10.7717/peerj.11266}

\leavevmode\hypertarget{ref-pavlovia2020}{}%
Pavlovia. (2020). \emph{Pavlovia}. \url{https://pavlovia.org/}

\leavevmode\hypertarget{ref-R-sp}{}%
Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. \url{https://CRAN.R-project.org/doc/Rnews/}

\leavevmode\hypertarget{ref-R-patchwork}{}%
Pedersen, T. L. (2020). \emph{Patchwork: The composer of plots}. \url{https://CRAN.R-project.org/package=patchwork}

\leavevmode\hypertarget{ref-peirce2019}{}%
Peirce, J., Gray, J. R., Simpson, S., MacAskill, M., Höchenberger, R., Sogo, H., Kastman, E., \& Lindeløv, J. K. (2019). PsychoPy2: Experiments in behavior made easy. \emph{Behavior Research Methods}, \emph{51}(1), 195--203. \url{https://doi.org/10.3758/s13428-018-01193-y}

\leavevmode\hypertarget{ref-Perea_2018}{}%
Perea, M., Marcet, A., Lozano, M., \& Gomez, P. (2018). Is masked priming modulated by memory load? A test of the automaticity of masked identity priming in lexical decision. \emph{Memory {\&} Cognition}, \emph{46}(7), 1127--1135. \url{https://doi.org/10.3758/s13421-018-0825-5}

\leavevmode\hypertarget{ref-perea2002does}{}%
Perea, M., \& Rosa, E. (2002). Does the proportion of associatively related pairs modulate the associative priming effect at very brief stimulus-onset asynchronies? \emph{Acta Psychologica}, \emph{110}(1), 103--124. \url{https://doi.org/10.1016/s0001-6918(01)00074-9}

\leavevmode\hypertarget{ref-prolific2021}{}%
Prolific. (2021). \emph{Prolific \textbar{} online participant recruitment for surveys and market research}. \url{https://www.prolific.co/}

\leavevmode\hypertarget{ref-qualtrics2020}{}%
Qualtrics. (2020). \emph{Qualtrics XM // the leading experience management software}. \url{https://www.qualtrics.com/uk/}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-ratcliff2004}{}%
Ratcliff, R., Gomez, P., \& McKoon, G. (2004). A diffusion model account of the lexical decision task. \emph{Psychological Review}, \emph{111}(1), 159--182. \url{https://doi.org/10.1037/0033-295X.111.1.159}

\leavevmode\hypertarget{ref-reimersPresentationResponseTiming2015}{}%
Reimers, S., \& Stewart, N. (2015). Presentation and response timing accuracy in {Adobe Flash} and {HTML5}/{JavaScript Web} experiments. \emph{Behavior Research Methods}, \emph{47}(2), 309--327. \url{https://doi.org/10.3758/s13428-014-0471-1}

\leavevmode\hypertarget{ref-rezlescu2020}{}%
Rezlescu, C., Danaila, I., Miron, A., \& Amariei, C. (2020). \emph{Chapter 13 - More time for science: Using Testable to create and share behavioral experiments faster, recruit better participants, and engage students in hands-on research} (B. L. Parkin, Ed.; Vol. 253, pp. 243--262). Elsevier. \url{https://doi.org/10.1016/bs.pbr.2020.06.005}

\leavevmode\hypertarget{ref-rodd2016impact}{}%
Rodd, J. M., Cai, Z. G., Betts, H. N., Hanby, B., Hutchinson, C., \& Adler, A. (2016). The impact of recent and long-term experience on access to word meanings: Evidence from large-scale internet-based experiments. \emph{Journal of Memory and Language}, \emph{87}, 16--37. \url{https://doi.org/10.1016/j.jml.2015.10.006}

\leavevmode\hypertarget{ref-R-rworldmap}{}%
South, A. (2011). Rworldmap: A new r package for mapping global data. \emph{The R Journal}, \emph{3}(1), 35--43. \url{http://journal.r-project.org/archive/2011-1/RJournal_2011-1_South.pdf}

\leavevmode\hypertarget{ref-Taikh_2020}{}%
Taikh, A., \& Lupker, S. J. (2020). Do visible semantic primes preactivate lexical representations? \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{46}(8), 1533--1569. \url{https://doi.org/10.1037/xlm0000825}

\leavevmode\hypertarget{ref-Tzur_2007}{}%
Tzur, B., \& Frost, R. (2007). {SOA} does not reveal the absolute time course of cognitive processing in fast priming experiments{{73}}. \emph{Journal of Memory and Language}, \emph{56}(3), 321--335. \url{https://doi.org/10.1016/j.jml.2006.11.007}

\leavevmode\hypertarget{ref-R-ggplot2}{}%
Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}

\leavevmode\hypertarget{ref-R-stringr}{}%
Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. \url{https://CRAN.R-project.org/package=stringr}

\leavevmode\hypertarget{ref-R-forcats}{}%
Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. \url{https://CRAN.R-project.org/package=forcats}

\leavevmode\hypertarget{ref-R-tidyr}{}%
Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. \url{https://CRAN.R-project.org/package=tidyr}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T. L., Miller, E., Bache, S. M., Müller, K., Ooms, J., Robinson, D., Seidel, D. P., Spinu, V., \ldots{} Yutani, H. (2019). Welcome to the {tidyverse}. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

\leavevmode\hypertarget{ref-R-readxl}{}%
Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. \url{https://CRAN.R-project.org/package=readxl}

\leavevmode\hypertarget{ref-R-dplyr}{}%
Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. \url{https://CRAN.R-project.org/package=dplyr}

\leavevmode\hypertarget{ref-R-readr}{}%
Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. \url{https://CRAN.R-project.org/package=readr}

\leavevmode\hypertarget{ref-witzelTestingViabilityWebDMDX2013}{}%
Witzel, J., Cornelius, S., Witzel, N., Forster, K. I., \& Forster, J. C. (2013). Testing the viability of {webDMDX} for masked priming experiments. \emph{The Mental Lexicon}, \emph{8}(3), 421--449. \url{https://doi.org/10.1075/ml.8.3.07wit}

\leavevmode\hypertarget{ref-R-xfun}{}%
Xie, Y. (2021). \emph{Xfun: Miscellaneous functions to support packages maintained by 'yihui xie'}. \url{https://CRAN.R-project.org/package=xfun}

\leavevmode\hypertarget{ref-Yang_2021}{}%
Yang, H., Jared, D., Perea, M., \& Lupker, S. J. (2021). Is letter position coding when reading in L2 affected by the nature of position coding used when bilinguals read in their L1? \emph{Memory {\&} Cognition}, \emph{49}(4), 771--786. \url{https://doi.org/10.3758/s13421-020-01126-1}

\leavevmode\hypertarget{ref-yarkoni2008}{}%
Yarkoni, T., Balota, D., \& Yap, M. (2008). Moving beyond Coltheart{'}s N: A new measure of orthographic similarity. \emph{Psychonomic Bulletin \& Review}, \emph{15}(5), 971--979. \url{https://doi.org/10.3758/PBR.15.5.971}

\leavevmode\hypertarget{ref-ziegler2000}{}%
Ziegler, J. C., Ferrand, L., Jacobs, A. M., Rey, A., \& Grainger, J. (2000). Visual and Phonological Codes in Letter and Word Recognition: Evidence from Incremental Priming. \emph{The Quarterly Journal of Experimental Psychology}, \emph{53A}(3), 671--692.

\leavevmode\hypertarget{ref-Zimmerman_2012}{}%
Zimmerman, R., \& Gomez, P. (2012). Drawing attention to primes increases inhibitory word priming effects. \emph{The Mental Lexicon}, \emph{7}(2), 119--146. \url{https://doi.org/10.1075/ml.7.2.01zim}

\end{CSLReferences}

\newpage

\hypertarget{appendix-a}{%
\section{Appendix A}\label{appendix-a}}

\hypertarget{words}{%
\subsection{Words:}\label{words}}

\begin{verbatim}
##   [1] GLANCE WINTER MILDEW SLEAZY BOTHER PORTAL COURSE SOCIAL CENSOR BACKUP
##  [11] STABLE PLAGUE OBJECT ABSENT RESIGN CREDIT STREAM WICKED INVOKE BEACON
##  [21] ADMIRE FACTOR PHRASE BURDEN LOUNGE TAILOR WREATH HOCKEY SEARCH MONKEY
##  [31] INFECT VERIFY SQUEAL INTAKE PHOBIA BEHALF LIQUOR SHRINK BUCKET VOYAGE
##  [41] MASCOT HINDER KIDNEY PERIOD VULGAR CASINO SELDOM MASTER MOTHER FRINGE
##  [51] EXPORT INJECT NATURE CLUMSY GRUMPY PIRATE POSTER FLOWER LUMBER FOREST
##  [61] FRIGHT BRIDGE KNIGHT TRENCH PLUNGE BUNDLE ANCHOR ABRUPT HUSTLE ETHNIC
##  [71] CRUISE ORANGE STRIVE ALMOST AMOUNT FAUCET CHARGE HUMBLE PATRON BREAST
##  [81] SIMPLE JOCKEY WEALTH PRAISE DOMAIN SPRINT SCREAM COMEDY SKETCH ORIENT
##  [91] WEAPON BUCKLE BUTLER JUNGLE SOCKET VANISH INSULT POWDER INSECT CONVEY
## [101] SPRING CHAPEL TONGUE DANGER CLERGY SINGLE INCOME WALNUT SURVEY SNATCH
## [111] HUNGRY IMPOSE POLICE RAMBLE STROKE AMBUSH CHANGE FOSTER SPLINT PENCIL
## [121] PONDER REGION LAUNCH THRONE SYMBOL GOSPEL POLICY FUMBLE PLENTY SQUARE
## [131] GARDEN BRIGHT SOURCE PLAQUE TROPHY EXOTIC RACKET COLUMN THEORY FAMILY
## [141] FRIEND STIGMA RESULT MORTAL SPRAWL RODENT FILTER HUNGER PERMIT RELISH
## [151] EXPAND STRAND PUBLIC TRAVEL THREAD IGNORE CLIENT BELONG FLUENT CARBON
## [161] WRENCH DIRECT BOUNCE STUDIO NUMBER RANSOM SLOGAN RECKON WONDER POLITE
## [171] INDUCE BREATH CHORUS PLACID GUITAR TUMBLE BRANCH FLIGHT SPIDER STRAIN
## [181] THRIVE LINGER STRIKE BLOUSE NICKEL ENOUGH CASTLE SENIOR MARVEL STUPID
## [191] QUENCH STRONG CHROME STAPLE IMPORT BLEACH FINGER MELODY DEBRIS PRINCE
## [201] ORPHAN SPRUCE REASON SPONGE PARISH COUPLE GARLIC CUSTOM INVADE RANDOM
## [211] MYSTIC ROCKET BEHOLD AUTHOR LIZARD CRADLE DRAGON ISLAND DETAIL VIOLET
## [221] PASTOR CANDLE STRING MARKET INVEST STARCH DESIGN ANSWER GENIUS POUNCE
## [231] DEPART PATROL SHOWER TURKEY FABRIC STRIFE ADVENT INFORM BASKET SILENT
\end{verbatim}

\hypertarget{non-words}{%
\subsection{Non-Words:}\label{non-words}}

\begin{verbatim}
##   [1] KNISMA ALCOUD STRELD PRAILE FRUDGE URIVEL SCHIND TANDLY FUNTLE CAROEY
##  [11] CHRUMS LUNKER DRANCE PITROM IMPURB FRUTAN SNAPEL BAITCH LIMPOR SARIDE
##  [21] RASTOE ABOUNE DORSEX JAUNCE MINKEL RUNAMO GIRCUE SADENT BRUNGE PHRECT
##  [31] CAINKY SURDEN BOLVIS SCOUGE TONDLE BROGET WANIGH BARCET BAFENT MINGAR
##  [41] JUSTRE ABSULT KISPEL CHAITE WHIVEX HOCITE GORBIE WICTOR PADIFS CRUDIO
##  [51] NOBEST CIGNEY CRIBLE HABLIN PEBRIC JOSTED PHOTIE ACRISE LOBUSH ROBULY
##  [61] SMENCO UNWERT MUSIED EATRIC ANOUGS PIATON BLARGE STROLE BATROL MILTED
##  [71] LUPICT STAPOD RESAIT VAROSH APIGHT INLORS VENIOD POLUTH SOUDAL UNJECT
##  [81] STUNCH QUILEW DOLICA VACKEL DISTAR VARMIT PASINK PACKES ORCHET WRIMSY
##  [91] AUBRID DAMILT SORTEL FUMBLO SLEIRT YARMON PETAIN UNIGHS CELOND CURBOL
## [101] MELATY PORLEX VERALF SHAPLE PRUDGE RELDON NYMBEL YACEUP STARBY SPLINO
## [111] PRETCH ABLINT SWANCE INHORT GLEATH BEINCH FERTIC PIERGY STURCH YARION
## [121] FAINCH MILUER FIREAM CLUDIE FORGLE SOUNGE KIRAFE PSETCH AMILOY DANIET
## [131] SPROLY NERAWL PAURSE SPRINE LASTON SCREGM WORBAL REAGLY ZOMBER JOCKAL
## [141] MIATOR SLANCH ROSAIL STEIKH THRUSE IGUADE PLENAC BROAKE YARIKE KENSOM
## [151] GILFEW VANGUE CATRIE WATMEG DESION GHODUS REJOLS WREASH FACHOW FIATCH
## [161] MYRTIE RANDOW AIMOSY SCRILY ABSEND SAUDIC KERIFT DUMPLE ASYLEN NAGURS
## [171] TIESCH TRINGE CLUREY VIRLEX ZINGLY OTHNIS DERAIN FLEACK FONVER DESORY
## [181] PAUCHE TIREAU BREALI IMPOTE GUAIRT TOSHEL SLIQUE HORNAL WRONCH SLEACT
## [191] GEILOY RAMILY BIGENT SLIANT YORQUE IGUARE INJORE SHRILE AUTING CAVORY
## [201] HUNIEK SARLEY AUNGRE GUESCO VEIGMA ANCUST GRONCE CRAGIN WITMER HATRUS
## [211] THELDY ROUNCY GANOUS SPAQUX COLURY FLENGY CAMBLE BLUNDE FOURET WEAROX
## [221] MUSTIL SYNTIC BRUATS CLUIRM FLUMNI NOUPLY SUIVER HURNIA ELOPIA TUNORY
## [231] ORCHIN JILUER EQUATS SERBOL HIGSTA PATHEL EAROUD SUIDLE SLOUNT GUSHOP
\end{verbatim}

\endgroup

\end{document}

### 2021-09-21 final_data_analyses_brms_distributional_revision.R

@@ -114,14 +114,17 @@ library(brms)
 ncores = parallel::detectCores()
 # Mean RTs in each condition
 
-
-prior_exp1 <- c(set_prior("normal(0,2500)", class = "b", coef = "", dpar = ""),
-                set_prior("normal(0,100)", class = "b", coef = "Condition1", dpar = ""),
-                set_prior("normal(0,100)", class = "b", coef = "Condition1:PrimeDuration1"),
-                set_prior("normal(0,100)", class = "b", coef = "PrimeDuration1"),
-                set_prior("normal(0,100)", class = "b", coef = "Condition1", dpar = ""),
+prior_exp1 <- c(set_prior("normal(0,100)", class = "b", coef = "Condition1"),
                 set_prior("normal(0,100)", class = "b", coef = "Condition1:PrimeDuration1"),
                 set_prior("normal(0,100)", class = "b", coef = "PrimeDuration1"))
+
+# prior_exp1 <- c(set_prior("normal(0,2500)", class = "b", coef = "", dpar = ""),
+#                 set_prior("normal(0,100)", class = "b", coef = "Condition1", dpar = ""),
+#                 set_prior("normal(0,100)", class = "b", coef = "Condition1:PrimeDuration1"),
+#                 set_prior("normal(0,100)", class = "b", coef = "PrimeDuration1"),
+#                 set_prior("normal(0,100)", class = "b", coef = "Condition1", dpar = ""),
+#                 set_prior("normal(0,100)", class = "b", coef = "Condition1:PrimeDuration1"),
+#                 set_prior("normal(0,100)", class = "b", coef = "PrimeDuration1"))
 
 # prior_exp1 <- c(set_prior("normal(0,1000)", class = "b"),
 #                 set_prior("normal(0,2500)", class = "Intercept"),
@@ -141,43 +144,12 @@ blmm_exp1_rt_dist <- brm(data = exp1_data_to_include %>% filter(corr == 1 & Stim
                     control = list(adapt_delta = 0.8),
                     cores = 4, backend = "cmdstanr", threads = threading(4))
 
-save(blmm_exp1_rt_dist, file = "blmm_exp1_rt_dist_full_ranef_5000_2.RData")
-
-
-blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 1800), 
[…]

### 2021-09-21 Appendix_B.Rmd
Add new appendix and revisions/reply to editor

# Diffusion model accounts for the data

```{r appendix_setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
```

## About this Appendix

The goal of this appendix is to present a brief description of how the diffusion model accounts for the data presented in the main article. While the diffusion model fits to the grouped data was part of the pre-registration plan, we believe that it is best to present such fits in this appendix as opposed to the main text to improve the readability of the article.  For a full description of the experimental setting and its goals please refer to the main text.

## The diffusion model

The diffusion model (Ratcliff, 1978) is a cognitive process model for perceptual decisions, and it has been quite successful at accounting for lexical decision data (Ratcliff et al, 2004) and more importantly for the present work, masked priming data (Gomez et al, 2012).

The model assumes that RTs to dual choice tasks are a sum of three distinct processes: stimulus encoding, evidence accumulation, and response execution.  The model makes the strong assumption that evidence accumulation is a processes distinct from the other two components, and for practical reasons, it groups response execution and encoding time in a single parameter.

The model is agnostic about the correlation between the encoding and the evidence accumulation processes; and we like to think about it as a tool to instantiate theoretical positions that can be articulated in terms of encoding, decision, and strategic processes.

## Data

The model was fit to the grouped data (as per the pre-registration plan) of the two experiments. For each stimulus type the proportion of word and nonword responses is calculated, then for each of the two responses, the RTs at the .1, .3, .5, .7, and .9 quantiles is obtained. We repeat this process for each participants, and then all of those quantities (response proportions and RTs at quantiles) are averaged across participants.  This process is also known as Vincentalizing, and the averaged quantiles are referred to as vintenciles

The diffusion model predicts the cumulative probability of a response at each RT vincentile, and these model predictions are compared to the empirical proportions, then the sum of the (Observed-Predicted)2/Predicted for correct and error responses for each condition that is minimized with a general
SIMPLEX minimization routine as described by Ratcliff \& Tuerlinckx (2002).

## Free and fixed parameters

In diffusion model fits, researchers can decide what parameters are free to vary across different conditions. In the present work we implemented 3 versions of the model.  These versions of the model varied in terms of which parameters were allowed to vary for which conditions.

In our case, we decided to examine two models as described below. For both models, the $a$ boundary separation, the $z$ starting point, the $\eta$ between trial variability in drift rate, and all other variability parameters are kept constant across all conditions.

**Model 1:** Drift rates vary as a function of lexicality and prime duration, but not from unrelated to identity primes. $T_{er}$ varied from as a function of prime duration and type and also of lexicality.

**Model 2:** The drift rates vary as a function of prime duration and type and also of lexicality. And the drift rate varied only as a function of prime type/duration but not lexicality.

In short, in Model 1, the priming effects are accounted by $T_{er}$ only, while in Model 2 they are accounted for by both drift rate and $T_{er}$.

The two models have equal number of parameters so a direct comparison in possible.   For both experiments the preferred model is Model 1 (the $T_{er}$ model).  This is in agreement with the Gomez et al (2012) study using in-person testing methods.

```{r model_parameters_table, warning=FALSE, echo=FALSE, message=FALSE}
Experiments <-c("1","2")
ModelTer <-  c(39.6512, 10.2111)
ModelDrift <-c(80.6537, 28.6464)

tibble(Experiments,ModelTer,ModelDrift) %>% apa_table(
  caption = "$\\chi^2$ values for the two models for both experiments."
  , escape = FALSE
)  
```

```{r experiment_data}
exp1.8ter <-c(0.1055,0.0562,0.0395,-0.2522,0.0000,-0.2503,0.0000,0.2909,0.0000,0.3119,0.0000,0.0128,0.5071,0.1275,0.0058,0.5090,0.5048,0.5074,0.4737,0.4920
              ,0.4589,0.4959,39.6512)

exp2.8ter <- c(0.1074,0.0543,0.0384,-0.2723,0.0000,-0.2536,0.0000,0.3219,0.0000,0.3232,0.0000,0.0137,0.5404,0.1225,0.0045,0.5408,0.5295,0.5293,0.5025,0.5026
               ,0.4945,0.5098,10.2111)

exp1.8drift.8 <- c(0.1085, 0.0655, 0.0262,-0.2746,-0.2878,-0.2547,-0.3166, 0.2927, 0.2549, 0.3139, 0.2818, 0.0113, 0.4867, 0.1378, 0.0058, 0.4966, 0.4742, 0.5031,80.6537)

exp2.8drift.8 <- c(0.1103, 0.0653, 0.0337,-0.2995,-0.2941,-0.2820,-0.3180, 0.3108, 0.3068, 0.3083, 0.2989, 0.0109, 0.5186, 0.1301, 0.0054, 0.5184, 0.5091, 0.5225,28.6464)
```

## Summary

Examining the parameter values for $T_{er}$ in the tables below shows that the $T_{er}$  effect follows the duration of the prime-TARGET SOA particularly in the word items and not so much in the nonword items.

This is in general agreement with the Gomez et al. (2013) original paper and Gomez and Perea's (2020) work with developmental readers.   In short, these fits confirm that masked priming effects are consistent with the idea of a head start in the encoding process when there is an identity relationship between primes and targets.

```{r appendix_table_2}
library(tidyverse)
Experiment1 <-c(0.5071,0.5090,0.5048,0.5074,0.4737,0.4920,0.4589,0.4959)

Experiment2 <-c(0.5404,0.5408,0.5295,0.5293,0.5025,0.5026,0.4945,0.5098)

Parameters <-c( "$T_{er}$ values for Experiment 1.  33ms nonword ID", "$T_{er}$ values for Experiment 1. 33ms nonword Unrel",
                "$T_{er}$ values for Experiment 1.  50ms nonword ID", "$T_{er}$ values for Experiment 1. 50ms nonword Unrel",
                "$T_{er}$ values for Experiment 1.  33ms word ID", "$T_{er}$ values for Experiment 1. 33ms word Unrel",
                "$T_{er}$ values for Experiment 1.  50ms word ID", "$T_{er}$ values for Experiment 1. 50ms word Unrel")

tibble(Parameters,Experiment1) %>%
  apa_table(
    caption = "$T_{er}$ values for Experiment 1."
    , escape = FALSE
  )

```

```{r appendix_table_3}

Parameters <-c( "$T_{er}$ 16ms nonword ID", "$T_{er}$ 16ms nonword Unrel",
                "$T_{er}$ 33ms nonword ID", "$T_{er}$ 33ms nonword Unrel",
                "$T_{er}$ 16ms word ID", "$T_{er}$ 16ms word Unrel",
                "$T_{er}$ 33ms word ID", "$T_{er}$ 33ms word Unrel")
tibble(Parameters,Experiment2) %>%
  apa_table(
    caption = " $T_{er}$ values for Experiment 2."
    , escape = TRUE
  )

```

\newpage

## References
Gomez, P., & Perea, M. (2020). Masked identity priming reflects an encoding advantage in developing readers. Journal of Experimental Child Psychology, 199, 104911. https://doi.org/10.1016/j.jecp.2020.104911

Gomez, P., Perea, M., & Ratcliff, R. (2013). A diffusion model account of masked versus unmasked priming: Are they qualitatively different? Journal of Experimental Psychology: Human Perception and Performance, 39 (6), 1731–1740. https://doi.org/10.1037/a0032333

Ratcliff, R. (1978). A theory of memory retrieval. Psychological Review, 85, 59–108. https://doi.org/10.1037/0033-295X.85.2.59

Ratcliff, R., Gomez, P., \& McKoon, G. (2004). A diffusion model account of the lexical decision task. Psychological Review, 111, 159–182. doi://10.1037/0033-295X.111.1.159

Ratcliff, R.,\& Tuerlinckx, F. (2002). Estimating the parameters of the diffusion model: Approaches to dealing with contaminant reaction times and parameter variability. Psychonomic Bulletin and Review, 9, 438–481. https://doi.org/10.3758/BF03196302

### 2021-09-21 Appendix_test.Rmd
Add new appendix and revisions/reply to editor

--- 2021-09-21 MaskedPriming_revision.Rmd
@@
 ---
-title             : |
-    | Does online masked priming pass the test?
-    | The effects of prime exposure duration on masked identity priming
-shorttitle        : "Online masked priming"
-author:
+appendix: 
+  - "./Appendix_A.Rmd"
+  - "./Appendix_B.Rmd"
+output: papaja::apa6_pdf
+---
 
-  - name          : "Bernhard Angele"
-    affiliation   : "1,2"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Psychology, Faculty of Science and Technology, Talbot Campus, Fern Barrow, Poole BH12 5BB, UK"
-    email         : "bangele@bournemouth.ac.uk"
-  - name          : "Ana Baciero"
-    affiliation   : "2,3"
-  - name          : "Pablo Gómez"
-    affiliation   : "4"
-  - name          : "Manuel Perea"
-    affiliation   : "2,5"
-affiliation:
-
-  - id            : "1"
-    institution   : "Bournemouth University, Bournemouth, UK"
-  - id            : "2"
-    institution   : "Universidad Antonio de Nebrija, Madrid, Spain"
-  - id            : "3"
-    institution   : "DePaul University, Chicago, USA"
-  - id            : "4"
-    institution   : "California State University San Bernardino, Palm Desert Campus, USA"
-  - id            : "5"
-    institution   : "Universitat de València, Valencia, Spain"
-note: "\\clearpage"
-authornote: |
-
-  We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.
-
-  This research has been partly supported by Grant PSI2017-86210-P from  the  Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).
-
-  This study was pre-registered on the Open Science Framework (OSF) prior to data collection.
-The registration form for Experiment 1, together with the materials, data files, and R scripts can be found at [https://osf.io/57rzq/].
-The registration form for Experiment 2 can be found at [https://osf.io/957s8].
-abstract: |
-  Masked priming is one of the most important paradigms in the study of visual word recognition, but it is usually thought to require a laboratory setup with a known monitor and keyboard.
-To test if this technique can be safely used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS [@peirce2019].
-Importantly, we also tested the role of prime exposure duration (33.3 vs.
-50 ms in Experiment 1 and 16.7 vs.
-33.3 ms in Experiment 2), thus allowing us to examine both across conditions and within-conditions effects.
-We found that our online data are indeed very similar to the masked priming data previously reported in the masked priming literature.
-Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33.3 ms and no priming effect at 16.7 ms prime duration.
-From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., PsychoPy) can present stimuli and collect responses on standard end user devices with enough precision.
-These findings provide us with confidence that masked priming can be used online, thus allowing us not only to run less time-consuming experiments, but also to reach populations that are difficult to test in a laboratory.
-
-keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
-wordcount         : "7916"
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-csl               : "apa.csl"
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-bibliography: ["references.bib", "r-references.bib"]
-editor_options: 
-  chunk_output_type: console
----
+This is the manuscript.
 
@@
 
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-knitr::opts_chunk$set(error = TRUE)
-```
-
-Masked priming [@forsterRepetitionPrimingFrequency1984] is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition [see @forster1998pros; @grainger2008cracking, for reviews].
-Priming refers to the influence of a prime stimulus (e.g., *nurse*, *horse*) on a subsequently presented stimulus that the participant has to respond to (e.g., "is *DOCTOR* a word?").
-Priming effects are measured as the difference in a dependent variable (e.g., response time [RT]) between two conditions (e.g., unrelated: *horse-DOCTOR*; related: *nurse-DOCTOR*).
-In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a pattern mask (e.g., \#\#\#\#\#) for a much longer duration (typically 500 ms).
-The rationale of the procedure is to make participants unaware of the identity of the masked prime [@forsterRepetitionPrimingFrequency1984; @forster1998pros], thus minimizing the role of participants' strategies.
-Indeed, masked priming experiments do not show the strategical effects that occur with visible, unmasked primes [e.g., @grossi2006relatedness; @perea2002does].
-
-The masked priming paradigm has been used in a large number of studies over the last decades.
-For instance, a search of the expression "masked priming" in Google Scholar in May 2021 produced more than 10,000 hits.
-Nearly all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003.
-The issue we examine in the present paper is whether masked priming experiments can be conducted in an online setting without significant changes in the pattern of results.
-Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
-Indeed, researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010].
-
-Cognitive psychologists have been much slower that their behavioral economics colleagues in taking up online paradigms [see @brysbaert2016impact; @cai2017accent; @Dufau_2011; @eerland2013influence; @rodd2016impact, for some exceptions], often due to concerns about the validity of the results.
-Such concerns are not limited to cognitive studies [see @austSeriousnessChecksAre2013], but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
-Furthermore, these concerns are even more central in the masked priming technique, where it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
-For instance, presenting the masked prime for longer than intended (e.g., 83 ms or longer instead of the nominal 50 ms) could counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest [see @Zimmerman_2012].
-
-There have been attempts to address these concerns.
-@witzelTestingViabilityWebDMDX2013 developed a Web version of DMDX (webDMDX) showing promising results in a trial experiment.
-However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a "true" online programming script that could be run inside of a browser.
-A downside of this format is that participants often are (and should be) understandably skeptical about downloading and running executable files from the Internet.
-Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
-As a consequence, the use of webDMDX in masked priming experiments has been rather limited so far [see @Alluhaybi_2020; @Dubey_2018, for exceptions].
-
-Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web.
-Most notably, the HTML5 standard now makes it possible to use Javascript in order to draw stimuli interactively and monitor participant responses with remarkable flexibility inside the browser.
-Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets [@reimersPresentationResponseTiming2015].
-There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020], and open-source such as jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of PsychoPy 3, @peirce2019].
-In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
-Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility of recruiting participants for on-line experiments based on various specific characteristics set up by the experimenters regardless of their location (e.g., native French speakers, not older than 30 years old, not currently in college).
-
-Of course, despite the technological advances, many cognitive psychologists still have concerns about timing and measurement precision.
-While Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (e.g., to avoid delays, all stimuli are usually downloaded before the start of the experiment), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
-Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
-As @reimersPresentationResponseTiming2015 pointed out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
-If the results of the Web-based study are comparable to previous lab-based results, this suggests that, whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
-
-The first approach has the advantage that differences in presentation timings can be objectively recorded and evaluated.
-A very thorough recent example of this approach is the "timing mega-study" by @bridges2020, who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
-The very similar study by @anwyl-irvine2020a compares only online packages and browsers with regard to timing.
-Overall, @bridges2020 found that online packages were capable of presenting visual stimuli with reasonable precision, although the lab-based packages were slightly better in this regard.
-This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
-If this is not possible, there is no point in moving forward to the second approach and replicating specific paradigms.
-However, it is of course impossible to test every possible device and configuration that participants might use.
-On the other hand, some of the differences in precision and accuracy between setups that can be observed using a photodiode may be too small to have an influence on actual participant performance.
-Therefore, we consider replication of previous key lab-based effects a more important test of online paradigms than photodiode measurements.
-Based on the results by @bridges2020 and @anwyl-irvine2020a, modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
-To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study.
-Importantly, we will do so using PsychoPy/PsychoJS [@peirce2019] as it showed high precision and accuracy across the great majority of platforms [@bridges2020; @anwyl-irvine2020a], in addition to being an open-source software.
-
-Specifically, in this study we were interested in whether we could replicate and extend a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming is commonly described as a savings effect.
-As first suggested by @forster1998pros, for a masked identity prime, "the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner", whereas for an unrelated prime, "the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur" (p.
-213).
-Thus, according to the savings account, a target word like *DOCTOR* would enjoy an encoding advantage when preceded by an identity prime such as *doctor* than when preceded by an unrelated prime such as *pencil* (i.e., a head-start).
-One implication of such benefit is that the RT distributions of the unrelated and identity pairs should reflect a shift rather than a change in shape.
-Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony (SOA).
-Empirical evidence supporting this view has been obtained in several studies not only with skilled adults but also with developing readers [e.g., @gomezDiffusionModelAccount2013; @Gomez_2020; @Taikh_2020; @Yang_2021].
-@gomezDiffusionModelAccount2013 proposed an implementation of this hypothesis within the diffusion model [@ratcliff2004].
-This implementation proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution ($T_{er}$) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached.
-Importantly, in the decision process, the information gathered from the stimulus can vary in noise, depending on its quality, which modifies the rate at which information is accumulated (i.e., the *drift rate*).
-With regards to RTs from masked priming tasks, @gomezDiffusionModelAccount2013 found that the difference between identity and unrelated conditions could be accounted for by a change in the $T_{er}$ parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a more skewed RT distribution in the slower, unrelated condition.
-
-Critically, the above pattern is specific to *masked* priming.
-In fact, the most common pattern of results in latency based tasks is that conditions that produce longer latencies will also produce larger variance.
-This pattern is evident in priming as well---when primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles [i.e., a change in shape rather than a shift in RT distributions; see @gomezDiffusionModelAccount2013].
-Fits from the diffusion model show that this result corresponds to changes in both the $T_{er}$ parameter and the drift rate.
-Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word, unlike in masked priming.
-Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.
-both encoding and information quality in unmasked priming.
-
-In the present paper, we took advantage of the above marker to examine whether online masked priming studies follow the same pattern as in-lab masked priming studies.
-Specifically, we manipulated prime exposure duration in identity vs.
-unrelated primes: 33.3 vs.
-50 ms in Experiment 1, and 16.7 vs.
-33.3 ms in Experiment 2---note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA).
-The rationale of Experiment 1 is that if the actual exposure duration of the primes is the nominal exposure duration, then we would expect the typical shift between the identity and unrelated response time distributions, which according to the savings hypothesis [@forster1998pros] would be greater for 50 ms than for 33.3 ms exposure duration (i.e., the head-start would be greater for 50 ms identity primes than for 33.3 ms identity primes).
-This outcome would indicate that the on-line masked priming studies reproduce a characteristic signature of laboratory masked priming studies.
-Alternatively, if the online presentation conditions lead to a greater actual exposure duration on the participant's device compared to that specified in our experiment (e.g.,if prime durations were, on average, 20 ms longer than intended), then the 50 ms primes may no longer be adequately masked, but may rather be consciously perceived.
-If this is the case, the prime could affect not only the encoding, but also core decision processes (i.e., the drift rate), which would be reflected as a stronger priming effect in the higher quantiles of the distribution (i.e., the two RT distributions would have a different shape).
-In this scenario, one should be very cautious when running online masked priming experiments---at least with the typical software and hardware currently available.
-
-To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for replacing the 50 ms prime exposure duration with a very short prime exposure duration, namely, 16.7 ms.
-Similar extremely brief prime exposure durations have shown very weak masked priming lexical decision experiments in a laboratory setting: less than 5 ms for a prime duration of 14 ms [@ziegler2000] and less than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16.7 ms when using a very high level of contrast in the computer screen.
-Thus, if the size of the priming effect is roughly similar to the prime exposure duration, we would expect a much larger priming effect at the 33.3 ms prime exposure duration than at the 16.7 ms prime exposure duration.
-If we do observe a large effect at the 16.7 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments.
-Keep in mind that we are using a software that has very good control over the exposure duration [@bridges2020; @anwyl-irvine2020a].
-Figure \ref{fig:hyp-mod-dat-figure} displays the link between all these verbal hypotheses, the process model that corresponds to each of them, and their predictions in the RT distributions.
-
-All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
-This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms [e.g., @aguasvivas2020; @brysbaert2021a; @mandera2020; @brysbaert2016impact].
-So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries [e.g., @adelman2014].
-Importantly, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.
-unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) [see @Jacobs_1995; @ziegler2000, for advantages of within-condition comparisons].
-Thus, the within-subject manipulation of prime exposure duration in both experiments allows us to obtain a comprehensive picture of masked identity priming effects--also including the examination of potential inhibitory effects of unrelated primes.
-
-\newpage
-
-```{r hyp-mod-dat-figure, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE, fig.height=3.4, fig.cap = "Mapping from hypotheses to data via evidence accumulation models.
-The bottom part of each graph represents sample paths, and the top part shows the cumulative density functions.
-From left to right: *Null Effect* - there are no differences between the conditions; *Effect in Encoding* - the difference between the conditions is on the encoding time, hence the RT distributions are shifted; and *Effect of Encoding and Evidence Accumulation* - the differences between the conditions is on the rate of evidence accumulation, thus increasing the effect size for longer RTs (right-tail of the distribution)."}
-
-suppressMessages(library("tidyverse"))
-
-#pdf("Fig1_ModelsToData.pdf", height = 3)
-
-par(mfrow=c(1,3))
-tdp   <- .386
-sd.dp <- .100
-
-nsims <- 1000000
-
-slope.gray  <- 0.00001
-slope.blue   <- rnorm(nsims, 3, .6)
-slope.yellow <- rnorm(nsims, 3, .6)
-
-sim.trials.blue<-matrix(ncol=4, nrow=nsims)
-sim.trials.yellow<-matrix(ncol=4, nrow=nsims)
-
-sim.trials.blue[,1]    <-  rep(tdp+.05, nsims)
-sim.trials.yellow[,1]  <-  rep(tdp+.05, nsims)
-
-sim.trials.blue[ ,2]   <- (slope.gray * sim.trials.blue[,1])
-sim.trials.yellow[ ,2] <- (slope.gray * sim.trials.yellow[,1])
-
-sim.trials.blue[ ,3]   <- (sim.trials.blue[,2] - slope.blue * sim.trials.blue[,1])
-sim.trials.yellow[ ,3] <- (sim.trials.yellow[,2] - slope.yellow * sim.trials.yellow[,1])
-
-sim.trials.blue[ ,4]   <- (1 - sim.trials.blue[,3]) / slope.blue
-sim.trials.yellow[ ,4] <- (1 - sim.trials.yellow[,3]) / slope.yellow
-
-nlines<- 1000
-sample.blue <- sample(1:nsims,nlines)
-sample.yellow <- sample(1:nsims,nlines)
-
-plot(c(rep(0,nlines),sim.trials.blue[sample.blue,1]), c(rep(.02,nlines),.02+sim.trials.blue[sample.blue,2]), type="l", col=alpha("dodgerblue2",alpha = .5), ylim = c(0,1.7), xlim=c(0,1.2), bty="n",yaxt='n', xlab="RT (sec)", ylab="", lwd=3)
-
-lines(c(rep(0,nlines),sim.trials.yellow[sample.yellow,1]), c(rep(0,nlines),sim.trials.yellow[sample.yellow,2]), type="l", col=alpha("deeppink2",alpha = .5), lwd=3)
-
-for(i in 1:nlines){
-    lines(c(sim.trials.blue[sample.blue[i],1], sim.trials.blue[sample.blue[i],4]), c(sim.trials.blue[sample.blue[i],2], 1), col=alpha("dodgerblue2",alpha = .005),lwd=2)
-
-    lines(c(sim.trials.yellow[sample.yellow[i],1], sim.trials.yellow[sample.yellow[i],4]), c(sim.trials.yellow[sample.yellow[i],2], 1), col=alpha("deeppink2",alpha = .005), lwd=2)
-}
-
-lines(density(sim.trials.yellow[,4], from=.4,to=1.5)$x,(density(sim.trials.yellow[,4],, from=.4,to=1.5)$y)/20+1, col=alpha("deeppink2",alpha = 1), lwd=1)
-lines(density(sim.trials.blue[,4], from=.4,to=1.5)$x,(density(sim.trials.blue[,4], from=.4,to=1.5)$y)/20+1, col=alpha("dodgerblue2",alpha = .3),lwd=4)
-
-lines(c(0, 1), c(1,1), lwd=1.5)
-
-lines(c(tdp, tdp), c(0,1), lty=2)
-lines(c(tdp+.05, tdp+.05), c(0,1), lty=2)
-
-text("Evidence\naccumulation",x = .88, y=.4,cex=.8)
-text("Encoding",x = .2, y=.4,cex=.8)
-title("Null Effect")
-
-###########################################################################
-
-tdp   <- .386
-sd.dp <- .100
-
-nsims <- 1000000
-
-slope.gray  <- 0.00001
-slope.blue   <- rnorm(nsims, 3, .6)
-slope.yellow <- rnorm(nsims, 3, .6)
-
-sim.trials.blue<-matrix(ncol=4, nrow=nsims)
-sim.trials.yellow<-matrix(ncol=4, nrow=nsims)
-
-sim.trials.blue[,1]    <-  rep(tdp, nsims)
-sim.trials.yellow[,1]  <-  rep(tdp+.05, nsims)
-
-sim.trials.blue[ ,2]   <- (slope.gray * sim.trials.blue[,1])
-sim.trials.yellow[ ,2] <- (slope.gray * sim.trials.yellow[,1])
-
-sim.trials.blue[ ,3]   <- (sim.trials.blue[,2] - slope.blue * sim.trials.blue[,1])
-sim.trials.yellow[ ,3] <- (sim.trials.yellow[,2] - slope.yellow * sim.trials.yellow[,1])
-
-sim.trials.blue[ ,4]   <- (1 - sim.trials.blue[,3]) / slope.blue
-sim.trials.yellow[ ,4] <- (1 - sim.trials.yellow[,3]) / slope.yellow
-
-nlines<- 1000
-sample.blue <- sample(1:nsims,nlines)
-sample.yellow <- sample(1:nsims,nlines)
-
-plot(c(rep(0,nlines),sim.trials.blue[sample.blue,1]), c(rep(.02,nlines),.02+sim.trials.blue[sample.blue,2]), type="l", col=alpha("dodgerblue2",alpha = .5), ylim = c(0,1.7), xlim=c(0,1.2), bty="n",yaxt='n', xlab="RT (sec)", ylab="", lwd=3)
-
-lines(c(rep(0,nlines),sim.trials.yellow[sample.yellow,1]), c(rep(0,nlines),sim.trials.yellow[sample.yellow,2]), type="l", col=alpha("deeppink2",alpha = .5), lwd=3)
-
-for(i in 1:nlines){
-    lines(c(sim.trials.blue[sample.blue[i],1], sim.trials.blue[sample.blue[i],4]), c(sim.trials.blue[sample.blue[i],2], 1), col=alpha("dodgerblue2",alpha = .006),lwd=2)
-
-    lines(c(sim.trials.yellow[sample.yellow[i],1], sim.trials.yellow[sample.yellow[i],4]), c(sim.trials.yellow[sample.yellow[i],2], 1), col=alpha("deeppink2",alpha = .006), lwd=2)
-
-}
-
-lines(density(sim.trials.yellow[,4], from=.4,to=1.5)$x,(density(sim.trials.yellow[,4],, from=.4,to=1.5)$y)/20+1, col=alpha("deeppink2",alpha = .7), lwd=2)
-lines(density(sim.trials.blue[,4], from=.4,to=1.5)$x,(density(sim.trials.blue[,4], from=.4,to=1.5)$y)/20+1, col=alpha("dodgerblue2",alpha = .7),lwd=2)
-
-lines(c(0, 1), c(1,1), lwd=1.5)
-
-lines(c(tdp, tdp), c(0,1), lty=2)
-lines(c(tdp+.05, tdp+.05), c(0,1), lty=2)
-
-text("Evidence\naccumulation",x = .88, y=.4,cex=.8)
-text("Encoding",x = .2, y=.4,cex=.8)
-
-title("Effect in\nEncoding")
-
-#############################################################################
-
-tdp   <- .386
-sd.dp <- .100
-
-nsims <- 1000000
-
-slope.gray  <- 0.00001 
-slope.blue   <- rnorm(nsims, 3.8, .6)
-slope.yellow <- rnorm(nsims, 3, .6)
-
-sim.trials.blue<-matrix(ncol=4, nrow=nsims)
-sim.trials.yellow<-matrix(ncol=4, nrow=nsims)
-
-sim.trials.blue[,1]    <-  rep(tdp, nsims)
-sim.trials.yellow[,1]  <-  rep(tdp+.05, nsims)
-
-sim.trials.blue[ ,2]   <- (slope.gray * sim.trials.blue[,1])
-sim.trials.yellow[ ,2] <- (slope.gray * sim.trials.yellow[,1])
-
-sim.trials.blue[ ,3]   <- (sim.trials.blue[,2] - slope.blue * sim.trials.blue[,1])
-sim.trials.yellow[ ,3] <- (sim.trials.yellow[,2] - slope.yellow * sim.trials.yellow[,1])
-
-sim.trials.blue[ ,4]   <- (1 - sim.trials.blue[,3]) / slope.blue
-sim.trials.yellow[ ,4] <- (1 - sim.trials.yellow[,3]) / slope.yellow
-
-nlines<- 1000
-
-sample.blue <- sample(1:nsims,nlines)
-sample.yellow <- sample(1:nsims,nlines)
-
-plot(c(rep(0,nlines),sim.trials.blue[sample.blue,1]), c(rep(.02,nlines),.02+sim.trials.blue[sample.blue,2]), type="l", col=alpha("dodgerblue2",alpha = .5), ylim = c(0,1.7), xlim=c(0,1.2), bty="n",yaxt='n', xlab="RT (sec)", ylab="", lwd=3)
-
-lines(c(rep(0,nlines),sim.trials.yellow[sample.yellow,1]), c(rep(0,nlines),sim.trials.yellow[sample.yellow,2]), type="l", col=alpha("deeppink2",alpha = .5), lwd=3)
-
-for(i in 1:nlines){
-    lines(c(sim.trials.blue[sample.blue[i],1], sim.trials.blue[sample.blue[i],4]), c(sim.trials.blue[sample.blue[i],2], 1), col=alpha("dodgerblue2",alpha = .006),lwd=2)
-
-    lines(c(sim.trials.yellow[sample.yellow[i],1], sim.trials.yellow[sample.yellow[i],4]), c(sim.trials.yellow[sample.yellow[i],2], 1), col=alpha("deeppink2",alpha = .006), lwd=2)
-
-}
-
-lines(density(sim.trials.yellow[,4], from=.4,to=1.5)$x,(density(sim.trials.yellow[,4],, from=.4,to=1.5)$y)/20+1, col=alpha("deeppink2",alpha = .7), lwd=2)
-lines(density(sim.trials.blue[,4], from=.4,to=1.5)$x,(density(sim.trials.blue[,4], from=.4,to=1.5)$y)/20+1, col=alpha("dodgerblue2",alpha = .7),lwd=2)
-
-lines(c(0, 1), c(1,1), lwd=1.5)
-
-lines(c(tdp, tdp), c(0,1), lty=2)
-lines(c(tdp+.05, tdp+.05), c(0,1), lty=2)
-
-text("Evidence\naccumulation",x = .88, y=.4,cex=.8)
-text("Encoding",x = .2, y=.4,cex=.8)
-
-title("Effect in Encoding and \nEvidence Accumulation")
-
-#dev.off()
-
-```
-
-# Experiment 1
-
-In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33.3 ms and 50 ms (roughly corresponding to two and three frames, respectively, at a refresh rate of 60 Hz).
-
-We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the two experiments.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
-
-## Method
-
-```{r load_exp1_data, message=FALSE, echo=FALSE, warning=FALSE}
-
-# Qualtrics survey data
-exp1_all_participants <- read_csv("participant_data_exp1.csv")
-
-# PsychoJS trial data
-exp1 <- fs::dir_ls(path = "./data_exp1", glob = "*.csv") %>%
-  map_dfr(read_csv, .id = "source", col_type = cols(
-  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
-  filter(!is.na(TrialID) & TrialID < 1000) %>%
-  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)
-
-exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
-
-# only consider participants who have actually participated in the whole experiment
-# also don't consider participants whose age is 99 (used for testing)
-# one participant is duplicate. Remove the first occurrence (likely incompatible device)
-
-exp1_actual_participants <- filter(exp1_all_participants, (PROLIFIC_PID %in% exp1$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & (`Response ID` != "R_sU4qJ6UCe9jRKs9"))
-
-# get participants with more than 80% correct responses
-
-exp1_accuracy_by_participant <- exp1 %>% filter(participant %in% exp1_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())
-
-exp1_participants_to_include <- exp1_accuracy_by_participant %>% filter(N == 480 & acc >= .8)
-
-exp1_participants_to_exclude <- exp1_accuracy_by_participant %>% filter(N != 480 | acc < .8)
-
-#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
-
-exp1_data_to_include <- exp1 %>% filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Relatedness = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identity", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33.3 ms", "50 ms")), rt = rt * 1000)
-
-# filter out any of the participants we eliminated from the Qualtrics file as well
-
-exp1_actual_participants <- filter(exp1_actual_participants, (PROLIFIC_PID %in% exp1_data_to_include$participant))
-
-exp1_participant_ages <- exp1_actual_participants$`What is your age?`
-
-exp1_male_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow
-
-exp1_female_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow
-
-# there aren't actually any of these, but will leave the code in just in case
-exp1_other_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
-
-exp1_NA_participants_nr <- filter(exp1_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow
-
-exp1_participant_coords <- exp1_actual_participants %>% select("Location Longitude", "Location Latitude")
-
-#coordinates(exp1_actual_participants) <- c("Location Longitude","Location Latitude")
-
-# from https://stackoverflow.com/questions/14334970/convert-latitude-and-longitude-coordinates-to-country-name-in-r
-
-# The single argument to this function, points, is a data.frame in which:
-#   - column 1 contains the longitude in degrees
-#   - column 2 contains the latitude in degrees
-coords2country = function(points)
-{  
-  countriesSP <- getMap(resolution='low')
-  #countriesSP <- getMap(resolution='high') #you could use high res map from rworldxtra if you were concerned about detail
-
-  # convert our list of points to a SpatialPoints object
-
-  # pointsSP = SpatialPoints(points, proj4string=CRS(" +proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0"))
-
-  #setting CRS directly to that from rworldmap
-  pointsSP = SpatialPoints(points, proj4string=CRS(proj4string(countriesSP)))
-
-  # use 'over' to get indices of the Polygons object containing each point 
-  indices = over(pointsSP, countriesSP)
-
-  # return the ADMIN names of each country
-  indices$ADMIN  
-  #indices$ISO3 # returns the ISO3 code 
-  #indices$continent   # returns the continent (6 continent model)
-  #indices$REGION   # returns the continent (7 continent model)
-}
-
-participant_coords <- exp1_actual_participants %>% select("Location Longitude", "Location Latitude")
-
-exp1_actual_participants$country <- coords2country(participant_coords)
-
-exp1_participant_countries <- table(exp1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
-```
-
-The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at <https://osf.io/57rzq/>.
-
-### Participants
-
-Participants were recruited through Prolific [www.prolific.co, -@prolific2021].
-The experiment was accessed by `r exp1_all_participants$PROLIFIC_PID %>% unique %>% length` participants.
-Out of these, `r exp1_accuracy_by_participant %>% nrow` provided experimental data.
-`r exp1_participants_to_exclude %>% filter(N != 480) %>% nrow %>% numbers_to_words() %>% str_to_sentence()` of these participants did not complete the experiment.
-A further `r exp1_participants_to_exclude %>% filter(N == 480 & acc < .8) %>% nrow %>% ifelse(.
-< 11, numbers_to_words(.), .)` were excluded because of low accuracy (less than .8, which was the pre-registered criterion).
-In the end, we analyzed the data from `r exp1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants (`r exp1_female_participants_nr` female), aged from `r exp1_participant_ages %>% min` to `r exp1_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
-All these participants indicated that English was their first language in the Prolific screening questions.
-Based on their IP addresses, `r exp1_participant_countries["United Kingdom"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in the UK, `r exp1_participant_countries["United States of America"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` were based in the US, `r exp1_participant_countries["Canada"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in Canada, and `r exp1_participant_countries["Ireland"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in Ireland.
-Two participants could not be localized in this way.
-All participants were naïve to the purpose of the experiment and received £1.25 for their participation (corresponding to £5/hour).
-Participants could use either a desktop/laptop computer or a mobile device.
-Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
-
-***Rationale for sample size and stopping rule.*** @brysbaert2018 recommended that masked priming experiments should have at least 1,600 observations per condition.
-In order to account for potentially smaller effect sizes in an online experiment, we set a target of 3,000 observations per condition (12,000 observations total), which corresponds to a minimum of 50 participants given that there were 240 word stimuli in the experiment (see below).
-Our stopping rule was to keep collecting data until 3,000 valid observations were found.
-This goal was met and exceeded in our initial data collection with a budget of £200.
-
-### Materials
-
 ```{r load_trial_data, message=FALSE, echo=FALSE}
@@
 ```
-
-We selected 240 six-letter English words from the English Lexicon Project [@balota2007].
-The mean Zipf frequency based on the HAL corpus [@lund1996] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(Freq_HAL %>% log10)) %>% signif(2)` (range: `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(Freq_HAL %>% log10)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(Freq_HAL %>% log10)) %>% signif(2)`).
-The mean OLD20 [@yarkoni2008] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(OLD)) %>% signif(2)` (range: `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(OLD)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(OLD)) %>% signif(2)`).
-We also selected 240 matched, orthographically legal six-letter nonwords.
-For each target, we created an identical prime (e.g.
-*region --- REGION* and *fainch --- FAINCH*) and an unrelated prime consisting of another word from the list (e.g.
-*launch --- REGION* and *miluer --- FAINCH*)[^1].Unrelated primes were orthographically were paired with the targets by rearranging the order of identity primes (controling for neighbors; see @Perea_2018).
-Appendix A contains a list of the target items, and all counterbalanced lists can be found in the on-line repository.
-
-[^1]: Note that the lexical status of the unrelated prime differed depending on the target type: for word targets, the unrelated primes were words, whereas for nonword targets, they were pseudowords.
-However, as shown by @Fern_ndez_L_pez_2019, the lexical status of the unrelated prime does not affect lexical decision times.
-
-### Procedure
-
-Participants were able to sign up for the experiment on the Prolific website.
-Upon signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment [@qualtrics2020].
-After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual lexical decision task was implemented in PsychoJS.
-In the experiment, all stimuli were presented in the center of the screen in black Courier New font on a white background.
-As we do not know the exact dimensions of each participant's screen, all stimulus sizes and positions were defined in PsychoPy's "height" units, with the bottom left of a 16:10 aspect ratio screen being represented as (-.8, -.5) and the top right being (.8, .5).
-The height for all text stimuli was 0.1 units.
-Each trial began with a six-character pattern mask (*\#\#\#\#\#\#*) set to be presented for 500 ms, followed first by the lowercase prime (e.g.
-*region*) set to be presented for either 33.3 or 50 ms, and then by the uppercase target (e.g.
-*REGION*).
-Participants were instructed to respond to the target stimulus as quickly as possible by pressing the "Z" key of their keyboard (if their device had one) if the target was not a valid English word or the "M" key if the target was a valid English word.
-Participants on a device without a keyboard were instructed to respond by touching one of two rectangular touch areas labeled "Z = Non-word" (presented at -0.4, -0.3) and "M = Word" (presented at 0.4, -0.3).
-The touch areas each had a width of 0.4 and a height of 0.2 and were presented in white with a black outline.
-If participants did not respond within two seconds of the target onset, a "Too slow!" feedback message was shown for 500 ms and the trial ended.
-The experimental trials were preceded by 16 practice trials during which participants also received feedback on the accuracy of their responses.
-No feedback apart from the trial timeout feedback was given during the experimental trials.
-Every 120 trials, participants were asked to take a short break before continuing the experiment.
-After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.
-
-### Data analysis
-
-We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the *brms* package [@R-brms_a; @R-brms_b] in R [@R-base][^2].
-We only analyzed trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as incorrect responses (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt >= 1800 | corr == 0))/nrow(.)}*100` % of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt >= 1800))/nrow(.)}*100` % of trials).
-For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.
-identical) and prime duration (33.3 ms vs.
-50 ms) as well as their interaction as the fixed effects.
-For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -0.5 and unrelated was coded as 0.5.
-For priming duration, 33.3 ms was coded as -0.5 and 50 ms was coded as 0.5.
-We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items.
-We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component $\mu$ and the scale parameter of the exponential component $\beta$ (equaling the inverse of the rate parameter $\lambda$) being allowed to vary between conditions.
-To model response accuracy, we used the Bernoulli distribution with a logit link.
-We used the default priors suggested by *brms* except for the coefficients for the fixed effects, for which we applied weakly informative priors of $\beta \sim N(0,100)$ in order to rule out improbably large effect sizes.
-Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warm-up iterations for the accuracy models).
-We consider an effect as credible if the 95% Credible Interval (CrI) estimated from the posterior distribution does not contain zero.
-In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.
-
-[^2]: The full list of software we used for our analyses is as follows: `r cite_r("r-references.bib")`.
-
-## Results
-
-Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table \@ref(tab:exp1-descriptive-rt-table) (although note that we only analyzed the word trials).
-
-(ref:exp1-descriptives-rt-table-caption) Mean, Median, Standard Deviation (SD), range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 1 for each condition.
-
-```{r exp1-descriptive-rt-table, as.is = TRUE,echo=FALSE, warning=FALSE, message=FALSE}
-#load raw Exp1 data
-
-#exp1 <- read_csv("Exp 1 data.csv")
-
-exp1_descriptives_rt <- exp1_data_to_include %>%
-  filter(rt > 250 & rt <= 1800 & corr == 1) %>%
-  group_by(StimulusType, PrimeDuration, Relatedness) %>%
-  summarize(
-    Mean = mean(rt)
-    , Median = median(rt)
-    , SD = sd(rt)
-    , Min = min(rt)
-    , Max = max(rt)
-  )
-
-exp1_descriptives_corr <- exp1_data_to_include %>%
-  filter(rt > 250 & rt <= 1800) %>%
-  group_by(StimulusType, PrimeDuration, Relatedness) %>%
-  summarize(
-    Accuracy = mean(corr)
-  )
-
-exp1_descriptives_rt[, -1] <- printnum(exp1_descriptives_rt[, -1], digits = 0)
-
-exp1_descriptives_corr[, -1] <- printnum(exp1_descriptives_corr[, -1], digits = 2)
-
-colnames(exp1_descriptives_rt)[1:2] <- c("Stimulus Type", "Prime Duration")
-
-exp1_descriptives_rt$Accuracy <- exp1_descriptives_corr$Accuracy
-
-apa_table(
-  exp1_descriptives_rt
-  , caption = "(ref:exp1-descriptives-rt-table-caption)"
-  , escape = TRUE
-)  
-```
-
-\newpage
-
-### Response times
-
-Table \@ref(tab:exp1-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-```{r exp1-models-rt, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
-
-# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
-
-load("blmm_exp1_rt_dist_revision.RData")
-# 
-# model name is blmm_exp1_rt_dist
-
-# adapted from a paper by Nalborczyk et al. (2019) -- https://osf.io/eancg/
-
-blmm_exp1_summary_rt <- summary(blmm_exp1_rt_dist)
-
-```
-
-The RT model indicates that the mean of the Gaussian component $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
-The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-The shape parameter of the exponential component $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1","u-95% CI"]`]).
-However, the 50 ms prime exposure duration seems to be associated with a slightly lower $\beta$, i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]).
-On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (*b* = `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]).
-
-(ref:exp1-blmm-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for the fixed effects of the model fitted for correct word RTs in Experiment 1.
-
-```{r exp1-blmm-table, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
-
-blmm_exp1_rt_fixed_for_print <- blmm_exp1_summary_rt$fixed
-
-parameter_names <- c(
-    "Intercept ($\\mu$)",
-    "Intercept ($\\beta$)",
-    "Relatedness ($\\mu$)",
-    "Prime Duration ($\\mu$)",
-    "Relatedness:Prime Duration ($\\mu$)",
-    "Relatedness ($\\beta$)",
-    "Prime Duration ($\\beta$)",
-    "Relatedness:Prime Duration ($\\beta$)"
-    )
-
-blmm_exp1_rt_fixed_for_print <- blmm_exp1_rt_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
-  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
-  dplyr::select(-ends_with("ESS"))
-
-write.csv(blmm_exp1_rt_fixed_for_print, file = "Table_1.csv", row.names = FALSE)
-
-apa_table(
-    blmm_exp1_rt_fixed_for_print,
-    placement = "H",
-    align = c("c", "c", "c", "c", "c"),
-    caption = "(ref:exp1-blmm-table-caption)",
-    note = "$\\beta$ is the scale parameter (the inverse of the rate parameter $\\lambda$) of the ex-Gaussian distribution.",
-    small = TRUE,
-    digits = 3,
-    escape = FALSE
-    )
-
-```
-
-These results can be visualized in the delta plots depicted in Figure \ref{fig:deltas-e1-words}.
-Delta plots are residual quantile plots that show the distributional differences between conditions [see @de1994conditional].
-As can be seen in Panel A, there is an identity priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33.3 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33.3 ms one.
-We also found a slight increase of priming effects for the longest responses (quantile .9) in the 33.3 ms prime duration condition.
-This apparent anomaly can be understood better by looking at Panel B of the same figure.
-In this panel, we show the size of the prime duration effect (computed as the difference in response times between responses to the 50 ms condition and responses to the 33.3 ms condition) across RT quantiles.
-While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition yielded virtually the same response times in the 33.3 and 50 ms conditions, except for a small increase at the 50 ms prime duration for the very long responses (i.e., .9 quantile)--we prefer not to over-interpret this latter finding with the slowest responses, as it did not appear in Experiment 2.
-
-```{r deltas-e1-words, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE, cache=TRUE, fig.cap = "Delta plots depicting the magnitude of the effect over time in Experiment 1.
-Each dot represents the mean RT at the .1, .3, .5, .7 and .9 quantiles.
-*Panel A)* Difference in RT between unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right).
-*Panel B)* Difference in RT between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions."}
-
-E1<- exp1_data_to_include%>% 
-  filter(rt > 250 & rt <= 1800)%>%
-  select(participant, TrialID, StimulusType, Relatedness, PrimeDuration, Prime, Target, corr, rt)%>%
-  mutate(participant=factor(participant),
-         TrialID = factor(TrialID))
-
-quibble <- function(x, q = seq(.1, .9, .2)) {
-  tibble(x = quantile(x, q), q = q)
-}
-
-E1 %>%
-  group_by(participant, StimulusType, Relatedness, PrimeDuration,corr) %>%
-  summarise(RT = list(quibble(rt, seq(.1, .9, .2)))) %>% 
-  tidyr::unnest(RT) -> data.E1.quantiles
-
-data.E1.quantiles %>%
-  filter(corr==1) %>%
-  select(-corr) %>%
-  group_by(StimulusType,PrimeDuration,Relatedness,q) %>%
-  summarize(RT=mean(x))%>%
-  ungroup()-> vincentiles.E1
-
-#Priming Effect (unrelated - identity):
-
-vincentiles.E1 %>%
-  filter(StimulusType == "Word")%>%
-  arrange(desc(Relatedness))%>%
-  group_by(PrimeDuration,q) %>%
-  summarize(MRT=mean(RT),
-            Delta=diff(rev(RT)))%>%
-  ungroup()%>%
-ggplot(aes(y=Delta, x=MRT)) +
-  geom_line(size = .7)+
-  geom_point(size = 1.7)+
-  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
-  ylim(-60, +60)+
-  xlim(450, 850)+
-  xlab("Mean RT per quantile")+
-  ylab("Effect (in ms)")+
-  ggtitle("Priming Effect")+
-  facet_wrap(~PrimeDuration)+
-  theme_minimal()+
-  theme(plot.title = element_text(size = 12),
-        axis.text=element_text(size=9),
-        axis.title=element_text(size=9))-> DeltaE1.PrimingEffect.W
-
-#Prime Duration Effect (33ms - 50 ms):
-
-vincentiles.E1 %>%
-  filter(StimulusType == "Word")%>%
-  group_by(Relatedness,q) %>%
-  summarize(MRT=mean(RT),
-            Delta=diff(rev(RT)))%>%
-  ggplot(aes(y=Delta, x=MRT)) +
-  geom_line(size = .7)+
-  geom_point(size = 1.7)+
-  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
-  ylim(-60, +60)+
-  xlim(450, 850)+
-  xlab("Mean RT per quantile")+
-  ylab("Effect (in ms)")+
-  ggtitle("Prime Duration Effect")+
-  facet_wrap(~ Relatedness)+
-  theme_minimal()+
-  theme(plot.title = element_text(size = 12),
-        axis.text=element_text(size=9),
-        axis.title=element_text(size=9))-> DeltaE1.PrimeDurationEffect.W
-
-cowplot::plot_grid(DeltaE1.PrimingEffect.W,
-                   DeltaE1.PrimeDurationEffect.W,
-                   ncol = 1,
-                   labels = c("A", "B"))+
-  plot_annotation(theme = theme(plot.title = element_text(size = 14)))
-
-```
-
-### Accuracy
-
-Table \@ref(tab:exp1-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-```{r exp1-models-acc, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
-
-load("blmm_exp1_acc_revision.RData")
-
-# Relatedness = Condition
-
-blmm_exp1_summary_acc <- summary(blmm_exp1_acc)
-
-```
-
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1","u-95% CI"]`]).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp1_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
-The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33.3 ms condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-
-(ref:exp1-blmm-accuracy-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for the fixed effects of the model fitted for response accuracy on word trials in Experiment 1.
-
-```{r exp1-acc-blmm-table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
-
-blmm_exp1_acc_fixed_for_print <- blmm_exp1_summary_acc$fixed
-
-parameter_names <- c(
-    "Intercept",
-    "Relatedness",
-    "Prime Duration",
-    "Relatedness:Prime Duration"
-    )
-
-blmm_exp1_acc_fixed_for_print <- blmm_exp1_acc_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
-  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
-  dplyr::select(-ends_with("ESS"))
-
-write.csv(blmm_exp1_acc_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
-
-apa_table(
-    blmm_exp1_acc_fixed_for_print,
-    placement = "H",
-    align = c("c", "c", "c", "c", "c"),
-    caption = "(ref:exp1-blmm-accuracy-table-caption)",
-    note = NULL,
-    small = TRUE,
-    digits = 3,
-    escape = FALSE
-    )
-
-```
-
-## Discussion
-
-The results from Experiment 1 reveal that we were able to replicate benchmark masked priming effects using an online experiment.
-The size and shape of the effect is similar to that observed in previous studies [e.g., @gomezDiffusionModelAccount2013; @Perea_2018; @Taikh_2020; @Yang_2021].
-In addition, we also saw a clear difference between the 33.3 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices.
-While the shape of the distribution changed slightly between the 33.3 ms and the 50 ms prime exposure durations, we did not observe an effect of the prime relatedness condition on the shape parameter $\beta$ of the exponential distribution, suggesting, according to the savings hypothesis by @forster1998pros, that only encoding processes were affected by the relatedness manipulation.
-Moreover, as can be observed in Figure \ref{fig:deltas-e1-words}, the effect magnitude was close to the stimulus-onset asynchrony [see also @Perea_2018].
-
-Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.
-Indeed, to better define the priming effect, one needs a baseline that serves as a reference point [i.e., an analog of the minimum "intensity" priming condition; see @Jacobs_1995].
-In order to further explore this question, we performed a second experiment in which we set the prime to be displayed for an even shorter duration.
-As described in the Introduction, a 16.7 ms prime exposure duration should yield a negligible priming effect [@Tzur_2007; @ziegler2000] so the pattern should be qualitatively different from the 33.3 and 50 ms durations used in Experiment 1.
-If it does not, this would cast doubt on the timing accuracy in online experiments.
-In this experiment, we also include the 33.3 ms prime duration condition to not only have a better scheme to compare the two experiments, but also to be able to test the within-condition effects [@Jacobs_1995]---assuming the 16.7 ms prime duration serves as a baseline.
-
-# Experiment 2
-
-In the second experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 16.7 ms and 33.3 ms (roughly corresponding to one and two frames at a refresh rate of 60 Hz).
-
-The pre-registration form for Experiment 2 can be found at [<https://osf.io/957s8>]. The materials, data files, and R scripts can be found at [<https://osf.io/57rzq/>]
-
-## Method
-
-```{r load-exp2-data, as.is = TRUE,echo=FALSE, warning=FALSE}
-#load raw Exp2 data
-
-exp2_all_participants <- read_csv("participant_data_exp2.csv")
-
-exp2 <- fs::dir_ls(path = "./data_exp2", glob = "*.csv") %>%
-  map_dfr(read_csv, .id = "source", col_type = cols(
-  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
-  filter(!is.na(TrialID) & TrialID < 1000) %>%
-  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)
-
-exp2$device <- ifelse(exp2$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")
-
-# only consider participants who have actually participated in the whole experiment
-# also don't consider participants whose age is 99 (used for testing)
-# one participant is duplicate. Remove the first occurrence (likely incompatible device)
-
-exp2_actual_participants <- filter(exp2_all_participants, (PROLIFIC_PID %in% exp2$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & !(`Response ID` %in% c("R_2c2dVRNmGvI6CH9", "R_3ELutaT6GNe5mmR", "R_XX7jgUk2NbIi41j", "R_125QKzJfHwoGHaT")))
-
-# get participants with more than 80% correct responses
-
-exp2_accuracy_by_participant <- exp2 %>% filter(participant %in% exp2_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())
-
-exp2_participants_to_include <- exp2_accuracy_by_participant %>% filter(N == 480 & acc >= .8)
-
-exp2_participants_to_exclude <- exp2_accuracy_by_participant %>% filter(N != 480 | acc < .8)
-
-#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
-
-exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Relatedness = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identity", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16.7 ms", "33.3 ms")), rt = rt * 1000)
-
-# filter out any of the participants we eliminated from the Qualtrics file as well
-
-exp2_actual_participants <- filter(exp2_actual_participants, (PROLIFIC_PID %in% exp2_data_to_include$participant))
-
-exp2_participant_ages <- exp2_actual_participants$`What is your age?`
-
-exp2_male_participants_nr <- filter(exp2_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow
-
-exp2_female_participants_nr <- filter(exp2_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow
-
-# there aren't actually any of these, but will leave the code in just in case
-exp2_other_participants_nr <- filter(exp2_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
-
-exp2_NA_participants_nr <- filter(exp2_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow
-
-exp2_participant_coords <- exp2_actual_participants %>% select("Location Longitude", "Location Latitude")
-
-# coords2country function definition in exp1 chunk above
-exp2_actual_participants$country <- coords2country(exp2_participant_coords)
-
-exp2_participant_countries <- table(exp2_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
-
-#paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows
-
-exclude_list_for_prolific <- str_extract(string = exp2_participants_to_exclude$source, pattern = "[a-z0-9]{24}") %>% paste0(collapse = "\n")
-
-```
-
-### Participants
-
-As in Experiment 1, participants were recruited through Prolific [www.prolific.co, -@prolific2021].
-The experiment was accessed by `r exp2_all_participants$PROLIFIC_PID %>% unique %>% length` participants.
-Out of these, `r exp2_accuracy_by_participant %>% nrow` provided experimental data.
-`r exp2_participants_to_exclude %>% filter(N != 480) %>% nrow %>% numbers_to_words() %>% str_to_sentence()` of these participants did not complete the experiment.
-A further `r exp2_participants_to_exclude %>% filter(N == 480 & acc < .8) %>% nrow %>% ifelse(.
-< 11, numbers_to_words(.), .)` were excluded because of low accuracy (again, less than .8).
-The remaining `r exp2_actual_participants$PROLIFIC_PID %>% unique %>% length` participants were aged from `r exp2_participant_ages %>% min` to `r exp2_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`).
-Of the participants, `r exp2_male_participants_nr` identified as male, and `r exp2_female_participants_nr` identified as female.
-All these participants indicated that English was their first language in the Prolific screening questions.
-Based on their IP addresses, `r exp2_participant_countries["United Kingdom"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in the UK, `r exp2_participant_countries["United States of America"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` were based in the US, `r exp2_participant_countries["Canada"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in Canada, `r exp2_participant_countries["South Africa"] %>% ifelse(.
-< 11, numbers_to_words(.), .)` participants were based in South Africa, and one participant each was based in Hungary and Ireland.
-`r exp2_actual_participants$country %>% is.na %>% sum %>% numbers_to_words %>% str_to_sentence()` participants could not be localized in this way.
-As in Experiment 1, all participants were naïve to the purpose of the experiment, and received £1.25 for their participation (corresponding to £5/hour).
-Participants could use either a desktop/laptop computer or a mobile device.
-Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
-
-***Rationale for sample size and stopping rule.*** As in Experiment 1, our stopping rule was to keep collecting data until 3,000 valid observations were collected.
-This goal was met and exceeded in our initial data collection with a budget of £200.
-
-### Materials
-
-The materials were identical to those used in Experiment 1.
-
-### Procedure
-
-The procedure was identical to Experiment 1, the only difference being that the primes were set to be displayed for either 16.7 ms or 33.3 ms.
-
-### Data analysis
-
-We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as those with incorrect responses (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 1800 | corr == 0))/nrow(.)}*100` % of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 1800))/nrow(.)}*100` % of trials).
-For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5.
-Otherwise, the model specifications were identical to those in Experiment 1.
-
-## Results
-
-Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table \@ref(tab:exp2-descriptive-rt-table).
-
-### Response times
-
-```{r exp2-models-rt, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
-
-# We fitted the models in a separate file to make sure that knitting the manuscript doesn't take too long
-load("blmm_exp2_rt_dist_revision.RData")
-
-# this file doesn't fit on GitHub
-# download it at https://1drv.ms/u/s!ApE7JQmoH0baocIO3qh2TNb_TlqvlA?e=q3vJml
-
-# model name is blmm_exp2_rt
-
-# adapted from a paper by Nalborczyk et al. (2019) -- https://osf.io/eancg/
-
-blmm_exp2_summary_rt <- summary(blmm_exp2_rt_dist)
-
-```
-
-As in Experiment 1, the RT model indicates that the mean of the Gaussian component $\mu$ was higher in the unrelated condition than the identical (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]).
-For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]).
-However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).
-The shape parameter of the exponential component $\beta$ was affected very little by prime relatedness (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1","u-95% CI"]`]), prime exposure duration (*b* = `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_PrimeDuration1","u-95% CI"]`]), or their interaction (*b* = `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["beta_Condition1:PrimeDuration1","u-95% CI"]`]), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
-
-Table \@ref(tab:exp2-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-\newpage
-
-(ref:exp2-descriptives-rt-table-caption) Mean, Median, Standard Deviation (SD), and range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 2 for all conditions.
-
-(ref:exp2-blmm-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for the fixed effects of the model fitted for correct word RTs in Experiment 2.
-
-```{r exp2-descriptive-rt-table, as.is = TRUE,echo=FALSE, message=FALSE, warning=FALSE}
-
-exp2_descriptives_rt <- exp2_data_to_include %>%
-  filter(rt > 250 & rt <= 1800 & corr == 1) %>%
-  group_by(StimulusType, PrimeDuration, Relatedness) %>%
-  summarize(
-    Mean = mean(rt)
-    , Median = median(rt)
-    , SD = sd(rt)
-    , Min = min(rt)
-    , Max = max(rt)
-  )
-
-exp2_descriptives_corr <- exp2_data_to_include %>%
-  filter(rt > 250 & rt <= 1800) %>%
-  group_by(StimulusType, PrimeDuration, Relatedness) %>%
-  summarize(
-    Accuracy = mean(corr)
-  )
-
-exp2_descriptives_rt[, -1] <- printnum(exp2_descriptives_rt[, -1], digits = 0)
-
-exp2_descriptives_corr[, -1] <- printnum(exp2_descriptives_corr[, -1], digits = 2)
-
-colnames(exp2_descriptives_rt)[1:2] <- c("Stimulus Type", "Prime Duration")
-
-exp2_descriptives_rt$Accuracy <- exp2_descriptives_corr$Accuracy
-
-apa_table(
-  exp2_descriptives_rt
-  , caption = "(ref:exp2-descriptives-rt-table-caption)"
-  , escape = TRUE
-)  
-```
-
-```{r exp2-blmm-table, as.is = TRUE,echo=FALSE, message=FALSE, warning=FALSE}
-
-blmm_exp2_rt_fixed_for_print <- blmm_exp2_summary_rt$fixed
-
-parameter_names <- c(
-    "Intercept ($\\mu$)",
-    "Intercept ($\\beta$)",
-    "Relatedness ($\\mu$)",
-    "Prime Duration ($\\mu$)",
-    "Relatedness:Prime Duration ($\\mu$)",
-    "Relatedness ($\\beta$)",
-    "Prime Duration ($\\beta$)",
-    "Relatedness:Prime Duration ($\\beta$)"
-    )
-
-blmm_exp2_rt_fixed_for_print <- blmm_exp2_rt_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
-  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
-  dplyr::select(-ends_with("ESS"))
-
-write.csv(blmm_exp2_rt_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
-
-apa_table(
-    blmm_exp2_rt_fixed_for_print,
-    placement = "H",
-    align = c("c", "c", "c", "c", "c"),
-    caption = "(ref:exp2-blmm-table-caption)",
-    note = "$\\beta$ is the scale parameter (the inverse of the rate parameter $\\lambda$) of the ex-Gaussian distribution.",
-    small = TRUE,
-    digits = 3,
-    escape = FALSE
-    )
-
-```
-
-We also created the delta plots of data from Experiment 2 (see Figure \ref{fig:deltas-e2-words}).
-Panel A, shows there is no priming effect for the 16.7 ms condition, in contrast with a consistent effect across quantiles for the 33.3 ms condition (parallel to the one found in Experiment 1).
-Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight hindering for unrelated primes.
-
-```{r deltas-e2-words, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.cap = "Delta plots depicting the magnitude of the effect over time in Experiment 2."}
-
-E2<- exp2_data_to_include%>%
-  select(participant, TrialID, StimulusType, Relatedness, PrimeDuration, Prime, Target, corr, rt)%>%
-  mutate(participant=factor(participant),
-         TrialID = factor(TrialID))
-
-E2 %>%
-  group_by(participant, StimulusType, Relatedness, PrimeDuration,corr) %>%
-  summarise(RT = list(quibble(rt, seq(.1, .9, .2)))) %>% 
-  tidyr::unnest(RT) -> data.E2.quantiles
-
-data.E2.quantiles %>%
-  filter(corr==1) %>%
-  select(-corr) %>%
-  group_by(StimulusType,PrimeDuration,Relatedness,q) %>%
-  summarize(RT=mean(x))%>%
-  ungroup()-> vincentiles.E2
-
-#Priming Effect (unrelated - identity):
-
-vincentiles.E2 %>%
-  filter(StimulusType == "Word")%>%
-  arrange(desc(Relatedness))%>%
-  group_by(PrimeDuration,q) %>%
-  summarize(MRT=mean(RT),
-            Delta=diff(rev(RT)))%>%
-  ungroup()%>%
-ggplot(aes(y=Delta, x=MRT)) +
-  geom_line(size = .7)+
-  geom_point(size = 1.7)+
-  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
-  ylim(-60, +60)+
-  xlim(450, 850)+
-  xlab("Mean RT per quantile")+
-  ylab("Effect (in ms)")+
-  ggtitle("Priming Effect")+
-  facet_wrap(~PrimeDuration)+
-  theme_minimal()+
-  theme(plot.title = element_text(size = 12),
-        axis.text=element_text(size=10),
-        axis.title=element_text(size=10))-> DeltaE2.PrimingEffect.W
-
-#Prime Duration Effect (16ms - 33 ms):
-
-vincentiles.E2 %>%
-  filter(StimulusType == "Word")%>%
-  group_by(Relatedness,q) %>%
-  summarize(MRT=mean(RT),
-            Delta=diff(rev(RT)))%>%
-  ggplot(aes(y=Delta, x=MRT)) +
-  geom_line(size = .7)+
-  geom_point(size = 1.7)+
-  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
-  ylim(-60, +60)+
-  xlim(450, 850)+
-  xlab("Mean RT per quantile")+
-  ylab("Effect (in ms)")+
-  ggtitle("Prime Duration Effect")+
-  facet_wrap(~ Relatedness)+
-  theme_minimal()+
-  theme(plot.title = element_text(size = 12),
-        axis.text=element_text(size=10),
-        axis.title=element_text(size=10))-> DeltaE2.PrimeDurationEffect.W
-
-#pdf("Fig_deltasE2.pdf", height = 5)
-
-cowplot::plot_grid(DeltaE2.PrimingEffect.W,
-                   DeltaE2.PrimeDurationEffect.W,
-                   ncol = 1,
-                   labels = c("A", "B"))+
-  plot_annotation(theme = theme(plot.title = element_text(size = 14)))
-
-```
-
-### Accuracy
-
-```{r exp2-models-acc, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
-
-load("blmm_exp2_acc_revision.RData")
-
-# This file doesn't fit on GitHub
-# Download it at https://1drv.ms/u/s!ApE7JQmoH0baobF4qRyXSfOymglf_g?e=0JGhre
-
-blmm_exp2_summary_acc <- summary(blmm_exp2_acc)
-
-```
-
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1","u-95% CI"]`]).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16.7 ms prime duration condition than in the 33.3 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp2_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]).
-The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33.3 ms condition, and reversed in the 16.7 ms condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]), although the effect in the 16.7 ms condition was very weak.
-Table \@ref(tab:exp2-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% CrI of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, indicating that the model was fitted successfully as they are all close to 1.
-
-(ref:exp2-blmm-accuracy-table-caption) Posterior Mean, Standard Error (SE), 95% CrI and $\hat{R}$ for fixed effects of the model fitted for response accuracy on word trials in Experiment 2.
-
-```{r exp2-acc-blmm-table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
-
-blmm_exp2_acc_fixed_for_print <- blmm_exp2_summary_acc$fixed
-
-parameter_names <- c(
-    "Intercept",
-    "Relatedness",
-    "Prime Duration",
-    "Relatedness:Prime Duration"
-    )
-
-blmm_exp2_acc_fixed_for_print <- blmm_exp2_acc_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
-  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
-  dplyr::select(-ends_with("ESS"))
-
-write.csv(blmm_exp2_acc_fixed_for_print, file = "Table_3.csv", row.names = FALSE)
-
-apa_table(
-    blmm_exp2_acc_fixed_for_print,
-    placement = "H",
-    align = c("c", "c", "c", "c", "c"),
-    caption = "(ref:exp2-blmm-accuracy-table-caption)",
-    note = NULL,
-    small = TRUE,
-    digits = 3,
-    escape = FALSE
-    )
-
-```
-
-## Discussion
-
-In Experiment 2, we found the pattern we expected from previous research: In the mean $\mu$ of the Gaussian component of the ex-Gaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration [@Tzur_2007; @ziegler2000].
-This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
-In addition, we did not observe an effect of the prime relatedness on the shape parameter $\beta$ of the exponential component [i.e., the effect corresponded to a shift of the RT distributions, as shown in in-lab studies; e.g., @Taikh_2020; @Yang_2021].
-Moreover, the magnitude of the priming effect at the 33.3 ms prime exposure duration was close to the magnitude of the prime-target stimulus-onset asynchrony, as can be seen in the delta plots in Figure \ref{fig:deltas-e2-words} [see @gomezDiffusionModelAccount2013; @Perea_2018].
-Hence, we replicated again the commonly observed savings effect [@forster1998pros].
-
-Critically, because the 16.7 ms prime duration condition yielded virtually no priming effects, this very short prime exposure duration serves as a within-condition baseline that allows us to qualify the facilitative vs.
-inhibitory nature of masked priming effects [@Jacobs_1995; @ziegler2000].
-Specifically, when compared to the baseline, our findings at the 33.3 ms prime duration show a combination of a slight facilitatory effect for identity primes and a small inhibitory effect for unrelated primes.
-
-# General Discussion
-
-In this study, we set out to test whether we could obtain benchmark masked priming effects both qualitatively (i.e., shift in the RT distributions) and quantitatively (i.e., effect sizes) using an online, browser-based experiment software.
-To that end, we conducted two online masked identity priming experiments (e.g., *region --- REGION* vs.
-*launch --- REGION*) in which we manipulated prime exposure duration (33.3 vs.
-50 ms in Experiment 1; 16.7 vs.
-33 ms in Experiment 2).
-The results of our online-based experiments replicated and extended benchmarks masked identity priming effects previous in the lab-based studies.
-We observed the effect sizes predicted by Forster's [-@forster1998pros] savings hypothesis: Our data show a shift in the mean of the Gaussian component of the ex-Gaussian distribution, but no change in the shape parameter $\beta$ of the exponential component, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes.
-Furthermore, the size of the priming effect was not only directly influenced by the prime duration, suggesting the experimental software was able to control the display timing of the prime accurately, but also of a similar magnitude to the prime duration [within the range reported in previous studies, e.g., 35-47 ms for a 50 ms prime duration in @Perea_2018].
-Importantly, the use of a within-condition baseline revealed that the identity priming effects at the 33 ms prime exposure duration were a combination of some small facilitation from identity primes and some small inhibition from unrelated primes [see @Jacobs_1995, for evidence with a psychophysical experiment].
-Likewise, the greater identity priming effects at the 50 ms rather than at the 33.3 ms prime exposure duration were essentially due to the facilitation from the identity pairs.
-
-While accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, they are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade.
-Similarly, unlike in-lab conditions, where the contrast of the computer screens can be measured and kept constant, there is no such a guarantee for the screens used by online participants---note that @Tzur_2007 were only able to observe strong effects for short prime exposure durations when using extreme contrast values.
-Thus, the fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy, PsychoJS.
-
-Furthermore, our results extend previous work showing the validity of on-line studies measuring response times [e.g., @brysbaert2016impact; @cai2017accent; @Dufau_2011; @eerland2013influence; @rodd2016impact, to cite a few instances] to the masked priming technique.
-Thus, the present study opens the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
-Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible.
-For instance, online participants can be people from different countries and/or cultures, from different age groups, bilinguals/multilinguals, even those who do not own a computer, only a smartphone.
-Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant.
-This opens up the possibility of masked-priming crowdsourced megastudies.
-In general, deploying masked priming experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
-
-In conclusion, our results give us confidence that high-quality behavioral data using the masked priming paradigm can be collected online using Javascript-based experiment platforms.
-We hope that future research takes advantage of these new methods in order to make research faster, more inclusive, and more efficient.
-
-\newpage
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
-
-\newpage
-
-# Appendix A
-
-## Words:
-
-```{r}
-trials%>%
-  filter(StimulusType=="WORD")%>%
-  pull(Target)%>%
-  noquote()->Word_targets
-
-Word_targets
-
-```
-
-## Non-Words:
-
-```{r}
-
-trials%>%
-  filter(StimulusType=="NW")%>%
-  pull(Target)%>%
-  noquote()->NonWord_targets
-
-NonWord_targets
-
-```
-
-\endgroup

### 2021-09-21 Appendix_test.tex
Add new appendix and revisions/reply to editor

--- 2021-09-21 MaskedPriming_revision.tex
@@
   english,
-  man,floatsintext]{apa6}
+  man]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \hypersetup{
-  pdfauthor={Bernhard Angele1,2, Ana Baciero2,3, Pablo Gómez4, \& Manuel Perea2,5},
   pdflang={en-EN},
-  pdfkeywords={Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration},
   hidelinks,
@@
 \makeatother
-\shorttitle{Online masked priming}
-\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 7916}
+\shorttitle{SHORTTITLE}
 \usepackage{csquotes}
@@
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\title{Does online masked priming pass the test?\\
-The effects of prime exposure duration on masked identity priming}
-\author{Bernhard Angele\textsuperscript{1,2}, Ana Baciero\textsuperscript{2,3}, Pablo Gómez\textsuperscript{4}, \& Manuel Perea\textsuperscript{2,5}}
+\title{TITLE}
+\author{\phantom{0}}
 \date{}
 
-\note{
-
-\clearpage
-
-}
-
-\authornote{
-
-We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.
-
-This research has been partly supported by Grant PSI2017-86210-P from the Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).
-
-This study was pre-registered on the Open Science Framework (OSF) prior to data collection.
-The registration form for Experiment 1, together with the materials, data files, and R scripts can be found at {[}\url{https://osf.io/57rzq/}{]}.
-The registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}.
-
-Correspondence concerning this article should be addressed to Bernhard Angele, Department of Psychology, Faculty of Science and Technology, Talbot Campus, Fern Barrow, Poole BH12 5BB, UK.
-E-mail: \href{mailto:bangele@bournemouth.ac.uk}{\nolinkurl{bangele@bournemouth.ac.uk}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Bournemouth University, Bournemouth, UK\\\textsuperscript{2} Universidad Antonio de Nebrija, Madrid, Spain\\\textsuperscript{3} DePaul University, Chicago, USA\\\textsuperscript{4} California State University San Bernardino, Palm Desert Campus, USA\\\textsuperscript{5} Universitat de València, Valencia, Spain}
-
-\abstract{
-Masked priming is one of the most important paradigms in the study of visual word recognition, but it is usually thought to require a laboratory setup with a known monitor and keyboard.
-To test if this technique can be safely used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS (Peirce et al., 2019).
-Importantly, we also tested the role of prime exposure duration (33.3 vs.~50 ms in Experiment 1 and 16.7 vs.~33.3 ms in Experiment 2), thus allowing us to examine both across conditions and within-conditions effects.
-We found that our online data are indeed very similar to the masked priming data previously reported in the masked priming literature.
-Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33.3 ms and no priming effect at 16.7 ms prime duration.
-From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., PsychoPy) can present stimuli and collect responses on standard end user devices with enough precision.
-These findings provide us with confidence that masked priming can be used online, thus allowing us not only to run less time-consuming experiments, but also to reach populations that are difficult to test in a laboratory.
-}
+\affiliation{\phantom{0}}
 
@@
 
-Masked priming (Forster \& Davis, 1984) is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition (see Forster, 1998; Grainger, 2008, for reviews).
-Priming refers to the influence of a prime stimulus (e.g., \emph{nurse}, \emph{horse}) on a subsequently presented stimulus that the participant has to respond to (e.g., ``is \emph{DOCTOR} a word?'').
-Priming effects are measured as the difference in a dependent variable (e.g., response time {[}RT{]}) between two conditions (e.g., unrelated: \emph{horse-DOCTOR}; related: \emph{nurse-DOCTOR}).
-In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a pattern mask (e.g., \#\#\#\#\#) for a much longer duration (typically 500 ms).
-The rationale of the procedure is to make participants unaware of the identity of the masked prime (Forster, 1998; Forster \& Davis, 1984), thus minimizing the role of participants' strategies.
-Indeed, masked priming experiments do not show the strategical effects that occur with visible, unmasked primes (e.g., Grossi, 2006; Perea \& Rosa, 2002).
+This is the manuscript.
 
-The masked priming paradigm has been used in a large number of studies over the last decades.
-For instance, a search of the expression ``masked priming'' in Google Scholar in May 2021 produced more than 10,000 hits.
-Nearly all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by Forster and Forster (2003).
-The issue we examine in the present paper is whether masked priming experiments can be conducted in an online setting without significant changes in the pattern of results.
-Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
-Indeed, researchers in decision making and economics have been using online paradigms for several decades now (e.g., Birnbaum \& Birnbaum, 2000; Paolacci et al., 2010).
+\clearpage
 
-Cognitive psychologists have been much slower that their behavioral economics colleagues in taking up online paradigms (see Brysbaert et al., 2016; Cai et al., 2017; Dufau et al., 2011; Eerland et al., 2013; Rodd et al., 2016, for some exceptions), often due to concerns about the validity of the results.
-Such concerns are not limited to cognitive studies (see Aust et al., 2013), but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
-Furthermore, these concerns are even more central in the masked priming technique, where it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
-For instance, presenting the masked prime for longer than intended (e.g., 83 ms or longer instead of the nominal 50 ms) could counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest (see Zimmerman \& Gomez, 2012).
-
-There have been attempts to address these concerns.
-Witzel et al.
-(2013) developed a Web version of DMDX (webDMDX) showing promising results in a trial experiment.
-However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a ``true'' online programming script that could be run inside of a browser.
-A downside of this format is that participants often are (and should be) understandably skeptical about downloading and running executable files from the Internet.
-Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
-As a consequence, the use of webDMDX in masked priming experiments has been rather limited so far (see Alluhaybi \& Witzel, 2020; Dubey et al., 2018, for exceptions).
-
-Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web.
-Most notably, the HTML5 standard now makes it possible to use Javascript in order to draw stimuli interactively and monitor participant responses with remarkable flexibility inside the browser.
-Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets (Reimers \& Stewart, 2015).
-There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla (Anwyl-Irvine, Massonni, et al., 2020) or Testable (Rezlescu et al., 2020), and open-source such as jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of PsychoPy 3, Peirce et al., 2019).
-In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
-Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility of recruiting participants for on-line experiments based on various specific characteristics set up by the experimenters regardless of their location (e.g., native French speakers, not older than 30 years old, not currently in college).
-
-Of course, despite the technological advances, many cognitive psychologists still have concerns about timing and measurement precision.
-While Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (e.g., to avoid delays, all stimuli are usually downloaded before the start of the experiment), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
-Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
-As Reimers and Stewart (2015) pointed out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
-If the results of the Web-based study are comparable to previous lab-based results, this suggests that, whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
-
-The first approach has the advantage that differences in presentation timings can be objectively recorded and evaluated.
-A very thorough recent example of this approach is the ``timing mega-study'' by Bridges et al.
-(2020), who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
-The very similar study by Anwyl-Irvine, Dalmaijer, et al.
-(2020) compares only online packages and browsers with regard to timing.
-Overall, Bridges et al.
-(2020) found that online packages were capable of presenting visual stimuli with reasonable precision, although the lab-based packages were slightly better in this regard.
-This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
-If this is not possible, there is no point in moving forward to the second approach and replicating specific paradigms.
-However, it is of course impossible to test every possible device and configuration that participants might use.
-On the other hand, some of the differences in precision and accuracy between setups that can be observed using a photodiode may be too small to have an influence on actual participant performance.
-Therefore, we consider replication of previous key lab-based effects a more important test of online paradigms than photodiode measurements.
-Based on the results by Bridges et al.
-(2020) and Anwyl-Irvine, Dalmaijer, et al.
-(2020), modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
-To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study.
-Importantly, we will do so using PsychoPy/PsychoJS (Peirce et al., 2019) as it showed high precision and accuracy across the great majority of platforms (Anwyl-Irvine, Dalmaijer, et al., 2020; Bridges et al., 2020), in addition to being an open-source software.
-
-Specifically, in this study we were interested in whether we could replicate and extend a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming is commonly described as a savings effect.
-As first suggested by Forster (1998), for a masked identity prime, ``the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner,'' whereas for an unrelated prime, ``the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur'' (p.~213).
-Thus, according to the savings account, a target word like \emph{DOCTOR} would enjoy an encoding advantage when preceded by an identity prime such as \emph{doctor} than when preceded by an unrelated prime such as \emph{pencil} (i.e., a head-start).
-One implication of such benefit is that the RT distributions of the unrelated and identity pairs should reflect a shift rather than a change in shape.
-Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony (SOA).
-Empirical evidence supporting this view has been obtained in several studies not only with skilled adults but also with developing readers (e.g., Gomez et al., 2013; Gomez \& Perea, 2020; Taikh \& Lupker, 2020; Yang et al., 2021).
-Gomez et al.
-(2013) proposed an implementation of this hypothesis within the diffusion model (Ratcliff et al., 2004).
-This implementation proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution (\(T_{er}\)) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached.
-Importantly, in the decision process, the information gathered from the stimulus can vary in noise, depending on its quality, which modifies the rate at which information is accumulated (i.e., the \emph{drift rate}).
-With regards to RTs from masked priming tasks, Gomez et al.
-(2013) found that the difference between identity and unrelated conditions could be accounted for by a change in the \(T_{er}\) parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a more skewed RT distribution in the slower, unrelated condition.
-
-Critically, the above pattern is specific to \emph{masked} priming.
-In fact, the most common pattern of results in latency based tasks is that conditions that produce longer latencies will also produce larger variance.
-This pattern is evident in priming as well---when primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles (i.e., a change in shape rather than a shift in RT distributions; see Gomez et al., 2013).
-Fits from the diffusion model show that this result corresponds to changes in both the \(T_{er}\) parameter and the drift rate.
-Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word, unlike in masked priming.
-Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.~both encoding and information quality in unmasked priming.
-
-In the present paper, we took advantage of the above marker to examine whether online masked priming studies follow the same pattern as in-lab masked priming studies.
-Specifically, we manipulated prime exposure duration in identity vs.~unrelated primes: 33.3 vs.~50 ms in Experiment 1, and 16.7 vs.~33.3 ms in Experiment 2---note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA).
-The rationale of Experiment 1 is that if the actual exposure duration of the primes is the nominal exposure duration, then we would expect the typical shift between the identity and unrelated response time distributions, which according to the savings hypothesis (Forster, 1998) would be greater for 50 ms than for 33.3 ms exposure duration (i.e., the head-start would be greater for 50 ms identity primes than for 33.3 ms identity primes).
-This outcome would indicate that the on-line masked priming studies reproduce a characteristic signature of laboratory masked priming studies.
-Alternatively, if the online presentation conditions lead to a greater actual exposure duration on the participant's device compared to that specified in our experiment (e.g.,if prime durations were, on average, 20 ms longer than intended), then the 50 ms primes may no longer be adequately masked, but may rather be consciously perceived.
-If this is the case, the prime could affect not only the encoding, but also core decision processes (i.e., the drift rate), which would be reflected as a stronger priming effect in the higher quantiles of the distribution (i.e., the two RT distributions would have a different shape).
-In this scenario, one should be very cautious when running online masked priming experiments---at least with the typical software and hardware currently available.
-
-To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for replacing the 50 ms prime exposure duration with a very short prime exposure duration, namely, 16.7 ms.
-Similar extremely brief prime exposure durations have shown very weak masked priming lexical decision experiments in a laboratory setting: less than 5 ms for a prime duration of 14 ms (Ziegler et al., 2000) and less than 9 ms for a prime duration of 20 ms (Tzur \& Frost, 2007)---in the Tzur and Frost (2007) experiment, this difference increased to 16.7 ms when using a very high level of contrast in the computer screen.
-Thus, if the size of the priming effect is roughly similar to the prime exposure duration, we would expect a much larger priming effect at the 33.3 ms prime exposure duration than at the 16.7 ms prime exposure duration.
-If we do observe a large effect at the 16.7 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments.
-Keep in mind that we are using a software that has very good control over the exposure duration (Anwyl-Irvine, Dalmaijer, et al., 2020; Bridges et al., 2020).
-Figure \ref{fig:hyp-mod-dat-figure} displays the link between all these verbal hypotheses, the process model that corresponds to each of them, and their predictions in the RT distributions.
-
-All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli (e.g., Parker et al., 2021).
-This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms (e.g., Aguasvivas et al., 2020; Brysbaert et al., 2021; Brysbaert et al., 2016; Mandera et al., 2020).
-So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries (e.g., Adelman et al., 2014).
-Importantly, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.~unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) (see Jacobs et al., 1995; Ziegler et al., 2000, for advantages of within-condition comparisons).
-Thus, the within-subject manipulation of prime exposure duration in both experiments allows us to obtain a comprehensive picture of masked identity priming effects--also including the examination of potential inhibitory effects of unrelated primes.
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/hyp-mod-dat-figure-1.pdf}
-\caption{\label{fig:hyp-mod-dat-figure}Mapping from hypotheses to data via evidence accumulation models.
-The bottom part of each graph represents sample paths, and the top part shows the cumulative density functions.
-From left to right: \emph{Null Effect} - there are no differences between the conditions; \emph{Effect in Encoding} - the difference between the conditions is on the encoding time, hence the RT distributions are shifted; and \emph{Effect of Encoding and Evidence Accumulation} - the differences between the conditions is on the rate of evidence accumulation, thus increasing the effect size for longer RTs (right-tail of the distribution).}
-\end{figure}
-
-\hypertarget{experiment-1}{%
-\section{Experiment 1}\label{experiment-1}}
-
-In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33.3 ms and 50 ms (roughly corresponding to two and three frames, respectively, at a refresh rate of 60 Hz).
-
-We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the two experiments.
-
-\hypertarget{method}{%
-\subsection{Method}\label{method}}
-
-The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at \url{https://osf.io/57rzq/}.
-
-\hypertarget{participants}{%
-\subsubsection{Participants}\label{participants}}
-
-Participants were recruited through Prolific (www.prolific.co, 2021).
-The experiment was accessed by 101 participants.
-Out of these, 89 provided experimental data.
-Two of these participants did not complete the experiment.
-A further ten were excluded because of low accuracy (less than .8, which was the pre-registered criterion).
-In the end, we analyzed the data from 77 participants (36 female), aged from 18 to 71 (mean age: 31.14).
-All these participants indicated that English was their first language in the Prolific screening questions.
-Based on their IP addresses, 47 participants were based in the UK, 23 were based in the US, three participants were based in Canada, and two participants were based in Ireland.
-Two participants could not be localized in this way.
-All participants were naïve to the purpose of the experiment and received £1.25 for their participation (corresponding to £5/hour).
-Participants could use either a desktop/laptop computer or a mobile device.
-Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
-
-\textbf{\emph{Rationale for sample size and stopping rule.}} Brysbaert and Stevens (2018) recommended that masked priming experiments should have at least 1,600 observations per condition.
-In order to account for potentially smaller effect sizes in an online experiment, we set a target of 3,000 observations per condition (12,000 observations total), which corresponds to a minimum of 50 participants given that there were 240 word stimuli in the experiment (see below).
-Our stopping rule was to keep collecting data until 3,000 valid observations were found.
-This goal was met and exceeded in our initial data collection with a budget of £200.
-
-\hypertarget{materials}{%
-\subsubsection{Materials}\label{materials}}
-
-We selected 240 six-letter English words from the English Lexicon Project (Balota et al., 2007).
-The mean Zipf frequency based on the HAL corpus (Lund \& Burgess, 1996) was 3.8 (range: 1.9--5.5).
-The mean OLD20 (Yarkoni et al., 2008) was 2.1 (range: 1.4--3).
-We also selected 240 matched, orthographically legal six-letter nonwords.
-For each target, we created an identical prime (e.g.~\emph{region --- REGION} and \emph{fainch --- FAINCH}) and an unrelated prime consisting of another word from the list (e.g.~\emph{launch --- REGION} and \emph{miluer --- FAINCH})\footnote{Note that the lexical status of the unrelated prime differed depending on the target type: for word targets, the unrelated primes were words, whereas for nonword targets, they were pseudowords.
-However, as shown by Fernández-López et al.
-(2019), the lexical status of the unrelated prime does not affect lexical decision times.}.Unrelated primes were orthographically were paired with the targets by rearranging the order of identity primes (controling for neighbors; see Perea et al.
-(2018)).
-Appendix A contains a list of the target items, and all counterbalanced lists can be found in the on-line repository.
-
-\hypertarget{procedure}{%
-\subsubsection{Procedure}\label{procedure}}
-
-Participants were able to sign up for the experiment on the Prolific website.
-Upon signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment (Qualtrics, 2020).
-After indicating their agreement to participate, participants were forwarded to Pavlovia (Pavlovia, 2020), where the actual lexical decision task was implemented in PsychoJS.
-In the experiment, all stimuli were presented in the center of the screen in black Courier New font on a white background.
-As we do not know the exact dimensions of each participant's screen, all stimulus sizes and positions were defined in PsychoPy's ``height'' units, with the bottom left of a 16:10 aspect ratio screen being represented as (-.8, -.5) and the top right being (.8, .5).
-The height for all text stimuli was 0.1 units.
-Each trial began with a six-character pattern mask (\emph{\#\#\#\#\#\#}) set to be presented for 500 ms, followed first by the lowercase prime (e.g.~\emph{region}) set to be presented for either 33.3 or 50 ms, and then by the uppercase target (e.g.~\emph{REGION}).
-Participants were instructed to respond to the target stimulus as quickly as possible by pressing the ``Z'' key of their keyboard (if their device had one) if the target was not a valid English word or the ``M'' key if the target was a valid English word.
-Participants on a device without a keyboard were instructed to respond by touching one of two rectangular touch areas labeled ``Z = Non-word'' (presented at -0.4, -0.3) and ``M = Word'' (presented at 0.4, -0.3).
-The touch areas each had a width of 0.4 and a height of 0.2 and were presented in white with a black outline.
-If participants did not respond within two seconds of the target onset, a ``Too slow!'' feedback message was shown for 500 ms and the trial ended.
-The experimental trials were preceded by 16 practice trials during which participants also received feedback on the accuracy of their responses.
-No feedback apart from the trial timeout feedback was given during the experimental trials.
-Every 120 trials, participants were asked to take a short break before continuing the experiment.
-After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.
-
-\hypertarget{data-analysis}{%
-\subsubsection{Data analysis}\label{data-analysis}}
-
-We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.10.5; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.7; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.3; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.3; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.25; Xie, 2021).}.
-We only analyzed trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as incorrect responses (5.84 \% of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.36 \% of trials).
-For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.~identical) and prime duration (33.3 ms vs.~50 ms) as well as their interaction as the fixed effects.
-For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -0.5 and unrelated was coded as 0.5.
-For priming duration, 33.3 ms was coded as -0.5 and 50 ms was coded as 0.5.
-We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items.
-We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component \(\mu\) and the scale parameter of the exponential component \(\beta\) (equaling the inverse of the rate parameter \(\lambda\)) being allowed to vary between conditions.
-To model response accuracy, we used the Bernoulli distribution with a logit link.
-We used the default priors suggested by \emph{brms} except for the coefficients for the fixed effects, for which we applied weakly informative priors of \(\beta \sim N(0,100)\) in order to rule out improbably large effect sizes.
-Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warm-up iterations for the accuracy models).
-We consider an effect as credible if the 95\% Credible Interval (CrI) estimated from the posterior distribution does not contain zero.
-In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.
-
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table \ref{tab:exp1-descriptive-rt-table} (although note that we only analyzed the word trials).
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp1-descriptive-rt-table}Mean, Median, Standard Deviation (SD), range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 1 for each condition.}
-
-\begin{tabular}{lllllllll}
-\toprule
-Stimulus Type & \multicolumn{1}{c}{Prime Duration} & \multicolumn{1}{c}{Relatedness} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Accuracy}\\
-\midrule
-Nonword & 33.3 ms & Identity & 700 & 665 & 187 & 263 & 1,776 & 0.91\\
-Nonword & 33.3 ms & Unrelated & 702 & 664 & 188 & 256 & 1,770 & 0.92\\
-Nonword & 50 ms & Identity & 700 & 658 & 189 & 256 & 1,760 & 0.91\\
-Nonword & 50 ms & Unrelated & 699 & 657 & 185 & 251 & 1,796 & 0.93\\
-Word & 33.3 ms & Identity & 630 & 599 & 164 & 254 & 1,796 & 0.94\\
-Word & 33.3 ms & Unrelated & 652 & 619 & 166 & 254 & 1,783 & 0.93\\
-Word & 50 ms & Identity & 608 & 575 & 161 & 265 & 1,784 & 0.96\\
-Word & 50 ms & Unrelated & 649 & 620 & 158 & 294 & 1,710 & 0.93\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\newpage
-
-\hypertarget{response-times}{%
-\subsubsection{Response times}\label{response-times}}
-
-Table \ref{tab:exp1-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-The RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 31.55, 95\% CrI {[}27.16, 35.92{]}), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (\emph{b} = -10.96, 95\% CrI {[}-14.83, -7.11{]}).
-The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = 19.31, 95\% CrI {[}11.39, 27.09{]}).
-The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.07{]}).
-However, the 50 ms prime exposure duration seems to be associated with a slightly lower \(\beta\), i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (\emph{b} = -0.07, 95\% CrI {[}-0.12, -0.03{]}).
-On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (\emph{b} = 0.03, 95\% CrI {[}-0.05, 0.12{]}).
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp1-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for correct word RTs in Experiment 1.}
-
-\small{
-
-\begin{tabular}{cccccc}
-\toprule
-Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
-\midrule
-Intercept ($\mu$) & 633.707 & 8.815 & 617.142 & 651.175 & 1.006\\
-Intercept ($\beta$) & 4.686 & 0.042 & 4.601 & 4.768 & 1.001\\
-Relatedness ($\mu$) & 31.551 & 2.228 & 27.162 & 35.915 & 1.000\\
-Prime Duration ($\mu$) & -10.959 & 1.947 & -14.825 & -7.105 & 1.000\\
-Relatedness:Prime Duration ($\mu$) & 19.306 & 4.026 & 11.388 & 27.094 & 1.000\\
-Relatedness ($\beta$) & 0.031 & 0.022 & -0.011 & 0.073 & 1.000\\
-Prime Duration ($\beta$) & -0.074 & 0.024 & -0.120 & -0.028 & 1.000\\
-Relatedness:Prime Duration ($\beta$) & 0.031 & 0.042 & -0.051 & 0.115 & 1.000\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $\beta$ is the scale parameter (the inverse of the rate parameter $\lambda$) of the ex-Gaussian distribution.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-These results can be visualized in the delta plots depicted in Figure \ref{fig:deltas-e1-words}.
-Delta plots are residual quantile plots that show the distributional differences between conditions (see De Jong et al., 1994).
-As can be seen in Panel A, there is an identity priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33.3 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33.3 ms one.
-We also found a slight increase of priming effects for the longest responses (quantile .9) in the 33.3 ms prime duration condition.
-This apparent anomaly can be understood better by looking at Panel B of the same figure.
-In this panel, we show the size of the prime duration effect (computed as the difference in response times between responses to the 50 ms condition and responses to the 33.3 ms condition) across RT quantiles.
-While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition yielded virtually the same response times in the 33.3 and 50 ms conditions, except for a small increase at the 50 ms prime duration for the very long responses (i.e., .9 quantile)--we prefer not to over-interpret this latter finding with the slowest responses, as it did not appear in Experiment 2.
-
-\begin{figure}
-\centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e1-words-1.pdf}
-\caption{\label{fig:deltas-e1-words}Delta plots depicting the magnitude of the effect over time in Experiment 1.
-Each dot represents the mean RT at the .1, .3, .5, .7 and .9 quantiles.
-\emph{Panel A)} Difference in RT between unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right).
-\emph{Panel B)} Difference in RT between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions.}
-\end{figure}
-
-\hypertarget{accuracy}{%
-\subsubsection{Accuracy}\label{accuracy}}
-
-Table \ref{tab:exp1-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.50, 95\% CrI {[}-0.72, -0.31{]}).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = 0.19, 95\% CrI {[}-0.02, 0.42{]}).
-The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = -0.53, 95\% CrI {[}-0.94, -0.14{]}).
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp1-acc-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for response accuracy on word trials in Experiment 1.}
-
-\small{
-
-\begin{tabular}{cccccc}
-\toprule
-Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
-\midrule
-Intercept & 3.458 & 0.122 & 3.224 & 3.705 & 1.000\\
-Relatedness & -0.503 & 0.105 & -0.720 & -0.305 & 1.000\\
-Prime Duration & 0.192 & 0.110 & -0.016 & 0.417 & 1.000\\
-Relatedness:Prime Duration & -0.530 & 0.206 & -0.944 & -0.138 & 1.000\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
-
-The results from Experiment 1 reveal that we were able to replicate benchmark masked priming effects using an online experiment.
-The size and shape of the effect is similar to that observed in previous studies (e.g., Gomez et al., 2013; Perea et al., 2018; Taikh \& Lupker, 2020; Yang et al., 2021).
-In addition, we also saw a clear difference between the 33.3 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices.
-While the shape of the distribution changed slightly between the 33.3 ms and the 50 ms prime exposure durations, we did not observe an effect of the prime relatedness condition on the shape parameter \(\beta\) of the exponential distribution, suggesting, according to the savings hypothesis by Forster (1998), that only encoding processes were affected by the relatedness manipulation.
-Moreover, as can be observed in Figure \ref{fig:deltas-e1-words}, the effect magnitude was close to the stimulus-onset asynchrony (see also Perea et al., 2018).
-
-Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.
-Indeed, to better define the priming effect, one needs a baseline that serves as a reference point (i.e., an analog of the minimum {``intensity''} priming condition; see Jacobs et al., 1995).
-In order to further explore this question, we performed a second experiment in which we set the prime to be displayed for an even shorter duration.
-As described in the Introduction, a 16.7 ms prime exposure duration should yield a negligible priming effect (Tzur \& Frost, 2007; Ziegler et al., 2000) so the pattern should be qualitatively different from the 33.3 and 50 ms durations used in Experiment 1.
-If it does not, this would cast doubt on the timing accuracy in online experiments.
-In this experiment, we also include the 33.3 ms prime duration condition to not only have a better scheme to compare the two experiments, but also to be able to test the within-condition effects (Jacobs et al., 1995)---assuming the 16.7 ms prime duration serves as a baseline.
-
-\hypertarget{experiment-2}{%
-\section{Experiment 2}\label{experiment-2}}
-
-In the second experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 16.7 ms and 33.3 ms (roughly corresponding to one and two frames at a refresh rate of 60 Hz).
-
-The pre-registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}. The materials, data files, and R scripts can be found at {[}\url{https://osf.io/57rzq/}{]}
-
-\hypertarget{method-1}{%
-\subsection{Method}\label{method-1}}
-
-\hypertarget{participants-1}{%
-\subsubsection{Participants}\label{participants-1}}
-
-As in Experiment 1, participants were recruited through Prolific (www.prolific.co, 2021).
-The experiment was accessed by 102 participants.
-Out of these, 87 provided experimental data.
-One of these participants did not complete the experiment.
-A further seven were excluded because of low accuracy (again, less than .8).
-The remaining 79 participants were aged from 18 to 69 (mean age: 31.14).
-Of the participants, 40 identified as male, and 39 identified as female.
-All these participants indicated that English was their first language in the Prolific screening questions.
-Based on their IP addresses, 56 participants were based in the UK, 14 were based in the US, two participants were based in Canada, two participants were based in South Africa, and one participant each was based in Hungary and Ireland.
-Three participants could not be localized in this way.
-As in Experiment 1, all participants were naïve to the purpose of the experiment, and received £1.25 for their participation (corresponding to £5/hour).
-Participants could use either a desktop/laptop computer or a mobile device.
-Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
-
-\textbf{\emph{Rationale for sample size and stopping rule.}} As in Experiment 1, our stopping rule was to keep collecting data until 3,000 valid observations were collected.
-This goal was met and exceeded in our initial data collection with a budget of £200.
-
-\hypertarget{materials-1}{%
-\subsubsection{Materials}\label{materials-1}}
-
-The materials were identical to those used in Experiment 1.
-
-\hypertarget{procedure-1}{%
-\subsubsection{Procedure}\label{procedure-1}}
-
-The procedure was identical to Experiment 1, the only difference being that the primes were set to be displayed for either 16.7 ms or 33.3 ms.
-
-\hypertarget{data-analysis-1}{%
-\subsubsection{Data analysis}\label{data-analysis-1}}
-
-We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as those with incorrect responses (4.93 \% of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.15 \% of trials).
-For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5.
-Otherwise, the model specifications were identical to those in Experiment 1.
-
-\hypertarget{results-1}{%
-\subsection{Results}\label{results-1}}
-
-Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table \ref{tab:exp2-descriptive-rt-table}.
-
-\hypertarget{response-times-1}{%
-\subsubsection{Response times}\label{response-times-1}}
-
-As in Experiment 1, the RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 8.53, 95\% CrI {[}5.07, 12.11{]}).
-For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (\emph{b} = -3.60, 95\% CrI {[}-7.22, -0.03{]}).
-However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (\emph{b} = 15.17, 95\% CrI {[}8.52, 21.73{]}).
-The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.02, 0.07{]}), prime exposure duration (\emph{b} = 0.01, 95\% CrI {[}-0.03, 0.05{]}), or their interaction (\emph{b} = -0.03, 95\% CrI {[}-0.12, 0.05{]}), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
-
-Table \ref{tab:exp2-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-\newpage
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp2-descriptive-rt-table}Mean, Median, Standard Deviation (SD), and range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 2 for all conditions.}
-
-\begin{tabular}{lllllllll}
-\toprule
-Stimulus Type & \multicolumn{1}{c}{Prime Duration} & \multicolumn{1}{c}{Relatedness} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Accuracy}\\
-\midrule
-Nonword & 16.7 ms & Identity & 719 & 680 & 185 & 330 & 1,787 & 0.93\\
-Nonword & 16.7 ms & Unrelated & 717 & 677 & 183 & 284 & 1,799 & 0.94\\
-Nonword & 33.3 ms & Identity & 717 & 668 & 193 & 351 & 1,787 & 0.94\\
-Nonword & 33.3 ms & Unrelated & 715 & 672 & 188 & 281 & 1,789 & 0.94\\
-Word & 16.7 ms & Identity & 659 & 625 & 160 & 311 & 1,785 & 0.94\\
-Word & 16.7 ms & Unrelated & 661 & 623 & 165 & 308 & 1,796 & 0.95\\
-Word & 33.3 ms & Identity & 649 & 618 & 154 & 280 & 1,657 & 0.96\\
-Word & 33.3 ms & Unrelated & 667 & 633 & 162 & 269 & 1,701 & 0.94\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp2-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for correct word RTs in Experiment 2.}
-
-\small{
-
-\begin{tabular}{cccccc}
-\toprule
-Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
-\midrule
-Intercept ($\mu$) & 656.975 & 9.036 & 639.056 & 674.711 & 1.003\\
-Intercept ($\beta$) & 4.658 & 0.043 & 4.573 & 4.741 & 1.003\\
-Relatedness ($\mu$) & 8.529 & 1.795 & 5.065 & 12.106 & 1.000\\
-Prime Duration ($\mu$) & -3.602 & 1.813 & -7.216 & -0.033 & 1.000\\
-Relatedness:Prime Duration ($\mu$) & 15.166 & 3.390 & 8.517 & 21.727 & 1.000\\
-Relatedness ($\beta$) & 0.028 & 0.023 & -0.016 & 0.073 & 1.000\\
-Prime Duration ($\beta$) & 0.011 & 0.021 & -0.031 & 0.053 & 1.000\\
-Relatedness:Prime Duration ($\beta$) & -0.034 & 0.043 & -0.119 & 0.049 & 1.000\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $\beta$ is the scale parameter (the inverse of the rate parameter $\lambda$) of the ex-Gaussian distribution.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-We also created the delta plots of data from Experiment 2 (see Figure \ref{fig:deltas-e2-words}).
-Panel A, shows there is no priming effect for the 16.7 ms condition, in contrast with a consistent effect across quantiles for the 33.3 ms condition (parallel to the one found in Experiment 1).
-Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight hindering for unrelated primes.
-
-\begin{figure}
-\centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e2-words-1.pdf}
-\caption{\label{fig:deltas-e2-words}Delta plots depicting the magnitude of the effect over time in Experiment 2.}
-\end{figure}
-
-\hypertarget{accuracy-1}{%
-\subsubsection{Accuracy}\label{accuracy-1}}
-
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.22, 95\% CrI {[}-0.43, 0.00{]}).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16.7 ms prime duration condition than in the 33.3 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = -0.05, 95\% CrI {[}-0.31, 0.18{]}).
-The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33.3 ms condition, and reversed in the 16.7 ms condition (\emph{b} = -0.71, 95\% CrI {[}-1.16, -0.30{]}), although the effect in the 16.7 ms condition was very weak.
-Table \ref{tab:exp2-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, indicating that the model was fitted successfully as they are all close to 1.
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp2-acc-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for fixed effects of the model fitted for response accuracy on word trials in Experiment 2.}
-
-\small{
-
-\begin{tabular}{cccccc}
-\toprule
-Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
-\midrule
-Intercept & 3.734 & 0.135 & 3.476 & 4.007 & 1.000\\
-Relatedness & -0.217 & 0.109 & -0.434 & -0.004 & 1.000\\
-Prime Duration & -0.055 & 0.126 & -0.306 & 0.184 & 1.000\\
-Relatedness:Prime Duration & -0.710 & 0.218 & -1.157 & -0.305 & 1.000\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{discussion-1}{%
-\subsection{Discussion}\label{discussion-1}}
-
-In Experiment 2, we found the pattern we expected from previous research: In the mean \(\mu\) of the Gaussian component of the ex-Gaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration (Tzur \& Frost, 2007; Ziegler et al., 2000).
-This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
-In addition, we did not observe an effect of the prime relatedness on the shape parameter \(\beta\) of the exponential component (i.e., the effect corresponded to a shift of the RT distributions, as shown in in-lab studies; e.g., Taikh \& Lupker, 2020; Yang et al., 2021).
-Moreover, the magnitude of the priming effect at the 33.3 ms prime exposure duration was close to the magnitude of the prime-target stimulus-onset asynchrony, as can be seen in the delta plots in Figure \ref{fig:deltas-e2-words} (see Gomez et al., 2013; Perea et al., 2018).
-Hence, we replicated again the commonly observed savings effect (Forster, 1998).
-
-Critically, because the 16.7 ms prime duration condition yielded virtually no priming effects, this very short prime exposure duration serves as a within-condition baseline that allows us to qualify the facilitative vs.~inhibitory nature of masked priming effects (Jacobs et al., 1995; Ziegler et al., 2000).
-Specifically, when compared to the baseline, our findings at the 33.3 ms prime duration show a combination of a slight facilitatory effect for identity primes and a small inhibitory effect for unrelated primes.
-
-\hypertarget{general-discussion}{%
-\section{General Discussion}\label{general-discussion}}
-
-In this study, we set out to test whether we could obtain benchmark masked priming effects both qualitatively (i.e., shift in the RT distributions) and quantitatively (i.e., effect sizes) using an online, browser-based experiment software.
-To that end, we conducted two online masked identity priming experiments (e.g., \emph{region --- REGION} vs.~\emph{launch --- REGION}) in which we manipulated prime exposure duration (33.3 vs.~50 ms in Experiment 1; 16.7 vs.~33 ms in Experiment 2).
-The results of our online-based experiments replicated and extended benchmarks masked identity priming effects previous in the lab-based studies.
-We observed the effect sizes predicted by Forster's (1998) savings hypothesis: Our data show a shift in the mean of the Gaussian component of the ex-Gaussian distribution, but no change in the shape parameter \(\beta\) of the exponential component, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes.
-Furthermore, the size of the priming effect was not only directly influenced by the prime duration, suggesting the experimental software was able to control the display timing of the prime accurately, but also of a similar magnitude to the prime duration (within the range reported in previous studies, e.g., 35-47 ms for a 50 ms prime duration in Perea et al., 2018).
-Importantly, the use of a within-condition baseline revealed that the identity priming effects at the 33 ms prime exposure duration were a combination of some small facilitation from identity primes and some small inhibition from unrelated primes (see Jacobs et al., 1995, for evidence with a psychophysical experiment).
-Likewise, the greater identity priming effects at the 50 ms rather than at the 33.3 ms prime exposure duration were essentially due to the facilitation from the identity pairs.
-
-While accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, they are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade.
-Similarly, unlike in-lab conditions, where the contrast of the computer screens can be measured and kept constant, there is no such a guarantee for the screens used by online participants---note that Tzur and Frost (2007) were only able to observe strong effects for short prime exposure durations when using extreme contrast values.
-Thus, the fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy, PsychoJS.
-
-Furthermore, our results extend previous work showing the validity of on-line studies measuring response times (e.g., Brysbaert et al., 2016; Cai et al., 2017; Dufau et al., 2011; Eerland et al., 2013; Rodd et al., 2016, to cite a few instances) to the masked priming technique.
-Thus, the present study opens the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
-Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible.
-For instance, online participants can be people from different countries and/or cultures, from different age groups, bilinguals/multilinguals, even those who do not own a computer, only a smartphone.
-Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant.
-This opens up the possibility of masked-priming crowdsourced megastudies.
-In general, deploying masked priming experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
-
-In conclusion, our results give us confidence that high-quality behavioral data using the masked priming paradigm can be collected online using Javascript-based experiment platforms.
-We hope that future research takes advantage of these new methods in order to make research faster, more inclusive, and more efficient.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-adelman2014}{}%
-Adelman, J.
-S., Johnson, R.
-L., McCormick, S.
-F., McKague, M., Kinoshita, S., Bowers, J.
-S., Perry, J.
-R., Lupker, S.
-J., Forster, K.
-I., Cortese, M.
-J., Scaltritti, M., Aschenbrenner, A.
-J., Coane, J.
-H., White, L., Yap, M.
-J., Davis, C., Kim, J., \& Davis, C.
-J.
-(2014).
-A behavioral database for masked form priming.
-\emph{Behavior Research Methods}, \emph{46}(4), 1052--1067.
-\url{https://doi.org/10.3758/s13428-013-0442-y}
-
-\leavevmode\hypertarget{ref-aguasvivas2020}{}%
-Aguasvivas, J., Carreiras, M., Brysbaert, M., Mandera, P., Keuleers, E., \& Duñabeitia, J.
-A.
-(2020).
-How do Spanish speakers read words?
-Insights from a crowdsourced lexical decision megastudy.
-\emph{Behavior Research Methods}, \emph{52}(5), 1867--1882.
-\url{https://doi.org/10.3758/s13428-020-01357-9}
-
-\leavevmode\hypertarget{ref-Alluhaybi_2020}{}%
-Alluhaybi, I., \& Witzel, J.
-(2020).
-Letter connectedness and arabic visual word recognition.
-\emph{Quarterly Journal of Experimental Psychology}, \emph{73}(10), 1660--1674.
-\url{https://doi.org/10.1177/1747021820926155}
-
-\leavevmode\hypertarget{ref-anwyl-irvine2020a}{}%
-Anwyl-Irvine, A., Dalmaijer, E.
-S., Hodges, N., \& Evershed, J.
-K.
-(2020).
-Realistic precision and accuracy of online experiment platforms, web browsers, and devices.
-\emph{Behavior Research Methods}.
-\url{https://doi.org/10.3758/s13428-020-01501-5}
-
-\leavevmode\hypertarget{ref-anwyl-irvine2020}{}%
-Anwyl-Irvine, A., Massonni, J., Flitton, A., Kirkham, N., \& Evershed, J.
-K.
-(2020).
-orilla in our midst: An online behavioral experiment builder.
-\emph{Behavior Research Methods}, \emph{52}(1), 388--407.
-\url{https://doi.org/10.3758/s13428-019-01237-x}
-
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}
-
-\leavevmode\hypertarget{ref-austSeriousnessChecksAre2013}{}%
-Aust, F., Diedenhofen, B., Ullrich, S., \& Musch, J.
-(2013).
-Seriousness checks are useful to improve data validity in online research.
-\emph{Behavior Research Methods}, \emph{45}(2), 527--535.
-\url{https://doi.org/10.3758/s13428-012-0265-2}
-
-\leavevmode\hypertarget{ref-balota2007}{}%
-Balota, D.
-A., Yap, M.
-J., Hutchison, K.
-A., Cortese, M.
-J., Kessler, B., Loftis, B., Neely, J.
-H., Nelson, D.
-L., Simpson, G.
-B., \& Treiman, R.
-(2007).
-The English Lexicon Project.
-\emph{Behavior Research Methods}, \emph{39}(3), 445--459.
-\url{https://doi.org/10.3758/BF03193014}
-
-\leavevmode\hypertarget{ref-R-tinylabels}{}%
-Barth, M. (2021). \emph{{tinylabels}: Lightweight variable labels}. \url{https://github.com/mariusbarth/tinylabels}
-
-\leavevmode\hypertarget{ref-birnbaumPsychologicalExperimentsInternet2000a}{}%
-Birnbaum, M. H., \& Birnbaum, M. O. (2000). \emph{Psychological {Experiments} on the {Internet}}. {Elsevier}. \url{http://books.google.com?id=sw4NHyThFFkC}
-
-\leavevmode\hypertarget{ref-bridges2020}{}%
-Bridges, D., Pitiot, A., MacAskill, M.
-R., \& Peirce, J.
-W.
-(2020).
-The timing mega-study: comparing a range of experiment generators, both lab-based and online.
-\emph{PeerJ}, \emph{8}, e9414.
-\url{https://doi.org/10.7717/peerj.9414}
-
-\leavevmode\hypertarget{ref-brysbaert2021a}{}%
-Brysbaert, M., Keuleers, E., \& Mandera, P.
-(2021).
-Which words do English non-native speakers know?
-New supernational levels based on yes/no decision.
-\emph{Second Language Research}, \emph{37}(2), 207--231.
-\url{https://doi.org/10.1177/0267658320934526}
-
-\leavevmode\hypertarget{ref-brysbaert2018}{}%
-Brysbaert, M., \& Stevens, M. (2018). Power Analysis and Effect Size in Mixed Effects Models: A Tutorial. \emph{Journal of Cognition}, \emph{1}(1), 9. \url{https://doi.org/10.5334/joc.10}
-
-\leavevmode\hypertarget{ref-brysbaert2016impact}{}%
-Brysbaert, M., Stevens, M., Mandera, P., \& Keuleers, E.
-(2016).
-The impact of word prevalence on lexical decision times: Evidence from the dutch lexicon project 2.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{42}(3), 441.
-
-\leavevmode\hypertarget{ref-R-brms_a}{}%
-Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
-
-\leavevmode\hypertarget{ref-R-brms_b}{}%
-Bürkner, P.-C. (2018). Advanced {Bayesian} multilevel modeling with the {R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://doi.org/10.32614/RJ-2018-017}
-
-\leavevmode\hypertarget{ref-cai2017accent}{}%
-Cai, Z.
-G., Gilbert, R.
-A., Davis, M.
-H., Gaskell, M.
-G., Farrar, L., Adler, S., \& Rodd, J.
-M.
-(2017).
-\emph{Accent modulates access to word meaning: Evidence for a speaker-model account of spoken word recognition}.
-\url{https://doi.org/10.31234/osf.io/5x3tb}
-
-\leavevmode\hypertarget{ref-de1994conditional}{}%
-De Jong, R., Liang, C.-C., \& Lauber, E.
-(1994).
-Conditional and unconditional automaticity: A dual-process model of effects of spatial stimulus-response correspondence.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{20}(4), 731.
-
-\leavevmode\hypertarget{ref-deleeuw2015}{}%
-de Leeuw, J.
-R.
-(2015).
-jsPsych: A JavaScript library for creating behavioral experiments in a Web browser.
-\emph{Behavior Research Methods}, \emph{47}(1), 1--12.
-\url{https://doi.org/10.3758/s13428-014-0458-y}
-
-\leavevmode\hypertarget{ref-Dubey_2018}{}%
-Dubey, N., Witzel, N., \& Witzel, J.
-(2018).
-Script differences and masked translation priming: Evidence from hindi-english bilinguals.
-\emph{Quarterly Journal of Experimental Psychology}, \emph{71}(11), 2421--2438.
-\url{https://doi.org/10.1177/1747021817743241}
-
-\leavevmode\hypertarget{ref-Dufau_2011}{}%
-Dufau, S., Duñabeitia, J.
-A., Moret-Tatay, C., McGonigal, A., Peeters, D., Alario, F.-X., Balota, D.
-A., Brysbaert, M., Carreiras, M., Ferrand, L., Ktori, M., Perea, M., Rastle, K., Sasburg, O., Yap, M.
-J., Ziegler, J.
-C., \& Grainger, J.
-(2011).
-Smart phone, smart science: How the use of smartphones can revolutionize research in cognitive science.
-\emph{{PLoS} {ONE}}, \emph{6}(9), e24974.
-\url{https://doi.org/10.1371/journal.pone.0024974}
-
-\leavevmode\hypertarget{ref-R-Rcpp_b}{}%
-Eddelbuettel, D., \& Balamuta, J.
-J.
-(2018).
-{Extending extit{R} with extit{C++}: A Brief Introduction to extit{Rcpp}}.
-\emph{The American Statistician}, \emph{72}(1), 28--36.
-\url{https://doi.org/10.1080/00031305.2017.1375990}
-
-\leavevmode\hypertarget{ref-R-Rcpp_a}{}%
-Eddelbuettel, D., \& François, R. (2011). {Rcpp}: Seamless {R} and {C++} integration. \emph{Journal of Statistical Software}, \emph{40}(8), 1--18. \url{https://doi.org/10.18637/jss.v040.i08}
-
-\leavevmode\hypertarget{ref-eerland2013influence}{}%
-Eerland, A., Engelen, J.
-A.
-A., \& Zwaan, R.
-A.
-(2013).
-The influence of direct and indirect speech on mental representations.
-\emph{{PLoS} {ONE}}, \emph{8}(6), e65480.
-\url{https://doi.org/10.1371/journal.pone.0065480}
-
-\leavevmode\hypertarget{ref-Fern_ndez_L_pez_2019}{}%
-Fernández-López, M., Marcet, A., \& Perea, M.
-(2019).
-Can response congruency effects be obtained in masked priming lexical decision?
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{45}(9), 1683--1702.
-\url{https://doi.org/10.1037/xlm0000666}
-
-\leavevmode\hypertarget{ref-forster1998pros}{}%
-Forster, K. (1998). The pros and cons of masked priming. \emph{Journal of Psycholinguistic Research}, \emph{27}(2), 203--233.
-
-\leavevmode\hypertarget{ref-forsterRepetitionPrimingFrequency1984}{}%
-Forster, K., \& Davis, C.
-(1984).
-Repetition priming and frequency attenuation in lexical access.
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{10}(4), 680--698.
-\url{https://doi.org/10.1037/0278-7393.10.4.680}
-
-\leavevmode\hypertarget{ref-forsterDMDXWindowsDisplay2003}{}%
-Forster, K., \& Forster, J. (2003). {DMDX}: {A Windows} display program with millisecond accuracy. \emph{Behavior Research Methods, Instruments, \& Computers}, \emph{35}(1), 116--124.
-
-\leavevmode\hypertarget{ref-Gomez_2020}{}%
-Gomez, P., \& Perea, M.
-(2020).
-Masked identity priming reflects an encoding advantage in developing readers.
-\emph{Journal of Experimental Child Psychology}, \emph{199}, 104911.
-\url{https://doi.org/10.1016/j.jecp.2020.104911}
-
-\leavevmode\hypertarget{ref-gomezDiffusionModelAccount2013}{}%
-Gomez, P., Perea, M., \& Ratcliff, R.
-(2013).
-A diffusion model account of masked versus unmasked priming: {Are} they qualitatively different?
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{39}(6), 1731--1740.
-\url{https://doi.org/10.1037/a0032333}
-
-\leavevmode\hypertarget{ref-grainger2008cracking}{}%
-Grainger, J. (2008). Cracking the orthographic code: An introduction. \emph{Language and Cognitive Processes}, \emph{23}(1), 1--35. \url{https://doi.org/10.1080/01690960701578013}
-
-\leavevmode\hypertarget{ref-grossi2006relatedness}{}%
-Grossi, G. (2006). Relatedness proportion effects on masked associative priming: An {ERP} study. \emph{Psychophysiology}, \emph{43}(1), 21--30. \url{https://doi.org/10.1111/j.1469-8986.2006.00383.x}
-
-\leavevmode\hypertarget{ref-R-purrr}{}%
-Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. \url{https://CRAN.R-project.org/package=purrr}
-
-\leavevmode\hypertarget{ref-Jacobs_1995}{}%
-Jacobs, A.
-M., Grainger, J., \& Ferrand, L.
-(1995).
-The incremental priming technique: A method for determining within-condition priming effects.
-\emph{Perception {\&} Psychophysics}, \emph{57}(8), 1101--1110.
-\url{https://doi.org/10.3758/bf03208367}
-
-\leavevmode\hypertarget{ref-lund1996}{}%
-Lund, K., \& Burgess, C.
-(1996).
-Producing high-dimensional semantic spaces from lexical co-occurrence.
-\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{28}(2), 203--208.
-\url{https://doi.org/10.3758/BF03204766}
-
-\leavevmode\hypertarget{ref-R-see}{}%
-Lüdecke, D., Ben-Shachar, M.
-S., Waggoner, P., \& Makowski, D.
-(2020).
-See: Visualisation toolbox for 'easystats' and extra geoms, themes and color palettes for 'ggplot2'.
-\emph{CRAN}.
-\url{https://doi.org/10.5281/zenodo.3952153}
-
-\leavevmode\hypertarget{ref-R-bayestestR}{}%
-Makowski, D., Ben-Shachar, M.
-S., \& Lüdecke, D.
-(2019).
-bayestestR: Describing effects and their uncertainty, existence and significance within the bayesian framework.
-\emph{Journal of Open Source Software}, \emph{4}(40), 1541.
-\url{https://doi.org/10.21105/joss.01541}
-
-\leavevmode\hypertarget{ref-mandera2020}{}%
-Mandera, P., Keuleers, E., \& Brysbaert, M.
-(2020).
-Recognition times for 62 thousand English words: Data from the English Crowdsourcing Project.
-\emph{Behavior Research Methods}, \emph{52}(2), 741--760.
-\url{https://doi.org/10.3758/s13428-019-01272-8}
-
-\leavevmode\hypertarget{ref-R-tibble}{}%
-Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. \url{https://CRAN.R-project.org/package=tibble}
-
-\leavevmode\hypertarget{ref-paolacciRunningExperimentsAmazon2010}{}%
-Paolacci, G., Chandler, J., \& Ipeirotis, P.
-G.
-(2010).
-\emph{Running {Experiments} on {Amazon Mechanical Turk}} (SSRN Scholarly Paper ID 1626226).
-{Social Science Research Network}.
-\url{https://papers.ssrn.com/abstract=1626226}
-
-\leavevmode\hypertarget{ref-Parker_2021}{}%
-Parker, A., Egan, C., Grant, J.
-H., Harte, S., Hudson, B.
-T., \& Woodhead, Z.
-V.
-J.
-(2021).
-The role of orthographic neighbourhood effects in lateralized lexical decision: A replication study and meta-analysis.
-\emph{{PeerJ}}, \emph{9}, e11266.
-\url{https://doi.org/10.7717/peerj.11266}
-
-\leavevmode\hypertarget{ref-pavlovia2020}{}%
-Pavlovia. (2020). \emph{Pavlovia}. \url{https://pavlovia.org/}
-
-\leavevmode\hypertarget{ref-R-sp}{}%
-Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. \url{https://CRAN.R-project.org/doc/Rnews/}
-
-\leavevmode\hypertarget{ref-R-patchwork}{}%
-Pedersen, T. L. (2020). \emph{Patchwork: The composer of plots}. \url{https://CRAN.R-project.org/package=patchwork}
-
-\leavevmode\hypertarget{ref-peirce2019}{}%
-Peirce, J., Gray, J.
-R., Simpson, S., MacAskill, M., Höchenberger, R., Sogo, H., Kastman, E., \& Lindeløv, J.
-K.
-(2019).
-PsychoPy2: Experiments in behavior made easy.
-\emph{Behavior Research Methods}, \emph{51}(1), 195--203.
-\url{https://doi.org/10.3758/s13428-018-01193-y}
-
-\leavevmode\hypertarget{ref-Perea_2018}{}%
-Perea, M., Marcet, A., Lozano, M., \& Gomez, P.
-(2018).
-Is masked priming modulated by memory load?
-A test of the automaticity of masked identity priming in lexical decision.
-\emph{Memory {\&} Cognition}, \emph{46}(7), 1127--1135.
-\url{https://doi.org/10.3758/s13421-018-0825-5}
-
-\leavevmode\hypertarget{ref-perea2002does}{}%
-Perea, M., \& Rosa, E.
-(2002).
-Does the proportion of associatively related pairs modulate the associative priming effect at very brief stimulus-onset asynchronies?
-\emph{Acta Psychologica}, \emph{110}(1), 103--124.
-\url{https://doi.org/10.1016/s0001-6918(01)00074-9}
-
-\leavevmode\hypertarget{ref-prolific2021}{}%
-Prolific. (2021). \emph{Prolific \textbar{} online participant recruitment for surveys and market research}. \url{https://www.prolific.co/}
-
-\leavevmode\hypertarget{ref-qualtrics2020}{}%
-Qualtrics. (2020). \emph{Qualtrics XM // the leading experience management software}. \url{https://www.qualtrics.com/uk/}
-
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
-\leavevmode\hypertarget{ref-ratcliff2004}{}%
-Ratcliff, R., Gomez, P., \& McKoon, G.
-(2004).
-A diffusion model account of the lexical decision task.
-\emph{Psychological Review}, \emph{111}(1), 159--182.
-\url{https://doi.org/10.1037/0033-295X.111.1.159}
-
-\leavevmode\hypertarget{ref-reimersPresentationResponseTiming2015}{}%
-Reimers, S., \& Stewart, N.
-(2015).
-Presentation and response timing accuracy in {Adobe Flash} and {HTML5}/{JavaScript Web} experiments.
-\emph{Behavior Research Methods}, \emph{47}(2), 309--327.
-\url{https://doi.org/10.3758/s13428-014-0471-1}
-
-\leavevmode\hypertarget{ref-rezlescu2020}{}%
-Rezlescu, C., Danaila, I., Miron, A., \& Amariei, C.
-(2020).
-\emph{Chapter 13 - More time for science: Using Testable to create and share behavioral experiments faster, recruit better participants, and engage students in hands-on research} (B.
-L.
-Parkin, Ed.; Vol.
-253, pp.
-243--262).
-Elsevier.
-\url{https://doi.org/10.1016/bs.pbr.2020.06.005}
-
-\leavevmode\hypertarget{ref-rodd2016impact}{}%
-Rodd, J.
-M., Cai, Z.
-G., Betts, H.
-N., Hanby, B., Hutchinson, C., \& Adler, A.
-(2016).
-The impact of recent and long-term experience on access to word meanings: Evidence from large-scale internet-based experiments.
-\emph{Journal of Memory and Language}, \emph{87}, 16--37.
-\url{https://doi.org/10.1016/j.jml.2015.10.006}
-
-\leavevmode\hypertarget{ref-R-rworldmap}{}%
-South, A. (2011). Rworldmap: A new r package for mapping global data. \emph{The R Journal}, \emph{3}(1), 35--43. \url{http://journal.r-project.org/archive/2011-1/RJournal_2011-1_South.pdf}
-
-\leavevmode\hypertarget{ref-Taikh_2020}{}%
-Taikh, A., \& Lupker, S.
-J.
-(2020).
-Do visible semantic primes preactivate lexical representations?
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{46}(8), 1533--1569.
-\url{https://doi.org/10.1037/xlm0000825}
-
-\leavevmode\hypertarget{ref-Tzur_2007}{}%
-Tzur, B., \& Frost, R.
-(2007).
-{SOA} does not reveal the absolute time course of cognitive processing in fast priming experiments{{73}}.
-\emph{Journal of Memory and Language}, \emph{56}(3), 321--335.
-\url{https://doi.org/10.1016/j.jml.2006.11.007}
-
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\hypertarget{ref-R-stringr}{}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. \url{https://CRAN.R-project.org/package=stringr}
-
-\leavevmode\hypertarget{ref-R-forcats}{}%
-Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. \url{https://CRAN.R-project.org/package=forcats}
-
-\leavevmode\hypertarget{ref-R-tidyr}{}%
-Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. \url{https://CRAN.R-project.org/package=tidyr}
-
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
-L., Miller, E., Bache, S.
-M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
-P., Spinu, V., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
-
-\leavevmode\hypertarget{ref-R-readxl}{}%
-Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. \url{https://CRAN.R-project.org/package=readxl}
-
-\leavevmode\hypertarget{ref-R-dplyr}{}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. \url{https://CRAN.R-project.org/package=dplyr}
-
-\leavevmode\hypertarget{ref-R-readr}{}%
-Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. \url{https://CRAN.R-project.org/package=readr}
-
-\leavevmode\hypertarget{ref-witzelTestingViabilityWebDMDX2013}{}%
-Witzel, J., Cornelius, S., Witzel, N., Forster, K.
-I., \& Forster, J.
-C.
-(2013).
-Testing the viability of {webDMDX} for masked priming experiments.
-\emph{The Mental Lexicon}, \emph{8}(3), 421--449.
-\url{https://doi.org/10.1075/ml.8.3.07wit}
-
-\leavevmode\hypertarget{ref-R-xfun}{}%
-Xie, Y. (2021). \emph{Xfun: Miscellaneous functions to support packages maintained by 'yihui xie'}. \url{https://CRAN.R-project.org/package=xfun}
-
-\leavevmode\hypertarget{ref-Yang_2021}{}%
-Yang, H., Jared, D., Perea, M., \& Lupker, S.
-J.
-(2021).
-Is letter position coding when reading in L2 affected by the nature of position coding used when bilinguals read in their L1?
-\emph{Memory {\&} Cognition}, \emph{49}(4), 771--786.
-\url{https://doi.org/10.3758/s13421-020-01126-1}
-
-\leavevmode\hypertarget{ref-yarkoni2008}{}%
-Yarkoni, T., Balota, D., \& Yap, M.
-(2008).
-Moving beyond Coltheart{'}s N: A new measure of orthographic similarity.
-\emph{Psychonomic Bulletin \& Review}, \emph{15}(5), 971--979.
-\url{https://doi.org/10.3758/PBR.15.5.971}
-
-\leavevmode\hypertarget{ref-ziegler2000}{}%
-Ziegler, J.
-C., Ferrand, L., Jacobs, A.
-M., Rey, A., \& Grainger, J.
-(2000).
-Visual and Phonological Codes in Letter and Word Recognition: Evidence from Incremental Priming.
-\emph{The Quarterly Journal of Experimental Psychology}, \emph{53A}(3), 671--692.
-
-\leavevmode\hypertarget{ref-Zimmerman_2012}{}%
-Zimmerman, R., \& Gomez, P. (2012). Drawing attention to primes increases inhibitory word priming effects. \emph{The Mental Lexicon}, \emph{7}(2), 119--146. \url{https://doi.org/10.1075/ml.7.2.01zim}
-
-\end{CSLReferences}
-
-\newpage
-
-\hypertarget{appendix-a}{%
-\section{Appendix A}\label{appendix-a}}
+\begin{appendix}
+\hypertarget{stimuli}{%
+\section{Stimuli}\label{stimuli}}
 
@@
 \end{verbatim}
+\end{appendix}
 
-\endgroup
+\clearpage
+
+\begin{appendix}
+\hypertarget{diffusion-model-accounts-for-the-data}{%
+\section{Diffusion model accounts for the
+data}\label{diffusion-model-accounts-for-the-data}}
+
+\hypertarget{about-this-appendix}{%
+\subsection{About this Appendix}\label{about-this-appendix}}
+
+The goal of this appendix is to present a brief description of how the
+diffusion model accounts for the data presented in the main article.
+While the diffusion model fits to the grouped data was part of the
+pre-registration plan, we believe that it is best to present such fits
+in this appendix as opposed to the main text to improve the readability
+of the article. For a full description of the experimental setting and
+its goals please refer to the main text.
+
+\hypertarget{the-diffusion-model}{%
+\subsection{The diffusion model}\label{the-diffusion-model}}
+
+The diffusion model (Ratcliff, 1978) is a cognitive process model for
+perceptual decisions, and it has been quite successful at accounting for
+lexical decision data (Ratcliff et al, 2004) and more importantly for
+the present work, masked priming data (Gomez et al, 2012).
+
+The model assumes that RTs to dual choice tasks are a sum of three
+distinct processes: stimulus encoding, evidence accumulation, and
+response execution. The model makes the strong assumption that evidence
+accumulation is a processes distinct from the other two components, and
+for practical reasons, it groups response execution and encoding time in
+a single parameter.
+
+The model is agnostic about the correlation between the encoding and the
+evidence accumulation processes; and we like to think about it as a tool
+to instantiate theoretical positions that can be articulated in terms of
+encoding, decision, and strategic processes.
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
+The model was fit to the grouped data (as per the pre-registration plan)
+of the two experiments. For each stimulus type the proportion of word
+and nonword responses is calculated, then for each of the two responses,
+the RTs at the .1, .3, .5, .7, and .9 quantiles is obtained. We repeat
+this process for each participants, and then all of those quantities
+(response proportions and RTs at quantiles) are averaged across
+participants. This process is also known as Vincentalizing, and the
+averaged quantiles are referred to as vintenciles
+
+The diffusion model predicts the cumulative probability of a response at
+each RT vincentile, and these model predictions are compared to the
+empirical proportions, then the sum of the
+(Observed-Predicted)2/Predicted for correct and error responses for each
+condition that is minimized with a general SIMPLEX minimization routine
+as described by Ratcliff \& Tuerlinckx (2002).
+
+\hypertarget{free-and-fixed-parameters}{%
+\subsection{Free and fixed parameters}\label{free-and-fixed-parameters}}
+
+In diffusion model fits, researchers can decide what parameters are free
+to vary across different conditions. In the present work we implemented
+3 versions of the model. These versions of the model varied in terms of
+which parameters were allowed to vary for which conditions.
+
+In our case, we decided to examine two models as described below. For
+both models, the \(a\) boundary separation, the \(z\) starting point,
+the \(\eta\) between trial variability in drift rate, and all other
+variability parameters are kept constant across all conditions.
+
+\textbf{Model 1:} Drift rates vary as a function of lexicality and prime
+duration, but not from unrelated to identity primes. \(T_{er}\) varied
+from as a function of prime duration and type and also of lexicality.
+
+\textbf{Model 2:} The drift rates vary as a function of prime duration
+and type and also of lexicality. And the drift rate varied only as a
+function of prime type/duration but not lexicality.
+
+In short, in Model 1, the priming effects are accounted by \(T_{er}\)
+only, while in Model 2 they are accounted for by both drift rate and
+\(T_{er}\).
+
+The two models have equal number of parameters so a direct comparison in
+possible. For both experiments the preferred model is Model 1 (the
+\(T_{er}\) model). This is in agreement with the Gomez et al (2012)
+study using in-person testing methods.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:model_parameters_table}$\chi^2$ values for the two models for both experiments.}
+
+\begin{tabular}{lll}
+\toprule
+Experiments & \multicolumn{1}{c}{ModelTer} & \multicolumn{1}{c}{ModelDrift}\\
+\midrule
+1 & 39.65 & 80.65\\
+2 & 10.21 & 28.65\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\hypertarget{summary}{%
+\subsection{Summary}\label{summary}}
+
+Examining the parameter values for \(T_{er}\) in the tables below shows
+that the \(T_{er}\) effect follows the duration of the prime-TARGET SOA
+particularly in the word items and not so much in the nonword items.
+
+This is in general agreement with the Gomez et al.~(2013) original paper
+and Gomez and Perea's (2020) work with developmental readers. In short,
+these fits confirm that masked priming effects are consistent with the
+idea of a head start in the encoding process when there is an identity
+relationship between primes and targets.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:appendix_table_2}$T_{er}$ values for Experiment 1.}
+
+\begin{tabular}{ll}
+\toprule
+Parameters & \multicolumn{1}{c}{Experiment1}\\
+\midrule
+$T_{er}$ values for Experiment 1.  33ms nonword ID & 0.51\\
+$T_{er}$ values for Experiment 1. 33ms nonword Unrel & 0.51\\
+$T_{er}$ values for Experiment 1.  50ms nonword ID & 0.50\\
+$T_{er}$ values for Experiment 1. 50ms nonword Unrel & 0.51\\
+$T_{er}$ values for Experiment 1.  33ms word ID & 0.47\\
+$T_{er}$ values for Experiment 1. 33ms word Unrel & 0.49\\
+$T_{er}$ values for Experiment 1.  50ms word ID & 0.46\\
+$T_{er}$ values for Experiment 1. 50ms word Unrel & 0.50\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:appendix_table_3} \$T\_\{er\}\$ values for Experiment 2.}
+
+\begin{tabular}{ll}
+\toprule
+Parameters & \multicolumn{1}{c}{Experiment2}\\
+\midrule
+\$T\_\{er\}\$ 16ms nonword ID & 0.54\\
+\$T\_\{er\}\$ 16ms nonword Unrel & 0.54\\
+\$T\_\{er\}\$ 33ms nonword ID & 0.53\\
+\$T\_\{er\}\$ 33ms nonword Unrel & 0.53\\
+\$T\_\{er\}\$ 16ms word ID & 0.50\\
+\$T\_\{er\}\$ 16ms word Unrel & 0.50\\
+\$T\_\{er\}\$ 33ms word ID & 0.49\\
+\$T\_\{er\}\$ 33ms word Unrel & 0.51\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+\hypertarget{references}{%
+\subsection{References}\label{references}}
+
+Gomez, P., \& Perea, M. (2020). Masked identity priming reflects an
+encoding advantage in developing readers. Journal of Experimental Child
+Psychology, 199, 104911. https://doi.org/10.1016/j.jecp.2020.104911
+
+Gomez, P., Perea, M., \& Ratcliff, R. (2013). A diffusion model account
+of masked versus unmasked priming: Are they qualitatively different?
+Journal of Experimental Psychology: Human Perception and Performance, 39
+(6), 1731--1740. https://doi.org/10.1037/a0032333
+
+Ratcliff, R. (1978). A theory of memory retrieval. Psychological Review,
+85, 59--108. https://doi.org/10.1037/0033-295X.85.2.59
+
+Ratcliff, R., Gomez, P., \& McKoon, G. (2004). A diffusion model account
+of the lexical decision task. Psychological Review, 111, 159--182.
+doi://10.1037/0033-295X.111.1.159
+
+Ratcliff, R.,\& Tuerlinckx, F. (2002). Estimating the parameters of the
+diffusion model: Approaches to dealing with contaminant reaction times
+and parameter variability. Psychonomic Bulletin and Review, 9, 438--481.
+https://doi.org/10.3758/BF03196302
+\end{appendix}
 

### 2021-09-21 Appendix_B.tex
Add new appendix and revisions/reply to editor

--- 2021-09-21 Appendix_test.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  english,
-  man]{apa6}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdflang={en-EN},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
-
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
-
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-\shorttitle{SHORTTITLE}
-\usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-
-\title{TITLE}
-\author{\phantom{0}}
-\date{}
-
-\affiliation{\phantom{0}}
-
-\begin{document}
-\maketitle
-
-This is the manuscript.
-
-\clearpage
-
-\begin{appendix}
-\hypertarget{stimuli}{%
-\section{Stimuli}\label{stimuli}}
-
-\hypertarget{words}{%
-\subsection{Words:}\label{words}}
-
-\begin{verbatim}
-##   [1] GLANCE WINTER MILDEW SLEAZY BOTHER PORTAL COURSE SOCIAL CENSOR BACKUP
-##  [11] STABLE PLAGUE OBJECT ABSENT RESIGN CREDIT STREAM WICKED INVOKE BEACON
-##  [21] ADMIRE FACTOR PHRASE BURDEN LOUNGE TAILOR WREATH HOCKEY SEARCH MONKEY
-##  [31] INFECT VERIFY SQUEAL INTAKE PHOBIA BEHALF LIQUOR SHRINK BUCKET VOYAGE
-##  [41] MASCOT HINDER KIDNEY PERIOD VULGAR CASINO SELDOM MASTER MOTHER FRINGE
-##  [51] EXPORT INJECT NATURE CLUMSY GRUMPY PIRATE POSTER FLOWER LUMBER FOREST
-##  [61] FRIGHT BRIDGE KNIGHT TRENCH PLUNGE BUNDLE ANCHOR ABRUPT HUSTLE ETHNIC
-##  [71] CRUISE ORANGE STRIVE ALMOST AMOUNT FAUCET CHARGE HUMBLE PATRON BREAST
-##  [81] SIMPLE JOCKEY WEALTH PRAISE DOMAIN SPRINT SCREAM COMEDY SKETCH ORIENT
-##  [91] WEAPON BUCKLE BUTLER JUNGLE SOCKET VANISH INSULT POWDER INSECT CONVEY
-## [101] SPRING CHAPEL TONGUE DANGER CLERGY SINGLE INCOME WALNUT SURVEY SNATCH
-## [111] HUNGRY IMPOSE POLICE RAMBLE STROKE AMBUSH CHANGE FOSTER SPLINT PENCIL
-## [121] PONDER REGION LAUNCH THRONE SYMBOL GOSPEL POLICY FUMBLE PLENTY SQUARE
-## [131] GARDEN BRIGHT SOURCE PLAQUE TROPHY EXOTIC RACKET COLUMN THEORY FAMILY
-## [141] FRIEND STIGMA RESULT MORTAL SPRAWL RODENT FILTER HUNGER PERMIT RELISH
-## [151] EXPAND STRAND PUBLIC TRAVEL THREAD IGNORE CLIENT BELONG FLUENT CARBON
-## [161] WRENCH DIRECT BOUNCE STUDIO NUMBER RANSOM SLOGAN RECKON WONDER POLITE
-## [171] INDUCE BREATH CHORUS PLACID GUITAR TUMBLE BRANCH FLIGHT SPIDER STRAIN
-## [181] THRIVE LINGER STRIKE BLOUSE NICKEL ENOUGH CASTLE SENIOR MARVEL STUPID
-## [191] QUENCH STRONG CHROME STAPLE IMPORT BLEACH FINGER MELODY DEBRIS PRINCE
-## [201] ORPHAN SPRUCE REASON SPONGE PARISH COUPLE GARLIC CUSTOM INVADE RANDOM
-## [211] MYSTIC ROCKET BEHOLD AUTHOR LIZARD CRADLE DRAGON ISLAND DETAIL VIOLET
-## [221] PASTOR CANDLE STRING MARKET INVEST STARCH DESIGN ANSWER GENIUS POUNCE
-## [231] DEPART PATROL SHOWER TURKEY FABRIC STRIFE ADVENT INFORM BASKET SILENT
-\end{verbatim}
-
-\hypertarget{non-words}{%
-\subsection{Non-Words:}\label{non-words}}
-
-\begin{verbatim}
-##   [1] KNISMA ALCOUD STRELD PRAILE FRUDGE URIVEL SCHIND TANDLY FUNTLE CAROEY
-##  [11] CHRUMS LUNKER DRANCE PITROM IMPURB FRUTAN SNAPEL BAITCH LIMPOR SARIDE
-##  [21] RASTOE ABOUNE DORSEX JAUNCE MINKEL RUNAMO GIRCUE SADENT BRUNGE PHRECT
-##  [31] CAINKY SURDEN BOLVIS SCOUGE TONDLE BROGET WANIGH BARCET BAFENT MINGAR
-##  [41] JUSTRE ABSULT KISPEL CHAITE WHIVEX HOCITE GORBIE WICTOR PADIFS CRUDIO
-##  [51] NOBEST CIGNEY CRIBLE HABLIN PEBRIC JOSTED PHOTIE ACRISE LOBUSH ROBULY
-##  [61] SMENCO UNWERT MUSIED EATRIC ANOUGS PIATON BLARGE STROLE BATROL MILTED
-##  [71] LUPICT STAPOD RESAIT VAROSH APIGHT INLORS VENIOD POLUTH SOUDAL UNJECT
-##  [81] STUNCH QUILEW DOLICA VACKEL DISTAR VARMIT PASINK PACKES ORCHET WRIMSY
-##  [91] AUBRID DAMILT SORTEL FUMBLO SLEIRT YARMON PETAIN UNIGHS CELOND CURBOL
-## [101] MELATY PORLEX VERALF SHAPLE PRUDGE RELDON NYMBEL YACEUP STARBY SPLINO
-## [111] PRETCH ABLINT SWANCE INHORT GLEATH BEINCH FERTIC PIERGY STURCH YARION
-## [121] FAINCH MILUER FIREAM CLUDIE FORGLE SOUNGE KIRAFE PSETCH AMILOY DANIET
-## [131] SPROLY NERAWL PAURSE SPRINE LASTON SCREGM WORBAL REAGLY ZOMBER JOCKAL
-## [141] MIATOR SLANCH ROSAIL STEIKH THRUSE IGUADE PLENAC BROAKE YARIKE KENSOM
-## [151] GILFEW VANGUE CATRIE WATMEG DESION GHODUS REJOLS WREASH FACHOW FIATCH
-## [161] MYRTIE RANDOW AIMOSY SCRILY ABSEND SAUDIC KERIFT DUMPLE ASYLEN NAGURS
-## [171] TIESCH TRINGE CLUREY VIRLEX ZINGLY OTHNIS DERAIN FLEACK FONVER DESORY
-## [181] PAUCHE TIREAU BREALI IMPOTE GUAIRT TOSHEL SLIQUE HORNAL WRONCH SLEACT
-## [191] GEILOY RAMILY BIGENT SLIANT YORQUE IGUARE INJORE SHRILE AUTING CAVORY
-## [201] HUNIEK SARLEY AUNGRE GUESCO VEIGMA ANCUST GRONCE CRAGIN WITMER HATRUS
-## [211] THELDY ROUNCY GANOUS SPAQUX COLURY FLENGY CAMBLE BLUNDE FOURET WEAROX
-## [221] MUSTIL SYNTIC BRUATS CLUIRM FLUMNI NOUPLY SUIVER HURNIA ELOPIA TUNORY
-## [231] ORCHIN JILUER EQUATS SERBOL HIGSTA PATHEL EAROUD SUIDLE SLOUNT GUSHOP
-\end{verbatim}
-\end{appendix}
-
 \clearpage
@@
 \end{appendix}
-
-\end{document}

### 2021-09-21 MaskedPriming_revision.Rmd
Add new appendix and revisions/reply to editor

@@
 bibliography: ["references.bib", "r-references.bib"]
+appendix:
+  - "Appendix_A.Rmd"
+  - "Appendix_B.Rmd"
 editor_options: 
@@
 Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets [@reimersPresentationResponseTiming2015].
-There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020], and open-source such as jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of PsychoPy 3, @peirce2019].
+There have been attempts to use this technology for online masked priming experiments: @crump2013 (Experiment 7) attempted a masked priming paradigm using custom written Javascript code, but failed to replicate the masked priming effect which may be due to problems with their implementation (unfortunately, their study does not provide many details about the Javascript code used).
+@barnhoorn2015 developed a software package called *QRTEngine* designed to run experiments within the Qualtrics online survey development environment [@qualtrics2020] and were able to successfully find masked priming effects (Experiment 3).
+Unfortunately, *QRTEngine* was only maintained for a few years and is now defunct, which is an issue with many custom-developed solutions.
+
+Nowadays, there a variety of well-maintained software packages taking advantage of the HTML5 capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla [@anwyl-irvine2020] or Testable [@rezlescu2020], and open-source such as jsPsych [@deleeuw2015] or PsychoJS [the Javascript version of PsychoPy 3, @peirce2019].
 In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
@@
 All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
-This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms [e.g., @aguasvivas2020; @brysbaert2021a; @mandera2020; @brysbaert2016impact].
+This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms [e.g., @aguasvivas2020; @brysbaert2021a; @mandera2020; @brysbaert2016impact, @ratcliff2021].
 So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries [e.g., @adelman2014].
@@
 
-The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at <https://osf.io/57rzq/>.
+The pre-registration form for Experiment 1 can be found at <https://osf.io/v97bp>, and the materials, data files, and R scripts can be found at <https://osf.io/57rzq/>.
 
@@
 
+papaja::render_appendix("Appendix_B.Rmd")
 ```
@@
 
-# Appendix A
-
-## Words:
-
-```{r}
-trials%>%
-  filter(StimulusType=="WORD")%>%
-  pull(Target)%>%
-  noquote()->Word_targets
-
-Word_targets
-
-```
-
-## Non-Words:
-
-```{r}
-
-trials%>%
-  filter(StimulusType=="NW")%>%
-  pull(Target)%>%
-  noquote()->NonWord_targets
-
-NonWord_targets
-
-```
-
 \endgroup

### 2021-09-21 MaskedPriming_revision.tex
Add new appendix and revisions/reply to editor

@@
 Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets (Reimers \& Stewart, 2015).
-There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla (Anwyl-Irvine, Massonni, et al., 2020) or Testable (Rezlescu et al., 2020), and open-source such as jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of PsychoPy 3, Peirce et al., 2019).
+There have been attempts to use this technology for online masked priming experiments: Crump et al.
+(2013) (Experiment 7) attempted a masked priming paradigm using custom written Javascript code, but failed to replicate the masked priming effect which may be due to problems with their implementation (unfortunately, their study does not provide many details about the Javascript code used).
+Barnhoorn et al.
+(2015) developed a software package called \emph{QRTEngine} designed to run experiments within the Qualtrics online survey development environment (Qualtrics, 2020) and were able to successfully find masked priming effects (Experiment 3).
+Unfortunately, \emph{QRTEngine} was only maintained for a few years and is now defunct, which is an issue with many custom-developed solutions.
+
+Nowadays, there a variety of well-maintained software packages taking advantage of the HTML5 capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla (Anwyl-Irvine, Massonni, et al., 2020) or Testable (Rezlescu et al., 2020), and open-source such as jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of PsychoPy 3, Peirce et al., 2019).
 In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
@@
 All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli (e.g., Parker et al., 2021).
-This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms (e.g., Aguasvivas et al., 2020; Brysbaert et al., 2021; Brysbaert et al., 2016; Mandera et al., 2020).
+This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms Ratcliff \& Hendrickson (2021).
 So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries (e.g., Adelman et al., 2014).
@@
 
-The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at \url{https://osf.io/57rzq/}.
+The pre-registration form for Experiment 1 can be found at \url{https://osf.io/v97bp}, and the materials, data files, and R scripts can be found at \url{https://osf.io/57rzq/}.
 
@@
 
-We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.10.5; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.7; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.3; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.3; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.25; Xie, 2021).}.
+We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.11.0; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.7; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.4; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.3; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.26; Xie, 2021).}.
 We only analyzed trials where the target stimulus was a word.
@@
 \end{table}
+
+\begin{verbatim}
+## Error: pandoc document conversion failed with error 99
+\end{verbatim}
 
@@
 
+\leavevmode\hypertarget{ref-barnhoorn2015}{}%
+Barnhoorn, J.
+S., Haasnoot, E., Bocanegra, B.
+R., \& van Steenbergen, H.
+(2015).
+QRTEngine: An easy solution for running online reaction time experiments using Qualtrics.
+\emph{Behavior Research Methods}, \emph{47}(4), 918--929.
+\url{https://doi.org/10.3758/s13428-014-0530-7}
+
 \leavevmode\hypertarget{ref-R-tinylabels}{}%
@@
 
+\leavevmode\hypertarget{ref-crump2013}{}%
+Crump, M.
+J.
+C., McDonnell, J.
+V., \& Gureckis, T.
+M.
+(2013).
+Evaluating Amazon's Mechanical Turk as a Tool for Experimental Behavioral Research.
+\emph{PLOS ONE}, \emph{8}(3), e57410.
+\url{https://doi.org/10.1371/journal.pone.0057410}
+
 \leavevmode\hypertarget{ref-de1994conditional}{}%
@@
 
+\leavevmode\hypertarget{ref-ratcliff2021}{}%
+Ratcliff, R., \& Hendrickson, A.
+T.
+(2021).
+Do data from mechanical Turk subjects replicate accuracy, response time, and diffusion modeling results?
+\emph{Behavior Research Methods}.
+\url{https://doi.org/10.3758/s13428-021-01573-x}
+
 \leavevmode\hypertarget{ref-reimersPresentationResponseTiming2015}{}%
@@
 
-\hypertarget{appendix-a}{%
-\section{Appendix A}\label{appendix-a}}
+\endgroup
+
+\begin{verbatim}
+## Error: pandoc document conversion failed with error 99
+\end{verbatim}
+
+\begin{verbatim}
+## Error in parse_block(g[-1], g[1], params.src, markdown_mode): Duplicate chunk label 'appendix_setup', which has been used for the chunk:
+## library(tidyverse)
+## knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
+\end{verbatim}
+
+\clearpage
+
+\begin{appendix}
+\hypertarget{stimuli}{%
+\section{Stimuli}\label{stimuli}}
 
@@
 \end{verbatim}
-
-\endgroup
+\end{appendix}
+
+\clearpage
+
+\begin{appendix}
+\hypertarget{diffusion-model-accounts-for-the-data}{%
+\section{Diffusion model accounts for the
+data}\label{diffusion-model-accounts-for-the-data}}
+
+\hypertarget{about-this-appendix}{%
+\subsection{About this Appendix}\label{about-this-appendix}}
+
+The goal of this appendix is to present a brief description of how the
+diffusion model accounts for the data presented in the main article.
+While the diffusion model fits to the grouped data was part of the
+pre-registration plan, we believe that it is best to present such fits
+in this appendix as opposed to the main text to improve the readability
+of the article. For a full description of the experimental setting and
+its goals please refer to the main text.
+
+\hypertarget{the-diffusion-model}{%
+\subsection{The diffusion model}\label{the-diffusion-model}}
+
+The diffusion model (Ratcliff, 1978) is a cognitive process model for
+perceptual decisions, and it has been quite successful at accounting for
+lexical decision data (Ratcliff et al, 2004) and more importantly for
+the present work, masked priming data (Gomez et al, 2012).
+
+The model assumes that RTs to dual choice tasks are a sum of three
+distinct processes: stimulus encoding, evidence accumulation, and
+response execution. The model makes the strong assumption that evidence
+accumulation is a processes distinct from the other two components, and
+for practical reasons, it groups response execution and encoding time in
+a single parameter.
+
+The model is agnostic about the correlation between the encoding and the
+evidence accumulation processes; and we like to think about it as a tool
+to instantiate theoretical positions that can be articulated in terms of
+encoding, decision, and strategic processes.
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
+The model was fit to the grouped data (as per the pre-registration plan)
+of the two experiments. For each stimulus type the proportion of word
+and nonword responses is calculated, then for each of the two responses,
+the RTs at the .1, .3, .5, .7, and .9 quantiles is obtained. We repeat
+this process for each participants, and then all of those quantities
+(response proportions and RTs at quantiles) are averaged across
+participants. This process is also known as Vincentalizing, and the
+averaged quantiles are referred to as vintenciles
+
+The diffusion model predicts the cumulative probability of a response at
+each RT vincentile, and these model predictions are compared to the
+empirical proportions, then the sum of the
+(Observed-Predicted)2/Predicted for correct and error responses for each
+condition that is minimized with a general SIMPLEX minimization routine
+as described by Ratcliff \& Tuerlinckx (2002).
+
+\hypertarget{free-and-fixed-parameters}{%
+\subsection{Free and fixed parameters}\label{free-and-fixed-parameters}}
+
+In diffusion model fits, researchers can decide what parameters are free
+to vary across different conditions. In the present work we implemented
+3 versions of the model. These versions of the model varied in terms of
+which parameters were allowed to vary for which conditions.
+
+In our case, we decided to examine two models as described below. For
+both models, the \(a\) boundary separation, the \(z\) starting point,
+the \(\eta\) between trial variability in drift rate, and all other
+variability parameters are kept constant across all conditions.
+
+\textbf{Model 1:} Drift rates vary as a function of lexicality and prime
+duration, but not from unrelated to identity primes. \(T_{er}\) varied
+from as a function of prime duration and type and also of lexicality.
+
+\textbf{Model 2:} The drift rates vary as a function of prime duration
+and type and also of lexicality. And the drift rate varied only as a
+function of prime type/duration but not lexicality.
+
+In short, in Model 1, the priming effects are accounted by \(T_{er}\)
+only, while in Model 2 they are accounted for by both drift rate and
+\(T_{er}\).
+
+The two models have equal number of parameters so a direct comparison in
+possible. For both experiments the preferred model is Model 1 (the
+\(T_{er}\) model). This is in agreement with the Gomez et al (2012)
+study using in-person testing methods.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:model_parameters_table}$\chi^2$ values for the two models for both experiments.}
+
+\begin{tabular}{lll}
+\toprule
+Experiments & \multicolumn{1}{c}{ModelTer} & \multicolumn{1}{c}{ModelDrift}\\
+\midrule
+1 & 39.65 & 80.65\\
+2 & 10.21 & 28.65\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\hypertarget{summary}{%
+\subsection{Summary}\label{summary}}
+
+Examining the parameter values for \(T_{er}\) in the tables below shows
+that the \(T_{er}\) effect follows the duration of the prime-TARGET SOA
+particularly in the word items and not so much in the nonword items.
+
+This is in general agreement with the Gomez et al.~(2013) original paper
+and Gomez and Perea's (2020) work with developmental readers. In short,
+these fits confirm that masked priming effects are consistent with the
+idea of a head start in the encoding process when there is an identity
+relationship between primes and targets.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:appendix_table_2}$T_{er}$ values for Experiment 1.}
+
+\begin{tabular}{ll}
+\toprule
+Parameters & \multicolumn{1}{c}{Experiment1}\\
+\midrule
+$T_{er}$ values for Experiment 1.  33ms nonword ID & 0.51\\
+$T_{er}$ values for Experiment 1. 33ms nonword Unrel & 0.51\\
+$T_{er}$ values for Experiment 1.  50ms nonword ID & 0.50\\
+$T_{er}$ values for Experiment 1. 50ms nonword Unrel & 0.51\\
+$T_{er}$ values for Experiment 1.  33ms word ID & 0.47\\
+$T_{er}$ values for Experiment 1. 33ms word Unrel & 0.49\\
+$T_{er}$ values for Experiment 1.  50ms word ID & 0.46\\
+$T_{er}$ values for Experiment 1. 50ms word Unrel & 0.50\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:appendix_table_3} \$T\_\{er\}\$ values for Experiment 2.}
+
+\begin{tabular}{ll}
+\toprule
+Parameters & \multicolumn{1}{c}{Experiment2}\\
+\midrule
+\$T\_\{er\}\$ 16ms nonword ID & 0.54\\
+\$T\_\{er\}\$ 16ms nonword Unrel & 0.54\\
+\$T\_\{er\}\$ 33ms nonword ID & 0.53\\
+\$T\_\{er\}\$ 33ms nonword Unrel & 0.53\\
+\$T\_\{er\}\$ 16ms word ID & 0.50\\
+\$T\_\{er\}\$ 16ms word Unrel & 0.50\\
+\$T\_\{er\}\$ 33ms word ID & 0.49\\
+\$T\_\{er\}\$ 33ms word Unrel & 0.51\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+\hypertarget{references}{%
+\subsection{References}\label{references}}
+
+Gomez, P., \& Perea, M. (2020). Masked identity priming reflects an
+encoding advantage in developing readers. Journal of Experimental Child
+Psychology, 199, 104911. https://doi.org/10.1016/j.jecp.2020.104911
+
+Gomez, P., Perea, M., \& Ratcliff, R. (2013). A diffusion model account
+of masked versus unmasked priming: Are they qualitatively different?
+Journal of Experimental Psychology: Human Perception and Performance, 39
+(6), 1731--1740. https://doi.org/10.1037/a0032333
+
+Ratcliff, R. (1978). A theory of memory retrieval. Psychological Review,
+85, 59--108. https://doi.org/10.1037/0033-295X.85.2.59
+
+Ratcliff, R., Gomez, P., \& McKoon, G. (2004). A diffusion model account
+of the lexical decision task. Psychological Review, 111, 159--182.
+doi://10.1037/0033-295X.111.1.159
+
+Ratcliff, R.,\& Tuerlinckx, F. (2002). Estimating the parameters of the
+diffusion model: Approaches to dealing with contaminant reaction times
+and parameter variability. Psychonomic Bulletin and Review, 9, 438--481.
+https://doi.org/10.3758/BF03196302
+\end{appendix}
 

### 2021-09-29 Appendix_B.Rmd
Ready repository for resubmission

@@
 
-The diffusion model (Ratcliff, 1978) is a cognitive process model for perceptual decisions, and it has been quite successful at accounting for lexical decision data (Ratcliff et al, 2004) and more importantly for the present work, masked priming data (Gomez et al, 2012).
+The diffusion model (Ratcliff, 1978) is a cognitive process model for perceptual decisions, and it has been quite successful at accounting for lexical decision data (Ratcliff et al., 2004) and more importantly for the present work, masked priming data (Gomez et al., 2012).
 
@@
 We repeat this process for each participants, and then all of those quantities (response proportions and RTs at quantiles) are averaged across participants.
-This process is also known as Vincentalizing, and the averaged quantiles are referred to as vintenciles
+This process is also known as Vincentizing, and the averaged quantiles are referred to as vintenciles
 
@@
 
-```{r model_parameters_table, warning=FALSE, echo=FALSE, message=FALSE}
+```{r appendix_model_parameters_table, warning=FALSE, echo=FALSE, message=FALSE}
 Experiments <-c("1","2")
@@
 
-```{r experiment_data}
+```{r appendix_experiment_data}
 exp1.8ter <-c(0.1055,0.0562,0.0395,-0.2522,0.0000,-0.2503,0.0000,0.2909,0.0000,0.3119,0.0000,0.0128,0.5071,0.1275,0.0058,0.5090,0.5048,0.5074,0.4737,0.4920
@@
 
-This is in general agreement with the Gomez et al.
-(2013) original paper and Gomez and Perea's (2020) work with developmental readers.
-In short, these fits confirm that masked priming effects are consistent with the idea of a head start in the encoding process when there is an identity relationship between primes and targets.
-
 ```{r appendix_table_2}
@@
 
-Parameters <-c( "$T_{er}$ values for Experiment 1.  33ms nonword ID", "$T_{er}$ values for Experiment 1. 33ms nonword Unrel",
-                "$T_{er}$ values for Experiment 1.  50ms nonword ID", "$T_{er}$ values for Experiment 1. 50ms nonword Unrel",
-                "$T_{er}$ values for Experiment 1.  33ms word ID", "$T_{er}$ values for Experiment 1. 33ms word Unrel",
-                "$T_{er}$ values for Experiment 1.  50ms word ID", "$T_{er}$ values for Experiment 1. 50ms word Unrel")
+Parameters <-c( "$T_{er}$  33ms nonword ID", "$T_{er}$ 33ms nonword Unrel",
+                "$T_{er}$  50ms nonword ID", "$T_{er}$ 50ms nonword Unrel",
+                "$T_{er}$  33ms word ID", "$T_{er}$ 33ms word Unrel",
+                "$T_{er}$  50ms word ID", "$T_{er}$ 50ms word Unrel")
 
@@
 ```
+
+This is in general agreement with the Gomez et al.
+(2013) original paper and Gomez and Perea's (2020) work with developmental readers.
+In short, these fits confirm that masked priming effects are consistent with the idea of a head start in the encoding process when there is an identity relationship between primes and targets.
 
@@
     caption = " $T_{er}$ values for Experiment 2."
-    , escape = TRUE
+    , escape = FALSE
   )
@@
 ```
-
-\newpage
-
-## References
-Gomez, P., & Perea, M.
-(2020).
-Masked identity priming reflects an encoding advantage in developing readers.
-Journal of Experimental Child Psychology, 199, 104911.
-https://doi.org/10.1016/j.jecp.2020.104911
-
-Gomez, P., Perea, M., & Ratcliff, R.
-(2013).
-A diffusion model account of masked versus unmasked priming: Are they qualitatively different?
-Journal of Experimental Psychology: Human Perception and Performance, 39 (6), 1731–1740.
-https://doi.org/10.1037/a0032333
-
-Ratcliff, R. (1978). A theory of memory retrieval. Psychological Review, 85, 59–108. https://doi.org/10.1037/0033-295X.85.2.59
-
-Ratcliff, R., Gomez, P., \& McKoon, G. (2004). A diffusion model account of the lexical decision task. Psychological Review, 111, 159–182. doi://10.1037/0033-295X.111.1.159
-
-Ratcliff, R.,\& Tuerlinckx, F.
-(2002).
-Estimating the parameters of the diffusion model: Approaches to dealing with contaminant reaction times and parameter variability.
-Psychonomic Bulletin and Review, 9, 438–481.
-https://doi.org/10.3758/BF03196302

### 2021-09-29 MaskedPriming_revision.Rmd
Ready repository for resubmission

@@
   We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.
-
   This research has been partly supported by Grant PSI2017-86210-P from  the  Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).
-
-  This study was pre-registered on the Open Science Framework (OSF) prior to data collection.
-The registration form for Experiment 1, together with the materials, data files, and R scripts can be found at [https://osf.io/57rzq/].
-The registration form for Experiment 2 can be found at [https://osf.io/957s8].
 abstract: |
@@
 bibliography: ["references.bib", "r-references.bib"]
+nocite: |
+  - @ratcliff2002
 appendix:
@@
 The issue we examine in the present paper is whether masked priming experiments can be conducted in an online setting without significant changes in the pattern of results.
-Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
+Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection had shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
 Indeed, researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010].
@@
 However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a "true" online programming script that could be run inside of a browser.
-A downside of this format is that participants often are (and should be) understandably skeptical about downloading and running executable files from the Internet.
+A downside of this format is that participants often are understandably skeptical about downloading and running executable files from the Internet.
 Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
@@
 Based on the results by @bridges2020 and @anwyl-irvine2020a, modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
-To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study.
+To establish whether masked priming studies can be successfully run online, the next step is to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study.
 Importantly, we will do so using PsychoPy/PsychoJS [@peirce2019] as it showed high precision and accuracy across the great majority of platforms [@bridges2020; @anwyl-irvine2020a], in addition to being an open-source software.
@@
 With regards to RTs from masked priming tasks, @gomezDiffusionModelAccount2013 found that the difference between identity and unrelated conditions could be accounted for by a change in the $T_{er}$ parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a more skewed RT distribution in the slower, unrelated condition.
+The same was found by @Gomez_2020 for developing readers.
 
@@
 All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli [e.g., @Parker_2021].
-This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms [e.g., @aguasvivas2020; @brysbaert2021a; @mandera2020; @brysbaert2016impact, @ratcliff2021].
+This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms [e.g., @aguasvivas2020; @brysbaert2021a; @mandera2020; @brysbaert2016impact; @ratcliff2021].
 So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries [e.g., @adelman2014].
@@
     )
-
-papaja::render_appendix("Appendix_B.Rmd")
 ```
@@
 
+# Open Science Statement
+
+Both experiments in this study were pre-registered prior to conducting the research on the Open Science Framework (OSF) prior to data collection.
+The registration form for Experiment 1 can be found at [https://osf.io/v97bp].
+The registration form for Experiment 2 can be found at [https://osf.io/957s8].
+The materials, data files, and R scripts for both experiments can be found at [https://osf.io/d2txs].
+
+\newpage
+
 # References

### 2021-11-03 MaskedPriming_revision_accepted.Rmd
Move old documents to different directory, make final Rmd and tex files

--- 2021-09-29 MaskedPriming_revision.Rmd
@@
   - id            : "2"
-    institution   : "Universidad Antonio de Nebrija, Madrid, Spain"
+    institution   : "Centro de Investigación Nebrija en Cognición (CINC), Universidad Nebrija, Madrid, Spain"
   - id            : "3"
@@
 keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
-wordcount         : "7916"
+wordcount         : "7192"
 floatsintext      : yes
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output:
+  papaja::apa6_pdf:
+    keep_tex: TRUE
 bibliography: ["references.bib", "r-references.bib"]
@@
 \endgroup
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+#papaja::render_appendix('Appendix_A.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+#papaja::render_appendix('Appendix_B.Rmd')
+```

### 2021-11-03 MaskedPriming_revision_accepted.tex
Move old documents to different directory, make final Rmd and tex files

--- 2021-09-21 MaskedPriming_revision.tex
@@
   man,floatsintext]{apa6}
+\title{Does online masked priming pass the test?\\
+The effects of prime exposure duration on masked identity priming}
+\author{Bernhard Angele\textsuperscript{1,2}, Ana Baciero\textsuperscript{2,3}, Pablo Gómez\textsuperscript{4}, \& Manuel Perea\textsuperscript{2,5}}
+\date{}
+
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 \shorttitle{Online masked priming}
-\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 7916}
+\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 7192}
 \usepackage{csquotes}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Does online masked priming pass the test?\\
-The effects of prime exposure duration on masked identity priming}
-\author{Bernhard Angele\textsuperscript{1,2}, Ana Baciero\textsuperscript{2,3}, Pablo Gómez\textsuperscript{4}, \& Manuel Perea\textsuperscript{2,5}}
-\date{}
 
@@
 We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.
-
 This research has been partly supported by Grant PSI2017-86210-P from the Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).
-
-This study was pre-registered on the Open Science Framework (OSF) prior to data collection.
-The registration form for Experiment 1, together with the materials, data files, and R scripts can be found at {[}\url{https://osf.io/57rzq/}{]}.
-The registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}.
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Bournemouth University, Bournemouth, UK\\\textsuperscript{2} Universidad Antonio de Nebrija, Madrid, Spain\\\textsuperscript{3} DePaul University, Chicago, USA\\\textsuperscript{4} California State University San Bernardino, Palm Desert Campus, USA\\\textsuperscript{5} Universitat de València, Valencia, Spain}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Bournemouth University, Bournemouth, UK\\\textsuperscript{2} Centro de Investigación Nebrija en Cognición (CINC), Universidad Nebrija, Madrid, Spain\\\textsuperscript{3} DePaul University, Chicago, USA\\\textsuperscript{4} California State University San Bernardino, Palm Desert Campus, USA\\\textsuperscript{5} Universitat de València, Valencia, Spain}
 
@@
 The issue we examine in the present paper is whether masked priming experiments can be conducted in an online setting without significant changes in the pattern of results.
-Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
+Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection had shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
 Indeed, researchers in decision making and economics have been using online paradigms for several decades now (e.g., Birnbaum \& Birnbaum, 2000; Paolacci et al., 2010).
@@
 However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a ``true'' online programming script that could be run inside of a browser.
-A downside of this format is that participants often are (and should be) understandably skeptical about downloading and running executable files from the Internet.
+A downside of this format is that participants often are understandably skeptical about downloading and running executable files from the Internet.
 Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
@@
 (2020), modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
-To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study.
+To establish whether masked priming studies can be successfully run online, the next step is to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study.
 Importantly, we will do so using PsychoPy/PsychoJS (Peirce et al., 2019) as it showed high precision and accuracy across the great majority of platforms (Anwyl-Irvine, Dalmaijer, et al., 2020; Bridges et al., 2020), in addition to being an open-source software.
@@
 (2013) found that the difference between identity and unrelated conditions could be accounted for by a change in the \(T_{er}\) parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a more skewed RT distribution in the slower, unrelated condition.
+The same was found by Gomez and Perea (2020) for developing readers.
 
@@
 All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli (e.g., Parker et al., 2021).
-This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms Ratcliff \& Hendrickson (2021).
+This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms (e.g., Aguasvivas et al., 2020; Brysbaert et al., 2021; Brysbaert et al., 2016; Mandera et al., 2020; Ratcliff \& Hendrickson, 2021).
 So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries (e.g., Adelman et al., 2014).
@@
 \centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/hyp-mod-dat-figure-1.pdf}
+\includegraphics{MaskedPriming_revision_accepted_files/figure-latex/hyp-mod-dat-figure-1.pdf}
 \caption{\label{fig:hyp-mod-dat-figure}Mapping from hypotheses to data via evidence accumulation models.
@@
 
-We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.11.0; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.7; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.4; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.3; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.26; Xie, 2021).}.
+We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.11.0; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.2; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.8; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.5; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.4; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.27; Xie, 2021).}.
 We only analyzed trials where the target stimulus was a word.
@@
 \centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e1-words-1.pdf}
+\includegraphics{MaskedPriming_revision_accepted_files/figure-latex/deltas-e1-words-1.pdf}
 \caption{\label{fig:deltas-e1-words}Delta plots depicting the magnitude of the effect over time in Experiment 1.
@@
 \centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e2-words-1.pdf}
+\includegraphics{MaskedPriming_revision_accepted_files/figure-latex/deltas-e2-words-1.pdf}
 \caption{\label{fig:deltas-e2-words}Delta plots depicting the magnitude of the effect over time in Experiment 2.}
@@
 
-\begin{verbatim}
-## Error: pandoc document conversion failed with error 99
-\end{verbatim}
-
 \hypertarget{discussion-1}{%
@@
 
+\hypertarget{open-science-statement}{%
+\section{Open Science Statement}\label{open-science-statement}}
+
+Both experiments in this study were pre-registered prior to conducting the research on the Open Science Framework (OSF) prior to data collection.
+The registration form for Experiment 1 can be found at {[}\url{https://osf.io/v97bp}{]}.
+The registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}.
+The materials, data files, and R scripts for both experiments can be found at {[}\url{https://osf.io/d2txs}{]}.
+
+\newpage
+
 \hypertarget{references}{%
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-adelman2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-adelman2014}{}}%
 Adelman, J.
@@
 
-\leavevmode\hypertarget{ref-aguasvivas2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-aguasvivas2020}{}}%
 Aguasvivas, J., Carreiras, M., Brysbaert, M., Mandera, P., Keuleers, E., \& Duñabeitia, J.
@@
 
-\leavevmode\hypertarget{ref-Alluhaybi_2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Alluhaybi_2020}{}}%
 Alluhaybi, I., \& Witzel, J.
@@
 
-\leavevmode\hypertarget{ref-anwyl-irvine2020a}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-anwyl-irvine2020a}{}}%
 Anwyl-Irvine, A., Dalmaijer, E.
@@
 
-\leavevmode\hypertarget{ref-anwyl-irvine2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-anwyl-irvine2020}{}}%
 Anwyl-Irvine, A., Massonni, J., Flitton, A., Kirkham, N., \& Evershed, J.
@@
 (2020).
-orilla in our midst: An online behavioral experiment builder.
+Gorilla in our midst: An online behavioral experiment builder.
 \emph{Behavior Research Methods}, \emph{52}(1), 388--407.
@@
 
-\leavevmode\hypertarget{ref-R-papaja}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}
 
-\leavevmode\hypertarget{ref-austSeriousnessChecksAre2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-austSeriousnessChecksAre2013}{}}%
 Aust, F., Diedenhofen, B., Ullrich, S., \& Musch, J.
@@
 
-\leavevmode\hypertarget{ref-balota2007}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-balota2007}{}}%
 Balota, D.
@@
 
-\leavevmode\hypertarget{ref-barnhoorn2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-barnhoorn2015}{}}%
 Barnhoorn, J.
@@
 
-\leavevmode\hypertarget{ref-R-tinylabels}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
 Barth, M. (2021). \emph{{tinylabels}: Lightweight variable labels}. \url{https://github.com/mariusbarth/tinylabels}
 
-\leavevmode\hypertarget{ref-birnbaumPsychologicalExperimentsInternet2000a}{}%
-Birnbaum, M. H., \& Birnbaum, M. O. (2000). \emph{Psychological {Experiments} on the {Internet}}. {Elsevier}. \url{http://books.google.com?id=sw4NHyThFFkC}
-
-\leavevmode\hypertarget{ref-bridges2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-birnbaumPsychologicalExperimentsInternet2000a}{}}%
+Birnbaum, M. H., \& Birnbaum, M. O. (2000). \emph{Psychological {Experiments} on the {Internet}}. {Elsevier}. \url{https://books.google.com?id=sw4NHyThFFkC}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bridges2020}{}}%
 Bridges, D., Pitiot, A., MacAskill, M.
@@
 The timing mega-study: comparing a range of experiment generators, both lab-based and online.
-\emph{PeerJ}, \emph{8}, e9414.
+\emph{PeerJ}, \emph{8}.
 \url{https://doi.org/10.7717/peerj.9414}
 
-\leavevmode\hypertarget{ref-brysbaert2021a}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-brysbaert2021a}{}}%
 Brysbaert, M., Keuleers, E., \& Mandera, P.
@@
 
-\leavevmode\hypertarget{ref-brysbaert2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-brysbaert2018}{}}%
 Brysbaert, M., \& Stevens, M. (2018). Power Analysis and Effect Size in Mixed Effects Models: A Tutorial. \emph{Journal of Cognition}, \emph{1}(1), 9. \url{https://doi.org/10.5334/joc.10}
 
-\leavevmode\hypertarget{ref-brysbaert2016impact}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-brysbaert2016impact}{}}%
 Brysbaert, M., Stevens, M., Mandera, P., \& Keuleers, E.
@@
 
-\leavevmode\hypertarget{ref-R-brms_a}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-brms_a}{}}%
 Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
 
-\leavevmode\hypertarget{ref-R-brms_b}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-brms_b}{}}%
 Bürkner, P.-C. (2018). Advanced {Bayesian} multilevel modeling with the {R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://doi.org/10.32614/RJ-2018-017}
 
-\leavevmode\hypertarget{ref-cai2017accent}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cai2017accent}{}}%
 Cai, Z.
@@
 
-\leavevmode\hypertarget{ref-crump2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
 Crump, M.
@@
 
-\leavevmode\hypertarget{ref-de1994conditional}{}%
-De Jong, R., Liang, C.-C., \& Lauber, E.
-(1994).
-Conditional and unconditional automaticity: A dual-process model of effects of spatial stimulus-response correspondence.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{20}(4), 731.
-
-\leavevmode\hypertarget{ref-deleeuw2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-deleeuw2015}{}}%
 de Leeuw, J.
@@
 
-\leavevmode\hypertarget{ref-Dubey_2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-de1994conditional}{}}%
+De Jong, R., Liang, C.-C., \& Lauber, E.
+(1994).
+Conditional and unconditional automaticity: A dual-process model of effects of spatial stimulus-response correspondence.
+\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{20}(4), 731.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dubey_2018}{}}%
 Dubey, N., Witzel, N., \& Witzel, J.
@@
 
-\leavevmode\hypertarget{ref-Dufau_2011}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Dufau_2011}{}}%
 Dufau, S., Duñabeitia, J.
@@
 
-\leavevmode\hypertarget{ref-R-Rcpp_b}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-Rcpp_b}{}}%
 Eddelbuettel, D., \& Balamuta, J.
@@
 
-\leavevmode\hypertarget{ref-R-Rcpp_a}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-Rcpp_a}{}}%
 Eddelbuettel, D., \& François, R. (2011). {Rcpp}: Seamless {R} and {C++} integration. \emph{Journal of Statistical Software}, \emph{40}(8), 1--18. \url{https://doi.org/10.18637/jss.v040.i08}
 
-\leavevmode\hypertarget{ref-eerland2013influence}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-eerland2013influence}{}}%
 Eerland, A., Engelen, J.
@@
 
-\leavevmode\hypertarget{ref-Fern_ndez_L_pez_2019}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Fern_ndez_L_pez_2019}{}}%
 Fernández-López, M., Marcet, A., \& Perea, M.
@@
 
-\leavevmode\hypertarget{ref-forster1998pros}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-forster1998pros}{}}%
 Forster, K. (1998). The pros and cons of masked priming. \emph{Journal of Psycholinguistic Research}, \emph{27}(2), 203--233.
 
-\leavevmode\hypertarget{ref-forsterRepetitionPrimingFrequency1984}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-forsterRepetitionPrimingFrequency1984}{}}%
 Forster, K., \& Davis, C.
@@
 
-\leavevmode\hypertarget{ref-forsterDMDXWindowsDisplay2003}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-forsterDMDXWindowsDisplay2003}{}}%
 Forster, K., \& Forster, J. (2003). {DMDX}: {A Windows} display program with millisecond accuracy. \emph{Behavior Research Methods, Instruments, \& Computers}, \emph{35}(1), 116--124.
 
-\leavevmode\hypertarget{ref-Gomez_2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Gomez_2020}{}}%
 Gomez, P., \& Perea, M.
@@
 
-\leavevmode\hypertarget{ref-gomezDiffusionModelAccount2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gomezDiffusionModelAccount2013}{}}%
 Gomez, P., Perea, M., \& Ratcliff, R.
@@
 
-\leavevmode\hypertarget{ref-grainger2008cracking}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-grainger2008cracking}{}}%
 Grainger, J. (2008). Cracking the orthographic code: An introduction. \emph{Language and Cognitive Processes}, \emph{23}(1), 1--35. \url{https://doi.org/10.1080/01690960701578013}
 
-\leavevmode\hypertarget{ref-grossi2006relatedness}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-grossi2006relatedness}{}}%
 Grossi, G. (2006). Relatedness proportion effects on masked associative priming: An {ERP} study. \emph{Psychophysiology}, \emph{43}(1), 21--30. \url{https://doi.org/10.1111/j.1469-8986.2006.00383.x}
 
-\leavevmode\hypertarget{ref-R-purrr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
 Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. \url{https://CRAN.R-project.org/package=purrr}
 
-\leavevmode\hypertarget{ref-Jacobs_1995}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Jacobs_1995}{}}%
 Jacobs, A.
@@
 
-\leavevmode\hypertarget{ref-lund1996}{}%
-Lund, K., \& Burgess, C.
-(1996).
-Producing high-dimensional semantic spaces from lexical co-occurrence.
-\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{28}(2), 203--208.
-\url{https://doi.org/10.3758/BF03204766}
-
-\leavevmode\hypertarget{ref-R-see}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-see}{}}%
 Lüdecke, D., Ben-Shachar, M.
@@
 
-\leavevmode\hypertarget{ref-R-bayestestR}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lund1996}{}}%
+Lund, K., \& Burgess, C.
+(1996).
+Producing high-dimensional semantic spaces from lexical co-occurrence.
+\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{28}(2), 203--208.
+\url{https://doi.org/10.3758/BF03204766}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-bayestestR}{}}%
 Makowski, D., Ben-Shachar, M.
@@
 
-\leavevmode\hypertarget{ref-mandera2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mandera2020}{}}%
 Mandera, P., Keuleers, E., \& Brysbaert, M.
@@
 
-\leavevmode\hypertarget{ref-R-tibble}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
 Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. \url{https://CRAN.R-project.org/package=tibble}
 
-\leavevmode\hypertarget{ref-paolacciRunningExperimentsAmazon2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-paolacciRunningExperimentsAmazon2010}{}}%
 Paolacci, G., Chandler, J., \& Ipeirotis, P.
@@
 
-\leavevmode\hypertarget{ref-Parker_2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Parker_2021}{}}%
 Parker, A., Egan, C., Grant, J.
@@
 
-\leavevmode\hypertarget{ref-pavlovia2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-pavlovia2020}{}}%
 Pavlovia. (2020). \emph{Pavlovia}. \url{https://pavlovia.org/}
 
-\leavevmode\hypertarget{ref-R-sp}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-sp}{}}%
 Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. \url{https://CRAN.R-project.org/doc/Rnews/}
 
-\leavevmode\hypertarget{ref-R-patchwork}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-patchwork}{}}%
 Pedersen, T. L. (2020). \emph{Patchwork: The composer of plots}. \url{https://CRAN.R-project.org/package=patchwork}
 
-\leavevmode\hypertarget{ref-peirce2019}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-peirce2019}{}}%
 Peirce, J., Gray, J.
@@
 
-\leavevmode\hypertarget{ref-Perea_2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Perea_2018}{}}%
 Perea, M., Marcet, A., Lozano, M., \& Gomez, P.
@@
 
-\leavevmode\hypertarget{ref-perea2002does}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-perea2002does}{}}%
 Perea, M., \& Rosa, E.
@@
 
-\leavevmode\hypertarget{ref-prolific2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-prolific2021}{}}%
 Prolific. (2021). \emph{Prolific \textbar{} online participant recruitment for surveys and market research}. \url{https://www.prolific.co/}
 
-\leavevmode\hypertarget{ref-qualtrics2020}{}%
-Qualtrics. (2020). \emph{Qualtrics XM // the leading experience management software}. \url{https://www.qualtrics.com/uk/}
-
-\leavevmode\hypertarget{ref-R-base}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-qualtrics2020}{}}%
+Qualtrics. (2020). \emph{Qualtrics}. \url{https://www.qualtrics.com/uk/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-ratcliff2004}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ratcliff2004}{}}%
 Ratcliff, R., Gomez, P., \& McKoon, G.
@@
 A diffusion model account of the lexical decision task.
-\emph{Psychological Review}, \emph{111}(1), 159--182.
+\emph{Psychological Review}, \emph{1}, 159--182.
 \url{https://doi.org/10.1037/0033-295X.111.1.159}
 
-\leavevmode\hypertarget{ref-ratcliff2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ratcliff2021}{}}%
 Ratcliff, R., \& Hendrickson, A.
@@
 
-\leavevmode\hypertarget{ref-reimersPresentationResponseTiming2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ratcliff2002}{}}%
+Ratcliff, R., \& Tuerlinckx, F.
+(2002).
+Estimating parameters of the diffusion model: Approaches to dealing with contaminant reaction times and parameter variability.
+\emph{Psychonomic Bulletin \& Review}, \emph{9}(3), 438--481.
+\url{https://doi.org/10.3758/BF03196302}
+
+\leavevmode\vadjust pre{\hypertarget{ref-reimersPresentationResponseTiming2015}{}}%
 Reimers, S., \& Stewart, N.
@@
 
-\leavevmode\hypertarget{ref-rezlescu2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rezlescu2020}{}}%
 Rezlescu, C., Danaila, I., Miron, A., \& Amariei, C.
@@
 
-\leavevmode\hypertarget{ref-rodd2016impact}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rodd2016impact}{}}%
 Rodd, J.
@@
 
-\leavevmode\hypertarget{ref-R-rworldmap}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-rworldmap}{}}%
 South, A. (2011). Rworldmap: A new r package for mapping global data. \emph{The R Journal}, \emph{3}(1), 35--43. \url{http://journal.r-project.org/archive/2011-1/RJournal_2011-1_South.pdf}
 
-\leavevmode\hypertarget{ref-Taikh_2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Taikh_2020}{}}%
 Taikh, A., \& Lupker, S.
@@
 
-\leavevmode\hypertarget{ref-Tzur_2007}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Tzur_2007}{}}%
 Tzur, B., \& Frost, R.
 (2007).
-{SOA} does not reveal the absolute time course of cognitive processing in fast priming experiments{{73}}.
+{SOA} does not reveal the absolute time course of cognitive processing in fast priming experiments.
 \emph{Journal of Memory and Language}, \emph{56}(3), 321--335.
@@
 
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
 Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}
 
-\leavevmode\hypertarget{ref-R-stringr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
 Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. \url{https://CRAN.R-project.org/package=stringr}
 
-\leavevmode\hypertarget{ref-R-forcats}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
 Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. \url{https://CRAN.R-project.org/package=forcats}
 
-\leavevmode\hypertarget{ref-R-tidyr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
 Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. \url{https://CRAN.R-project.org/package=tidyr}
 
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
@@
 
-\leavevmode\hypertarget{ref-R-readxl}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
 Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. \url{https://CRAN.R-project.org/package=readxl}
 
-\leavevmode\hypertarget{ref-R-dplyr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
 Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. \url{https://CRAN.R-project.org/package=dplyr}
 
-\leavevmode\hypertarget{ref-R-readr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
 Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. \url{https://CRAN.R-project.org/package=readr}
 
-\leavevmode\hypertarget{ref-witzelTestingViabilityWebDMDX2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-witzelTestingViabilityWebDMDX2013}{}}%
 Witzel, J., Cornelius, S., Witzel, N., Forster, K.
@@
 
-\leavevmode\hypertarget{ref-R-xfun}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-xfun}{}}%
 Xie, Y. (2021). \emph{Xfun: Miscellaneous functions to support packages maintained by 'yihui xie'}. \url{https://CRAN.R-project.org/package=xfun}
 
-\leavevmode\hypertarget{ref-Yang_2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Yang_2021}{}}%
 Yang, H., Jared, D., Perea, M., \& Lupker, S.
@@
 
-\leavevmode\hypertarget{ref-yarkoni2008}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-yarkoni2008}{}}%
 Yarkoni, T., Balota, D., \& Yap, M.
@@
 
-\leavevmode\hypertarget{ref-ziegler2000}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ziegler2000}{}}%
 Ziegler, J.
@@
 
-\leavevmode\hypertarget{ref-Zimmerman_2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Zimmerman_2012}{}}%
 Zimmerman, R., \& Gomez, P. (2012). Drawing attention to primes increases inhibitory word priming effects. \emph{The Mental Lexicon}, \emph{7}(2), 119--146. \url{https://doi.org/10.1075/ml.7.2.01zim}
@@
 \endgroup
-
-\begin{verbatim}
-## Error: pandoc document conversion failed with error 99
-\end{verbatim}
-
-\begin{verbatim}
-## Error in parse_block(g[-1], g[1], params.src, markdown_mode): Duplicate chunk label 'appendix_setup', which has been used for the chunk:
-## library(tidyverse)
-## knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
-\end{verbatim}
 
@@
 perceptual decisions, and it has been quite successful at accounting for
-lexical decision data (Ratcliff et al, 2004) and more importantly for
-the present work, masked priming data (Gomez et al, 2012).
+lexical decision data (Ratcliff et al., 2004) and more importantly for
+the present work, masked priming data (Gomez et al., 2012).
 
@@
 (response proportions and RTs at quantiles) are averaged across
-participants. This process is also known as Vincentalizing, and the
+participants. This process is also known as Vincentizing, and the
 averaged quantiles are referred to as vintenciles
@@
 
-\caption{\label{tab:model_parameters_table}$\chi^2$ values for the two models for both experiments.}
+\caption{\label{tab:appendix_model_parameters_table}$\chi^2$ values for the two models for both experiments.}
 
@@
 
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:appendix_table_2}$T_{er}$ values for Experiment 1.}
+
+\begin{tabular}{ll}
+\toprule
+Parameters & \multicolumn{1}{c}{Experiment1}\\
+\midrule
+$T_{er}$  33ms nonword ID & 0.51\\
+$T_{er}$ 33ms nonword Unrel & 0.51\\
+$T_{er}$  50ms nonword ID & 0.50\\
+$T_{er}$ 50ms nonword Unrel & 0.51\\
+$T_{er}$  33ms word ID & 0.47\\
+$T_{er}$ 33ms word Unrel & 0.49\\
+$T_{er}$  50ms word ID & 0.46\\
+$T_{er}$ 50ms word Unrel & 0.50\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 This is in general agreement with the Gomez et al.~(2013) original paper
@@
 
-\caption{\label{tab:appendix_table_2}$T_{er}$ values for Experiment 1.}
-
-\begin{tabular}{ll}
-\toprule
-Parameters & \multicolumn{1}{c}{Experiment1}\\
-\midrule
-$T_{er}$ values for Experiment 1.  33ms nonword ID & 0.51\\
-$T_{er}$ values for Experiment 1. 33ms nonword Unrel & 0.51\\
-$T_{er}$ values for Experiment 1.  50ms nonword ID & 0.50\\
-$T_{er}$ values for Experiment 1. 50ms nonword Unrel & 0.51\\
-$T_{er}$ values for Experiment 1.  33ms word ID & 0.47\\
-$T_{er}$ values for Experiment 1. 33ms word Unrel & 0.49\\
-$T_{er}$ values for Experiment 1.  50ms word ID & 0.46\\
-$T_{er}$ values for Experiment 1. 50ms word Unrel & 0.50\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:appendix_table_3} \$T\_\{er\}\$ values for Experiment 2.}
+\caption{\label{tab:appendix_table_3} $T_{er}$ values for Experiment 2.}
 
@@
 \midrule
-\$T\_\{er\}\$ 16ms nonword ID & 0.54\\
-\$T\_\{er\}\$ 16ms nonword Unrel & 0.54\\
-\$T\_\{er\}\$ 33ms nonword ID & 0.53\\
-\$T\_\{er\}\$ 33ms nonword Unrel & 0.53\\
-\$T\_\{er\}\$ 16ms word ID & 0.50\\
-\$T\_\{er\}\$ 16ms word Unrel & 0.50\\
-\$T\_\{er\}\$ 33ms word ID & 0.49\\
-\$T\_\{er\}\$ 33ms word Unrel & 0.51\\
+$T_{er}$ 16ms nonword ID & 0.54\\
+$T_{er}$ 16ms nonword Unrel & 0.54\\
+$T_{er}$ 33ms nonword ID & 0.53\\
+$T_{er}$ 33ms nonword Unrel & 0.53\\
+$T_{er}$ 16ms word ID & 0.50\\
+$T_{er}$ 16ms word Unrel & 0.50\\
+$T_{er}$ 33ms word ID & 0.49\\
+$T_{er}$ 33ms word Unrel & 0.51\\
 \bottomrule
@@
 \end{table}
-
-\newpage
-
-\hypertarget{references}{%
-\subsection{References}\label{references}}
-
-Gomez, P., \& Perea, M. (2020). Masked identity priming reflects an
-encoding advantage in developing readers. Journal of Experimental Child
-Psychology, 199, 104911. https://doi.org/10.1016/j.jecp.2020.104911
-
-Gomez, P., Perea, M., \& Ratcliff, R. (2013). A diffusion model account
-of masked versus unmasked priming: Are they qualitatively different?
-Journal of Experimental Psychology: Human Perception and Performance, 39
-(6), 1731--1740. https://doi.org/10.1037/a0032333
-
-Ratcliff, R. (1978). A theory of memory retrieval. Psychological Review,
-85, 59--108. https://doi.org/10.1037/0033-295X.85.2.59
-
-Ratcliff, R., Gomez, P., \& McKoon, G. (2004). A diffusion model account
-of the lexical decision task. Psychological Review, 111, 159--182.
-doi://10.1037/0033-295X.111.1.159
-
-Ratcliff, R.,\& Tuerlinckx, F. (2002). Estimating the parameters of the
-diffusion model: Approaches to dealing with contaminant reaction times
-and parameter variability. Psychonomic Bulletin and Review, 9, 438--481.
-https://doi.org/10.3758/BF03196302
 \end{appendix}

### 2021-11-03 previous revisions/MaskedPriming_complete_ms.tex
Move old documents to different directory, make final Rmd and tex files

--- 2021-09-21 MaskedPriming_revision.tex
@@
 
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
-
 % \usepackage{etoolbox}
@@
 \shorttitle{Online masked priming}
-\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 7916}
+\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: XXXXX}
 \usepackage{csquotes}
@@
 
-\title{Does online masked priming pass the test?\\
+\title{Does online masked priming passes the Turing test?\\
 The effects of prime exposure duration on masked identity priming}
@@
 
-\note{
-
-\clearpage
-
-}
-
 \authornote{
 
-We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.
-
-This research has been partly supported by Grant PSI2017-86210-P from the Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).
-
-This study was pre-registered on the Open Science Framework (OSF) prior to data collection.
-The registration form for Experiment 1, together with the materials, data files, and R scripts can be found at {[}\url{https://osf.io/57rzq/}{]}.
-The registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}.
+This research has been partly supported by Grant PSI2017-86210-P from the Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), \color{red} and\ldots{} PABLO, BERNHARD \color{black}
 
@@
 Importantly, we also tested the role of prime exposure duration (33.3 vs.~50 ms in Experiment 1 and 16.7 vs.~33.3 ms in Experiment 2), thus allowing us to examine both across conditions and within-conditions effects.
-We found that our online data are indeed very similar to the masked priming data previously reported in the masked priming literature.
+We found that our online data are indeed very similar to the masked priming data reported by Gomez et al.
+(2013).
 Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33.3 ms and no priming effect at 16.7 ms prime duration.
@@
 Masked priming (Forster \& Davis, 1984) is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition (see Forster, 1998; Grainger, 2008, for reviews).
-Priming refers to the influence of a prime stimulus (e.g., \emph{nurse}, \emph{horse}) on a subsequently presented stimulus that the participant has to respond to (e.g., ``is \emph{DOCTOR} a word?'').
-Priming effects are measured as the difference in a dependent variable (e.g., response time {[}RT{]}) between two conditions (e.g., unrelated: \emph{horse-DOCTOR}; related: \emph{nurse-DOCTOR}).
+Priming refers to the influence of a prime stimulus (e.g., \emph{nurse}, \emph{horse}) on a subsequently presented stimulus that the participant has to respond (e.g., ``is \emph{DOCTOR} a word?'').
+It is measured as the difference in a dependent variable (e.g., response time {[}RT{]}) between two conditions (e.g., unrelated: \emph{horse-DOCTOR}; related: \emph{nurse-DOCTOR}).
 In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a pattern mask (e.g., \#\#\#\#\#) for a much longer duration (typically 500 ms).
@@
 Nearly all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by Forster and Forster (2003).
-The issue we examine in the present paper is whether masked priming experiments can be conducted in an online setting without significant changes in the pattern of results.
-Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
+The issue we examine in the present paper is whether masked priming experiments can be safely conducted in an online setting.
+Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or with minimal activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
 Indeed, researchers in decision making and economics have been using online paradigms for several decades now (e.g., Birnbaum \& Birnbaum, 2000; Paolacci et al., 2010).
 
-Cognitive psychologists have been much slower that their behavioral economics colleagues in taking up online paradigms (see Brysbaert et al., 2016; Cai et al., 2017; Dufau et al., 2011; Eerland et al., 2013; Rodd et al., 2016, for some exceptions), often due to concerns about the validity of the results.
+However, cognitive psychologists have been much slower in taking up online paradigms (see Brysbaert et al., 2016; Cai et al., 2017; Eerland et al., 2013; Rodd et al., 2016, for some exceptions), often due to concerns about the validity of the results.
 Such concerns are not limited to cognitive studies (see Aust et al., 2013), but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
-Furthermore, these concerns are even more central in the masked priming technique, where it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
+Furthermore, this concerns are even more central in the masked priming technique, where it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
 For instance, presenting the masked prime for longer than intended (e.g., 83 ms or longer instead of the nominal 50 ms) could counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest (see Zimmerman \& Gomez, 2012).
@@
 In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
-Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility of recruiting participants for on-line experiments based on various specific characteristics set up by the experimenters regardless of their location (e.g., native French speakers, not older than 30 years old, not currently in college).
+Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility to recruit participants for on-line experiments based on various specific characteristics set up by the experimenter not necessarily in the country's lab (e.g., native French speakers, not older than 30 years old, not currently in college).
 
@@
 As Reimers and Stewart (2015) pointed out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
-If the results of the Web-based study are comparable to previous lab-based results, this suggests that, whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
+If the results of the Web-based study are comparable to previous lab-based results, this suggests that whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
 
@@
 
-Specifically, in this study we were interested in whether we could replicate and extend a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming is commonly described as a savings effect.
+Specifically, in this study we were interested in whether we could replicate, and extend, a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming is commonly described as a savings effect.
 As first suggested by Forster (1998), for a masked identity prime, ``the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner,'' whereas for an unrelated prime, ``the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur'' (p.~213).
@@
 Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony (SOA).
-Empirical evidence supporting this view has been obtained in several studies not only with skilled adults but also with developing readers (e.g., Gomez et al., 2013; Gomez \& Perea, 2020; Taikh \& Lupker, 2020; Yang et al., 2021).
-Gomez et al.
-(2013) proposed an implementation of this hypothesis within the diffusion model (Ratcliff et al., 2004).
-This implementation proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution (\(T_{er}\)) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached.
+Empirical evidence supporting this view has been obtained in several papers not only with skilled adults but also with developing readers (e.g., Gomez et al., 2013; Gomez \& Perea, 2020; Taikh \& Lupker, 2020; Yang et al., 2021).
+Moreover, this pattern of results fits very well with the diffusion model (Ratcliff et al., 2004).
+This model proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution (\(T_{er}\)) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached.
 Importantly, in the decision process, the information gathered from the stimulus can vary in noise, depending on its quality, which modifies the rate at which information is accumulated (i.e., the \emph{drift rate}).
 With regards to RTs from masked priming tasks, Gomez et al.
-(2013) found that the difference between identity and unrelated conditions could be accounted for by a change in the \(T_{er}\) parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a more skewed RT distribution in the slower, unrelated condition.
-
-Critically, the above pattern is specific to \emph{masked} priming.
-In fact, the most common pattern of results in latency based tasks is that conditions that produce longer latencies will also produce larger variance.
-This pattern is evident in priming as well---when primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles (i.e., a change in shape rather than a shift in RT distributions; see Gomez et al., 2013).
-Fits from the diffusion model show that this result corresponds to changes in both the \(T_{er}\) parameter and the drift rate.
-Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word, unlike in masked priming.
-Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.~both encoding and information quality in unmasked priming.
+(2013) found that the difference between identity and unrelated conditions could be accounted by a change in the \(T_{er}\) parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a skewer RT distribution in the slower, unrelated condition.
+
+Critically, the above pattern is \emph{specific} to masked priming.
+When primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles (i.e., a change in shape rather than a shift in RT distributions; see Gomez et al., 2013).
+Fits from the diffusion model show that this result corresponds to changes in both the \(T_{er}\) parameter and the drift rate (see Gomez et al., 2013).
+Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word.
+Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.~both encoding + information quality in unmasked priming.
 
@@
 
-All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli (e.g., Parker et al., 2021).
-This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms (e.g., Aguasvivas et al., 2020; Brysbaert et al., 2021; Brysbaert et al., 2016; Mandera et al., 2020).
-So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries (e.g., Adelman et al., 2014).
+All in all, replicating the results observed in controlled laboratory masked priming studies would provide some grounds to the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli (e.g., Parker et al., 2021).
 Importantly, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.~unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) (see Jacobs et al., 1995; Ziegler et al., 2000, for advantages of within-condition comparisons).
@@
 
-\newpage
-
 \begin{figure}
 \centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/hyp-mod-dat-figure-1.pdf}
+\includegraphics{MaskedPriming_complete_ms_files/figure-latex/hyp-mod-dat-figure-1.pdf}
 \caption{\label{fig:hyp-mod-dat-figure}Mapping from hypotheses to data via evidence accumulation models.
@@
 
+The study was pre-registered on the Open Science Framework (OSF) prior to data collection.
+The registration form, together with the materials, data files, and R scripts can be found at \url{https://osf.io/d2txs/}.
+
 \hypertarget{experiment-1}{%
@@
 \subsection{Method}\label{method}}
-
-The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at \url{https://osf.io/57rzq/}.
 
@@
 We also selected 240 matched, orthographically legal six-letter nonwords.
-For each target, we created an identical prime (e.g.~\emph{region --- REGION} and \emph{fainch --- FAINCH}) and an unrelated prime consisting of another word from the list (e.g.~\emph{launch --- REGION} and \emph{miluer --- FAINCH})\footnote{Note that the lexical status of the unrelated prime differed depending on the target type: for word targets, the unrelated primes were words, whereas for nonword targets, they were pseudowords.
+For each target, we created an identical prime (e.g.~\emph{region --- REGION} and \emph{fainch --- FAINCH}) and an unrelated prime consisting of another word from the list (e.g.~\emph{launch --- REGION} and \emph{miluer --- FAINCH})\footnote{Someone could argue that, for word targets, the unrelated primes were words, whereas for nonword targets, they were pseudowords.
 However, as shown by Fernández-López et al.
@@
 Participants were able to sign up for the experiment on the Prolific website.
-Upon signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment (Qualtrics, 2020).
+On signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment (Qualtrics, 2020).
 After indicating their agreement to participate, participants were forwarded to Pavlovia (Pavlovia, 2020), where the actual lexical decision task was implemented in PsychoJS.
@@
 
-We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.10.5; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.7; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.3; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.3; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.25; Xie, 2021).}.
+We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R {[}Version 4.0.5; R Core Team (2021){]} and the R-packages \emph{bayestestR} {[}Version 0.9.0; Makowski et al.
+(2019){]}, \emph{brms} {[}Version 2.15.0; Bürkner (2017); Bürkner (2018){]}, \emph{dplyr} {[}Version 1.0.5; Wickham et al.
+(2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{patchwork} {[}Version 1.1.1; Pedersen (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{Rcpp} {[}Version 1.0.6; Eddelbuettel and François (2011); Eddelbuettel and Balamuta (2018){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{readxl} {[}Version 1.3.1; Wickham and Bryan (2019){]}, \emph{rworldmap} {[}Version 1.3.6; South (2011){]}, \emph{see} {[}Version 0.6.2; Lüdecke et al.
+(2020){]}, \emph{sp} {[}Version 1.4.5; Pebesma and Bivand (2005){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.1.0; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]}, \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
+(2019){]}, and \emph{xfun} {[}Version 0.22; Xie (2021){]}.}.
 We only analyzed trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as incorrect responses (5.84 \% of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.36 \% of trials).
+For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (5.77 \% of trials).
+For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (0.28 \% of trials).
+As the trials automatically ended after 2000 ms, there were no RTs longer than this.
 For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.~identical) and prime duration (33.3 ms vs.~50 ms) as well as their interaction as the fixed effects.
@@
 We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items.
-We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component \(\mu\) and the scale parameter of the exponential component \(\beta\) (equaling the inverse of the rate parameter \(\lambda\)) being allowed to vary between conditions.
+We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component \(\mu\) and the scale parameter of the exponential component \(\beta\) (equalling the inverse of the rate parameter \(\lambda\)) being allowed to vary between conditions.
 To model response accuracy, we used the Bernoulli distribution with a logit link.
 We used the default priors suggested by \emph{brms} except for the coefficients for the fixed effects, for which we applied weakly informative priors of \(\beta \sim N(0,100)\) in order to rule out improbably large effect sizes.
-Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warm-up iterations for the accuracy models).
+Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warmup iterations for the accuracy models).
 We consider an effect as credible if the 95\% Credible Interval (CrI) estimated from the posterior distribution does not contain zero.
@@
 
-Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table \ref{tab:exp1-descriptive-rt-table} (although note that we only analyzed the word trials).
+Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table~\ref{tab:exp1-descriptive-rt-table} (although note that we only analyzed the word trials).
 
@@
 \midrule
-Nonword & 33.3 ms & Identity & 700 & 665 & 187 & 263 & 1,776 & 0.91\\
-Nonword & 33.3 ms & Unrelated & 702 & 664 & 188 & 256 & 1,770 & 0.92\\
-Nonword & 50 ms & Identity & 700 & 658 & 189 & 256 & 1,760 & 0.91\\
-Nonword & 50 ms & Unrelated & 699 & 657 & 185 & 251 & 1,796 & 0.93\\
-Word & 33.3 ms & Identity & 630 & 599 & 164 & 254 & 1,796 & 0.94\\
-Word & 33.3 ms & Unrelated & 652 & 619 & 166 & 254 & 1,783 & 0.93\\
-Word & 50 ms & Identity & 608 & 575 & 161 & 265 & 1,784 & 0.96\\
-Word & 50 ms & Unrelated & 649 & 620 & 158 & 294 & 1,710 & 0.93\\
+Nonword & 33.3 ms & Identity & 701 & 665 & 191 & 263 & 1,885 & 0.91\\
+Nonword & 33.3 ms & Unrelated & 705 & 665 & 195 & 256 & 1,949 & 0.92\\
+Nonword & 50 ms & Identity & 701 & 658 & 192 & 256 & 1,938 & 0.91\\
+Nonword & 50 ms & Unrelated & 702 & 658 & 193 & 251 & 1,952 & 0.93\\
+Word & 33.3 ms & Identity & 631 & 599 & 169 & 254 & 1,942 & 0.94\\
+Word & 33.3 ms & Unrelated & 654 & 619 & 171 & 254 & 1,887 & 0.93\\
+Word & 50 ms & Identity & 609 & 575 & 162 & 265 & 1,866 & 0.95\\
+Word & 50 ms & Unrelated & 650 & 620 & 159 & 294 & 1,801 & 0.93\\
 \bottomrule
@@
 
-Table \ref{tab:exp1-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-The RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 31.55, 95\% CrI {[}27.16, 35.92{]}), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (\emph{b} = -10.96, 95\% CrI {[}-14.83, -7.11{]}).
-The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = 19.31, 95\% CrI {[}11.39, 27.09{]}).
-The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.07{]}).
-However, the 50 ms prime exposure duration seems to be associated with a slightly lower \(\beta\), i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (\emph{b} = -0.07, 95\% CrI {[}-0.12, -0.03{]}).
-On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (\emph{b} = 0.03, 95\% CrI {[}-0.05, 0.12{]}).
+Table~\ref{tab:exp1-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+
+The RT model indicates that the mean of the normal distribution \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 31.35, 95\% CrI {[}27.66, 35.01{]}), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (\emph{b} = -11.38, 95\% CrI {[}-14.75, -8.02{]}).
+The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = 19.31, 95\% CrI {[}12.14, 26.46{]}).
+The shape parameter of the exponential distribution \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.07{]}).
+However, the 50 ms prime exposure duration seems to be associated with a slightly lower \(\beta\), i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (\emph{b} = -0.08, 95\% CrI {[}-0.12, -0.04{]}).
+On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (\emph{b} = 0.03, 95\% CrI {[}-0.05, 0.11{]}).
 
@@
 \midrule
-Intercept ($\mu$) & 633.707 & 8.815 & 617.142 & 651.175 & 1.006\\
-Intercept ($\beta$) & 4.686 & 0.042 & 4.601 & 4.768 & 1.001\\
-Relatedness ($\mu$) & 31.551 & 2.228 & 27.162 & 35.915 & 1.000\\
-Prime Duration ($\mu$) & -10.959 & 1.947 & -14.825 & -7.105 & 1.000\\
-Relatedness:Prime Duration ($\mu$) & 19.306 & 4.026 & 11.388 & 27.094 & 1.000\\
-Relatedness ($\beta$) & 0.031 & 0.022 & -0.011 & 0.073 & 1.000\\
-Prime Duration ($\beta$) & -0.074 & 0.024 & -0.120 & -0.028 & 1.000\\
-Relatedness:Prime Duration ($\beta$) & 0.031 & 0.042 & -0.051 & 0.115 & 1.000\\
+Intercept ($\mu$) & 633.620 & 6.504 & 620.936 & 646.430 & 1.009\\
+Intercept ($\beta$) & 4.669 & 0.031 & 4.607 & 4.729 & 1.003\\
+Relatedness ($\mu$) & 31.353 & 1.878 & 27.659 & 35.006 & 1.001\\
+Prime Duration ($\mu$) & -11.382 & 1.704 & -14.746 & -8.018 & 1.001\\
+Relatedness:Prime Duration ($\mu$) & 19.309 & 3.699 & 12.141 & 26.455 & 1.000\\
+Relatedness ($\beta$) & 0.032 & 0.020 & -0.007 & 0.070 & 1.000\\
+Prime Duration ($\beta$) & -0.081 & 0.022 & -0.124 & -0.038 & 1.000\\
+Relatedness:Prime Duration ($\beta$) & 0.029 & 0.041 & -0.052 & 0.110 & 1.000\\
 \bottomrule
@@
 \centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e1-words-1.pdf}
+\includegraphics{MaskedPriming_complete_ms_files/figure-latex/deltas-e1-words-1.pdf}
 \caption{\label{fig:deltas-e1-words}Delta plots depicting the magnitude of the effect over time in Experiment 1.
 Each dot represents the mean RT at the .1, .3, .5, .7 and .9 quantiles.
-\emph{Panel A)} Difference in RT between unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right).
-\emph{Panel B)} Difference in RT between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions.}
+\emph{Panel A)} Difference of RTs between unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right).
+\emph{Panel B)} Difference of RTs between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions.}
 \end{figure}
@@
 
-Table \ref{tab:exp1-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.50, 95\% CrI {[}-0.72, -0.31{]}).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = 0.19, 95\% CrI {[}-0.02, 0.42{]}).
+Table~\ref{tab:exp1-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+
+The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.50, 95\% CrI {[}-0.71, -0.30{]}).
+The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = 0.20, 95\% CrI {[}-0.01, 0.42{]}).
 The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = -0.53, 95\% CrI {[}-0.94, -0.14{]}).
@@
 \midrule
-Intercept & 3.458 & 0.122 & 3.224 & 3.705 & 1.000\\
-Relatedness & -0.503 & 0.105 & -0.720 & -0.305 & 1.000\\
-Prime Duration & 0.192 & 0.110 & -0.016 & 0.417 & 1.000\\
-Relatedness:Prime Duration & -0.530 & 0.206 & -0.944 & -0.138 & 1.000\\
+Intercept & 3.451 & 0.122 & 3.217 & 3.695 & 1.000\\
+Relatedness & -0.496 & 0.105 & -0.714 & -0.301 & 1.000\\
+Prime Duration & 0.195 & 0.109 & -0.012 & 0.417 & 1.000\\
+Relatedness:Prime Duration & -0.533 & 0.204 & -0.943 & -0.145 & 1.000\\
 \bottomrule
@@
 While the shape of the distribution changed slightly between the 33.3 ms and the 50 ms prime exposure durations, we did not observe an effect of the prime relatedness condition on the shape parameter \(\beta\) of the exponential distribution, suggesting, according to the savings hypothesis by Forster (1998), that only encoding processes were affected by the relatedness manipulation.
-Moreover, as can be observed in Figure \ref{fig:deltas-e1-words}, the effect magnitude was close to the stimulus-onset asynchrony (see also Perea et al., 2018).
+Moreover, as can be observed in Figure \ref{fig:deltas-e1-words} the effect magnitude was close to the stimulus-onset asynchrony (see also Perea et al., 2018).
 
@@
 In the second experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 16.7 ms and 33.3 ms (roughly corresponding to one and two frames at a refresh rate of 60 Hz).
-
-The pre-registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}. The materials, data files, and R scripts can be found at {[}\url{https://osf.io/57rzq/}{]}
 
@@
 
-We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as those with incorrect responses (4.93 \% of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.15 \% of trials).
+We analyzed the data in the same way as in Experiment 1, again only analyzing trials where the target stimulus was a word.
+For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (4.86 \% of trials).
+For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (0.08 \% of trials).
 For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5.
@@
 
-Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table \ref{tab:exp2-descriptive-rt-table}.
+Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table~\ref{tab:exp2-descriptive-rt-table}.
 
@@
 
-As in Experiment 1, the RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 8.53, 95\% CrI {[}5.07, 12.11{]}).
-For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (\emph{b} = -3.60, 95\% CrI {[}-7.22, -0.03{]}).
-However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (\emph{b} = 15.17, 95\% CrI {[}8.52, 21.73{]}).
-The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.02, 0.07{]}), prime exposure duration (\emph{b} = 0.01, 95\% CrI {[}-0.03, 0.05{]}), or their interaction (\emph{b} = -0.03, 95\% CrI {[}-0.12, 0.05{]}), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
-
-Table \ref{tab:exp2-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
+As in Experiment 1, the RT model indicates that the mean of the normal distribution \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 8.80, 95\% CrI {[}5.42, 12.29{]}).
+For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (\emph{b} = -3.48, 95\% CrI {[}-7.09, 0.16{]}).
+However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (\emph{b} = 15.35, 95\% CrI {[}8.64, 22.05{]}).
+The shape parameter of the exponential distribution \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.08{]}), prime exposure duration (\emph{b} = 0.01, 95\% CrI {[}-0.03, 0.06{]}), or their interaction (\emph{b} = -0.03, 95\% CrI {[}-0.12, 0.05{]}), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
+
+Table~\ref{tab:exp2-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
 
@@
 \midrule
-Nonword & 16.7 ms & Identity & 719 & 680 & 185 & 330 & 1,787 & 0.93\\
-Nonword & 16.7 ms & Unrelated & 717 & 677 & 183 & 284 & 1,799 & 0.94\\
-Nonword & 33.3 ms & Identity & 717 & 668 & 193 & 351 & 1,787 & 0.94\\
-Nonword & 33.3 ms & Unrelated & 715 & 672 & 188 & 281 & 1,789 & 0.94\\
-Word & 16.7 ms & Identity & 659 & 625 & 160 & 311 & 1,785 & 0.94\\
-Word & 16.7 ms & Unrelated & 661 & 623 & 165 & 308 & 1,796 & 0.95\\
-Word & 33.3 ms & Identity & 649 & 618 & 154 & 280 & 1,657 & 0.96\\
-Word & 33.3 ms & Unrelated & 667 & 633 & 162 & 269 & 1,701 & 0.94\\
+Nonword & 16.7 ms & Identity & 721 & 680 & 191 & 330 & 1,929 & 0.93\\
+Nonword & 16.7 ms & Unrelated & 719 & 677 & 187 & 284 & 1,920 & 0.94\\
+Nonword & 33.3 ms & Identity & 719 & 668 & 198 & 351 & 1,924 & 0.94\\
+Nonword & 33.3 ms & Unrelated & 718 & 672 & 197 & 281 & 1,912 & 0.94\\
+Word & 16.7 ms & Identity & 660 & 625 & 162 & 311 & 1,892 & 0.94\\
+Word & 16.7 ms & Unrelated & 662 & 623 & 169 & 308 & 1,899 & 0.95\\
+Word & 33.3 ms & Identity & 650 & 618 & 158 & 280 & 1,873 & 0.96\\
+Word & 33.3 ms & Unrelated & 667 & 633 & 164 & 269 & 1,920 & 0.94\\
 \bottomrule
@@
 
-\caption{\label{tab:exp2-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for correct word RTs in Experiment 2.}
+\caption{\label{tab:exp2-blmm-table}(ref:exp2-blmm-rt-table-caption)}
 
@@
 \midrule
-Intercept ($\mu$) & 656.975 & 9.036 & 639.056 & 674.711 & 1.003\\
-Intercept ($\beta$) & 4.658 & 0.043 & 4.573 & 4.741 & 1.003\\
-Relatedness ($\mu$) & 8.529 & 1.795 & 5.065 & 12.106 & 1.000\\
-Prime Duration ($\mu$) & -3.602 & 1.813 & -7.216 & -0.033 & 1.000\\
-Relatedness:Prime Duration ($\mu$) & 15.166 & 3.390 & 8.517 & 21.727 & 1.000\\
-Relatedness ($\beta$) & 0.028 & 0.023 & -0.016 & 0.073 & 1.000\\
-Prime Duration ($\beta$) & 0.011 & 0.021 & -0.031 & 0.053 & 1.000\\
-Relatedness:Prime Duration ($\beta$) & -0.034 & 0.043 & -0.119 & 0.049 & 1.000\\
+Intercept ($\mu$) & 658.462 & 9.372 & 640.004 & 676.606 & 1.002\\
+Intercept ($\beta$) & 4.668 & 0.042 & 4.585 & 4.749 & 1.005\\
+Relatedness ($\mu$) & 8.799 & 1.758 & 5.420 & 12.286 & 1.000\\
+Prime Duration ($\mu$) & -3.481 & 1.841 & -7.095 & 0.161 & 1.000\\
+Relatedness:Prime Duration ($\mu$) & 15.347 & 3.425 & 8.639 & 22.046 & 1.000\\
+Relatedness ($\beta$) & 0.031 & 0.023 & -0.013 & 0.076 & 1.000\\
+Prime Duration ($\beta$) & 0.013 & 0.022 & -0.030 & 0.055 & 1.000\\
+Relatedness:Prime Duration ($\beta$) & -0.030 & 0.043 & -0.116 & 0.055 & 1.000\\
 \bottomrule
@@
 We also created the delta plots of data from Experiment 2 (see Figure \ref{fig:deltas-e2-words}).
-Panel A, shows there is no priming effect for the 16.7 ms condition, in contrast with a consistent effect across quantiles for the 33.3 ms condition (parallel to the one found in Experiment 1).
+Panel A, shows there is no priming effect for the 16.7 ms condition, but a consistent effect across quantiles for the 33.3 ms condition (parallel to the one found in Experiment 1).
 Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight hindering for unrelated primes.
@@
 \centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e2-words-1.pdf}
+\includegraphics{MaskedPriming_complete_ms_files/figure-latex/deltas-e2-words-1.pdf}
 \caption{\label{fig:deltas-e2-words}Delta plots depicting the magnitude of the effect over time in Experiment 2.}
@@
 The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33.3 ms condition, and reversed in the 16.7 ms condition (\emph{b} = -0.71, 95\% CrI {[}-1.16, -0.30{]}), although the effect in the 16.7 ms condition was very weak.
-Table \ref{tab:exp2-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, indicating that the model was fitted successfully as they are all close to 1.
+Table~\ref{tab:exp2-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, indicating that the model was fitted successfully as they are all close to 1.
 
@@
 \midrule
-Intercept & 3.734 & 0.135 & 3.476 & 4.007 & 1.000\\
-Relatedness & -0.217 & 0.109 & -0.434 & -0.004 & 1.000\\
-Prime Duration & -0.055 & 0.126 & -0.306 & 0.184 & 1.000\\
-Relatedness:Prime Duration & -0.710 & 0.218 & -1.157 & -0.305 & 1.000\\
+Intercept & 3.736 & 0.135 & 3.475 & 4.007 & 1.000\\
+Relatedness & -0.218 & 0.109 & -0.434 & -0.004 & 1.000\\
+Prime Duration & -0.054 & 0.126 & -0.313 & 0.183 & 1.000\\
+Relatedness:Prime Duration & -0.708 & 0.219 & -1.165 & -0.302 & 1.000\\
 \bottomrule
@@
 
-In Experiment 2, we found the pattern we expected from previous research: In the mean \(\mu\) of the Gaussian component of the ex-Gaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration (Tzur \& Frost, 2007; Ziegler et al., 2000).
+In Experiment 2, we found the pattern we expected from previous research: In the mean \(\mu\) of the Gaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration (Tzur \& Frost, 2007; Ziegler et al., 2000).
 This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
-In addition, we did not observe an effect of the prime relatedness on the shape parameter \(\beta\) of the exponential component (i.e., the effect corresponded to a shift of the RT distributions, as shown in in-lab studies; e.g., Taikh \& Lupker, 2020; Yang et al., 2021).
+In addition, we did not observe an effect of the prime relatedness on the shape parameter \(\beta\) of the exponential distribution (i.e., the effect corresponded to a shift of the RT distributions, as shown in in-lab studies; e.g., Taikh \& Lupker, 2020; Yang et al., 2021).
 Moreover, the magnitude of the priming effect at the 33.3 ms prime exposure duration was close to the magnitude of the prime-target stimulus-onset asynchrony, as can be seen in the delta plots in Figure \ref{fig:deltas-e2-words} (see Gomez et al., 2013; Perea et al., 2018).
@@
 To that end, we conducted two online masked identity priming experiments (e.g., \emph{region --- REGION} vs.~\emph{launch --- REGION}) in which we manipulated prime exposure duration (33.3 vs.~50 ms in Experiment 1; 16.7 vs.~33 ms in Experiment 2).
+\color{red} EXPLAIN A BIT WHAT WE DID \color{black}
+
 The results of our online-based experiments replicated and extended benchmarks masked identity priming effects previous in the lab-based studies.
-We observed the effect sizes predicted by Forster's (1998) savings hypothesis: Our data show a shift in the mean of the Gaussian component of the ex-Gaussian distribution, but no change in the shape parameter \(\beta\) of the exponential component, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes.
+We observed the effect sizes predicted by Forster's (1998) savings hypothesis: Our data show a shift in the mean of the Gaussian distribution, but no change in the shape parameter \(\beta\) of the exponential distribution, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes.
 Furthermore, the size of the priming effect was not only directly influenced by the prime duration, suggesting the experimental software was able to control the display timing of the prime accurately, but also of a similar magnitude to the prime duration (within the range reported in previous studies, e.g., 35-47 ms for a 50 ms prime duration in Perea et al., 2018).
@@
 While accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, they are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade.
-Similarly, unlike in-lab conditions, where the contrast of the computer screens can be measured and kept constant, there is no such a guarantee for the screens used by online participants---note that Tzur and Frost (2007) were only able to observe strong effects for short prime exposure durations when using extreme contrast values.
-Thus, the fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy, PsychoJS.
-
-Furthermore, our results extend previous work showing the validity of on-line studies measuring response times (e.g., Brysbaert et al., 2016; Cai et al., 2017; Dufau et al., 2011; Eerland et al., 2013; Rodd et al., 2016, to cite a few instances) to the masked priming technique.
+Similarly, unlike in-lab conditions, were the contrast of the computer screens can be measured and kept constants, there is no such a guarantee in the monitors of online participnts--note that the manipulation of contrast in the Tzur and Frost (2007) experiments used extreme values.
+Thus, the fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy.
+
+Furthermore, our results extend previous work showing the validity of on-line studies measuring response times (e.g., Brysbaert et al., 2016; Cai et al., 2017; Eerland et al., 2013; Rodd et al., 2016, to cite a few instances) to the masked priming technique.
 Thus, the present study opens the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
 Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible.
-For instance, online participants can be people from different countries and/or cultures, from different age groups, bilinguals/multilinguals, even those who do not own a computer, only a smartphone.
+For instance, people from different countries and/or cultures, from different age groups, bilinguals/multilinguals, even from those who do not have computers at home, but they do have smartphones.
 Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant.
-This opens up the possibility of masked-priming crowdsourced megastudies.
-In general, deploying masked priming experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
+Additionally, deploying masked priming experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-adelman2014}{}%
-Adelman, J.
-S., Johnson, R.
-L., McCormick, S.
-F., McKague, M., Kinoshita, S., Bowers, J.
-S., Perry, J.
-R., Lupker, S.
-J., Forster, K.
-I., Cortese, M.
-J., Scaltritti, M., Aschenbrenner, A.
-J., Coane, J.
-H., White, L., Yap, M.
-J., Davis, C., Kim, J., \& Davis, C.
-J.
-(2014).
-A behavioral database for masked form priming.
-\emph{Behavior Research Methods}, \emph{46}(4), 1052--1067.
-\url{https://doi.org/10.3758/s13428-013-0442-y}
-
-\leavevmode\hypertarget{ref-aguasvivas2020}{}%
-Aguasvivas, J., Carreiras, M., Brysbaert, M., Mandera, P., Keuleers, E., \& Duñabeitia, J.
-A.
-(2020).
-How do Spanish speakers read words?
-Insights from a crowdsourced lexical decision megastudy.
-\emph{Behavior Research Methods}, \emph{52}(5), 1867--1882.
-\url{https://doi.org/10.3758/s13428-020-01357-9}
-
 \leavevmode\hypertarget{ref-Alluhaybi_2020}{}%
@@
 
-\leavevmode\hypertarget{ref-R-tinylabels}{}%
-Barth, M. (2021). \emph{{tinylabels}: Lightweight variable labels}. \url{https://github.com/mariusbarth/tinylabels}
-
 \leavevmode\hypertarget{ref-birnbaumPsychologicalExperimentsInternet2000a}{}%
@@
 \url{https://doi.org/10.7717/peerj.9414}
-
-\leavevmode\hypertarget{ref-brysbaert2021a}{}%
-Brysbaert, M., Keuleers, E., \& Mandera, P.
-(2021).
-Which words do English non-native speakers know?
-New supernational levels based on yes/no decision.
-\emph{Second Language Research}, \emph{37}(2), 207--231.
-\url{https://doi.org/10.1177/0267658320934526}
 
@@
 
-\leavevmode\hypertarget{ref-Dufau_2011}{}%
-Dufau, S., Duñabeitia, J.
-A., Moret-Tatay, C., McGonigal, A., Peeters, D., Alario, F.-X., Balota, D.
-A., Brysbaert, M., Carreiras, M., Ferrand, L., Ktori, M., Perea, M., Rastle, K., Sasburg, O., Yap, M.
-J., Ziegler, J.
-C., \& Grainger, J.
-(2011).
-Smart phone, smart science: How the use of smartphones can revolutionize research in cognitive science.
-\emph{{PLoS} {ONE}}, \emph{6}(9), e24974.
-\url{https://doi.org/10.1371/journal.pone.0024974}
-
 \leavevmode\hypertarget{ref-R-Rcpp_b}{}%
@@
 \url{https://doi.org/10.21105/joss.01541}
-
-\leavevmode\hypertarget{ref-mandera2020}{}%
-Mandera, P., Keuleers, E., \& Brysbaert, M.
-(2020).
-Recognition times for 62 thousand English words: Data from the English Crowdsourcing Project.
-\emph{Behavior Research Methods}, \emph{52}(2), 741--760.
-\url{https://doi.org/10.3758/s13428-019-01272-8}
 

### 2021-11-03 previous revisions/MaskedPriming_complete_mspg.tex
Move old documents to different directory, make final Rmd and tex files

--- 2021-09-21 MaskedPriming_revision.tex
@@
 \shorttitle{Online masked priming}
-\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 7916}
+\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 8051}
 \usepackage{csquotes}
@@
 \centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/hyp-mod-dat-figure-1.pdf}
+\includegraphics{MaskedPriming_complete_mspg_files/figure-latex/hyp-mod-dat-figure-1.pdf}
 \caption{\label{fig:hyp-mod-dat-figure}Mapping from hypotheses to data via evidence accumulation models.
@@
 
-We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.10.5; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.7; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.3; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.3; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.25; Xie, 2021).}.
+We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R {[}Version 4.0.5; R Core Team (2021){]} and the R-packages \emph{bayestestR} {[}Version 0.9.0; Makowski et al.
+(2019){]}, \emph{brms} {[}Version 2.15.0; Bürkner (2017); Bürkner (2018){]}, \emph{dplyr} {[}Version 1.0.5; Wickham et al.
+(2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{patchwork} {[}Version 1.1.1; Pedersen (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{Rcpp} {[}Version 1.0.6; Eddelbuettel and François (2011); Eddelbuettel and Balamuta (2018){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{readxl} {[}Version 1.3.1; Wickham and Bryan (2019){]}, \emph{rworldmap} {[}Version 1.3.6; South (2011){]}, \emph{see} {[}Version 0.6.2; Lüdecke et al.
+(2020){]}, \emph{sp} {[}Version 1.4.5; Pebesma and Bivand (2005){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.1.0; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]}, \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
+(2019){]}, \emph{tinylabels} (Barth, 2021), and \emph{xfun} {[}Version 0.22; Xie (2021){]}.}.
 We only analyzed trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as incorrect responses (5.84 \% of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.36 \% of trials).
+For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (5.77 \% of trials).
+For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (0.28 \% of trials).
+As the trials automatically ended after 2000 ms, there were no RTs longer than this.
 For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.~identical) and prime duration (33.3 ms vs.~50 ms) as well as their interaction as the fixed effects.
@@
 
-The RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 31.55, 95\% CrI {[}27.16, 35.92{]}), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (\emph{b} = -10.96, 95\% CrI {[}-14.83, -7.11{]}).
-The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = 19.31, 95\% CrI {[}11.39, 27.09{]}).
+The RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 31.35, 95\% CrI {[}27.66, 35.01{]}), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (\emph{b} = -11.38, 95\% CrI {[}-14.75, -8.02{]}).
+The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = 19.31, 95\% CrI {[}12.14, 26.46{]}).
 The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.07{]}).
-However, the 50 ms prime exposure duration seems to be associated with a slightly lower \(\beta\), i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (\emph{b} = -0.07, 95\% CrI {[}-0.12, -0.03{]}).
-On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (\emph{b} = 0.03, 95\% CrI {[}-0.05, 0.12{]}).
+However, the 50 ms prime exposure duration seems to be associated with a slightly lower \(\beta\), i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (\emph{b} = -0.08, 95\% CrI {[}-0.12, -0.04{]}).
+On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (\emph{b} = 0.03, 95\% CrI {[}-0.05, 0.11{]}).
 
@@
 \centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e1-words-1.pdf}
+\includegraphics{MaskedPriming_complete_mspg_files/figure-latex/deltas-e1-words-1.pdf}
 \caption{\label{fig:deltas-e1-words}Delta plots depicting the magnitude of the effect over time in Experiment 1.
@@
 
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.50, 95\% CrI {[}-0.72, -0.31{]}).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = 0.19, 95\% CrI {[}-0.02, 0.42{]}).
+The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.50, 95\% CrI {[}-0.71, -0.30{]}).
+The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = 0.20, 95\% CrI {[}-0.01, 0.42{]}).
 The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = -0.53, 95\% CrI {[}-0.94, -0.14{]}).
@@
 We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as those with incorrect responses (4.93 \% of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.15 \% of trials).
+For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (4.86 \% of trials).
+For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (0.08 \% of trials).
 For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5.
@@
 
-As in Experiment 1, the RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 8.53, 95\% CrI {[}5.07, 12.11{]}).
-For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (\emph{b} = -3.60, 95\% CrI {[}-7.22, -0.03{]}).
-However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (\emph{b} = 15.17, 95\% CrI {[}8.52, 21.73{]}).
-The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.02, 0.07{]}), prime exposure duration (\emph{b} = 0.01, 95\% CrI {[}-0.03, 0.05{]}), or their interaction (\emph{b} = -0.03, 95\% CrI {[}-0.12, 0.05{]}), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
+As in Experiment 1, the RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 8.80, 95\% CrI {[}5.42, 12.29{]}).
+For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (\emph{b} = -3.48, 95\% CrI {[}-7.09, 0.16{]}).
+However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (\emph{b} = 15.35, 95\% CrI {[}8.64, 22.05{]}).
+The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.08{]}), prime exposure duration (\emph{b} = 0.01, 95\% CrI {[}-0.03, 0.06{]}), or their interaction (\emph{b} = -0.03, 95\% CrI {[}-0.12, 0.05{]}), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
 
@@
 \centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e2-words-1.pdf}
+\includegraphics{MaskedPriming_complete_mspg_files/figure-latex/deltas-e2-words-1.pdf}
 \caption{\label{fig:deltas-e2-words}Delta plots depicting the magnitude of the effect over time in Experiment 2.}

### 2021-11-03 previous revisions/data_analysis_brms_old.Rmd
Move old documents to different directory, make final Rmd and tex files

--- 2021-03-27 data_analysis_brms_updated.Rmd
@@
 
+blmm_exp1_acc <- brm(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
+                 formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
+                 warmup = 1000,
+                 iter = 5000,
+                 chains = 4,
+                 prior = prior_exp1,
+                 family = bernoulli(link = "logit"),
+                 inits = "random",
+                 control = list(adapt_delta = 0.95),
+                 cores = 4, backend = "cmdstanr", threads = threading(2))
+
+save(blmm_exp1_acc, file = "blmm_exp1_acc_new.RData")
+
+                 #blmm_exp1_full <- update(blmm_exp1,
+#                         warmup = 1000,
+#                         iter = 5000, 
+#                         chains = 4,
+#                         prior = prior_exp1,
+#                         family = exgaussian(),
+#                         inits = "random",
+#                         control = list(adapt_delta = 0.95),
+#                         cores = 4, 
+#                         backend = "cmdstanr", 
+#                         threads = threading(2))
+
+#save(blmm_exp2, file = "blmm_exp2.RData")
+
 blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
@@
 
-blmm_exp1_acc <- brm(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
-                 formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
-                 warmup = 1000,
-                 iter = 5000,
-                 chains = 4,
-                 prior = prior_exp1,
-                 family = bernoulli(link = "logit"),
-                 inits = "random",
-                 control = list(adapt_delta = 0.95),
-                 cores = 4, backend = "cmdstanr", threads = threading(2))
-
-save(blmm_exp1_acc, file = "blmm_exp1_acc_new.RData")
-
-### Experiment 2
-
-blmm_exp2_rt <- brm(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
-                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
-                        warmup = 1000,
-                        iter = 5000,
-                        chains = 4,
-                        prior = prior_exp1,
-                        family = exgaussian(),
-                        inits = "random",
-                        control = list(adapt_delta = 0.95),
-                        cores = 4, backend = "cmdstanr", threads = threading(2))
-
-save(blmm_exp2_rt, file = "blmm_exp2_rt_new.RData")
-
-blmm_exp2_acc <- brm(data = exp2_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
-                 formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
-                 warmup = 1000,
-                 iter = 5000,
-                 chains = 4,
-                 prior = prior_exp1,
-                 family = bernoulli(link = "logit"),
-                 inits = "random",
-                 control = list(adapt_delta = 0.95),
-                 cores = 4, backend = "cmdstanr", threads = threading(2))
-
-save(blmm_exp2_acc, file = "blmm_exp2_acc_new.RData")
-
 ```

### 2021-11-06 Appendix_A.tex

--- 2021-09-21 MaskedPriming_revision.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  english,
-  man,floatsintext]{apa6}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdfauthor={Bernhard Angele1,2, Ana Baciero2,3, Pablo Gómez4, \& Manuel Perea2,5},
-  pdflang={en-EN},
-  pdfkeywords={Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
-
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
-
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-\shorttitle{Online masked priming}
-\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 7916}
-\usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Does online masked priming pass the test?\\
-The effects of prime exposure duration on masked identity priming}
-\author{Bernhard Angele\textsuperscript{1,2}, Ana Baciero\textsuperscript{2,3}, Pablo Gómez\textsuperscript{4}, \& Manuel Perea\textsuperscript{2,5}}
-\date{}
-
-\note{
-
 \clearpage
 
-}
-
-\authornote{
-
-We thank Grace Backhouse for her help with data collection. The data for Experiment 1 were collected as part of her MSc dissertation.
-
-This research has been partly supported by Grant PSI2017-86210-P from the Spanish Ministry of Science and Innovation (MP), Grant PGC2018-097145-B-I00 from the Spanish State Research Agency (AB), and internal funding from Bournemouth University (BA).
-
-This study was pre-registered on the Open Science Framework (OSF) prior to data collection.
-The registration form for Experiment 1, together with the materials, data files, and R scripts can be found at {[}\url{https://osf.io/57rzq/}{]}.
-The registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}.
-
-Correspondence concerning this article should be addressed to Bernhard Angele, Department of Psychology, Faculty of Science and Technology, Talbot Campus, Fern Barrow, Poole BH12 5BB, UK.
-E-mail: \href{mailto:bangele@bournemouth.ac.uk}{\nolinkurl{bangele@bournemouth.ac.uk}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Bournemouth University, Bournemouth, UK\\\textsuperscript{2} Universidad Antonio de Nebrija, Madrid, Spain\\\textsuperscript{3} DePaul University, Chicago, USA\\\textsuperscript{4} California State University San Bernardino, Palm Desert Campus, USA\\\textsuperscript{5} Universitat de València, Valencia, Spain}
-
-\abstract{
-Masked priming is one of the most important paradigms in the study of visual word recognition, but it is usually thought to require a laboratory setup with a known monitor and keyboard.
-To test if this technique can be safely used in an online setting, we conducted two online masked priming lexical decision task experiments using PsychoPy/PsychoJS (Peirce et al., 2019).
-Importantly, we also tested the role of prime exposure duration (33.3 vs.~50 ms in Experiment 1 and 16.7 vs.~33.3 ms in Experiment 2), thus allowing us to examine both across conditions and within-conditions effects.
-We found that our online data are indeed very similar to the masked priming data previously reported in the masked priming literature.
-Additionally, we found a clear effect of prime duration, with the priming effect (measured in terms of response time and accuracy) being stronger at 50 ms than 33.3 ms and no priming effect at 16.7 ms prime duration.
-From these results, we can conclude that modern online browser-based experimental psychophysics packages (e.g., PsychoPy) can present stimuli and collect responses on standard end user devices with enough precision.
-These findings provide us with confidence that masked priming can be used online, thus allowing us not only to run less time-consuming experiments, but also to reach populations that are difficult to test in a laboratory.
-}
-
-\begin{document}
-\maketitle
-
-Masked priming (Forster \& Davis, 1984) is one of the most important techniques to study the effects of orthography, phonology, morphology, and meaning in visual word recognition (see Forster, 1998; Grainger, 2008, for reviews).
-Priming refers to the influence of a prime stimulus (e.g., \emph{nurse}, \emph{horse}) on a subsequently presented stimulus that the participant has to respond to (e.g., ``is \emph{DOCTOR} a word?'').
-Priming effects are measured as the difference in a dependent variable (e.g., response time {[}RT{]}) between two conditions (e.g., unrelated: \emph{horse-DOCTOR}; related: \emph{nurse-DOCTOR}).
-In masked priming, the prime stimulus is presented very briefly (for less than 60 ms) and is itself preceded by a pattern mask (e.g., \#\#\#\#\#) for a much longer duration (typically 500 ms).
-The rationale of the procedure is to make participants unaware of the identity of the masked prime (Forster, 1998; Forster \& Davis, 1984), thus minimizing the role of participants' strategies.
-Indeed, masked priming experiments do not show the strategical effects that occur with visible, unmasked primes (e.g., Grossi, 2006; Perea \& Rosa, 2002).
-
-The masked priming paradigm has been used in a large number of studies over the last decades.
-For instance, a search of the expression ``masked priming'' in Google Scholar in May 2021 produced more than 10,000 hits.
-Nearly all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by Forster and Forster (2003).
-The issue we examine in the present paper is whether masked priming experiments can be conducted in an online setting without significant changes in the pattern of results.
-Even before the exceptional situation due to the COVID pandemic in 2020-21, in which many labs around the world were closed (or reduced their activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc.
-Indeed, researchers in decision making and economics have been using online paradigms for several decades now (e.g., Birnbaum \& Birnbaum, 2000; Paolacci et al., 2010).
-
-Cognitive psychologists have been much slower that their behavioral economics colleagues in taking up online paradigms (see Brysbaert et al., 2016; Cai et al., 2017; Dufau et al., 2011; Eerland et al., 2013; Rodd et al., 2016, for some exceptions), often due to concerns about the validity of the results.
-Such concerns are not limited to cognitive studies (see Aust et al., 2013), but they are exacerbated by the reliance on precise presentation times in cognitive psychology.
-Furthermore, these concerns are even more central in the masked priming technique, where it is critical for the onset of the mask, the prime, and the target to occur at the nominal times.
-For instance, presenting the masked prime for longer than intended (e.g., 83 ms or longer instead of the nominal 50 ms) could counteract the effect of the mask, making the prime consciously visible to the participant and possibly altering the processes of interest (see Zimmerman \& Gomez, 2012).
-
-There have been attempts to address these concerns.
-Witzel et al.
-(2013) developed a Web version of DMDX (webDMDX) showing promising results in a trial experiment.
-However, webDMDX is a self-contained Windows executable file that participants have to download and run rather than a ``true'' online programming script that could be run inside of a browser.
-A downside of this format is that participants often are (and should be) understandably skeptical about downloading and running executable files from the Internet.
-Additionally, many participants may not have access to a Windows PC, or may be discouraged from participating by the extra work it takes to deploy the experiment on their computer.
-As a consequence, the use of webDMDX in masked priming experiments has been rather limited so far (see Alluhaybi \& Witzel, 2020; Dubey et al., 2018, for exceptions).
-
-Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web.
-Most notably, the HTML5 standard now makes it possible to use Javascript in order to draw stimuli interactively and monitor participant responses with remarkable flexibility inside the browser.
-Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets (Reimers \& Stewart, 2015).
-There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla (Anwyl-Irvine, Massonni, et al., 2020) or Testable (Rezlescu et al., 2020), and open-source such as jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of PsychoPy 3, Peirce et al., 2019).
-In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds.
-Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility of recruiting participants for on-line experiments based on various specific characteristics set up by the experimenters regardless of their location (e.g., native French speakers, not older than 30 years old, not currently in college).
-
-Of course, despite the technological advances, many cognitive psychologists still have concerns about timing and measurement precision.
-While Javascript-based experiments run on the participants' devices and thereby avoid any lag due to connection issues (e.g., to avoid delays, all stimuli are usually downloaded before the start of the experiment), experimenters have little control over which devices the experiment is run on beyond the option of explicitly preventing the experiment to run on specific device types such as mobile devices.
-Moreover, experimenters have no control at all over what other applications are running on the device, screen size and resolution, viewing distance, properties of the keyboard/touchscreen, etc., as all of these are determined by the device or the participants' preferences.
-As Reimers and Stewart (2015) pointed out, there are two ways of testing whether timing and response issues are problematic: (1) comparing a Web-based experiment directly with an established lab-based version by measuring presentation timings (using a photodiode) and response timings on various device configurations and (2) attempting to replicate existing lab-based findings using a Web-based paradigm.
-If the results of the Web-based study are comparable to previous lab-based results, this suggests that, whatever the deviations in stimulus and response timing are, they are not severe enough to affect the overall findings in the paradigm in question.
-
-The first approach has the advantage that differences in presentation timings can be objectively recorded and evaluated.
-A very thorough recent example of this approach is the ``timing mega-study'' by Bridges et al.
-(2020), who compared the timing in experiments run in lab-based setups with the timing in online packages run in different browsers.
-The very similar study by Anwyl-Irvine, Dalmaijer, et al.
-(2020) compares only online packages and browsers with regard to timing.
-Overall, Bridges et al.
-(2020) found that online packages were capable of presenting visual stimuli with reasonable precision, although the lab-based packages were slightly better in this regard.
-This first approach is important in order to establish that a certain level of precision and accuracy can be achieved at all.
-If this is not possible, there is no point in moving forward to the second approach and replicating specific paradigms.
-However, it is of course impossible to test every possible device and configuration that participants might use.
-On the other hand, some of the differences in precision and accuracy between setups that can be observed using a photodiode may be too small to have an influence on actual participant performance.
-Therefore, we consider replication of previous key lab-based effects a more important test of online paradigms than photodiode measurements.
-Based on the results by Bridges et al.
-(2020) and Anwyl-Irvine, Dalmaijer, et al.
-(2020), modern Javascript-based stimulus presentation systems are capable of sufficiently fast and precise stimulus presentation.
-To establish whether masked priming studies can be successfully run online, the next step is now to follow the second approach and implement the masked priming paradigm online and test whether results obtained via in-lab studies can be replicated, which is at the heart of the present study.
-Importantly, we will do so using PsychoPy/PsychoJS (Peirce et al., 2019) as it showed high precision and accuracy across the great majority of platforms (Anwyl-Irvine, Dalmaijer, et al., 2020; Bridges et al., 2020), in addition to being an open-source software.
-
-Specifically, in this study we were interested in whether we could replicate and extend a key phenomenon in laboratory masked priming lexical decision using an online setup: masked identity priming is commonly described as a savings effect.
-As first suggested by Forster (1998), for a masked identity prime, ``the lexical entry is already in the process of being opened, and hence the evaluation of this entry begins sooner,'' whereas for an unrelated prime, ``the entry for the target word would be closed down (since it fails to match the prime), and no savings would occur'' (p.~213).
-Thus, according to the savings account, a target word like \emph{DOCTOR} would enjoy an encoding advantage when preceded by an identity prime such as \emph{doctor} than when preceded by an unrelated prime such as \emph{pencil} (i.e., a head-start).
-One implication of such benefit is that the RT distributions of the unrelated and identity pairs should reflect a shift rather than a change in shape.
-Furthermore, this shift should be approximately similar in magnitude to the prime-target stimulus-onset asynchrony (SOA).
-Empirical evidence supporting this view has been obtained in several studies not only with skilled adults but also with developing readers (e.g., Gomez et al., 2013; Gomez \& Perea, 2020; Taikh \& Lupker, 2020; Yang et al., 2021).
-Gomez et al.
-(2013) proposed an implementation of this hypothesis within the diffusion model (Ratcliff et al., 2004).
-This implementation proposes that, when making a two-choice decision, the resultant RT can be explained as the sum of non-decision parameters, which are the encoding time and response execution (\(T_{er}\)) and decision parameters, which refer to the process of accumulation of information until a decision criteria is reached.
-Importantly, in the decision process, the information gathered from the stimulus can vary in noise, depending on its quality, which modifies the rate at which information is accumulated (i.e., the \emph{drift rate}).
-With regards to RTs from masked priming tasks, Gomez et al.
-(2013) found that the difference between identity and unrelated conditions could be accounted for by a change in the \(T_{er}\) parameter, while there were no differences across conditions in the parameter that corresponds to the quality of evidence gathered (i.e., drift rate)--note that changes in drift rate would necessarily produce a more skewed RT distribution in the slower, unrelated condition.
-
-Critically, the above pattern is specific to \emph{masked} priming.
-In fact, the most common pattern of results in latency based tasks is that conditions that produce longer latencies will also produce larger variance.
-This pattern is evident in priming as well---when primes are visible (i.e., unmasked priming), identity priming effects are stronger in the upper quantiles of the RT distribution than in the lower quantiles (i.e., a change in shape rather than a shift in RT distributions; see Gomez et al., 2013).
-Fits from the diffusion model show that this result corresponds to changes in both the \(T_{er}\) parameter and the drift rate.
-Hence, when the prime is visible, it does influence the quality of the information accumulated of the target word, unlike in masked priming.
-Clearly, this dissociation between masked and unmasked priming reflects qualitative differences in the way primes affect the processing of the target: purely encoding in masked priming (with an expected effect close to the prime duration) vs.~both encoding and information quality in unmasked priming.
-
-In the present paper, we took advantage of the above marker to examine whether online masked priming studies follow the same pattern as in-lab masked priming studies.
-Specifically, we manipulated prime exposure duration in identity vs.~unrelated primes: 33.3 vs.~50 ms in Experiment 1, and 16.7 vs.~33.3 ms in Experiment 2---note that targets were presented immediately after the primes (i.e., prime exposure duration was equal to the prime-target SOA).
-The rationale of Experiment 1 is that if the actual exposure duration of the primes is the nominal exposure duration, then we would expect the typical shift between the identity and unrelated response time distributions, which according to the savings hypothesis (Forster, 1998) would be greater for 50 ms than for 33.3 ms exposure duration (i.e., the head-start would be greater for 50 ms identity primes than for 33.3 ms identity primes).
-This outcome would indicate that the on-line masked priming studies reproduce a characteristic signature of laboratory masked priming studies.
-Alternatively, if the online presentation conditions lead to a greater actual exposure duration on the participant's device compared to that specified in our experiment (e.g.,if prime durations were, on average, 20 ms longer than intended), then the 50 ms primes may no longer be adequately masked, but may rather be consciously perceived.
-If this is the case, the prime could affect not only the encoding, but also core decision processes (i.e., the drift rate), which would be reflected as a stronger priming effect in the higher quantiles of the distribution (i.e., the two RT distributions would have a different shape).
-In this scenario, one should be very cautious when running online masked priming experiments---at least with the typical software and hardware currently available.
-
-To further constrain the research questions, Experiment 2 was designed to be analogous to Experiment 1, except for replacing the 50 ms prime exposure duration with a very short prime exposure duration, namely, 16.7 ms.
-Similar extremely brief prime exposure durations have shown very weak masked priming lexical decision experiments in a laboratory setting: less than 5 ms for a prime duration of 14 ms (Ziegler et al., 2000) and less than 9 ms for a prime duration of 20 ms (Tzur \& Frost, 2007)---in the Tzur and Frost (2007) experiment, this difference increased to 16.7 ms when using a very high level of contrast in the computer screen.
-Thus, if the size of the priming effect is roughly similar to the prime exposure duration, we would expect a much larger priming effect at the 33.3 ms prime exposure duration than at the 16.7 ms prime exposure duration.
-If we do observe a large effect at the 16.7 ms prime exposure duration (e.g., above 20-25 ms), this would suggest, again, that there is a qualitative difference between using the masked priming technique in the laboratory and in online experiments.
-Keep in mind that we are using a software that has very good control over the exposure duration (Anwyl-Irvine, Dalmaijer, et al., 2020; Bridges et al., 2020).
-Figure \ref{fig:hyp-mod-dat-figure} displays the link between all these verbal hypotheses, the process model that corresponds to each of them, and their predictions in the RT distributions.
-
-All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli (e.g., Parker et al., 2021).
-This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms (e.g., Aguasvivas et al., 2020; Brysbaert et al., 2021; Brysbaert et al., 2016; Mandera et al., 2020).
-So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries (e.g., Adelman et al., 2014).
-Importantly, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.~unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) (see Jacobs et al., 1995; Ziegler et al., 2000, for advantages of within-condition comparisons).
-Thus, the within-subject manipulation of prime exposure duration in both experiments allows us to obtain a comprehensive picture of masked identity priming effects--also including the examination of potential inhibitory effects of unrelated primes.
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/hyp-mod-dat-figure-1.pdf}
-\caption{\label{fig:hyp-mod-dat-figure}Mapping from hypotheses to data via evidence accumulation models.
-The bottom part of each graph represents sample paths, and the top part shows the cumulative density functions.
-From left to right: \emph{Null Effect} - there are no differences between the conditions; \emph{Effect in Encoding} - the difference between the conditions is on the encoding time, hence the RT distributions are shifted; and \emph{Effect of Encoding and Evidence Accumulation} - the differences between the conditions is on the rate of evidence accumulation, thus increasing the effect size for longer RTs (right-tail of the distribution).}
-\end{figure}
-
-\hypertarget{experiment-1}{%
-\section{Experiment 1}\label{experiment-1}}
-
-In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33.3 ms and 50 ms (roughly corresponding to two and three frames, respectively, at a refresh rate of 60 Hz).
-
-We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the two experiments.
-
-\hypertarget{method}{%
-\subsection{Method}\label{method}}
-
-The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at \url{https://osf.io/57rzq/}.
-
-\hypertarget{participants}{%
-\subsubsection{Participants}\label{participants}}
-
-Participants were recruited through Prolific (www.prolific.co, 2021).
-The experiment was accessed by 101 participants.
-Out of these, 89 provided experimental data.
-Two of these participants did not complete the experiment.
-A further ten were excluded because of low accuracy (less than .8, which was the pre-registered criterion).
-In the end, we analyzed the data from 77 participants (36 female), aged from 18 to 71 (mean age: 31.14).
-All these participants indicated that English was their first language in the Prolific screening questions.
-Based on their IP addresses, 47 participants were based in the UK, 23 were based in the US, three participants were based in Canada, and two participants were based in Ireland.
-Two participants could not be localized in this way.
-All participants were naïve to the purpose of the experiment and received £1.25 for their participation (corresponding to £5/hour).
-Participants could use either a desktop/laptop computer or a mobile device.
-Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
-
-\textbf{\emph{Rationale for sample size and stopping rule.}} Brysbaert and Stevens (2018) recommended that masked priming experiments should have at least 1,600 observations per condition.
-In order to account for potentially smaller effect sizes in an online experiment, we set a target of 3,000 observations per condition (12,000 observations total), which corresponds to a minimum of 50 participants given that there were 240 word stimuli in the experiment (see below).
-Our stopping rule was to keep collecting data until 3,000 valid observations were found.
-This goal was met and exceeded in our initial data collection with a budget of £200.
-
-\hypertarget{materials}{%
-\subsubsection{Materials}\label{materials}}
-
-We selected 240 six-letter English words from the English Lexicon Project (Balota et al., 2007).
-The mean Zipf frequency based on the HAL corpus (Lund \& Burgess, 1996) was 3.8 (range: 1.9--5.5).
-The mean OLD20 (Yarkoni et al., 2008) was 2.1 (range: 1.4--3).
-We also selected 240 matched, orthographically legal six-letter nonwords.
-For each target, we created an identical prime (e.g.~\emph{region --- REGION} and \emph{fainch --- FAINCH}) and an unrelated prime consisting of another word from the list (e.g.~\emph{launch --- REGION} and \emph{miluer --- FAINCH})\footnote{Note that the lexical status of the unrelated prime differed depending on the target type: for word targets, the unrelated primes were words, whereas for nonword targets, they were pseudowords.
-However, as shown by Fernández-López et al.
-(2019), the lexical status of the unrelated prime does not affect lexical decision times.}.Unrelated primes were orthographically were paired with the targets by rearranging the order of identity primes (controling for neighbors; see Perea et al.
-(2018)).
-Appendix A contains a list of the target items, and all counterbalanced lists can be found in the on-line repository.
-
-\hypertarget{procedure}{%
-\subsubsection{Procedure}\label{procedure}}
-
-Participants were able to sign up for the experiment on the Prolific website.
-Upon signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment (Qualtrics, 2020).
-After indicating their agreement to participate, participants were forwarded to Pavlovia (Pavlovia, 2020), where the actual lexical decision task was implemented in PsychoJS.
-In the experiment, all stimuli were presented in the center of the screen in black Courier New font on a white background.
-As we do not know the exact dimensions of each participant's screen, all stimulus sizes and positions were defined in PsychoPy's ``height'' units, with the bottom left of a 16:10 aspect ratio screen being represented as (-.8, -.5) and the top right being (.8, .5).
-The height for all text stimuli was 0.1 units.
-Each trial began with a six-character pattern mask (\emph{\#\#\#\#\#\#}) set to be presented for 500 ms, followed first by the lowercase prime (e.g.~\emph{region}) set to be presented for either 33.3 or 50 ms, and then by the uppercase target (e.g.~\emph{REGION}).
-Participants were instructed to respond to the target stimulus as quickly as possible by pressing the ``Z'' key of their keyboard (if their device had one) if the target was not a valid English word or the ``M'' key if the target was a valid English word.
-Participants on a device without a keyboard were instructed to respond by touching one of two rectangular touch areas labeled ``Z = Non-word'' (presented at -0.4, -0.3) and ``M = Word'' (presented at 0.4, -0.3).
-The touch areas each had a width of 0.4 and a height of 0.2 and were presented in white with a black outline.
-If participants did not respond within two seconds of the target onset, a ``Too slow!'' feedback message was shown for 500 ms and the trial ended.
-The experimental trials were preceded by 16 practice trials during which participants also received feedback on the accuracy of their responses.
-No feedback apart from the trial timeout feedback was given during the experimental trials.
-Every 120 trials, participants were asked to take a short break before continuing the experiment.
-After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.
-
-\hypertarget{data-analysis}{%
-\subsubsection{Data analysis}\label{data-analysis}}
-
-We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.10.5; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.7; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.3; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.3; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.25; Xie, 2021).}.
-We only analyzed trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as incorrect responses (5.84 \% of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.36 \% of trials).
-For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.~identical) and prime duration (33.3 ms vs.~50 ms) as well as their interaction as the fixed effects.
-For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -0.5 and unrelated was coded as 0.5.
-For priming duration, 33.3 ms was coded as -0.5 and 50 ms was coded as 0.5.
-We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items.
-We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component \(\mu\) and the scale parameter of the exponential component \(\beta\) (equaling the inverse of the rate parameter \(\lambda\)) being allowed to vary between conditions.
-To model response accuracy, we used the Bernoulli distribution with a logit link.
-We used the default priors suggested by \emph{brms} except for the coefficients for the fixed effects, for which we applied weakly informative priors of \(\beta \sim N(0,100)\) in order to rule out improbably large effect sizes.
-Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warm-up iterations for the accuracy models).
-We consider an effect as credible if the 95\% Credible Interval (CrI) estimated from the posterior distribution does not contain zero.
-In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.
-
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table \ref{tab:exp1-descriptive-rt-table} (although note that we only analyzed the word trials).
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp1-descriptive-rt-table}Mean, Median, Standard Deviation (SD), range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 1 for each condition.}
-
-\begin{tabular}{lllllllll}
-\toprule
-Stimulus Type & \multicolumn{1}{c}{Prime Duration} & \multicolumn{1}{c}{Relatedness} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Accuracy}\\
-\midrule
-Nonword & 33.3 ms & Identity & 700 & 665 & 187 & 263 & 1,776 & 0.91\\
-Nonword & 33.3 ms & Unrelated & 702 & 664 & 188 & 256 & 1,770 & 0.92\\
-Nonword & 50 ms & Identity & 700 & 658 & 189 & 256 & 1,760 & 0.91\\
-Nonword & 50 ms & Unrelated & 699 & 657 & 185 & 251 & 1,796 & 0.93\\
-Word & 33.3 ms & Identity & 630 & 599 & 164 & 254 & 1,796 & 0.94\\
-Word & 33.3 ms & Unrelated & 652 & 619 & 166 & 254 & 1,783 & 0.93\\
-Word & 50 ms & Identity & 608 & 575 & 161 & 265 & 1,784 & 0.96\\
-Word & 50 ms & Unrelated & 649 & 620 & 158 & 294 & 1,710 & 0.93\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\newpage
-
-\hypertarget{response-times}{%
-\subsubsection{Response times}\label{response-times}}
-
-Table \ref{tab:exp1-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-The RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 31.55, 95\% CrI {[}27.16, 35.92{]}), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (\emph{b} = -10.96, 95\% CrI {[}-14.83, -7.11{]}).
-The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = 19.31, 95\% CrI {[}11.39, 27.09{]}).
-The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.07{]}).
-However, the 50 ms prime exposure duration seems to be associated with a slightly lower \(\beta\), i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (\emph{b} = -0.07, 95\% CrI {[}-0.12, -0.03{]}).
-On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (\emph{b} = 0.03, 95\% CrI {[}-0.05, 0.12{]}).
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp1-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for correct word RTs in Experiment 1.}
-
-\small{
-
-\begin{tabular}{cccccc}
-\toprule
-Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
-\midrule
-Intercept ($\mu$) & 633.707 & 8.815 & 617.142 & 651.175 & 1.006\\
-Intercept ($\beta$) & 4.686 & 0.042 & 4.601 & 4.768 & 1.001\\
-Relatedness ($\mu$) & 31.551 & 2.228 & 27.162 & 35.915 & 1.000\\
-Prime Duration ($\mu$) & -10.959 & 1.947 & -14.825 & -7.105 & 1.000\\
-Relatedness:Prime Duration ($\mu$) & 19.306 & 4.026 & 11.388 & 27.094 & 1.000\\
-Relatedness ($\beta$) & 0.031 & 0.022 & -0.011 & 0.073 & 1.000\\
-Prime Duration ($\beta$) & -0.074 & 0.024 & -0.120 & -0.028 & 1.000\\
-Relatedness:Prime Duration ($\beta$) & 0.031 & 0.042 & -0.051 & 0.115 & 1.000\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $\beta$ is the scale parameter (the inverse of the rate parameter $\lambda$) of the ex-Gaussian distribution.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-These results can be visualized in the delta plots depicted in Figure \ref{fig:deltas-e1-words}.
-Delta plots are residual quantile plots that show the distributional differences between conditions (see De Jong et al., 1994).
-As can be seen in Panel A, there is an identity priming effect (computed as the difference in response times between responses to the unrelated condition and responses to the identity condition) of a parallel magnitude across all quantiles for both the 33.3 ms and the 50 ms prime durations, and the effect size is greater for the 50 ms prime duration condition than for the 33.3 ms one.
-We also found a slight increase of priming effects for the longest responses (quantile .9) in the 33.3 ms prime duration condition.
-This apparent anomaly can be understood better by looking at Panel B of the same figure.
-In this panel, we show the size of the prime duration effect (computed as the difference in response times between responses to the 50 ms condition and responses to the 33.3 ms condition) across RT quantiles.
-While the identity condition produced a shift in the distributions of response times (i.e., the difference between conditions is constant across quantiles), the unrelated condition yielded virtually the same response times in the 33.3 and 50 ms conditions, except for a small increase at the 50 ms prime duration for the very long responses (i.e., .9 quantile)--we prefer not to over-interpret this latter finding with the slowest responses, as it did not appear in Experiment 2.
-
-\begin{figure}
-\centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e1-words-1.pdf}
-\caption{\label{fig:deltas-e1-words}Delta plots depicting the magnitude of the effect over time in Experiment 1.
-Each dot represents the mean RT at the .1, .3, .5, .7 and .9 quantiles.
-\emph{Panel A)} Difference in RT between unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right).
-\emph{Panel B)} Difference in RT between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions.}
-\end{figure}
-
-\hypertarget{accuracy}{%
-\subsubsection{Accuracy}\label{accuracy}}
-
-Table \ref{tab:exp1-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.50, 95\% CrI {[}-0.72, -0.31{]}).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = 0.19, 95\% CrI {[}-0.02, 0.42{]}).
-The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = -0.53, 95\% CrI {[}-0.94, -0.14{]}).
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp1-acc-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for response accuracy on word trials in Experiment 1.}
-
-\small{
-
-\begin{tabular}{cccccc}
-\toprule
-Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
-\midrule
-Intercept & 3.458 & 0.122 & 3.224 & 3.705 & 1.000\\
-Relatedness & -0.503 & 0.105 & -0.720 & -0.305 & 1.000\\
-Prime Duration & 0.192 & 0.110 & -0.016 & 0.417 & 1.000\\
-Relatedness:Prime Duration & -0.530 & 0.206 & -0.944 & -0.138 & 1.000\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
-
-The results from Experiment 1 reveal that we were able to replicate benchmark masked priming effects using an online experiment.
-The size and shape of the effect is similar to that observed in previous studies (e.g., Gomez et al., 2013; Perea et al., 2018; Taikh \& Lupker, 2020; Yang et al., 2021).
-In addition, we also saw a clear difference between the 33.3 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices.
-While the shape of the distribution changed slightly between the 33.3 ms and the 50 ms prime exposure durations, we did not observe an effect of the prime relatedness condition on the shape parameter \(\beta\) of the exponential distribution, suggesting, according to the savings hypothesis by Forster (1998), that only encoding processes were affected by the relatedness manipulation.
-Moreover, as can be observed in Figure \ref{fig:deltas-e1-words}, the effect magnitude was close to the stimulus-onset asynchrony (see also Perea et al., 2018).
-
-Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different.
-Indeed, to better define the priming effect, one needs a baseline that serves as a reference point (i.e., an analog of the minimum {``intensity''} priming condition; see Jacobs et al., 1995).
-In order to further explore this question, we performed a second experiment in which we set the prime to be displayed for an even shorter duration.
-As described in the Introduction, a 16.7 ms prime exposure duration should yield a negligible priming effect (Tzur \& Frost, 2007; Ziegler et al., 2000) so the pattern should be qualitatively different from the 33.3 and 50 ms durations used in Experiment 1.
-If it does not, this would cast doubt on the timing accuracy in online experiments.
-In this experiment, we also include the 33.3 ms prime duration condition to not only have a better scheme to compare the two experiments, but also to be able to test the within-condition effects (Jacobs et al., 1995)---assuming the 16.7 ms prime duration serves as a baseline.
-
-\hypertarget{experiment-2}{%
-\section{Experiment 2}\label{experiment-2}}
-
-In the second experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 16.7 ms and 33.3 ms (roughly corresponding to one and two frames at a refresh rate of 60 Hz).
-
-The pre-registration form for Experiment 2 can be found at {[}\url{https://osf.io/957s8}{]}. The materials, data files, and R scripts can be found at {[}\url{https://osf.io/57rzq/}{]}
-
-\hypertarget{method-1}{%
-\subsection{Method}\label{method-1}}
-
-\hypertarget{participants-1}{%
-\subsubsection{Participants}\label{participants-1}}
-
-As in Experiment 1, participants were recruited through Prolific (www.prolific.co, 2021).
-The experiment was accessed by 102 participants.
-Out of these, 87 provided experimental data.
-One of these participants did not complete the experiment.
-A further seven were excluded because of low accuracy (again, less than .8).
-The remaining 79 participants were aged from 18 to 69 (mean age: 31.14).
-Of the participants, 40 identified as male, and 39 identified as female.
-All these participants indicated that English was their first language in the Prolific screening questions.
-Based on their IP addresses, 56 participants were based in the UK, 14 were based in the US, two participants were based in Canada, two participants were based in South Africa, and one participant each was based in Hungary and Ireland.
-Three participants could not be localized in this way.
-As in Experiment 1, all participants were naïve to the purpose of the experiment, and received £1.25 for their participation (corresponding to £5/hour).
-Participants could use either a desktop/laptop computer or a mobile device.
-Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.
-
-\textbf{\emph{Rationale for sample size and stopping rule.}} As in Experiment 1, our stopping rule was to keep collecting data until 3,000 valid observations were collected.
-This goal was met and exceeded in our initial data collection with a budget of £200.
-
-\hypertarget{materials-1}{%
-\subsubsection{Materials}\label{materials-1}}
-
-The materials were identical to those used in Experiment 1.
-
-\hypertarget{procedure-1}{%
-\subsubsection{Procedure}\label{procedure-1}}
-
-The procedure was identical to Experiment 1, the only difference being that the primes were set to be displayed for either 16.7 ms or 33.3 ms.
-
-\hypertarget{data-analysis-1}{%
-\subsubsection{Data analysis}\label{data-analysis-1}}
-
-We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word.
-For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as those with incorrect responses (4.93 \% of trials).
-For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.15 \% of trials).
-For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5.
-Otherwise, the model specifications were identical to those in Experiment 1.
-
-\hypertarget{results-1}{%
-\subsection{Results}\label{results-1}}
-
-Descriptive statistics for RTs and accuracy in all the experimental conditions are reported in Table \ref{tab:exp2-descriptive-rt-table}.
-
-\hypertarget{response-times-1}{%
-\subsubsection{Response times}\label{response-times-1}}
-
-As in Experiment 1, the RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 8.53, 95\% CrI {[}5.07, 12.11{]}).
-For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (\emph{b} = -3.60, 95\% CrI {[}-7.22, -0.03{]}).
-However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (\emph{b} = 15.17, 95\% CrI {[}8.52, 21.73{]}).
-The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.02, 0.07{]}), prime exposure duration (\emph{b} = 0.01, 95\% CrI {[}-0.03, 0.05{]}), or their interaction (\emph{b} = -0.03, 95\% CrI {[}-0.12, 0.05{]}), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.
-
-Table \ref{tab:exp2-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the RT model, as well as the \(\hat{R}\) for each estimate, which indicate that the model was fitted successfully as they are all close to 1.
-
-\newpage
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp2-descriptive-rt-table}Mean, Median, Standard Deviation (SD), and range of correct RTs (in ms) and Accuracy (proportion of all responses) in Experiment 2 for all conditions.}
-
-\begin{tabular}{lllllllll}
-\toprule
-Stimulus Type & \multicolumn{1}{c}{Prime Duration} & \multicolumn{1}{c}{Relatedness} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Accuracy}\\
-\midrule
-Nonword & 16.7 ms & Identity & 719 & 680 & 185 & 330 & 1,787 & 0.93\\
-Nonword & 16.7 ms & Unrelated & 717 & 677 & 183 & 284 & 1,799 & 0.94\\
-Nonword & 33.3 ms & Identity & 717 & 668 & 193 & 351 & 1,787 & 0.94\\
-Nonword & 33.3 ms & Unrelated & 715 & 672 & 188 & 281 & 1,789 & 0.94\\
-Word & 16.7 ms & Identity & 659 & 625 & 160 & 311 & 1,785 & 0.94\\
-Word & 16.7 ms & Unrelated & 661 & 623 & 165 & 308 & 1,796 & 0.95\\
-Word & 33.3 ms & Identity & 649 & 618 & 154 & 280 & 1,657 & 0.96\\
-Word & 33.3 ms & Unrelated & 667 & 633 & 162 & 269 & 1,701 & 0.94\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp2-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for the fixed effects of the model fitted for correct word RTs in Experiment 2.}
-
-\small{
-
-\begin{tabular}{cccccc}
-\toprule
-Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
-\midrule
-Intercept ($\mu$) & 656.975 & 9.036 & 639.056 & 674.711 & 1.003\\
-Intercept ($\beta$) & 4.658 & 0.043 & 4.573 & 4.741 & 1.003\\
-Relatedness ($\mu$) & 8.529 & 1.795 & 5.065 & 12.106 & 1.000\\
-Prime Duration ($\mu$) & -3.602 & 1.813 & -7.216 & -0.033 & 1.000\\
-Relatedness:Prime Duration ($\mu$) & 15.166 & 3.390 & 8.517 & 21.727 & 1.000\\
-Relatedness ($\beta$) & 0.028 & 0.023 & -0.016 & 0.073 & 1.000\\
-Prime Duration ($\beta$) & 0.011 & 0.021 & -0.031 & 0.053 & 1.000\\
-Relatedness:Prime Duration ($\beta$) & -0.034 & 0.043 & -0.119 & 0.049 & 1.000\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $\beta$ is the scale parameter (the inverse of the rate parameter $\lambda$) of the ex-Gaussian distribution.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-We also created the delta plots of data from Experiment 2 (see Figure \ref{fig:deltas-e2-words}).
-Panel A, shows there is no priming effect for the 16.7 ms condition, in contrast with a consistent effect across quantiles for the 33.3 ms condition (parallel to the one found in Experiment 1).
-Interestingly, when examining the delta plots for the prime duration effect, we can observe a slight facilitation for identity primes, together with a slight hindering for unrelated primes.
-
-\begin{figure}
-\centering
-\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e2-words-1.pdf}
-\caption{\label{fig:deltas-e2-words}Delta plots depicting the magnitude of the effect over time in Experiment 2.}
-\end{figure}
-
-\hypertarget{accuracy-1}{%
-\subsubsection{Accuracy}\label{accuracy-1}}
-
-The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.22, 95\% CrI {[}-0.43, 0.00{]}).
-The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16.7 ms prime duration condition than in the 33.3 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = -0.05, 95\% CrI {[}-0.31, 0.18{]}).
-The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33.3 ms condition, and reversed in the 16.7 ms condition (\emph{b} = -0.71, 95\% CrI {[}-1.16, -0.30{]}), although the effect in the 16.7 ms condition was very weak.
-Table \ref{tab:exp2-acc-blmm-table} shows the mean, standard error, lower and upper bounds of the 95\% CrI of the estimate of each fixed effect in the accuracy model, as well as the \(\hat{R}\) for each estimate, indicating that the model was fitted successfully as they are all close to 1.
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp2-acc-blmm-table}Posterior Mean, Standard Error (SE), 95\% CrI and \(\hat{R}\) for fixed effects of the model fitted for response accuracy on word trials in Experiment 2.}
-
-\small{
-
-\begin{tabular}{cccccc}
-\toprule
-Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
-\midrule
-Intercept & 3.734 & 0.135 & 3.476 & 4.007 & 1.000\\
-Relatedness & -0.217 & 0.109 & -0.434 & -0.004 & 1.000\\
-Prime Duration & -0.055 & 0.126 & -0.306 & 0.184 & 1.000\\
-Relatedness:Prime Duration & -0.710 & 0.218 & -1.157 & -0.305 & 1.000\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{discussion-1}{%
-\subsection{Discussion}\label{discussion-1}}
-
-In Experiment 2, we found the pattern we expected from previous research: In the mean \(\mu\) of the Gaussian component of the ex-Gaussian distribution, we observed a robust identity priming effect in response time and accuracy in the 33.3 ms prime duration, but a very weak effect in the 16.7 ms prime duration (Tzur \& Frost, 2007; Ziegler et al., 2000).
-This outcome suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.
-In addition, we did not observe an effect of the prime relatedness on the shape parameter \(\beta\) of the exponential component (i.e., the effect corresponded to a shift of the RT distributions, as shown in in-lab studies; e.g., Taikh \& Lupker, 2020; Yang et al., 2021).
-Moreover, the magnitude of the priming effect at the 33.3 ms prime exposure duration was close to the magnitude of the prime-target stimulus-onset asynchrony, as can be seen in the delta plots in Figure \ref{fig:deltas-e2-words} (see Gomez et al., 2013; Perea et al., 2018).
-Hence, we replicated again the commonly observed savings effect (Forster, 1998).
-
-Critically, because the 16.7 ms prime duration condition yielded virtually no priming effects, this very short prime exposure duration serves as a within-condition baseline that allows us to qualify the facilitative vs.~inhibitory nature of masked priming effects (Jacobs et al., 1995; Ziegler et al., 2000).
-Specifically, when compared to the baseline, our findings at the 33.3 ms prime duration show a combination of a slight facilitatory effect for identity primes and a small inhibitory effect for unrelated primes.
-
-\hypertarget{general-discussion}{%
-\section{General Discussion}\label{general-discussion}}
-
-In this study, we set out to test whether we could obtain benchmark masked priming effects both qualitatively (i.e., shift in the RT distributions) and quantitatively (i.e., effect sizes) using an online, browser-based experiment software.
-To that end, we conducted two online masked identity priming experiments (e.g., \emph{region --- REGION} vs.~\emph{launch --- REGION}) in which we manipulated prime exposure duration (33.3 vs.~50 ms in Experiment 1; 16.7 vs.~33 ms in Experiment 2).
-The results of our online-based experiments replicated and extended benchmarks masked identity priming effects previous in the lab-based studies.
-We observed the effect sizes predicted by Forster's (1998) savings hypothesis: Our data show a shift in the mean of the Gaussian component of the ex-Gaussian distribution, but no change in the shape parameter \(\beta\) of the exponential component, suggesting that our priming manipulations affected --- as intended --- encoding processes, but not conscious decision-making processes.
-Furthermore, the size of the priming effect was not only directly influenced by the prime duration, suggesting the experimental software was able to control the display timing of the prime accurately, but also of a similar magnitude to the prime duration (within the range reported in previous studies, e.g., 35-47 ms for a 50 ms prime duration in Perea et al., 2018).
-Importantly, the use of a within-condition baseline revealed that the identity priming effects at the 33 ms prime exposure duration were a combination of some small facilitation from identity primes and some small inhibition from unrelated primes (see Jacobs et al., 1995, for evidence with a psychophysical experiment).
-Likewise, the greater identity priming effects at the 50 ms rather than at the 33.3 ms prime exposure duration were essentially due to the facilitation from the identity pairs.
-
-While accurate display timings are expected in a laboratory-based experiment, where the equipment is known and can be measured, they are much less certain in a situation where the experiment runs on a participant's own device, which could be any of a wide variety of consumer devices including Windows PCs, Macs, tablets, and mobile phones sold in the last decade.
-Similarly, unlike in-lab conditions, where the contrast of the computer screens can be measured and kept constant, there is no such a guarantee for the screens used by online participants---note that Tzur and Frost (2007) were only able to observe strong effects for short prime exposure durations when using extreme contrast values.
-Thus, the fact that we can observe results that very closely resemble lab results demonstrates the sophistication in modern browsers' Javascript performance, including browsers on mobile devices, as well as the quality of the Javascript implementation of PsychoPy, PsychoJS.
-
-Furthermore, our results extend previous work showing the validity of on-line studies measuring response times (e.g., Brysbaert et al., 2016; Cai et al., 2017; Dufau et al., 2011; Eerland et al., 2013; Rodd et al., 2016, to cite a few instances) to the masked priming technique.
-Thus, the present study opens the door to a wider use of online experiments in cognitive research, especially in reaction-time sensitive fields like word recognition.
-Not only does this enable researchers to continue collecting data in times of social distancing, but it also makes it possible to collect data from a larger population than previously possible.
-For instance, online participants can be people from different countries and/or cultures, from different age groups, bilinguals/multilinguals, even those who do not own a computer, only a smartphone.
-Using a Javascript-based experiment software, anyone with a smartphone can be an experiment participant.
-This opens up the possibility of masked-priming crowdsourced megastudies.
-In general, deploying masked priming experiments online also means that data can be collected very quickly and efficiently, allowing research to progress more rapidly.
-
-In conclusion, our results give us confidence that high-quality behavioral data using the masked priming paradigm can be collected online using Javascript-based experiment platforms.
-We hope that future research takes advantage of these new methods in order to make research faster, more inclusive, and more efficient.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-adelman2014}{}%
-Adelman, J.
-S., Johnson, R.
-L., McCormick, S.
-F., McKague, M., Kinoshita, S., Bowers, J.
-S., Perry, J.
-R., Lupker, S.
-J., Forster, K.
-I., Cortese, M.
-J., Scaltritti, M., Aschenbrenner, A.
-J., Coane, J.
-H., White, L., Yap, M.
-J., Davis, C., Kim, J., \& Davis, C.
-J.
-(2014).
-A behavioral database for masked form priming.
-\emph{Behavior Research Methods}, \emph{46}(4), 1052--1067.
-\url{https://doi.org/10.3758/s13428-013-0442-y}
-
-\leavevmode\hypertarget{ref-aguasvivas2020}{}%
-Aguasvivas, J., Carreiras, M., Brysbaert, M., Mandera, P., Keuleers, E., \& Duñabeitia, J.
-A.
-(2020).
-How do Spanish speakers read words?
-Insights from a crowdsourced lexical decision megastudy.
-\emph{Behavior Research Methods}, \emph{52}(5), 1867--1882.
-\url{https://doi.org/10.3758/s13428-020-01357-9}
-
-\leavevmode\hypertarget{ref-Alluhaybi_2020}{}%
-Alluhaybi, I., \& Witzel, J.
-(2020).
-Letter connectedness and arabic visual word recognition.
-\emph{Quarterly Journal of Experimental Psychology}, \emph{73}(10), 1660--1674.
-\url{https://doi.org/10.1177/1747021820926155}
-
-\leavevmode\hypertarget{ref-anwyl-irvine2020a}{}%
-Anwyl-Irvine, A., Dalmaijer, E.
-S., Hodges, N., \& Evershed, J.
-K.
-(2020).
-Realistic precision and accuracy of online experiment platforms, web browsers, and devices.
-\emph{Behavior Research Methods}.
-\url{https://doi.org/10.3758/s13428-020-01501-5}
-
-\leavevmode\hypertarget{ref-anwyl-irvine2020}{}%
-Anwyl-Irvine, A., Massonni, J., Flitton, A., Kirkham, N., \& Evershed, J.
-K.
-(2020).
-orilla in our midst: An online behavioral experiment builder.
-\emph{Behavior Research Methods}, \emph{52}(1), 388--407.
-\url{https://doi.org/10.3758/s13428-019-01237-x}
-
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}
-
-\leavevmode\hypertarget{ref-austSeriousnessChecksAre2013}{}%
-Aust, F., Diedenhofen, B., Ullrich, S., \& Musch, J.
-(2013).
-Seriousness checks are useful to improve data validity in online research.
-\emph{Behavior Research Methods}, \emph{45}(2), 527--535.
-\url{https://doi.org/10.3758/s13428-012-0265-2}
-
-\leavevmode\hypertarget{ref-balota2007}{}%
-Balota, D.
-A., Yap, M.
-J., Hutchison, K.
-A., Cortese, M.
-J., Kessler, B., Loftis, B., Neely, J.
-H., Nelson, D.
-L., Simpson, G.
-B., \& Treiman, R.
-(2007).
-The English Lexicon Project.
-\emph{Behavior Research Methods}, \emph{39}(3), 445--459.
-\url{https://doi.org/10.3758/BF03193014}
-
-\leavevmode\hypertarget{ref-R-tinylabels}{}%
-Barth, M. (2021). \emph{{tinylabels}: Lightweight variable labels}. \url{https://github.com/mariusbarth/tinylabels}
-
-\leavevmode\hypertarget{ref-birnbaumPsychologicalExperimentsInternet2000a}{}%
-Birnbaum, M. H., \& Birnbaum, M. O. (2000). \emph{Psychological {Experiments} on the {Internet}}. {Elsevier}. \url{http://books.google.com?id=sw4NHyThFFkC}
-
-\leavevmode\hypertarget{ref-bridges2020}{}%
-Bridges, D., Pitiot, A., MacAskill, M.
-R., \& Peirce, J.
-W.
-(2020).
-The timing mega-study: comparing a range of experiment generators, both lab-based and online.
-\emph{PeerJ}, \emph{8}, e9414.
-\url{https://doi.org/10.7717/peerj.9414}
-
-\leavevmode\hypertarget{ref-brysbaert2021a}{}%
-Brysbaert, M., Keuleers, E., \& Mandera, P.
-(2021).
-Which words do English non-native speakers know?
-New supernational levels based on yes/no decision.
-\emph{Second Language Research}, \emph{37}(2), 207--231.
-\url{https://doi.org/10.1177/0267658320934526}
-
-\leavevmode\hypertarget{ref-brysbaert2018}{}%
-Brysbaert, M., \& Stevens, M. (2018). Power Analysis and Effect Size in Mixed Effects Models: A Tutorial. \emph{Journal of Cognition}, \emph{1}(1), 9. \url{https://doi.org/10.5334/joc.10}
-
-\leavevmode\hypertarget{ref-brysbaert2016impact}{}%
-Brysbaert, M., Stevens, M., Mandera, P., \& Keuleers, E.
-(2016).
-The impact of word prevalence on lexical decision times: Evidence from the dutch lexicon project 2.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{42}(3), 441.
-
-\leavevmode\hypertarget{ref-R-brms_a}{}%
-Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
-
-\leavevmode\hypertarget{ref-R-brms_b}{}%
-Bürkner, P.-C. (2018). Advanced {Bayesian} multilevel modeling with the {R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://doi.org/10.32614/RJ-2018-017}
-
-\leavevmode\hypertarget{ref-cai2017accent}{}%
-Cai, Z.
-G., Gilbert, R.
-A., Davis, M.
-H., Gaskell, M.
-G., Farrar, L., Adler, S., \& Rodd, J.
-M.
-(2017).
-\emph{Accent modulates access to word meaning: Evidence for a speaker-model account of spoken word recognition}.
-\url{https://doi.org/10.31234/osf.io/5x3tb}
-
-\leavevmode\hypertarget{ref-de1994conditional}{}%
-De Jong, R., Liang, C.-C., \& Lauber, E.
-(1994).
-Conditional and unconditional automaticity: A dual-process model of effects of spatial stimulus-response correspondence.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{20}(4), 731.
-
-\leavevmode\hypertarget{ref-deleeuw2015}{}%
-de Leeuw, J.
-R.
-(2015).
-jsPsych: A JavaScript library for creating behavioral experiments in a Web browser.
-\emph{Behavior Research Methods}, \emph{47}(1), 1--12.
-\url{https://doi.org/10.3758/s13428-014-0458-y}
-
-\leavevmode\hypertarget{ref-Dubey_2018}{}%
-Dubey, N., Witzel, N., \& Witzel, J.
-(2018).
-Script differences and masked translation priming: Evidence from hindi-english bilinguals.
-\emph{Quarterly Journal of Experimental Psychology}, \emph{71}(11), 2421--2438.
-\url{https://doi.org/10.1177/1747021817743241}
-
-\leavevmode\hypertarget{ref-Dufau_2011}{}%
-Dufau, S., Duñabeitia, J.
-A., Moret-Tatay, C., McGonigal, A., Peeters, D., Alario, F.-X., Balota, D.
-A., Brysbaert, M., Carreiras, M., Ferrand, L., Ktori, M., Perea, M., Rastle, K., Sasburg, O., Yap, M.
-J., Ziegler, J.
-C., \& Grainger, J.
-(2011).
-Smart phone, smart science: How the use of smartphones can revolutionize research in cognitive science.
-\emph{{PLoS} {ONE}}, \emph{6}(9), e24974.
-\url{https://doi.org/10.1371/journal.pone.0024974}
-
-\leavevmode\hypertarget{ref-R-Rcpp_b}{}%
-Eddelbuettel, D., \& Balamuta, J.
-J.
-(2018).
-{Extending extit{R} with extit{C++}: A Brief Introduction to extit{Rcpp}}.
-\emph{The American Statistician}, \emph{72}(1), 28--36.
-\url{https://doi.org/10.1080/00031305.2017.1375990}
-
-\leavevmode\hypertarget{ref-R-Rcpp_a}{}%
-Eddelbuettel, D., \& François, R. (2011). {Rcpp}: Seamless {R} and {C++} integration. \emph{Journal of Statistical Software}, \emph{40}(8), 1--18. \url{https://doi.org/10.18637/jss.v040.i08}
-
-\leavevmode\hypertarget{ref-eerland2013influence}{}%
-Eerland, A., Engelen, J.
-A.
-A., \& Zwaan, R.
-A.
-(2013).
-The influence of direct and indirect speech on mental representations.
-\emph{{PLoS} {ONE}}, \emph{8}(6), e65480.
-\url{https://doi.org/10.1371/journal.pone.0065480}
-
-\leavevmode\hypertarget{ref-Fern_ndez_L_pez_2019}{}%
-Fernández-López, M., Marcet, A., \& Perea, M.
-(2019).
-Can response congruency effects be obtained in masked priming lexical decision?
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{45}(9), 1683--1702.
-\url{https://doi.org/10.1037/xlm0000666}
-
-\leavevmode\hypertarget{ref-forster1998pros}{}%
-Forster, K. (1998). The pros and cons of masked priming. \emph{Journal of Psycholinguistic Research}, \emph{27}(2), 203--233.
-
-\leavevmode\hypertarget{ref-forsterRepetitionPrimingFrequency1984}{}%
-Forster, K., \& Davis, C.
-(1984).
-Repetition priming and frequency attenuation in lexical access.
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{10}(4), 680--698.
-\url{https://doi.org/10.1037/0278-7393.10.4.680}
-
-\leavevmode\hypertarget{ref-forsterDMDXWindowsDisplay2003}{}%
-Forster, K., \& Forster, J. (2003). {DMDX}: {A Windows} display program with millisecond accuracy. \emph{Behavior Research Methods, Instruments, \& Computers}, \emph{35}(1), 116--124.
-
-\leavevmode\hypertarget{ref-Gomez_2020}{}%
-Gomez, P., \& Perea, M.
-(2020).
-Masked identity priming reflects an encoding advantage in developing readers.
-\emph{Journal of Experimental Child Psychology}, \emph{199}, 104911.
-\url{https://doi.org/10.1016/j.jecp.2020.104911}
-
-\leavevmode\hypertarget{ref-gomezDiffusionModelAccount2013}{}%
-Gomez, P., Perea, M., \& Ratcliff, R.
-(2013).
-A diffusion model account of masked versus unmasked priming: {Are} they qualitatively different?
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{39}(6), 1731--1740.
-\url{https://doi.org/10.1037/a0032333}
-
-\leavevmode\hypertarget{ref-grainger2008cracking}{}%
-Grainger, J. (2008). Cracking the orthographic code: An introduction. \emph{Language and Cognitive Processes}, \emph{23}(1), 1--35. \url{https://doi.org/10.1080/01690960701578013}
-
-\leavevmode\hypertarget{ref-grossi2006relatedness}{}%
-Grossi, G. (2006). Relatedness proportion effects on masked associative priming: An {ERP} study. \emph{Psychophysiology}, \emph{43}(1), 21--30. \url{https://doi.org/10.1111/j.1469-8986.2006.00383.x}
-
-\leavevmode\hypertarget{ref-R-purrr}{}%
-Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. \url{https://CRAN.R-project.org/package=purrr}
-
-\leavevmode\hypertarget{ref-Jacobs_1995}{}%
-Jacobs, A.
-M., Grainger, J., \& Ferrand, L.
-(1995).
-The incremental priming technique: A method for determining within-condition priming effects.
-\emph{Perception {\&} Psychophysics}, \emph{57}(8), 1101--1110.
-\url{https://doi.org/10.3758/bf03208367}
-
-\leavevmode\hypertarget{ref-lund1996}{}%
-Lund, K., \& Burgess, C.
-(1996).
-Producing high-dimensional semantic spaces from lexical co-occurrence.
-\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{28}(2), 203--208.
-\url{https://doi.org/10.3758/BF03204766}
-
-\leavevmode\hypertarget{ref-R-see}{}%
-Lüdecke, D., Ben-Shachar, M.
-S., Waggoner, P., \& Makowski, D.
-(2020).
-See: Visualisation toolbox for 'easystats' and extra geoms, themes and color palettes for 'ggplot2'.
-\emph{CRAN}.
-\url{https://doi.org/10.5281/zenodo.3952153}
-
-\leavevmode\hypertarget{ref-R-bayestestR}{}%
-Makowski, D., Ben-Shachar, M.
-S., \& Lüdecke, D.
-(2019).
-bayestestR: Describing effects and their uncertainty, existence and significance within the bayesian framework.
-\emph{Journal of Open Source Software}, \emph{4}(40), 1541.
-\url{https://doi.org/10.21105/joss.01541}
-
-\leavevmode\hypertarget{ref-mandera2020}{}%
-Mandera, P., Keuleers, E., \& Brysbaert, M.
-(2020).
-Recognition times for 62 thousand English words: Data from the English Crowdsourcing Project.
-\emph{Behavior Research Methods}, \emph{52}(2), 741--760.
-\url{https://doi.org/10.3758/s13428-019-01272-8}
-
-\leavevmode\hypertarget{ref-R-tibble}{}%
-Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. \url{https://CRAN.R-project.org/package=tibble}
-
-\leavevmode\hypertarget{ref-paolacciRunningExperimentsAmazon2010}{}%
-Paolacci, G., Chandler, J., \& Ipeirotis, P.
-G.
-(2010).
-\emph{Running {Experiments} on {Amazon Mechanical Turk}} (SSRN Scholarly Paper ID 1626226).
-{Social Science Research Network}.
-\url{https://papers.ssrn.com/abstract=1626226}
-
-\leavevmode\hypertarget{ref-Parker_2021}{}%
-Parker, A., Egan, C., Grant, J.
-H., Harte, S., Hudson, B.
-T., \& Woodhead, Z.
-V.
-J.
-(2021).
-The role of orthographic neighbourhood effects in lateralized lexical decision: A replication study and meta-analysis.
-\emph{{PeerJ}}, \emph{9}, e11266.
-\url{https://doi.org/10.7717/peerj.11266}
-
-\leavevmode\hypertarget{ref-pavlovia2020}{}%
-Pavlovia. (2020). \emph{Pavlovia}. \url{https://pavlovia.org/}
-
-\leavevmode\hypertarget{ref-R-sp}{}%
-Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. \url{https://CRAN.R-project.org/doc/Rnews/}
-
-\leavevmode\hypertarget{ref-R-patchwork}{}%
-Pedersen, T. L. (2020). \emph{Patchwork: The composer of plots}. \url{https://CRAN.R-project.org/package=patchwork}
-
-\leavevmode\hypertarget{ref-peirce2019}{}%
-Peirce, J., Gray, J.
-R., Simpson, S., MacAskill, M., Höchenberger, R., Sogo, H., Kastman, E., \& Lindeløv, J.
-K.
-(2019).
-PsychoPy2: Experiments in behavior made easy.
-\emph{Behavior Research Methods}, \emph{51}(1), 195--203.
-\url{https://doi.org/10.3758/s13428-018-01193-y}
-
-\leavevmode\hypertarget{ref-Perea_2018}{}%
-Perea, M., Marcet, A., Lozano, M., \& Gomez, P.
-(2018).
-Is masked priming modulated by memory load?
-A test of the automaticity of masked identity priming in lexical decision.
-\emph{Memory {\&} Cognition}, \emph{46}(7), 1127--1135.
-\url{https://doi.org/10.3758/s13421-018-0825-5}
-
-\leavevmode\hypertarget{ref-perea2002does}{}%
-Perea, M., \& Rosa, E.
-(2002).
-Does the proportion of associatively related pairs modulate the associative priming effect at very brief stimulus-onset asynchronies?
-\emph{Acta Psychologica}, \emph{110}(1), 103--124.
-\url{https://doi.org/10.1016/s0001-6918(01)00074-9}
-
-\leavevmode\hypertarget{ref-prolific2021}{}%
-Prolific. (2021). \emph{Prolific \textbar{} online participant recruitment for surveys and market research}. \url{https://www.prolific.co/}
-
-\leavevmode\hypertarget{ref-qualtrics2020}{}%
-Qualtrics. (2020). \emph{Qualtrics XM // the leading experience management software}. \url{https://www.qualtrics.com/uk/}
-
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
-\leavevmode\hypertarget{ref-ratcliff2004}{}%
-Ratcliff, R., Gomez, P., \& McKoon, G.
-(2004).
-A diffusion model account of the lexical decision task.
-\emph{Psychological Review}, \emph{111}(1), 159--182.
-\url{https://doi.org/10.1037/0033-295X.111.1.159}
-
-\leavevmode\hypertarget{ref-reimersPresentationResponseTiming2015}{}%
-Reimers, S., \& Stewart, N.
-(2015).
-Presentation and response timing accuracy in {Adobe Flash} and {HTML5}/{JavaScript Web} experiments.
-\emph{Behavior Research Methods}, \emph{47}(2), 309--327.
-\url{https://doi.org/10.3758/s13428-014-0471-1}
-
-\leavevmode\hypertarget{ref-rezlescu2020}{}%
-Rezlescu, C., Danaila, I., Miron, A., \& Amariei, C.
-(2020).
-\emph{Chapter 13 - More time for science: Using Testable to create and share behavioral experiments faster, recruit better participants, and engage students in hands-on research} (B.
-L.
-Parkin, Ed.; Vol.
-253, pp.
-243--262).
-Elsevier.
-\url{https://doi.org/10.1016/bs.pbr.2020.06.005}
-
-\leavevmode\hypertarget{ref-rodd2016impact}{}%
-Rodd, J.
-M., Cai, Z.
-G., Betts, H.
-N., Hanby, B., Hutchinson, C., \& Adler, A.
-(2016).
-The impact of recent and long-term experience on access to word meanings: Evidence from large-scale internet-based experiments.
-\emph{Journal of Memory and Language}, \emph{87}, 16--37.
-\url{https://doi.org/10.1016/j.jml.2015.10.006}
-
-\leavevmode\hypertarget{ref-R-rworldmap}{}%
-South, A. (2011). Rworldmap: A new r package for mapping global data. \emph{The R Journal}, \emph{3}(1), 35--43. \url{http://journal.r-project.org/archive/2011-1/RJournal_2011-1_South.pdf}
-
-\leavevmode\hypertarget{ref-Taikh_2020}{}%
-Taikh, A., \& Lupker, S.
-J.
-(2020).
-Do visible semantic primes preactivate lexical representations?
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{46}(8), 1533--1569.
-\url{https://doi.org/10.1037/xlm0000825}
-
-\leavevmode\hypertarget{ref-Tzur_2007}{}%
-Tzur, B., \& Frost, R.
-(2007).
-{SOA} does not reveal the absolute time course of cognitive processing in fast priming experiments{{73}}.
-\emph{Journal of Memory and Language}, \emph{56}(3), 321--335.
-\url{https://doi.org/10.1016/j.jml.2006.11.007}
-
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\hypertarget{ref-R-stringr}{}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. \url{https://CRAN.R-project.org/package=stringr}
-
-\leavevmode\hypertarget{ref-R-forcats}{}%
-Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. \url{https://CRAN.R-project.org/package=forcats}
-
-\leavevmode\hypertarget{ref-R-tidyr}{}%
-Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. \url{https://CRAN.R-project.org/package=tidyr}
-
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
-L., Miller, E., Bache, S.
-M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
-P., Spinu, V., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
-
-\leavevmode\hypertarget{ref-R-readxl}{}%
-Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. \url{https://CRAN.R-project.org/package=readxl}
-
-\leavevmode\hypertarget{ref-R-dplyr}{}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. \url{https://CRAN.R-project.org/package=dplyr}
-
-\leavevmode\hypertarget{ref-R-readr}{}%
-Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. \url{https://CRAN.R-project.org/package=readr}
-
-\leavevmode\hypertarget{ref-witzelTestingViabilityWebDMDX2013}{}%
-Witzel, J., Cornelius, S., Witzel, N., Forster, K.
-I., \& Forster, J.
-C.
-(2013).
-Testing the viability of {webDMDX} for masked priming experiments.
-\emph{The Mental Lexicon}, \emph{8}(3), 421--449.
-\url{https://doi.org/10.1075/ml.8.3.07wit}
-
-\leavevmode\hypertarget{ref-R-xfun}{}%
-Xie, Y. (2021). \emph{Xfun: Miscellaneous functions to support packages maintained by 'yihui xie'}. \url{https://CRAN.R-project.org/package=xfun}
-
-\leavevmode\hypertarget{ref-Yang_2021}{}%
-Yang, H., Jared, D., Perea, M., \& Lupker, S.
-J.
-(2021).
-Is letter position coding when reading in L2 affected by the nature of position coding used when bilinguals read in their L1?
-\emph{Memory {\&} Cognition}, \emph{49}(4), 771--786.
-\url{https://doi.org/10.3758/s13421-020-01126-1}
-
-\leavevmode\hypertarget{ref-yarkoni2008}{}%
-Yarkoni, T., Balota, D., \& Yap, M.
-(2008).
-Moving beyond Coltheart{'}s N: A new measure of orthographic similarity.
-\emph{Psychonomic Bulletin \& Review}, \emph{15}(5), 971--979.
-\url{https://doi.org/10.3758/PBR.15.5.971}
-
-\leavevmode\hypertarget{ref-ziegler2000}{}%
-Ziegler, J.
-C., Ferrand, L., Jacobs, A.
-M., Rey, A., \& Grainger, J.
-(2000).
-Visual and Phonological Codes in Letter and Word Recognition: Evidence from Incremental Priming.
-\emph{The Quarterly Journal of Experimental Psychology}, \emph{53A}(3), 671--692.
-
-\leavevmode\hypertarget{ref-Zimmerman_2012}{}%
-Zimmerman, R., \& Gomez, P. (2012). Drawing attention to primes increases inhibitory word priming effects. \emph{The Mental Lexicon}, \emph{7}(2), 119--146. \url{https://doi.org/10.1075/ml.7.2.01zim}
-
-\end{CSLReferences}
-
-\newpage
-
-\hypertarget{appendix-a}{%
-\section{Appendix A}\label{appendix-a}}
+\begin{appendix}
+\hypertarget{stimuli}{%
+\section{Stimuli}\label{stimuli}}
 
@@
 \end{verbatim}
-
-\endgroup
-
-\end{document}
+\end{appendix}

### 2021-11-06 Appendix_B.tex

@@
 
-\caption{\label{tab:appendix_table_2}$T_{er}$ values for Experiment 1.}
+\caption{\label{tab:appendix_table_3} $T_{er}$ values for Experiment 2.}
 
@@
 \toprule
-Parameters & \multicolumn{1}{c}{Experiment1}\\
+Parameters & \multicolumn{1}{c}{Experiment2}\\
 \midrule
-$T_{er}$ values for Experiment 1.  33ms nonword ID & 0.51\\
-$T_{er}$ values for Experiment 1. 33ms nonword Unrel & 0.51\\
-$T_{er}$ values for Experiment 1.  50ms nonword ID & 0.50\\
-$T_{er}$ values for Experiment 1. 50ms nonword Unrel & 0.51\\
-$T_{er}$ values for Experiment 1.  33ms word ID & 0.47\\
-$T_{er}$ values for Experiment 1. 33ms word Unrel & 0.49\\
-$T_{er}$ values for Experiment 1.  50ms word ID & 0.46\\
-$T_{er}$ values for Experiment 1. 50ms word Unrel & 0.50\\
+$T_{er}$ 16ms nonword ID & 0.54\\
+$T_{er}$ 16ms nonword Unrel & 0.54\\
+$T_{er}$ 33ms nonword ID & 0.53\\
+$T_{er}$ 33ms nonword Unrel & 0.53\\
+$T_{er}$ 16ms word ID & 0.50\\
+$T_{er}$ 16ms word Unrel & 0.50\\
+$T_{er}$ 33ms word ID & 0.49\\
+$T_{er}$ 33ms word Unrel & 0.51\\
 \bottomrule
@@
 \end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:appendix_table_3} \$T\_\{er\}\$ values for Experiment 2.}
-
-\begin{tabular}{ll}
-\toprule
-Parameters & \multicolumn{1}{c}{Experiment2}\\
-\midrule
-\$T\_\{er\}\$ 16ms nonword ID & 0.54\\
-\$T\_\{er\}\$ 16ms nonword Unrel & 0.54\\
-\$T\_\{er\}\$ 33ms nonword ID & 0.53\\
-\$T\_\{er\}\$ 33ms nonword Unrel & 0.53\\
-\$T\_\{er\}\$ 16ms word ID & 0.50\\
-\$T\_\{er\}\$ 16ms word Unrel & 0.50\\
-\$T\_\{er\}\$ 33ms word ID & 0.49\\
-\$T\_\{er\}\$ 33ms word Unrel & 0.51\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\newpage
-
-\hypertarget{references}{%
-\subsection{References}\label{references}}
-
-Gomez, P., \& Perea, M. (2020). Masked identity priming reflects an
-encoding advantage in developing readers. Journal of Experimental Child
-Psychology, 199, 104911. https://doi.org/10.1016/j.jecp.2020.104911
-
-Gomez, P., Perea, M., \& Ratcliff, R. (2013). A diffusion model account
-of masked versus unmasked priming: Are they qualitatively different?
-Journal of Experimental Psychology: Human Perception and Performance, 39
-(6), 1731--1740. https://doi.org/10.1037/a0032333
-
-Ratcliff, R. (1978). A theory of memory retrieval. Psychological Review,
-85, 59--108. https://doi.org/10.1037/0033-295X.85.2.59
-
-Ratcliff, R., Gomez, P., \& McKoon, G. (2004). A diffusion model account
-of the lexical decision task. Psychological Review, 111, 159--182.
-doi://10.1037/0033-295X.111.1.159
-
-Ratcliff, R.,\& Tuerlinckx, F. (2002). Estimating the parameters of the
-diffusion model: Approaches to dealing with contaminant reaction times
-and parameter variability. Psychonomic Bulletin and Review, 9, 438--481.
-https://doi.org/10.3758/BF03196302
 \end{appendix}

### 2021-11-06 Appendix_test.Rmd

@@
 
-```{r setup, include = FALSE}
+```{r app_test_setup, include = FALSE}
 library(tidyverse)

### 2021-11-06 Appendix_test.tex

@@
   man]{apa6}
+\title{TITLE}
+\author{\phantom{0}}
+\date{}
+
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \usepackage{csquotes}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-
-\title{TITLE}
-\author{\phantom{0}}
-\date{}
 

### 2021-11-06 previous revisions/EDA_OnlineMaskedPriming.Rmd

--- 2021-04-23 EDA_OnlineMaskedPriming.Rmd
@@
 library(papaja)
+library(patchwork)
 
@@
 E1<- exp1_data_to_include%>% 
+  filter(rt > 250 & rt < 2000)%>%
   select(participant, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target, corr, rt)%>%
@@
 
-#Priming Effect (related vs. unrelated):
+#Priming Effect (unrelated - identity):
 
@@
 
-#Prime Duration Effect (33ms vs 50 ms):
+#Prime Duration Effect (33ms - 50 ms):
 
@@
 
+```{r Deltas E1 Words, message=FALSE, warning=FALSE}
+
+#Priming Effect (unrelated - identity):
+
+vincentiles.E1 %>%
+  filter(StimulusType == "Word")%>%
+  arrange(desc(Condition))%>%
+  group_by(PrimeDuration,q) %>%
+  summarize(MRT=mean(RT),
+            Delta=diff(rev(RT)))%>%
+  ungroup()%>%
+ggplot(aes(y=Delta, x=MRT)) +
+  geom_line(size = .75)+
+  geom_point(size = 2)+
+  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
+  ylim(-60, +60)+
+  xlim(450, 850)+
+  xlab("Mean RT per quantile")+
+  ylab("Effect (in ms)")+
+  ggtitle("Priming Effect")+
+  facet_wrap(~PrimeDuration)+
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12),
+        axis.text=element_text(size=10),
+        axis.title=element_text(size=10))-> DeltaE1.PrimingEffect.W
+
+#Prime Duration Effect (33ms - 50 ms):
+
+vincentiles.E1 %>%
+  filter(StimulusType == "Word")%>%
+  group_by(Condition,q) %>%
+  summarize(MRT=mean(RT),
+            Delta=diff(rev(RT)))%>%
+  ggplot(aes(y=Delta, x=MRT)) +
+  geom_line(size = .75)+
+  geom_point(size = 2)+
+  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
+  ylim(-60, +60)+
+  xlim(450, 850)+
+  xlab("Mean RT per quantile")+
+  ylab("Effect (in ms)")+
+  ggtitle("Prime duration effect")+
+  facet_wrap(~ Condition)+
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12),
+        axis.text=element_text(size=10),
+        axis.title=element_text(size=10))-> DeltaE1.PrimeDurationEffect.W
+
+#pdf("Fig_deltasE1.pdf", height = 5)
+
+cowplot::plot_grid(DeltaE1.PrimingEffect.W,
+                   DeltaE1.PrimeDurationEffect.W,
+                   ncol = 1,
+                   labels = c("A", "B"))+
+  plot_annotation(title = "Experiment 1: 33 vs. 50 ms",
+                  theme = theme(plot.title = element_text(size = 14)))
+
+#dev.off()
+
+```
+
 ```{r Deltas E2, message=FALSE, warning=FALSE}
@@
 
-#Prime Duration Effect (33ms vs 50 ms):
+#Prime Duration Effect (16ms - 33 ms):
 
@@
 DeltaE2.PrimeDurationEffect
+
+```
+
+```{r Deltas E2 Words, message=FALSE, warning=FALSE}
+
+#Priming Effect (unrelated - identity):
+
+vincentiles.E2 %>%
+  filter(StimulusType == "Word")%>%
+  arrange(desc(Condition))%>%
+  group_by(PrimeDuration,q) %>%
+  summarize(MRT=mean(RT),
+            Delta=diff(rev(RT)))%>%
+  ungroup()%>%
+ggplot(aes(y=Delta, x=MRT)) +
+  geom_line(size = .75)+
+  geom_point(size = 2)+
+  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
+  ylim(-60, +60)+
+  xlim(450, 850)+
+  xlab("Mean RT per quantile")+
+  ylab("Effect (in ms)")+
+  ggtitle("Priming Effect")+
+  facet_wrap(~PrimeDuration)+
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12),
+        axis.text=element_text(size=10),
+        axis.title=element_text(size=10))-> DeltaE2.PrimingEffect.W
+
+#Prime Duration Effect (16ms - 33 ms):
+
+vincentiles.E2 %>%
+  filter(StimulusType == "Word")%>%
+  group_by(Condition,q) %>%
+  summarize(MRT=mean(RT),
+            Delta=diff(rev(RT)))%>%
+  ggplot(aes(y=Delta, x=MRT)) +
+  geom_line(size = .75)+
+  geom_point(size = 2)+
+  geom_hline(yintercept = 0, color = "darkmagenta", alpha = .25)+
+  ylim(-60, +60)+
+  xlim(450, 850)+
+  xlab("Mean RT per quantile")+
+  ylab("Effect (in ms)")+
+  ggtitle("Prime duration effect")+
+  facet_wrap(~ Condition)+
+  theme_minimal()+
+  theme(plot.title = element_text(size = 12),
+        axis.text=element_text(size=10),
+        axis.title=element_text(size=10))-> DeltaE2.PrimeDurationEffect.W
+
+#pdf("Fig_deltasE2.pdf", height = 5)
+
+cowplot::plot_grid(DeltaE2.PrimingEffect.W,
+                   DeltaE2.PrimeDurationEffect.W,
+                   ncol = 1,
+                   labels = c("A", "B"))+
+  plot_annotation(title = "Experiment 2: 16 vs. 33 ms",
+                  theme = theme(plot.title = element_text(size = 14)))
 

### 2021-11-06 previous revisions/Manuscript_intro_method_results.Rmd

--- 2021-05-05 Manuscript_intro_method_results.Rmd
@@
 load("blmm_exp1_rt_dist_full_ranef_5000.RData")
-# model name is blmm_exp1_rt
+# This file does not fit on GitHub
+# Download it at https://1drv.ms/u/s!ApE7JQmoH0baocARuxg21SFrS4riyg?e=8ZgbHA
+# model name is blmm_exp1_rt_dist
 
@@
 # We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
-load("blmm_exp2_rt_dist.RData")
-# model name is blmm_exp2_rt
+load("blmm_exp2_rt_dist_full_ranef_5000.RData")
+# this file doesn't fit on GitHub
+# download it at https://1drv.ms/u/s!ApE7JQmoH0baocIO3qh2TNb_TlqvlA?e=q3vJml
+
+# model name is blmm_exp2_rt_dist
 

### 2021-11-06 previous revisions/MaskedPriming_complete_mspg.Rmd

--- 2021-05-27 MaskedPriming_complete_mspg.Rmd
@@
 We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items.
-We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component $\mu$ and the scale parameter of the exponential component $\beta$ (equalling the inverse of the rate parameter $\lambda$) being allowed to vary between conditions.
+We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component $\mu$ and the scale parameter of the exponential component $\beta$ (equaling the inverse of the rate parameter $\lambda$) being allowed to vary between conditions.
 To model response accuracy, we used the Bernoulli distribution with a logit link.
